### 2024-08-09 Phase_II/draft/II.tex
the first draft

\section{Intensity Interferometry with ICTA}
R. Hanbury Brown and Robert Q. Twiss first carried out II. They successfully installed the Narrabri Stellar Intensity Interferometer to resolve the diameter of bright stars at visible wavelengths \citep{brown1954lxxiv, brown1974intensity}.
\subsection{The signal for II}\label{sec:signal}
In a simple case, an II consists of two light collectors, for example, MAGIC-I and MAGIC-II, which are pointed to a star and measure the intensity $I_1(t), I_2(t)$ respectively \citep{acciari2020optical, dravins2013optical}. The signals from both detectors are cross-correlated and averaged over time, which results in an equation form
\begin{equation}
	g^{(2)} = \frac{\left\langle I_1(t) \cdot I_2(t + \tau) \right\rangle}{\langle I_1(t) \rangle \cdot \langle I_2(t) \rangle} 
	\label{eqn:HBT}
\end{equation}
where $\tau$ is the time delay between both telescopes. If the light source is chaotic and randomly polarized, we have:
\begin{equation}
	g^{(2)} = 1 + \frac{\Delta f}{\Delta \nu} \abs{V_{12}}^2
	\label{eqn:HBT2}
\end{equation}
here, $\Delta f$ is the electronic bandwidth, $\Delta \nu$ is the optical bandwidth, and $\Delta f \ll \Delta \nu$ \cite{acciari2020optical}. $V_{12}$ is the Fourier transform of the source brightness distribution and is called complex visibility. Eqn.~\ref{eqn:HBT2} carry the information about the source's structure and shape. However, the phase information is lost due to the involvement of the absolute value of $V_{12}$. In observational astronomy, the correlation is often expressed in terms of the normalized contrast, given by:
\begin{equation}
	c = \frac{\left\langle \left( I_1(t) - \left\langle I_1 \right\rangle \right) \cdot \left( I_2(t + \tau) - \left\langle I_2 \right\rangle \right) \right\rangle}{\langle I_1(t) \rangle \cdot \langle I_2(t) \rangle} = g^{(2)} - 1
\end{equation}
where, $\left\langle I_1 \right\rangle$ and $\left\langle I_2 \right\rangle$ are the mean intensity from two telescopes.

\subsection{The Signal-to-Noise Ratio for II}
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{fig/telescope.png}
	\caption{The telescope configuration with similar properties each used to simulate the signal for II.}
	\label{fig:teles}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{fig/baseline.png}
	\caption{The tracking of baselines with four telescopes arranged in fig.~\ref{fig:teles} for one night of observation.}
	\label{fig:base}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{fig/ellipse/ellipse6018.jpg}
	\caption{This figure shows the simulated fast rotating star. The brightness is highest at the pole and there is gravitational darkening at the equator.}
	\label{fig:image}
\end{figure}
\begin{figure*}
	\centering
	\begin{subfigure}{0.5\linewidth}
		\includegraphics[width=\linewidth]{fig/ft/ft.jpg}
		\caption{The fourier transform of source.}
	\end{subfigure}\hfill
	\begin{subfigure}{0.5\linewidth}
		\includegraphics[width=\linewidth]{fig/ft/ft_log.jpg}
		\caption{The logarithmic fourier transform of source.}
	\end{subfigure}
	\caption{Absolute value of the two-dimensional Fast Fourier Transform of fig.~\ref{fig:image} measured by Intensity Interferometry, and observation of maximum (u, v) plane with finite number of baselines can be completed with help of earth's rotation.}
	\label{fig:ft}
\end{figure*}
\begin{figure*}
	\centering
	\begin{subfigure}{0.5\linewidth}
		\includegraphics[width=\linewidth]{fig/ft/ft_base.jpg}
		\caption{The fourier transform with baselines.}
	\end{subfigure}\hfill
	\begin{subfigure}{0.5\linewidth}
		\includegraphics[width=\linewidth]{fig/ft/ft_log_base.jpg}
		\caption{The logarithmic fourier transform with baselines.}
	\end{subfigure}
	\caption{The left panel shows the absolute value of the two-dimensional Fast Fourier Transform of fig.~\ref{fig:image} measured by baselines shown in fig.~\ref{fig:teles}. The right panel shows the same on logarithmic scale}
	\label{fig:ft_base}
\end{figure*}
The main physics channel of ICTAs is the study of Very High Energy gamma rays ($\geq 30$ GeV) originating from particle showers in the atmosphere. Telescopes have an array of mirrors, which focus the light onto an array of photo-multiplier tubes (PMTs) \cite{aleksic2016major}. Here, fig.~\ref{fig:teles} shows an arrangement of four IACTs with similar properties each. For II, the light of a stellar source is focused on a single PMT, which has a filter in front. The purpose of this filter is to efficiently transmit light around mean observational frequency, which protects the PMTs from excessive light. It is necessary, as II observations are mainly done during full moon nights, where it is too bright for Very High Energy $\gamma$-ray observations. The optical signal of the PMTs is transmitted with optical fibers, converted to an electrical signal, and digitized \cite{acciari2020optical}. The measurable observable is the Pearson's correlation coefficient:
\begin{equation}
	\rho(\tau) = \frac{\left\langle \left( I_1(t) - \left\langle I_1 \right\rangle \right) \cdot \left( I_2(t + \tau) - \left\langle I_2 \right\rangle \right) \right\rangle}{\sqrt{\langle \left( I_1(t) - \langle I_1 \rangle \right)^2 \rangle} \cdot \sqrt{\langle \left( I_2(t) - \langle I_2 \rangle \right) ^2 \rangle}}
	\label{eqn:pearson}
\end{equation}
Since $I_1$ and $I_2$ are proportional to the direct current of the PMTs ($DC_i$), the normalized contrast can be calculated as in equation \ref{eq:norm_contrast2}. One must also correct for a non-constant gain of the PMTs, as well as the moon. The latter can be done by measuring the background light with an additional PMT with no mirrors focused on it \cite{acciari2020optical}. 
\begin{equation}
	c \propto \frac{\rho}{\sqrt{\left(DC_1 \cdot DC_2 \right)}}
	\label{eq:norm_contrast2}
\end{equation}
It must be noted that the calculation of Pearson's correlation coefficient is non-trivial: MAGIC makes use of the convolution theorem for discrete Fourier transforms because it is computationally more efficient.

The significance of the signal can be expressed as the signal-to-noise ratio (SNR), which depends on many factors. However, most importantly, it is proportional to the absolute value of visibility, which itself depends on the distance between the telescopes, shown in equation (\ref{eq:SNR}) \cite{acciari2020optical}.  
\begin{equation}
	SNR = A \cdot \alpha \cdot q \cdot n \cdot \abs{V_{12}}^{2}(d) \cdot \sqrt{b_v} \cdot F^{-1} \cdot \sqrt{\frac{T}{2}} \cdot \sigma
	\label{eq:SNR}
\end{equation}
here, $A$ is the total mirror area, $\alpha$ the quantum efficiency of the PMTs, $q$ the quantum efficiency of the optics, $n$ the differential photon flux from the source, and $b_v$ the cross-correlation bandwidth. The noise of the PMTs is accounted for with $F$, $T$ denotes the observation time, and $\sigma$ is the normalized spectral distribution of the light (including filters) \cite{acciari2020optical}. While most of the parameters can be optimized with hardware, the only way to obtain a better SNR is to increase the observation time with fixed telescopes.

\subsection{Baseline considerations}
The measurement of the size of stellar objects through absolute visibility depends on the distance between the telescopes, which is called the baseline $B$. 
\begin{equation}
	V_{12}(B) = \frac{c(B)}{c(0)}
	\label{eq:angular_size_meas}
\end{equation}
However, this work needs a good SNR value for high precision of measurement, so the large covered observational plane with telescopes is a necessity for II \cite{acciari2020optical, abeysekara2020demonstration}. If the source is at the zenith, the coordinates in the Fourier plane ($u,v$) are given by:
\begin{equation}
	(u,v) = \frac{1}{\lambda} (B_N, B_E)
\end{equation}
where $B_N$ and $B_E$ are the baselines expressed in north and east coordinates. Since not all sources are at the zenith, and the telescopes are stationary, Earth's rotation plays an important role in covering the maximum observational plane through the rotated baselines. It is given by equation (\ref{eq:baseline_rot}), which traces an ellipse for every pair of telescopes. Furthermore, the different altitudes $B_A$ of the telescopes must be considered \cite{dravins2013optical, saha2020theory}.  
\begin{equation}
	\begin{pmatrix} u\\ v\\ w\\ \end{pmatrix} = R_x(\delta) \cdot R_y(h) \cdot R_x(-l) \begin{pmatrix} B_N\\ B_E\\ B_A\\ \end{pmatrix}
	\label{eq:baseline_rot}
\end{equation}
here, $\delta$ is the declination and $h$ is the hour angle of the stellar source, and $l$ is the latitude of the telescopes. The three matrices $R_i$ correspond to the fundamental representation of the SO(3) group \cite{saha2020theory}. Fig.~\ref{fig:base} shows the track of six baselines generated from the telescopes (fig.~\ref{fig:teles}) due to Earth's rotation. Since every pair of telescopes traces an ellipse in the Fourier plane, the total number of ellipses scales as follows:
\begin{equation}
	\label{eq:N_telescopes}
	\mathcal{N} = \frac{N_T \cdot (N_T -1)}{2}
\end{equation}

As the number of baselines increases non-linearly, II benefits greatly from a large number of telescopes. So, the planned Cherenkov Telescope Array (CTA) will cover the maximum observational plane and provide insight into stellar objects with optical wavelengths in the future.

\subsection{An Object: Fast Rotating Stars}
In our work, we simulate a single fast-rotating star to test image reconstruction using a GAN. Fast rotation causes stars to take on an oblate shape, flattening at the poles and bulging at the equator due to the existence of stronger centrifugal force \cite{von1924radiative, 1999A&A...347..185M}. Fig.~\ref{fig:image} shows one of the simulations of a fast-rotating star, where the star takes on an elliptical shape with brightness distributed across the object. The brightness is at its maximum at the poles and minimum at the equator, a phenomenon known as gravity darkening \cite{lucy1967gravity}. This effect has been observed first through the interferometric and spectroscopic data from the CHARA Array for the fast-rotating star Regulus \cite{mcalister2005first}. Fast-rotating stars are crucial for understanding various astrophysical processes, including stellar evolution, structure, and dynamics over time.

Intensity Interferometry observes the stellar object in the form of photons, and the correlation of it results in squared visibility (explained in subsection.\ref{sec:signal}). According to Van Cittert Zernike's theorem, this signal is the Fourier transform of brightness distribution in the sky. Fig.~\ref {fig:ft} shows the same statement for the source shown in fig.~\ref{fig:image} using II on linear and logarithmic scale. However, we do not have an existing technique to observe the complete signals, and we could capture some parts of it only with a one-night simulation, which has been shown in fig.~\ref{fig:ft_base}. It is the covered observational plane using the baselines shown in fig.~\ref{fig:teles}. However, the upcoming CTA promises to cover the maximum observational plane for stellar objects.

### 2024-08-09 Phase_II/draft/ParaGan.tex
the first draft

\section{The Parameter Analysis for GAN}
\begin{figure*}
	\centering
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/testing_image/image_0.png}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/testing_image/image_16.png}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/testing_image/image_35.png}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/testing_image/image_38.png}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/testing_image/image_42.png}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/testing_image/image_47.png}
	\end{subfigure}
	\caption{This set of figures shows the result of GAN for II. The left panels are signals using six baselines, which work as input for GAN. The first, middle panel is the real image, also called ground truth, and GAN tries to mimic it during the training. The second middle panel is the reconstructed image, also called the predicted image, with trained GAN, and the end panel is the difference between the ground truth and the predicted image.}
	\label{fig:GAN}
\end{figure*}
Here, we discuss the parameters for the GAN structure which is trained to reconstruct the image of stellar objects using II.
\subsection{Data preparation}
First, we simulate fast-rotating stars, which are modeled as oblate spheroids with different radii and oblateness between 0.5 and 1. Different viewed angles have also been considered, with the effect of gravity darkening being linear dependence. The traced ellipses arise when integrating over the hour angle of the source. For the hyperparameter tuning and comparison of different telescopes, the total hour angle is about 11.5 hours. The ellipses are plotted and converted into grayscale images, resized, and stored as pure arrays to simplify further analysis. 
\begin{figure*}
	\centering
	\begin{subfigure}{0.33\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom0.png}
		\caption{The monopole.}
		\label{fig:mom1}
	\end{subfigure}\hfill
	\begin{subfigure}{0.33\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom1.png}
		\caption{The centroids along x direction.}
		\label{fig:mom2}
	\end{subfigure}\hfill
	\begin{subfigure}{0.33\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom2.png}
		\caption{The centroids along y direction.}
		\label{fig:mom3}
	\end{subfigure}\hfill
	\caption{The monopole, centroid along x and y direction of ground truth and predicted image.}
	\label{fig:cen}
\end{figure*}
\begin{figure*}
	\centering
	\begin{subfigure}{0.33\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom3.png}
		\caption{The 2nd order moment $\mu_{11}$.}
		\label{fig:mom4}
	\end{subfigure}\hfill
	\begin{subfigure}{0.33\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom4.png}
		\caption{The 2nd order moment $\mu_{20}$.}
		\label{fig:mom5}
	\end{subfigure}\hfill
	\begin{subfigure}{0.33\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom5.png}
		\caption{The 2nd order moment $\mu_{02}$.}
		\label{fig:mom6}
	\end{subfigure}\hfill
	\caption{The second order central moments which provides the information about the size and shape of stellar objects.}
	\label{fig:struc}
\end{figure*}
\begin{figure*}
	\centering
	\begin{subfigure}{0.50\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom6.png}
		\caption{The 3rd order moment $\mu_{30}$.}
		\label{fig:mom7}
	\end{subfigure}\hfill
	\begin{subfigure}{0.50\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom7.png}
		\caption{The 3rd order moment $\mu_{03}$.}
		\label{fig:mom8}
	\end{subfigure}\hfill
	\begin{subfigure}{0.50\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom8.png}
		\caption{The 3rd order moment $\mu_{21}$.}
		\label{fig:mom9}
	\end{subfigure}\hfill
	\begin{subfigure}{0.50\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom9.png}
		\caption{The 3rd order moment $\mu_{12}$.}
		\label{fig:mom10}
	\end{subfigure}\hfill
	\caption{This figure shows the 3rd moments for reconstructed images and represents the brightness distribution.}
	\label{fig:moments}
\end{figure*}

First, Salt and Pepper noise is introduced at a rate of $\alpha$ (usually 0.5\%). Then, the images are resized, and the mean is subtracted. A two-dimensional Fast Fourier Transform, as well as a Fourier shift, is applied, which yields a complex number of every pixel. As II does not measure the phase, the absolute value is calculated (shown in fig.~ \ref{fig:ft} on a linear and logarithmic scale for visualization). It is also where the sparse sampling is introduced, namely by a pixel-wise multiplication between the absolute valued Fourier transformed image and the sparse sampling map. The result is a map in the Fourier plane with several ellipses, also called the sparse sampling map. The fig.~\ref{fig:ft_base} shows the sparse sampling for fig.~\ref{fig:image} as the source with four telescopes (fig.~\ref{fig:teles}). Finally, the pixels are normalized and converted to 8-bit integers. This image represents the sparsely sampled complex visibility, as it can be measured with II. The image shown in figure \ref{fig:ft_base} is the input image for the GAN, which also requires the ground truth image. So, the simulated stars are also resized using the same algorithm and converted to 8-bit integers to reduce the bias. The GAN must know the ground truth corresponding to an input image. Hence, they are merged side-by-side, shown in figure \ref{fig:GANinput}, and used as input to train the GAN. This procedure is conducted for all the simulated stars, with 10\% acting as test data, 10\% as validation data, and the remaining 80\% as training data.

\subsection{GAN architecture}
The GAN used in this work is based on pix2pix \cite{isola2017image}, which uses a cGAN discussed in the last section. It is very robust and could already be applied to various problems. An example can be found in the TensorFlow tutorials\footnote{\url{https://www.tensorflow.org/tutorials/generative/pix2pix}}, where it is applied to a data set of architectural facades. However, to adapt the pix2pix GAN for the phase retrieval problem, some modifications are necessary. The network uses the TensorFlow \cite{abadi2016tensorflow} library, calculations are performed with scipy \cite{virtanen2020scipy}, and plots are drawn with matplotlib \cite{4160265}.
\begin{figure*}
	\includegraphics[width=\linewidth]{fig/reconstruction.png}
	\caption{The elliptical image of ground truth and predicted image by trained GAN. The elliptic curve (in red color) has been drwan using the second order moment and cyan dots show the centroids (mx, my) of images. There are two arraows in each image showing the skewness of pixel distributuion along x and y axis (magenta and blue color).}
	\label{fig:recons}
\end{figure*}
\subsection{Hyperparameter tuning}
The GAN used for this work depends on several parameters which will be explained here briefly. An in-depth discussion can be found in \cite{murphy2022probabilistic}.

The learning rate of the optimizer is a measure of how much the model changes per iteration. Small learning rates can lead to underfitting, and large learning rates can make the model unstable. It is therefore important to carefully choose the learning rate \cite{murphy2022probabilistic}. Figure \ref{fig:Plot_learning_rate_loss} shows the effect of the learning rate on both generator and discriminator loss for three different values of learning rate. Both loss functions have fewer outliers with decreasing learning rates, which is expected, as there is less change in the models with low learning rates. Even though all models stabilize at the same level, low learning rates are preferred.

The kernel size is the size of the kernel in the convolutional layer. It determines the amount of pixels that are linearly combined into a new pixel. A large kernel size allows one to catch features that are a few pixels away, but it also means that unrelated features might be introduced. The kernel size does not have a big effect on the loss functions, as shown in figure \ref{fig:Plot_kernel_size_loss}. Smaller kernel sizes seem to have more outliers, which means that either generator or discriminator gains an advantage. Therefore, a kernel size of 5 is preferred.

The amount of noise is reflected by the two parameters $\alpha$ and $\beta$. Both indicate the percentage of pixels that change to either black or white, hence the name Salt and Pepper noise, where $\alpha$ is introduced in the real image, $\beta$ in the generated image. Different ratios $\frac{\alpha}{\beta}$ can lead to different model performances. There is no significant difference between distinct noise rates introduced in the images. Fig.~\ref{fig:Plot_noise_loss} shows the loss functions on smaller images (64 x 64). As there is no effect, it was not necessary to repeat this analysis for larger images.

The batch size defines the number of images that pass the network simultaneously. It is observed that smaller batch sizes can lead to better generalization \cite{prince2023understanding}. Figure \ref{fig:Plot_batchsize_loss} shows two different batch sizes. Here, when two images are processed simultaneously, there are fewer outliers, but since it increases the training time heavily, a batch size of 1 is used.

While training GANs, one can give the discriminator an advantage by increasing the number of training steps for it before returning to the generator training. It can increase the performance of the model. However, it increases the training time as well and leads to a lower discriminator loss score, as shown in \ref{fig:Plot_discrep_loss}. At the same time, the generator score increases slightly, which should be no surprise. Because the generated images did not improve with higher discriminator training, they are usually trained in the same amount as the generator.

Finally, the amount of sparse sampling can be varied, giving the model access to more pixels. More telescopes automatically lead to more baselines and, hence, more pixels that are available. Figure \ref{fig:Plot_telescopes_loss} shows the loss functions for different numbers of telescopes. There is a huge disparity, which can partly be explained by the fact that the relation between telescopes and baselines is not linear. The Fourier plane can be sampled sixfold when using four telescopes in contrast to only two telescopes. In the latter case, both the generator and discriminator are not trained smoothly, as seen by the outliers. It is already better with three telescopes and very promising when using four telescopes. The degree of sparse sampling seems to have the biggest effect of all hyperparameters.

### 2024-08-09 Phase_II/draft/intro.tex
the first draft

\section{Introduction}

Intensity Interferometry (II) emerged in the 1970s as a groundbreaking technique for measuring the diameters, orbits, and limb-darkening coefficients of 32 stars in the N-body system. Despite these significant achievements, the method did not gain widespread adoption due to the then-required highly sensitive photon detectors and sophisticated data analysis techniques. However, advancements in computational methods and modern electronics, which now offer time resolution of detectors in the nanoseconds (ns) to picoseconds (ps) range, have renewed II as a feasible technique for resolving astrophysical objects at visible wavelengths. Current simulations with ns resolution of photon detectors show that II is effective in achieving high precision measurement of parameters for stellar objects \citep{10.1093/mnras/stab2391, 10.1093/mnras/stac2433}. However, a significant drawback of II is the loss of phase information. Consequently, a full reconstruction of the brightness distribution of a source with II necessitates phase information.

Several theoretical and computational approaches to phase reconstruction with II have been proposed. \cite{gamo1963triple} introduced the concept of triple-intensity correlation, which \cite{goldberger1963use} further applied in an experiment to observe scattered particles in microscopic systems. Sato conducted experiments to measure the diameter and phase of asymmetrical objects, suggesting that triple correlation could extend II to image stellar bodies \citep{sato1978imaging, sato1979computer, sato1981adaptive}. Despite its potential, the sensitivity of the signal to noise poses a significant challenge for this approach.

Later \cite{holmes2010two} proposed an alternative method, utilizing the Cauchy-Riemann relations to reconstruct 1-D images and extending this to 2-D images across a range of signal-to-noise (SNR) values. This algorithm was applied to simulated data of stellar objects using II, considering existing and forthcoming Imaging Cherenkov Telescope Arrays (IACTs) with a large number of telescopes \citep{nunez2010stellar, nunez2012high, nunez2012imaging}.

In this paper, we propose an alternative approach using Generative Adversarial Networks (GANs) \citep{goodfellow2014generative} to reconstruct images of stellar objects using II. We consider four Imaging Cherenkov Telescope Arrays (IACTs) located in the Northern Hemisphere and perform a one-night simulation for a fast-rotating star. The predicted image using a trained GAN shows promising results for reconstructing the image's shape and size. The evaluation of the predicted image is conducted using image moments, demonstrating that the size and shape of the fast-rotating star are reconstructed. However, the brightness distribution recovers only at the third-order moment.

This paper is organized as follows: The first section discusses Intensity Interferometry following its signal and noise for fast-rotating stars along the Earth's rotation. The second section introduces the GAN formulation and its structure. Following the third section details the parameter selection for training the GAN to reconstruct the image. After that, the fourth section presents the results of trained GAN visually and using image moments. At the end, there is a discussion of the entire result.

### 2024-08-09 Phase_II/draft/main.tex
the first draft

\documentclass[fleqn,usenatbib,twocolumn]{mnras}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{siunitx}
\usepackage{enumerate}
\usepackage{caption,subcaption}
\usepackage{comment}
\captionsetup{compatibility=false}
\usepackage{animate}
\usepackage{amsmath} % For \text and many other math symbols
\usepackage{amssymb} % For \mathbb
\usepackage{amsfonts} % For \mathbb

\newcommand{\abs}[1]{\left|#1\right|}
\newcommand{\norm}[2]{\left\lVert#1\right\rVert}

\title{Image reconstruction of stellar objects with Intensity Interferometry using Generative Adversarial Networks}
\date{}

\begin{document}
\maketitle

\begin{abstract}
In current astronomy, the simulation of Intensity Interferometry is demonstrating significant advancements in the high-precision resolution of stellar objects at optical wavelengths. Despite these achievements, phase retrieval remains challenging due to photon correlation. This paper proposes the application of a conditional Generative Adversarial Network (GAN) to address this issue of image reconstruction with Intensity Interferometry. Here, the GAN effectively reconstructs the shape, size, and brightness distribution of a fast-rotating star by utilizing sparsely sampled, phase-subtracted Fourier transforms of the star. This innovative approach promises to enhance the capabilities of Intensity Interferometry for image reconstruction in addition to estimating the parameters with high precision in astronomical observations.
\end{abstract}
\input{intro}
\input{II}
\input{GAN}
\input{ParaGan}
\input{Result}
\input{conclusion}

\bibliographystyle{mnras}
\bibliography{refs.bib}

\end{document}

### 2024-09-30 Phase_II/draft/GAN.tex
second edit

\section{Generative Adversarial Networks}
Generative Adversarial Networks (GANs) were invented by Ian Goodfellow in 2014. The concept is rather simple, as it consists of two competing networks. The first network is called a generator and creates new images based on an input image. Here, for consistency, the images generated by the generator will be denoted as generated images. The second network is the discriminator, which tries to distinguish between the generated image and the real image (ground truth) \citep{goodfellow2014generative}.
As a consequence of training both networks alternately, the generated images eventually become indistinguishable from the real images. It is nothing more than a two-player min-max game, a famous problem in game theory. GAN was initially proposed in the formulation form as:
\begin{equation}
	\centering
	\begin{aligned}
		\min_{G} \max_{D} V(D, G) &= \mathbb{E}_{x \sim p_{data}(x)} \left[ \log D(x) \right] \\
		&+ \mathbb{E}_{z \sim p_{z}(z)} \left[ \log \left( 1-D(G(z)) \right) \right]
	\end{aligned}
	\label{eq:Basic_GAN}
\end{equation}
here, $V(D, G)$ is the value function of the min-max game.

The goal is now to learn the distribution of the generator $p_g$ over the data $x$. We have input noise variables $p_z(z)$, as well as the two perceptrons $G(z; \theta_g)$ and $D(x; \theta_d)$ with parameters $\theta_i$. $G$ represents a differential function that maps from $z$ to the data space $x$, while $D(x)$ represents the probability that $x$ is from the real data \citep{goodfellow2014generative}. The problem can be reformulated as: 
\begin{equation}
	\centering
	\begin{aligned}
		\max_{D} V(G, D) &= \mathbb{E}_{x \sim p_{data}} \left[ \log D^{*}_{G}(x) \right] \\ 
		&+ \mathbb{E}_{x \sim p_{g}} \left[ \log \left( 1 - D^{*}_{G}(x) \right) \right]
	\end{aligned}
	\label{eq:GAN_reformulated}
\end{equation}
where $D^{*}_{G}$ denotes the optimum of the discriminator for a given fixed generator and is expressed as
\begin{equation}
	\centering
	D^*_G(x) = \frac{p_{data}(x)}{p_{data}(x) + p_g(g)}
	\label{eq:Disc_optimum}
\end{equation}
It can now be shown that the global optimum of equation (\ref{eq:GAN_reformulated}) is reached if and only if $p_g = p_{data}$. Furthermore, if both $G$ and $D$ are allowed to reach their optima, $p_g$ converges to $p_{data}$. A more detailed discussion of the problem, including proofs, can be found in \citep{goodfellow2014generative}.
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{fig/ellipsoid_0.jpg}
	\caption{Merged image, which includes the original and the sparsely sampled Fourier plane. It is exactly what the GAN receives. }
	\label{fig:GANinput}
\end{figure}
\begin{figure}
	\centering
	\begin{subfigure}{\linewidth}
		\centering
		\includegraphics[width=\textwidth]{fig/analysis/Plot_learning_rate_disc_loss.pdf}
		\caption{Discriminator loss for three different learning rates. }
		\label{fig:Plot_learning_rate_discloss}
	\end{subfigure}\hfill
	\begin{subfigure}{\linewidth}
		\centering
		\includegraphics[width=\textwidth]{fig/analysis/Plot_learning_rate_gen_total_loss.pdf}
		\caption{Total generator loss for different learning rates (eqn. (\ref{eq:total_gen_loss})).}
		\label{fig:Plot_learning_rate_genloss}
	\end{subfigure}\hfill
	\caption{Generator and discriminator losses for three different learning rates. The upper figure shows the total discriminator loss, and the lower figure shows the total generator loss. There is no significant difference, but the highest learning rate might be prone to outliers. }
	\label{fig:Plot_learning_rate_loss}
\end{figure}
\begin{figure}
	\centering
	\begin{subfigure}{\linewidth}
		\centering
		\includegraphics[width=\textwidth]{fig/analysis/Plot_Kernel_size_disc_loss.pdf}
		\caption{Discriminator loss for three different kernel sizes. }
		\label{fig:Plot_kernel_size_discloss}
	\end{subfigure}\hfill
	\begin{subfigure}{\linewidth}
		\centering
		\includegraphics[width=\textwidth]{fig/analysis/Plot_Kernel_size_gen_total_loss.pdf}
		\caption{Total generator loss for three different kernel sizes.}
		\label{fig:Plot_kernel_size_genloss}
	\end{subfigure}\hfill
	\caption{Generator and discriminator losses for three different kernel sizes in the convolutional layers. Here, the smallest kernel size has many outliers, while the largest kernel size seems to be the most stable.}
	\label{fig:Plot_kernel_size_loss}
\end{figure}
\begin{figure*}
	\centering
	\begin{subfigure}{0.5\linewidth}
		\centering
		\includegraphics[width=\textwidth]{fig/analysis/Plot_noise_factor_disc_loss.pdf}
		\caption{Discriminator loss for different noise percentages.}
		\label{fig:Plot_noise_discloss}
	\end{subfigure}\hfill
	\begin{subfigure}{0.5\linewidth}
		\centering
		\includegraphics[width=\textwidth]{fig/analysis/Plot_noise_factor_gen_total_loss.pdf}
		\caption{Generator losses for different noise percentages.}
		\label{fig:Plot_noise_genloss}
	\end{subfigure}\hfill
	\caption{Effect of the Salt and Pepper noise introduced in the images. Different ratios between $\alpha$ and $\beta$ are shown. There is no significant effect. Please note that these results are from training on 64-pixel images.}
	\label{fig:Plot_noise_loss}
\end{figure*}
\begin{figure*}
	\centering
	\begin{subfigure}{0.5\linewidth}
		\centering
		\includegraphics[width=\textwidth]{fig/analysis/Plot_Batchsize_disc_loss.pdf}
		\caption{Discriminator loss for different batch sizes.}
		\label{fig:Plot_batchsize_discloss}
	\end{subfigure}\hfill
	\begin{subfigure}{0.5\linewidth}
		\centering
		\includegraphics[width=\textwidth]{fig/analysis/Plot_Batchsize_gen_total_loss.pdf}
		\caption{Generator losses for different batch sizes.}
		\label{fig:Plot_batchsize_genloss}
	\end{subfigure}\hfill
	\caption{Loss functions for two different batch sizes. Large batch sizes seem to be more robust, but they also increase training time significantly. }
	\label{fig:Plot_batchsize_loss}
\end{figure*}
\begin{figure*}
	\centering
	\begin{subfigure}{0.5\linewidth}
		\centering
		\includegraphics[width=\textwidth]{fig/analysis/Plot_Disc_rep_disc_loss.pdf}
		\caption{Discriminator loss for different discriminator training.}
		\label{fig:Plot_discrep_discloss}
	\end{subfigure}\hfill
	\begin{subfigure}{0.5\linewidth}
		\centering
		\includegraphics[width=\textwidth]{fig/analysis/Plot_Disc_rep_gen_total_loss.pdf}
		\caption{Generator losses for different discriminator training.}
		\label{fig:Plot_discrep_genloss}
	\end{subfigure}\hfill
	\caption{The amount of discriminator training has a high impact on the discriminator score. The discriminator repetition indicates the factor by which the discriminator is trained more with respect to the generator.}
	\label{fig:Plot_discrep_loss}
\end{figure*}
\begin{figure*}
	\centering
	\begin{subfigure}{0.5\linewidth}
		\centering
		\includegraphics[width=\textwidth]{fig/analysis/Plot_N_telescopes_disc_loss.pdf}
		\caption{Discriminator loss for different amounts of telescopes.}
		\label{fig:Plot_telescopes_discloss}
	\end{subfigure}\hfill
	\begin{subfigure}{0.5\linewidth}
		\centering
		\includegraphics[width=\textwidth]{fig/analysis/Plot_N_telescopes_gen_total_loss.pdf}
		\caption{Generator loss for different amount of telescopes.}
		\label{fig:Plot_telescopes_genloss}
	\end{subfigure}\hfill
	\caption{The number of telescopes has a very impact on the model performance. If there are only two telescopes (1 baseline), both discriminator and generator are not trained smoothly: One gains a big advantage over the other. The result of four telescopes (6 baselines) is a lot better because the loss functions change only slightly with increasing steps.}
	\label{fig:Plot_telescopes_loss}
\end{figure*}
GANs can be extended to a conditional model \citep{mirza2014conditional}. In this case, both generator and discriminator receive extra information $y$, such that the value function of the conditional GAN (cGAN) can be expressed as:
\begin{equation}
	\centering
	\begin{aligned}
		V(D, G) &= \mathbb{E}_{x \sim p_{data}(x)} \left[ \log D(x|y) \right] \\
		&+ \mathbb{E}_{z \sim p_{z}(z)} \left[ \log \left( 1-D(G(z|y) \right) \right]
	\end{aligned}
	\label{eq:conditional_GAN}
\end{equation}

Furthermore, \citep{isola2017image} observed that combining the cGAN given in equation \ref{eq:conditional_GAN} with the traditional L1-loss improves results, as the generator tries to be close to the ground truth. Hence, the function that is minimized as:
\begin{equation}
	\centering
	L_{tot} = \arg \min_{G} \max_{D} V(D, G) + \lambda \cdot L_1(G)
	\label{eq:total_gen_loss}
\end{equation}
where $\lambda$ = 100 and $L_1(g)$ is given by equation (\ref{eq:l1_loss})
\begin{equation}
	\centering
	L_1(g) = \mathbb{E}_{x,y,z} \left[ ||{y - G(x,z)}||_1 \right]
	\label{eq:l1_loss}
\end{equation}

This type of network is shown to be very robust, as it has been applied to several problems. Examples include creating colored images from grayscale images, creating images of facades based on architectural labels, changing from day to night in different pictures, and predicting a map based on satellite data. A longer list of applications is given in \citep{isola2017image}.

\subsection{Generator}
The used generator in this paper is a common U-Net convolutional network \citep{ronneberger2015u}. It consists of a contracting part, reducing the image size, and an expansive part, where the image is enlarged. The contracting part consists of repeated application of alternating convolutional layers and rectified linear unit (ReLU) layers. The expansion consists of repeated convolution, batch normalization, and ReLU layers. The first contracting step also includes a dropout layer \citep{isola2017image}

\subsection{Discriminator}
The discriminator that has been taken here, named PatchGAN, does not work globally but rather classifies single patches as real or fake. The overall result is then estimated based on the average. The model architecture is as follows: zero padding, convolution, batch-norm, ReLu, zero-padding, and convolution \citep{isola2017image}.

### 2024-09-30 Phase_II/draft/II.tex
second edit

@@
 \section{Intensity Interferometry with ICTA}
+Recently, Intensity Interferometry (II) has emerged as an additional tool to resolve stellar objects as it solves some of the key limitations of classical optical interferometry (atmospheric turbulence, length of baseline, and the sensitivity of the optical aperture).
+It is suitable for the high-resolution study of very massive, hot, and short-lived stars, such as OB-type, Wolf-Rayet, and Pulsating stars in N-body systems.
 R.
 Hanbury Brown and Robert Q.
-Twiss first carried out II.
-They successfully installed the Narrabri Stellar Intensity Interferometer to resolve the diameter of bright stars at visible wavelengths \citep{brown1954lxxiv, brown1974intensity}.
+Twiss first installed the Narrabri Stellar Intensity Interferometer (NSII) in 1974 to resolve the diameter of bright stars at visible wavelengths \citep{brown1954lxxiv, brown1974intensity}.
+Nowadays, Cherenkov Telescope Arrays (CTAs), which are primarily used for gamma-ray observations, are at the forefront of implementing II during moonlit nights when it does not detect gamma-ray radiation.
+Intensity correlation and angular size measurements of stars have been detected, particularly using Very Energetic Radiation Imaging Telescope Array Systems (VERITAS), High Energy Stereoscopic Systems (HESS) and Major Atmospheric Gamma Imaging Cherenkov Telescopes (MAGIC) \citep{kieda2022performance, zmija2022optical, abe2024performance}.
+
 \subsection{The signal for II}\label{sec:signal}
-In a simple case, an II consists of two light collectors, for example, MAGIC-I and MAGIC-II, which are pointed to a star and measure the intensity $I_1(t), I_2(t)$ respectively \citep{acciari2020optical, dravins2013optical}.
+In a simple case, an II consists of two light collectors, for example, MAGIC-I and MAGIC-II, which are pointed to a star and measure the intensity $I_1(t)$ and $I_2(t)$ respectively \citep{acciari2020optical, dravins2013optical}.
 The signals from both detectors are cross-correlated and averaged over time, which results in an equation form
@@
 \end{equation}
-here, $\Delta f$ is the electronic bandwidth, $\Delta \nu$ is the optical bandwidth, and $\Delta f \ll \Delta \nu$ \cite{acciari2020optical}.
+here, $\Delta f$ is the electronic bandwidth, $\Delta \nu$ is the optical bandwidth, and $\Delta f \ll \Delta \nu$ \citep{acciari2020optical}.
 $V_{12}$ is the Fourier transform of the source brightness distribution and is called complex visibility.
@@
 \end{figure}
+The main physics channel of ICTAs is the study of Very High Energy gamma rays ($\geq 30$ GeV) originating from particle showers in the atmosphere.
+Telescopes have an array of mirrors, which focus the light onto an array of photo-multiplier tubes (PMTs) \citep{aleksic2016major}.
+Here, fig.~\ref{fig:teles} shows an arrangement of four IACTs with similar properties each.
+For II, the light of a stellar source is focused on a single PMT, which has a filter in front.
+The purpose of this filter is to efficiently transmit light around mean observational frequency, which protects the PMTs from excessive light.
+It is necessary, as II observations are mainly done during full moon nights, where it is too bright for Very High Energy $\gamma$-ray observations.
+The optical signal of the PMTs is transmitted with optical fibers, converted to an electrical signal, and digitized \citep{acciari2020optical}.
+The measurable observable is the Pearson's correlation coefficient:
+\begin{equation}
+	\rho(\tau) = \frac{\left\langle \left( I_1(t) - \left\langle I_1 \right\rangle \right) \cdot \left( I_2(t + \tau) - \left\langle I_2 \right\rangle \right) \right\rangle}{\sqrt{\langle \left( I_1(t) - \langle I_1 \rangle \right)^2 \rangle} \cdot \sqrt{\langle \left( I_2(t) - \langle I_2 \rangle \right) ^2 \rangle}}
+	\label{eqn:pearson}
+\end{equation}
+It must be noted that the calculation of Pearson's correlation coefficient is non-trivial: MAGIC makes use of the convolution theorem for discrete Fourier transforms because it is computationally more efficient.
+Since $I_1$ and $I_2$ are proportional to the direct current of the PMTs ($DC_i$), the normalized contrast can be calculated as
+\begin{equation}
+	c \propto \frac{\rho}{\sqrt{\left(DC_1 \cdot DC_2 \right)}}.
+	\label{eq:norm_contrast2}
+\end{equation}
+One must also correct for a non-constant gain of the PMTs, as well as the moon.
+The latter can be done by measuring the background light with an additional PMT with no mirrors focused on it \citep{acciari2020optical}.
+
+The significance of the signal can be expressed as the signal-to-noise ratio (SNR), which depends on many factors.
+However, most importantly, it is proportional to the absolute value of visibility, which itself depends on the distance between the telescopes \citep{acciari2020optical}
+\begin{equation}
+	SNR = A \cdot \alpha \cdot q \cdot n \cdot \abs{V_{12}}^{2}(d) \cdot \sqrt{b_v} \cdot F^{-1} \cdot \sqrt{\frac{T}{2}} \cdot \sigma.
+	\label{eq:SNR}
+\end{equation}
+Here, $A$ is the total mirror area, $\alpha$ the quantum efficiency of the PMTs, $q$ the quantum efficiency of the optics, $n$ the differential photon flux from the source, and $b_v$ the cross-correlation bandwidth.
+The noise of the PMTs is accounted with $F$, $T$ denotes the observation time, and $\sigma$ is the normalized spectral distribution of the light (including filters) \citep{acciari2020optical}.
+While most of the parameters can be optimized with hardware, the only way to obtain a better SNR is to increase the observation time with fixed telescopes.
 \begin{figure}
@@
 \end{figure}
-\begin{figure*}
-	\centering
-	\begin{subfigure}{0.5\linewidth}
-		\includegraphics[width=\linewidth]{fig/ft/ft.jpg}
-		\caption{The fourier transform of source.}
-	\end{subfigure}\hfill
-	\begin{subfigure}{0.5\linewidth}
-		\includegraphics[width=\linewidth]{fig/ft/ft_log.jpg}
-		\caption{The logarithmic fourier transform of source.}
-	\end{subfigure}
-	\caption{Absolute value of the two-dimensional Fast Fourier Transform of fig.~\ref{fig:image} measured by Intensity Interferometry, and observation of maximum (u, v) plane with finite number of baselines can be completed with help of earth's rotation.}
-	\label{fig:ft}
-\end{figure*}
-\begin{figure*}
-	\centering
-	\begin{subfigure}{0.5\linewidth}
-		\includegraphics[width=\linewidth]{fig/ft/ft_base.jpg}
-		\caption{The fourier transform with baselines.}
-	\end{subfigure}\hfill
-	\begin{subfigure}{0.5\linewidth}
-		\includegraphics[width=\linewidth]{fig/ft/ft_log_base.jpg}
-		\caption{The logarithmic fourier transform with baselines.}
-	\end{subfigure}
-	\caption{The left panel shows the absolute value of the two-dimensional Fast Fourier Transform of fig.~\ref{fig:image} measured by baselines shown in fig.~\ref{fig:teles}.
-The right panel shows the same on logarithmic scale}
-	\label{fig:ft_base}
-\end{figure*}
-The main physics channel of ICTAs is the study of Very High Energy gamma rays ($\geq 30$ GeV) originating from particle showers in the atmosphere.
-Telescopes have an array of mirrors, which focus the light onto an array of photo-multiplier tubes (PMTs) \cite{aleksic2016major}.
-Here, fig.~\ref{fig:teles} shows an arrangement of four IACTs with similar properties each.
-For II, the light of a stellar source is focused on a single PMT, which has a filter in front.
-The purpose of this filter is to efficiently transmit light around mean observational frequency, which protects the PMTs from excessive light.
-It is necessary, as II observations are mainly done during full moon nights, where it is too bright for Very High Energy $\gamma$-ray observations.
-The optical signal of the PMTs is transmitted with optical fibers, converted to an electrical signal, and digitized \cite{acciari2020optical}.
-The measurable observable is the Pearson's correlation coefficient:
-\begin{equation}
-	\rho(\tau) = \frac{\left\langle \left( I_1(t) - \left\langle I_1 \right\rangle \right) \cdot \left( I_2(t + \tau) - \left\langle I_2 \right\rangle \right) \right\rangle}{\sqrt{\langle \left( I_1(t) - \langle I_1 \rangle \right)^2 \rangle} \cdot \sqrt{\langle \left( I_2(t) - \langle I_2 \rangle \right) ^2 \rangle}}
-	\label{eqn:pearson}
-\end{equation}
-Since $I_1$ and $I_2$ are proportional to the direct current of the PMTs ($DC_i$), the normalized contrast can be calculated as in equation \ref{eq:norm_contrast2}.
-One must also correct for a non-constant gain of the PMTs, as well as the moon.
-The latter can be done by measuring the background light with an additional PMT with no mirrors focused on it \cite{acciari2020optical}.
-\begin{equation}
-	c \propto \frac{\rho}{\sqrt{\left(DC_1 \cdot DC_2 \right)}}
-	\label{eq:norm_contrast2}
-\end{equation}
-It must be noted that the calculation of Pearson's correlation coefficient is non-trivial: MAGIC makes use of the convolution theorem for discrete Fourier transforms because it is computationally more efficient.
-
-The significance of the signal can be expressed as the signal-to-noise ratio (SNR), which depends on many factors.
-However, most importantly, it is proportional to the absolute value of visibility, which itself depends on the distance between the telescopes, shown in equation (\ref{eq:SNR}) \cite{acciari2020optical}.
-\begin{equation}
-	SNR = A \cdot \alpha \cdot q \cdot n \cdot \abs{V_{12}}^{2}(d) \cdot \sqrt{b_v} \cdot F^{-1} \cdot \sqrt{\frac{T}{2}} \cdot \sigma
-	\label{eq:SNR}
-\end{equation}
-here, $A$ is the total mirror area, $\alpha$ the quantum efficiency of the PMTs, $q$ the quantum efficiency of the optics, $n$ the differential photon flux from the source, and $b_v$ the cross-correlation bandwidth.
-The noise of the PMTs is accounted for with $F$, $T$ denotes the observation time, and $\sigma$ is the normalized spectral distribution of the light (including filters) \cite{acciari2020optical}.
-While most of the parameters can be optimized with hardware, the only way to obtain a better SNR is to increase the observation time with fixed telescopes.
-
 \subsection{Baseline considerations}
@@
 \end{equation}
-However, this work needs a good SNR value for high precision of measurement, so the large covered observational plane with telescopes is a necessity for II \cite{acciari2020optical, abeysekara2020demonstration}.
+However, this work needs a good SNR value for high precision of measurement, so the large covered observational plane with telescopes is a necessity for II \citep{acciari2020optical, abeysekara2020demonstration}.
 If the source is at the zenith, the coordinates in the Fourier plane ($u,v$) are given by:
@@
 Since not all sources are at the zenith, and the telescopes are stationary, Earth's rotation plays an important role in covering the maximum observational plane through the rotated baselines.
-It is given by equation (\ref{eq:baseline_rot}), which traces an ellipse for every pair of telescopes.
-Furthermore, the different altitudes $B_A$ of the telescopes must be considered \cite{dravins2013optical, saha2020theory}.
+It is given as
 \begin{equation}
@@
 \end{equation}
-here, $\delta$ is the declination and $h$ is the hour angle of the stellar source, and $l$ is the latitude of the telescopes.
-The three matrices $R_i$ correspond to the fundamental representation of the SO(3) group \cite{saha2020theory}.
+It traces an ellipse for every pair of telescopes.
+Furthermore, the different altitudes $B_A$ of the telescopes must be considered \citep{dravins2013optical, saha2020theory}.
+Here, $\delta$ is the declination and $h$ is the hour angle of the stellar source, and $l$ is the latitude of the telescopes.
+The three matrices $R_i$ correspond to the fundamental representation of the SO(3) group \citep{saha2020theory}.
 Fig.~\ref{fig:base} shows the track of six baselines generated from the telescopes (fig.~\ref{fig:teles}) due to Earth's rotation.
@@
 As the number of baselines increases non-linearly, II benefits greatly from a large number of telescopes.
-So, the planned Cherenkov Telescope Array (CTA) will cover the maximum observational plane and provide insight into stellar objects with optical wavelengths in the future.
+So, the existing and upcoming Cherenkov Telescope Array Observatory (CTAO) will cover the maximum observational plane and provide insight into stellar objects with optical wavelengths in the future.
+\begin{figure}
+	\centering
+	\begin{subfigure}{\linewidth}
+		\includegraphics[width=\linewidth]{fig/ft/ft.jpg}
+		\caption{The fourier transform of source.}
+	\end{subfigure}\hfill
+	\begin{subfigure}{\linewidth}
+		\includegraphics[width=\linewidth]{fig/ft/ft_log.jpg}
+		\caption{The logarithmic fourier transform of source.}
+	\end{subfigure}
+	\caption{Absolute value of the two-dimensional Fast Fourier Transform of fig.~\ref{fig:image} on linear and logarithmic scales.
+Observation of maximum (u, v) plane with finite number of baselines can be completed with help of earth's rotation.}
+	\label{fig:ft}
+\end{figure}
+\begin{figure}
+	\centering
+	\begin{subfigure}{\linewidth}
+		\includegraphics[width=\linewidth]{fig/ft/ft_base.jpg}
+		\caption{The fourier transform with baselines.}
+	\end{subfigure}\hfill
+	\begin{subfigure}{\linewidth}
+		\includegraphics[width=\linewidth]{fig/ft/ft_log_base.jpg}
+		\caption{The logarithmic fourier transform with baselines.}
+	\end{subfigure}
+	\caption{The above panel shows the absolute value of the two-dimensional Fast Fourier Transform of fig.~\ref{fig:image} measured by baselines shown in fig.~\ref{fig:teles} on linear scale and below one shows the same on logarithmic scale.}
+	\label{fig:ft_base}
+\end{figure}
+\subsection{An Object: Fast Rotating Stars}
+In our work, we simulate a single fast-rotating star to test image reconstruction with II in intersection with the Generative Adversarial Networks (GAN).
+Fast rotation causes stars to take on an oblate shape, flattening at the poles and bulging at the equator due to the existence of stronger centrifugal force \citep{von1924radiative, 1999A&A...347..185M}.
+Fig.~\ref{fig:image} shows one of the simulations of a fast-rotating star, where the star takes on an elliptical shape with brightness distributed across the object.
+The brightness is maximum at the poles and minimum at the equator, a phenomenon known as gravity darkening \citep{lucy1967gravity}.
+This effect was first observed in the fast-rotating star Regulus through interferometric and spectroscopic data from the Center for High Angular Resolution Astronomy (CHARA) Array \citep{mcalister2005first}.
+These stars are crucial for understanding a variety of astrophysical processes and help to understand the stellar evolution, internal structure, and rotational dynamics over time.
 
-\subsection{An Object: Fast Rotating Stars}
-In our work, we simulate a single fast-rotating star to test image reconstruction using a GAN.
-Fast rotation causes stars to take on an oblate shape, flattening at the poles and bulging at the equator due to the existence of stronger centrifugal force \cite{von1924radiative, 1999A&A...347..185M}.
-Fig.~\ref{fig:image} shows one of the simulations of a fast-rotating star, where the star takes on an elliptical shape with brightness distributed across the object.
-The brightness is at its maximum at the poles and minimum at the equator, a phenomenon known as gravity darkening \cite{lucy1967gravity}.
-This effect has been observed first through the interferometric and spectroscopic data from the CHARA Array for the fast-rotating star Regulus \cite{mcalister2005first}.
-Fast-rotating stars are crucial for understanding various astrophysical processes, including stellar evolution, structure, and dynamics over time.
-
-Intensity Interferometry observes the stellar object in the form of photons, and the correlation of it results in squared visibility (explained in subsection.\ref{sec:signal}).
+Intensity Interferometry (II) detects the photon from the stellar objects, and the correlation of it results in squared visibility (explained in subsection.\ref{sec:signal}).
 According to Van Cittert Zernike's theorem, this signal is the Fourier transform of brightness distribution in the sky.
-Fig.~\ref {fig:ft} shows the same statement for the source shown in fig.~\ref{fig:image} using II on linear and logarithmic scale.
-However, we do not have an existing technique to observe the complete signals, and we could capture some parts of it only with a one-night simulation, which has been shown in fig.~\ref{fig:ft_base}.
-It is the covered observational plane using the baselines shown in fig.~\ref{fig:teles}.
-However, the upcoming CTA promises to cover the maximum observational plane for stellar objects.
+Fig.~\ref {fig:ft} visualize this statement for the source shown in fig.~\ref{fig:image} using II on linear and logarithmic scales.
+However, current observational techniques are unable to capture the full signal, and only partial data can be collected with a single night's simulation, which has been shown in fig.~\ref{fig:ft_base}.
+It is the covered observational plane using the baselines shown in fig.~\ref{fig:teles} on linear and logarithmic scales, respectively.
+However, the upcoming CTAO promises to greatly expand the observable portion of the visibility plane for stellar objects, offering new insights into the mysteries of the universe.

### 2024-09-30 Phase_II/draft/ParaGan.tex
second edit

@@
 The left panels are signals using six baselines, which work as input for GAN.
-The first, middle panel is the real image, also called ground truth, and GAN tries to mimic it during the training.
+The first middle panel is the real image, also called ground truth, and GAN tries to mimic it during the training.
 The second middle panel is the reconstructed image, also called the predicted image, with trained GAN, and the end panel is the difference between the ground truth and the predicted image.}
@@
 \end{figure*}
-Here, we discuss the parameters for the GAN structure which is trained to reconstruct the image of stellar objects using II.
+Here, we discuss the parameters for the GAN structure, which is trained to reconstruct the image of stellar objects using II.
+Due to the adversarial nature of GANs, where the generator and discriminator compete in a min-max game, careful tuning of key parameters ensures that both networks converge properly.
+
 \subsection{Data preparation}
@@
 	\end{subfigure}\hfill
-	\caption{The second order central moments which provides the information about the size and shape of stellar objects.}
+	\caption{The second-order central moments provide information about the size and shape of stellar objects.}
 	\label{fig:struc}
@@
 	\end{subfigure}\hfill
-	\caption{This figure shows the 3rd moments for reconstructed images and represents the brightness distribution.}
+	\caption{This figure shows the 3rd-order central moments for reconstructed images and represents the brightness distribution.}
 	\label{fig:moments}
@@
 As II does not measure the phase, the absolute value is calculated (shown in fig.~ \ref{fig:ft} on a linear and logarithmic scale for visualization).
-It is also where the sparse sampling is introduced, namely by a pixel-wise multiplication between the absolute valued Fourier transformed image and the sparse sampling map.
+The sparse sampling is also introduced, namely by a pixel-wise multiplication between the absolute valued Fourier transformed image and the sparse sampling map.
 The result is a map in the Fourier plane with several ellipses, also called the sparse sampling map.
@@
 \subsection{GAN architecture}
-The GAN used in this work is based on pix2pix \cite{isola2017image}, which uses a cGAN discussed in the last section.
+The GAN used in this work is based on pix2pix \citep{isola2017image}, which uses a cGAN discussed in the last section.
 It is very robust and could already be applied to various problems.
@@
 However, to adapt the pix2pix GAN for the phase retrieval problem, some modifications are necessary.
-The network uses the TensorFlow \cite{abadi2016tensorflow} library, calculations are performed with scipy \cite{virtanen2020scipy}, and plots are drawn with matplotlib \cite{4160265}.
+The network uses the TensorFlow \citep{abadi2016tensorflow} library, calculations are performed with scipy \citep{virtanen2020scipy}, and plots are drawn with matplotlib \citep{4160265}.
 \begin{figure*}
@@
 	\caption{The elliptical image of ground truth and predicted image by trained GAN.
-The elliptic curve (in red color) has been drwan using the second order moment and cyan dots show the centroids (mx, my) of images.
-There are two arraows in each image showing the skewness of pixel distributuion along x and y axis (magenta and blue color).}
+The elliptic curve (in red) was drawn using the second-order moment, and cyan dots show the centroids (mx, my) of the images.
+There are two arrows in each image showing the skewness of pixel distribution along the x and y axes (magenta and blue color).}
 	\label{fig:recons}
@@
 \subsection{Hyperparameter tuning}
-The GAN used for this work depends on several parameters which will be explained here briefly. An in-depth discussion can be found in \cite{murphy2022probabilistic}.
+The GAN used for this work depends on several parameters, which will be explained here briefly (an in-depth discussion can be found in \citep{murphy2022probabilistic}).
 
@@
 Small learning rates can lead to underfitting, and large learning rates can make the model unstable.
-It is therefore important to carefully choose the learning rate \cite{murphy2022probabilistic}.
-Figure \ref{fig:Plot_learning_rate_loss} shows the effect of the learning rate on both generator and discriminator loss for three different values of learning rate.
+It is therefore important to carefully choose the learning rate \citep{murphy2022probabilistic}.
+Figure \ref{fig:Plot_learning_rate_loss} shows the effect of the learning rate on both generator and discriminator loss for three different values of it.
 Both loss functions have fewer outliers with decreasing learning rates, which is expected, as there is less change in the models with low learning rates.
@@
 The batch size defines the number of images that pass the network simultaneously.
-It is observed that smaller batch sizes can lead to better generalization \cite{prince2023understanding}.
+It is observed that smaller batch sizes can lead to better generalization \citep{prince2023understanding}.
 Figure \ref{fig:Plot_batchsize_loss} shows two different batch sizes.

### 2024-09-30 Phase_II/draft/Result.tex
second edit

\section{The Reconstructed Image with GAN}
In this section, we will first discuss phase retrieval using hyperparameters, as mentioned earlier, followed by an analysis where multiple sources are trained simultaneously. The best performance for image reconstruction has been observed with a learning rate of $2 \cdot 10^{-4}$, a kernel size of 5x5, and equal noise percentages in original and generated images. The batch size selected is 1, and the discriminator-generator receives equal training.
\subsection{The Predicted Image with Trained GAN}
The success of the GAN in training the model for Intensity Interferometry to reconstruct images of fast-rotating stars is demonstrated in Fig.~\ref{fig:GAN}. The GAN was trained on training datasets for 60,000 steps. After training, the GAN was tested on different validation datasets, producing predicted images of a fast-rotating star. Fig.~\ref{fig:GAN} presents a set of four combined images demonstrating the GAN's performance in reconstructing the shape, size, and brightness distribution of the fast-rotating star using II. The left panel shows the signals covered by six baselines, which serve as the input for the generator to train the GAN. The first middle panel displays the real image, or ground truth, which the discriminator uses to differentiate between real and generated images from the generator. During training, the GAN aims to mimic this ground truth. The second middle panel depicts the reconstructed image, or predicted image, produced by the trained GAN. This panel illustrates the success of the GAN in image reconstruction using II. The right panel shows the difference between the ground truth and the predicted image. This difference should be minimized for high-precision image reconstruction with the application of GAN on II. The predicted images of Fig.~\ref{fig:GAN} showed positive results, accurately providing visual information about the source's size and shape, as well as the distributed brightness. This image reconstruction was achieved using only six baselines. However, the results can be further improved by increasing the number of telescopes to cover more (u, v) planes, making the existing and upcoming Cherenkov Telescope Array Observatory (CTAO) an ideal candidate in collaboration with existing CTA. 
\subsection{Evaluation of GAN using moments}
After the success of GAN in reconstructing the image using II, there is a need for evaluation of it. So, we use the image moments. Image moments are statistical properties that provide information about the reconstructed shape, size, and intensity distribution of the objects in the image. These moments help quantify key features like the position, orientation, and distribution of brightness in the image, allowing for an objective evaluation of how well the predicted image corresponds to the actual object. We will analyze the consistency and accuracy of the GAN-generated image by comparing its moments to those of the ground truth. It provides a reliable framework for evaluating reconstruction quality, as image moments highlight the subtle differences in geometric and intensity properties that might not be visually apparent.

The raw moment $M_{ij}$ of an image I(x, y) is defined as \citep{hu1962visual}
\begin{equation}
	M_{ij} = \sum_{x} \sum_{y} x^i y^j I(x, y).
	\label{eqn:Mom}
\end{equation}

The zeroth order raw moment, which is the total intensity of an image and is called the monopole. It sums up all the pixel values across the image, providing an overall intensity value. So, the study of monopole provides the total flux of fast-rotating stars here. According to eqn.~\ref{eqn:Mom}, the monopole of a image is calculated as 
\begin{equation}
	M_{00} = \sum_{x} \sum_{y} I(x, y).
\end{equation}
Fig.~\ref{fig:mom1} shows the monopole for 50 different reconstructed images. It shows the linear behavior for the monopole between the ground truth (the real image) along the x-axis and the predicted image (reconstructed image) along the y-axis, which is obvious for different shape-size sources. This result explains the similarity between the total intensity of both images. It ensures that the predicted image has the approximately correct total brightness (the flux) compared to the ground truth. However, monopole does not explain the shape, size, and brightness distribution of fast-rotating stars. So, there is a need for higher-order moments.

The center of mass for the fast-rotating star or any other stellar object is calculated using the centroid (in x and y directions). These centroids are given in terms of first-order raw moment and monopole as
\begin{equation}
	\begin{aligned}
		&m_x = \frac{\sum_{x} x I(x,y)}{\sum_{x} \sum_{y} I(x, y)} = \frac{M_{10}}{M_{00}} \\
		&m_y = \frac{\sum_{y} y I(x,y)}{\sum_{x} \sum_{y} I(x, y)} = \frac{M_{01}}{M_{00}}
	\end{aligned}  
\end{equation}
Fig.~\ref{fig:mom2} and Fig.~\ref{fig:mom3} show the comparison of centroid along the x and y axis for 50 predicted images with respect to ground truths. The clustering of centroids in a given scale range for all the results explains that the reconstructed image correctly represents the spatial location of the fast-rotating star in compare with the ground truth.

Further, these calculated centroids will help to study the shape, size, and brightness distribution of fast-rotating stars in terms of higher-order image moments. For that, the central moment of an image is calculated according to
\begin{equation}
	\mu_{pq} = \frac{1}{M_{00}}\sum_{x} \sum_{y} (x - m_x)^p (y - m_y)^q I(x, y).
\end{equation}
The sum of $p$ and $q$ defines the order of the central moment.

The second order central moment ($\mu_{11}, \mu_{20}, \mu_{02}$) has been shown in Fig.~\ref{fig:struc}, which is used to study the structure of a fast-rotating star along the line of sight of observation (explain in upcoming subsection). All these three plots explain the linear relation of second-order moments again as for monopole and show the success of the application of GAN to reconstruct the image with II.

The information on brightness distribution is gathered using the skewness of the image by calculating third-order central moment ($\mu_{30}, \mu_{03}, \mu_{21}, \mu_{12}$) of images. Fig.~\ref{fig:moments} shows all third-order moments for the ground truth and reconstructed image. The skewness along the x and y axis ($\mu_{30}, \mu_{03}$) to test the GAN for II are acceptable, which can be seen in Fig.~\ref{fig:mom7} and Fig.~\ref{fig:mom8}, where a linear relation exists between ground truth and predicted image. However, the remaining higher moments $(\mu_{21}, \mu_{12})$ shown in Fig.~\ref{fig:mom9} and Fig.~\ref{fig:mom10} are not in good terms specially $\mu_{12}$.

\subsection{The reconstructed Parameters for object}
The centroids $(m_x, m_y)$ represents the center of the fast-rotating star. However, the calculated second-order central moment defines the orientation, semi-major axis, and eccentricity of the source \citep{teague1980image}. These parameters fully describe the ellipse that fits the image data based on the moments.

The orientation along the line of sight is defined as
\begin{equation}
	\theta = \frac{1}{2}\arctan \big(\frac{2\mu_{11}}{\mu_{20} - \mu_{02}}\big).
	\label{eqn:orn}
\end{equation}
The semi-major and semi-minor axis will be calculated according to
\begin{equation}
	\begin{aligned}
		&a = 2\sqrt{mp + \delta} \\
		&b = 2\sqrt{mp - \delta}
	\end{aligned}
	\label{eqn:semi}
\end{equation}
where,
\begin{equation}
	mp = \frac{\mu_{20} + \mu_{02}}{2}
	\label{eqn:mp}
\end{equation}
and
\begin{equation}
	\delta = \frac{\sqrt{4\mu_{11}^2 + (\mu_{20} - \mu_{02})^2}}{2}.	
	\label{eqn:delta}
\end{equation}
So, the eccentricity of the fast-rotating star in terms of axis value is 
\begin{equation}
	e = \sqrt{1 - a/b}.
	\label{eqn:eccen}
\end{equation}
Fig.~\ref{fig:recons} shows all zeroth to third order moments only for one ground and predicted image. In this figure, there is a red curve for both ground truth and predicted image, which is the representation of all second-order moments in terms of eqn.~\ref{eqn:orn} to eqn.~\ref{eqn:eccen} as orientation, axis value, and eccentricity. There is a cyan dot point as well, which represents the zeroth order moment for both images. There is also a third-order moment, which is expressed in terms of arrows in magenta and blue color to view the skewness along the x and y axes.

### 2024-09-30 Phase_II/draft/conclusion.tex
second edit

\section{Conclusion}
The challenge of phase retrieval in Intensity Interferometry (II) has been effectively addressed through the application of machine learning techniques, particularly with Generative Adversarial Networks (GANs). Our study demonstrates that using a GAN on II data successfully recovers the size, shape, and brightness distribution of a fast-rotating star. The evaluation based on image moments, specifically the monopole, second, and third-order moments, supports the effectiveness of the GAN in achieving accurate image reconstruction from a one-night simulation of II using six baselines.

A critical factor in the performance of the reconstruction process is the extent of Fourier plane coverage, which is determined by the number of available telescopes and the total observing time. The brightness distribution can likely be reconstructed with even higher precision with a full night of observation using four telescopes. Future work could explore different observatory layouts, such as the Southern Cherenkov Telescope Array (CTA) layout, to evaluate the impact on image reconstruction quality.

This study has not considered the detector efficiencies, which could influence the signal-to-noise ratio (SNR) in practical scenarios. Incorporating these efficiencies in future work will be important for providing a more accurate estimate of the SNR and the robustness of the GAN in real-world applications. While conditional GANs have proven effective in this study, there are other methods for generating images from image data. Exploring and comparing alternative methods, as well as adapting the GAN architecture itself, could offer improvements. For instance, different loss functions could be implemented and compared to enhance reconstruction quality. Further testing is required to refine the GAN and make it more robust and reliable. However, our findings suggest that machine learning is a promising approach for phase reconstruction in II.

In summary, while the current implementation shows strong potential, further exploration and refinement of machine learning models are needed to optimize their application in phase retrieval and image reconstruction in Intensity Interferometry.

### 2024-09-30 Phase_II/draft/intro.tex
second edit

@@
 Current simulations with ns resolution of photon detectors show that II is effective in achieving high precision measurement of parameters for stellar objects \citep{10.1093/mnras/stab2391, 10.1093/mnras/stac2433}.
-However, a significant drawback of II is the loss of phase information.
-Consequently, a full reconstruction of the brightness distribution of a source with II necessitates phase information.
+However, a significant drawback of II is the need for phase information.
+Consequently, a full reconstruction of the brightness distribution of a stellar source remains challenging.
 
 Several theoretical and computational approaches to phase reconstruction with II have been proposed.
-\cite{gamo1963triple} introduced the concept of triple-intensity correlation, which \cite{goldberger1963use} further applied in an experiment to observe scattered particles in microscopic systems.
+\citep{gamo1963triple} introduced the concept of triple-intensity correlation, which \citep{goldberger1963use} further applied in an experiment to observe scattered particles in microscopic systems.
 Sato conducted experiments to measure the diameter and phase of asymmetrical objects, suggesting that triple correlation could extend II to image stellar bodies \citep{sato1978imaging, sato1979computer, sato1981adaptive}.
@@
 
-Later \cite{holmes2010two} proposed an alternative method, utilizing the Cauchy-Riemann relations to reconstruct 1-D images and extending this to 2-D images across a range of signal-to-noise (SNR) values.
+Later \citep{holmes2010two} proposed an alternative method, utilizing the Cauchy-Riemann relations to reconstruct 1-D images and extending this to 2-D images across a range of signal-to-noise (SNR) values.
 This algorithm was applied to simulated data of stellar objects using II, considering existing and forthcoming Imaging Cherenkov Telescope Arrays (IACTs) with a large number of telescopes \citep{nunez2010stellar, nunez2012high, nunez2012imaging}.
 
-In this paper, we propose an alternative approach using Generative Adversarial Networks (GANs) \citep{goodfellow2014generative} to reconstruct images of stellar objects using II.
-We consider four Imaging Cherenkov Telescope Arrays (IACTs) located in the Northern Hemisphere and perform a one-night simulation for a fast-rotating star.
+Nowadays, artificial intelligence (AI) is applied to high-volume data to reduce human computing resources and time effort.
+New analysis techniques using Machine Learning (ML) applications on observed data are playing at the front to reveal the astronomical mystery.
+In radio morphologies, the supervised and unsupervised algorithm is used to distinguish the radio components from the infrared source \citep{wu2019radio, galvin2020cataloguing}.
+Recently, the image reconstruction of the M87 black hole using Generative Adversarial Networks (GANs) has been performed \citep{10.1093/mnras/stad3797}.
+There is also a need to introduce the application of ML to II data for high-resolution optical astronomy, which will also aim to overcome the limitations of image reconstruction.
+In this paper, we propose an alternative approach using GAN \citep{goodfellow2014generative} to reconstruct images of stellar objects using II.
+We consider four Imaging Cherenkov Telescope Arrays (IACTs) and perform a one-night simulation for a fast-rotating star.
 The predicted image using a trained GAN shows promising results for reconstructing the image's shape and size.
@@
 The second section introduces the GAN formulation and its structure.
-Following the third section details the parameter selection for training the GAN to reconstruct the image.
+The third section details the parameter selection for training the GAN to reconstruct the image.
 After that, the fourth section presents the results of trained GAN visually and using image moments.

### 2024-09-30 Phase_II/draft/main.tex
second edit

@@
 \begin{abstract}
-In current astronomy, the simulation of Intensity Interferometry is demonstrating significant advancements in the high-precision resolution of stellar objects at optical wavelengths.
-Despite these achievements, phase retrieval remains challenging due to photon correlation.
-This paper proposes the application of a conditional Generative Adversarial Network (GAN) to address this issue of image reconstruction with Intensity Interferometry.
-Here, the GAN effectively reconstructs the shape, size, and brightness distribution of a fast-rotating star by utilizing sparsely sampled, phase-subtracted Fourier transforms of the star.
-This innovative approach promises to enhance the capabilities of Intensity Interferometry for image reconstruction in addition to estimating the parameters with high precision in astronomical observations.
+In modern astronomy, the simulation of Intensity Interferometry demonstrates significant advancements in the high-precision resolution of stellar objects at optical wavelengths.
+Despite these achievements, phase retrieval remains challenging due to photon correlation, hence the image reconstruction.
+This paper proposes the application of a conditional Generative Adversarial Network (GAN) to Intensity Interferometry (II) data for high-resolution optical astronomy, aiming to overcome the limitations of traditional image reconstruction methods, as artificial intelligence (AI) techniques are at the forefront of revealing astronomical mysteries by analyzing observed data.
+Here, the cGAN effectively reconstructs the shape, size, and brightness distribution of a fast-rotating star by utilizing sparsely sampled, phase-subtracted Fourier transforms of the star.
+Simulations of II are based on an assembly of four telescopes similar to existing arrays.
+However, the sensitivity of the signal and high resolution are expected to improve with additional baselines.
+It makes the current and future Cherenkov Telescope Array Observatory (CTAO) an ideal candidate for II applications.
+This approach is highly relevant and innovative, addressing key challenges in phase reconstruction and proposing novel solutions that could revolutionize high-resolution imaging in astronomy.
 \end{abstract}

### 2024-10-02 Phase_II/draft/GAN.tex
second edit

@@
 \end{figure*}
-GANs can be extended to a conditional model \citep{mirza2014conditional}.
+GAN can be extended to a conditional model \citep{mirza2014conditional}.
 In this case, both generator and discriminator receive extra information $y$, such that the value function of the conditional GAN (cGAN) can be expressed as:
@@
 
-Furthermore, \citep{isola2017image} observed that combining the cGAN given in equation \ref{eq:conditional_GAN} with the traditional L1-loss improves results, as the generator tries to be close to the ground truth.
+Furthermore, \cite{isola2017image} observed that combining the cGAN given in equation \ref{eq:conditional_GAN} with the traditional L1-loss improves results, as the generator tries to be close to the ground truth.
 Hence, the function that is minimized as:
@@
 \end{equation}
-where $\lambda$ = 100 and $L_1(g)$ is given by equation (\ref{eq:l1_loss})
+where $\lambda$ = 100 and $L_1(G)$ is given as
 \begin{equation}
 	\centering
-	L_1(g) = \mathbb{E}_{x,y,z} \left[ ||{y - G(x,z)}||_1 \right]
+	L_1(G) = \mathbb{E}_{x,y,z} \left[ ||{y - G(x,z)}||_1 \right]
 	\label{eq:l1_loss}
@@
 Examples include creating colored images from grayscale images, creating images of facades based on architectural labels, changing from day to night in different pictures, and predicting a map based on satellite data.
-A longer list of applications is given in \citep{isola2017image}.
+A longer list of applications is given in \cite{isola2017image}.
 
@@
 The expansion consists of repeated convolution, batch normalization, and ReLU layers.
-The first contracting step also includes a dropout layer \citep{isola2017image}
+The first contracting step also includes a dropout layer \citep{isola2017image}.
 

### 2024-10-02 Phase_II/draft/II.tex
second edit

@@
-\section{Intensity Interferometry with ICTA}
-Recently, Intensity Interferometry (II) has emerged as an additional tool to resolve stellar objects as it solves some of the key limitations of classical optical interferometry (atmospheric turbulence, length of baseline, and the sensitivity of the optical aperture).
+\section{Intensity Interferometry with Imaging Cherenkov Telescope Array}
+Recently, Intensity Interferometry (II) has emerged again as an additional tool to resolve stellar objects as it solves some of the key limitations of classical optical interferometry (atmospheric turbulence, length of baseline, and the sensitivity of the optical aperture).
 It is suitable for the high-resolution study of very massive, hot, and short-lived stars, such as OB-type, Wolf-Rayet, and Pulsating stars in N-body systems.
@@
 Twiss first installed the Narrabri Stellar Intensity Interferometer (NSII) in 1974 to resolve the diameter of bright stars at visible wavelengths \citep{brown1954lxxiv, brown1974intensity}.
-Nowadays, Cherenkov Telescope Arrays (CTAs), which are primarily used for gamma-ray observations, are at the forefront of implementing II during moonlit nights when it does not detect gamma-ray radiation.
-Intensity correlation and angular size measurements of stars have been detected, particularly using Very Energetic Radiation Imaging Telescope Array Systems (VERITAS), High Energy Stereoscopic Systems (HESS) and Major Atmospheric Gamma Imaging Cherenkov Telescopes (MAGIC) \citep{kieda2022performance, zmija2022optical, abe2024performance}.
+Nowadays, Imaging Cherenkov Telescope Arrays (ICTAs), which are primarily used for gamma-ray observations, are at the forefront of implementing II during moonlit nights when it does not detect gamma-ray radiation.
+As a result, detection of intensity correlation and angular size measurements of stars is going on for highly resolved imaging with optical wavelength, particularly using Very Energetic Radiation Imaging Telescope Array Systems (VERITAS), High Energy Stereoscopic Systems (HESS), and Major Atmospheric Gamma Imaging Cherenkov Telescopes (MAGIC) \citep{kieda2022performance, zmija2022optical, abe2024performance}.
 
@@
 
-\subsection{The Signal-to-Noise Ratio for II}
+\subsection{Signal-to-Noise Ratio for Intensity Interferometry}
 \begin{figure}
@@
 	\includegraphics[width=\linewidth]{fig/telescope.png}
-	\caption{The telescope configuration with similar properties each used to simulate the signal for II.}
+	\caption{Configuration of the four Imaging Cherenkov Telescope Array (ICTAs) with similar properties each used to simulate the signal for II.}
 	\label{fig:teles}
@@
 Telescopes have an array of mirrors, which focus the light onto an array of photo-multiplier tubes (PMTs) \citep{aleksic2016major}.
-Here, fig.~\ref{fig:teles} shows an arrangement of four IACTs with similar properties each.
-For II, the light of a stellar source is focused on a single PMT, which has a filter in front.
+Here, Fig.~\ref{fig:teles} shows an arrangement of four ICTAs with similar properties each.
+For the simulation of II, the light of a stellar source is focused on a single PMT, which has a filter in front.
 The purpose of this filter is to efficiently transmit light around mean observational frequency, which protects the PMTs from excessive light.
-It is necessary, as II observations are mainly done during full moon nights, where it is too bright for Very High Energy $\gamma$-ray observations.
+It is necessary, as II observations are mainly done during full moon nights when it is too bright for Very High Energy $\gamma$-ray observations.
 The optical signal of the PMTs is transmitted with optical fibers, converted to an electrical signal, and digitized \citep{acciari2020optical}.
@@
 The noise of the PMTs is accounted with $F$, $T$ denotes the observation time, and $\sigma$ is the normalized spectral distribution of the light (including filters) \citep{acciari2020optical}.
-While most of the parameters can be optimized with hardware, the only way to obtain a better SNR is to increase the observation time with fixed telescopes.
+While most of the parameters can be optimized with hardware, the only way to obtain a better SNR is to increase the observation time with a fixed number of telescopes.
 \begin{figure}
@@
 	\includegraphics[width=0.8\linewidth]{fig/ellipse/ellipse6018.jpg}
-	\caption{This figure shows the simulated fast rotating star. The brightness is highest at the pole and there is gravitational darkening at the equator.}
+	\caption{This figure shows the simulated fast-rotating star. The brightness is highest at the pole, and gravitational darkening is present at the equator.}
 	\label{fig:image}
@@
 where $B_N$ and $B_E$ are the baselines expressed in north and east coordinates.
-Since not all sources are at the zenith, and the telescopes are stationary, Earth's rotation plays an important role in covering the maximum observational plane through the rotated baselines.
-It is given as
+Since not all sources are at the zenith, and the telescopes are stationary, Earth's rotation plays an important role in covering the maximum observational plane through the rotated baselines, which is given as
 \begin{equation}
@@
 It traces an ellipse for every pair of telescopes.
-Furthermore, the different altitudes $B_A$ of the telescopes must be considered \citep{dravins2013optical, saha2020theory}.
-Here, $\delta$ is the declination and $h$ is the hour angle of the stellar source, and $l$ is the latitude of the telescopes.
+Furthermore, the different altitudes of the telescopes $B_A$ must be considered \citep{dravins2013optical, saha2020theory}.
+Here, $\delta$ is the declination, and $h$ is the hour angle of the stellar source, and $l$ is the latitude of the telescopes.
 The three matrices $R_i$ correspond to the fundamental representation of the SO(3) group \citep{saha2020theory}.
@@
 As the number of baselines increases non-linearly, II benefits greatly from a large number of telescopes.
-So, the existing and upcoming Cherenkov Telescope Array Observatory (CTAO) will cover the maximum observational plane and provide insight into stellar objects with optical wavelengths in the future.
+The existing and upcoming Cherenkov Telescope Array Observatory (CTAO) can promise to cover the maximum observational plane and provide insight into stellar objects with optical wavelengths in the future.
 \begin{figure}
@@
 		\includegraphics[width=\linewidth]{fig/ft/ft.jpg}
-		\caption{The fourier transform of source.}
+		\caption{The Fourier transform of the source.}
 	\end{subfigure}\hfill
@@
 		\includegraphics[width=\linewidth]{fig/ft/ft_log.jpg}
-		\caption{The logarithmic fourier transform of source.}
+		\caption{The logarithmic Fourier transform of the source.}
 	\end{subfigure}
-	\caption{Absolute value of the two-dimensional Fast Fourier Transform of fig.~\ref{fig:image} on linear and logarithmic scales.
-Observation of maximum (u, v) plane with finite number of baselines can be completed with help of earth's rotation.}
+	\caption{Absolute value of the two-dimensional Fast Fourier Transform of Fig.~\ref{fig:image} on linear and logarithmic scales.
+Observation of the maximum (u, v) plane with a finite number of baselines can be completed with the help of Earth's rotation.}
 	\label{fig:ft}
@@
 		\includegraphics[width=\linewidth]{fig/ft/ft_base.jpg}
-		\caption{The fourier transform with baselines.}
+		\caption{The Fourier transform with baselines.}
 	\end{subfigure}\hfill
@@
 		\includegraphics[width=\linewidth]{fig/ft/ft_log_base.jpg}
-		\caption{The logarithmic fourier transform with baselines.}
+		\caption{The logarithmic Fourier transform with baselines.}
 	\end{subfigure}
-	\caption{The above panel shows the absolute value of the two-dimensional Fast Fourier Transform of fig.~\ref{fig:image} measured by baselines shown in fig.~\ref{fig:teles} on linear scale and below one shows the same on logarithmic scale.}
+	\caption{The upper panel shows the absolute value of the two-dimensional Fast Fourier Transform of Fig.~\ref{fig:image} measured by baselines shown in Fig.~\ref{fig:teles} on a linear scale, and the lower panel shows the same on a logarithmic scale.}
 	\label{fig:ft_base}
@@
 According to Van Cittert Zernike's theorem, this signal is the Fourier transform of brightness distribution in the sky.
-Fig.~\ref {fig:ft} visualize this statement for the source shown in fig.~\ref{fig:image} using II on linear and logarithmic scales.
-However, current observational techniques are unable to capture the full signal, and only partial data can be collected with a single night's simulation, which has been shown in fig.~\ref{fig:ft_base}.
-It is the covered observational plane using the baselines shown in fig.~\ref{fig:teles} on linear and logarithmic scales, respectively.
-However, the upcoming CTAO promises to greatly expand the observable portion of the visibility plane for stellar objects, offering new insights into the mysteries of the universe.
+Fig.~\ref {fig:ft} visualize this statement for the source shown in Fig.~\ref{fig:image} using II on linear and logarithmic scales.
+However, current observational techniques are unable to capture the full signal, and only partial data can be collected with a single night's simulation, which has been shown in Fig.~\ref{fig:ft_base}.
+It is the covered observational plane using the baselines shown in Fig.~\ref{fig:teles} on linear and logarithmic scales, respectively.
+However, the upcoming CTAO can promise to greatly expand the observable portion of the visibility plane for stellar objects, offering new insights into the mysteries of the universe.

### 2024-10-02 Phase_II/draft/ParaGan.tex
second edit

@@
 Here, we discuss the parameters for the GAN structure, which is trained to reconstruct the image of stellar objects using II.
-Due to the adversarial nature of GANs, where the generator and discriminator compete in a min-max game, careful tuning of key parameters ensures that both networks converge properly.
+Due to the adversarial nature of GAN, where the generator and discriminator compete in a min-max game, careful tuning of key parameters ensures that both networks converge properly.
 
@@
 	\end{subfigure}\hfill
-	\caption{The monopole, centroid along x and y direction of ground truth and predicted image.}
+	\caption{This set of figures shows the comparison of monopole, x-centroid, and y-centroid for ground truth and predicted images generated by trained GAN.}
 	\label{fig:cen}
@@
 	\end{subfigure}\hfill
-	\caption{The second-order central moments provide information about the size and shape of stellar objects.}
+	\caption{The second-order central moments provide information about the size and shape of stellar objects.
+This set of figures shows all the second-order central moments for ground truth and predicted images generated by trained GAN.}
 	\label{fig:struc}
@@
 	\end{subfigure}\hfill
-	\caption{This figure shows the 3rd-order central moments for reconstructed images and represents the brightness distribution.}
+	\caption{This set of figures shows all the 3rd-order central moments for ground truth and predicted images generated by trained GAN.
+It calculates the skewness and evaluates the brightness distribution of images.}
 	\label{fig:moments}
@@
 A two-dimensional Fast Fourier Transform, as well as a Fourier shift, is applied, which yields a complex number of every pixel.
-As II does not measure the phase, the absolute value is calculated (shown in fig.~ \ref{fig:ft} on a linear and logarithmic scale for visualization).
+As II does not measure the phase, the absolute value is calculated (shown in Fig.~\ref{fig:ft} on a linear and logarithmic scale for visualization).
 The sparse sampling is also introduced, namely by a pixel-wise multiplication between the absolute valued Fourier transformed image and the sparse sampling map.
 The result is a map in the Fourier plane with several ellipses, also called the sparse sampling map.
-The fig.~\ref{fig:ft_base} shows the sparse sampling for fig.~\ref{fig:image} as the source with four telescopes (fig.~\ref{fig:teles}).
+Fig.~\ref{fig:ft_base} shows the sparse sampling for Fig.~\ref{fig:image} as the source with four telescopes (Fig.~\ref{fig:teles}).
 Finally, the pixels are normalized and converted to 8-bit integers.
 This image represents the sparsely sampled complex visibility, as it can be measured with II.
-The image shown in figure \ref{fig:ft_base} is the input image for the GAN, which also requires the ground truth image.
+The image shown in Fig.~\ref{fig:ft_base} is the input image for the GAN, which also requires the ground truth image.
 So, the simulated stars are also resized using the same algorithm and converted to 8-bit integers to reduce the bias.
 The GAN must know the ground truth corresponding to an input image.
-Hence, they are merged side-by-side, shown in figure \ref{fig:GANinput}, and used as input to train the GAN.
+Hence, they are merged side-by-side, shown in Fig.~\ref{fig:GANinput}, and used as input to train the GAN.
 This procedure is conducted for all the simulated stars, with 10\% acting as test data, 10\% as validation data, and the remaining 80\% as training data.
@@
 It is therefore important to carefully choose the learning rate \citep{murphy2022probabilistic}.
-Figure \ref{fig:Plot_learning_rate_loss} shows the effect of the learning rate on both generator and discriminator loss for three different values of it.
+Fig.~\ref{fig:Plot_learning_rate_loss} shows the effect of the learning rate on both generator and discriminator loss for three different values of it.
 Both loss functions have fewer outliers with decreasing learning rates, which is expected, as there is less change in the models with low learning rates.
@@
 A large kernel size allows one to catch features that are a few pixels away, but it also means that unrelated features might be introduced.
-The kernel size does not have a big effect on the loss functions, as shown in figure \ref{fig:Plot_kernel_size_loss}.
+The kernel size does not have a big effect on the loss functions, as shown in Fig.~\ref{fig:Plot_kernel_size_loss}.
 Smaller kernel sizes seem to have more outliers, which means that either generator or discriminator gains an advantage.
@@
 It is observed that smaller batch sizes can lead to better generalization \citep{prince2023understanding}.
-Figure \ref{fig:Plot_batchsize_loss} shows two different batch sizes.
+Fig.~\ref{fig:Plot_batchsize_loss} shows two different batch sizes.
 Here, when two images are processed simultaneously, there are fewer outliers, but since it increases the training time heavily, a batch size of 1 is used.
 
-While training GANs, one can give the discriminator an advantage by increasing the number of training steps for it before returning to the generator training.
+While training GAN, one can give the discriminator an advantage by increasing the number of training steps before returning to the generator training.
 It can increase the performance of the model.
-However, it increases the training time as well and leads to a lower discriminator loss score, as shown in \ref{fig:Plot_discrep_loss}.
+However, it increases the training time as well and leads to a lower discriminator loss score, as shown in Fig.~\ref{fig:Plot_discrep_loss}.
 At the same time, the generator score increases slightly, which should be no surprise.
@@
 More telescopes automatically lead to more baselines and, hence, more pixels that are available.
-Figure \ref{fig:Plot_telescopes_loss} shows the loss functions for different numbers of telescopes.
+Fig.~\ref{fig:Plot_telescopes_loss} shows the loss functions for different numbers of telescopes.
 There is a huge disparity, which can partly be explained by the fact that the relation between telescopes and baselines is not linear.

### 2024-10-02 Phase_II/draft/Result.tex
second edit

@@
 The first middle panel displays the real image, or ground truth, which the discriminator uses to differentiate between real and generated images from the generator.
-During training, the GAN aims to mimic this ground truth.
+During training, the GAN aims to mimic these ground truth images.
 The second middle panel depicts the reconstructed image, or predicted image, produced by the trained GAN.
@@
 \subsection{Evaluation of GAN using moments}
-After the success of GAN in reconstructing the image using II, there is a need for evaluation of it.
-So, we use the image moments.
+The reconstructed images are good enough visually to claim the success of GAN in reconstructing the image using II.
+However, there is a need for statistical evaluation of this predicted image to guarantee success.
+So, we use image moments as a statistical method.
 Image moments are statistical properties that provide information about the reconstructed shape, size, and intensity distribution of the objects in the image.
@@
 
-The zeroth order raw moment, which is the total intensity of an image and is called the monopole.
+The zeroth order raw moment called the monopole is the total intensity of an image.
 It sums up all the pixel values across the image, providing an overall intensity value.
 So, the study of monopole provides the total flux of fast-rotating stars here.
-According to eqn.~\ref{eqn:Mom}, the monopole of a image is calculated as
+According to eqn.~\ref{eqn:Mom}, the monopole of an image is calculated as
 \begin{equation}
@@
 It ensures that the predicted image has the approximately correct total brightness (the flux) compared to the ground truth.
-However, monopole does not explain the shape, size, and brightness distribution of fast-rotating stars.
-So, there is a need for higher-order moments.
+However, monopole does not explain the position, shape, size, and brightness distribution of fast-rotating stars; there is a need for higher-order moments.
 
-The center of mass for the fast-rotating star or any other stellar object is calculated using the centroid (in x and y directions).
-These centroids are given in terms of first-order raw moment and monopole as
+The center of mass for the fast-rotating star or any other stellar object is calculated using the centroid (x-centroid and y-centroid).
+It represents the spatial position of the image and is calculated using first-order raw moment and monopole.
+The formulation of centroid along the x and y directions is
 \begin{equation}
@@
 \end{equation}
-Fig.~\ref{fig:mom2} and Fig.~\ref{fig:mom3} show the comparison of centroid along the x and y axis for 50 predicted images with respect to ground truths.
+Fig.~\ref{fig:mom2} and Fig.~\ref{fig:mom3} show the comparison of the x-centroid and y-centroid for 50 predicted images with respect to ground truths, respectively.
 The clustering of centroids in a given scale range for all the results explains that the reconstructed image correctly represents the spatial location of the fast-rotating star in compare with the ground truth.
@@
 However, the remaining higher moments $(\mu_{21}, \mu_{12})$ shown in Fig.~\ref{fig:mom9} and Fig.~\ref{fig:mom10} are not in good terms specially $\mu_{12}$.
+Further improvement is possible and needs to be studied.
 
 \subsection{The reconstructed Parameters for object}
-The centroids $(m_x, m_y)$ represents the center of the fast-rotating star.
+The centroids $(m_x, m_y)$ represent the center of the fast-rotating star and spatial location on the image.
 However, the calculated second-order central moment defines the orientation, semi-major axis, and eccentricity of the source \citep{teague1980image}.
@@
 
-The orientation along the line of sight is defined as
+The orientation of a fast-rotating star along the line of sight is defined in terms of second-order central moments as
 \begin{equation}
@@
 \end{equation}
-The semi-major and semi-minor axis will be calculated according to
+The semi-major and semi-minor axis of the stellar object will be calculated with the help of second-order central moment again and denoted as a and b here, respectively
 \begin{equation}
@@
 \end{equation}
-So, the eccentricity of the fast-rotating star in terms of axis value is 
+With the help of the axis value, the eccentricity of the fast-rotating star is calculated as
 \begin{equation}
@@
 Fig.~\ref{fig:recons} shows all zeroth to third order moments only for one ground and predicted image.
-In this figure, there is a red curve for both ground truth and predicted image, which is the representation of all second-order moments in terms of eqn.~\ref{eqn:orn} to eqn.~\ref{eqn:eccen} as orientation, axis value, and eccentricity.
+In this figure, there is a red curve for both ground truth and predicted image, which is the representation of all second-order moments in terms of Eqn.~\ref{eqn:orn} to Eqn.~\ref{eqn:eccen} as orientation, axis value, and eccentricity.
 There is a cyan dot point as well, which represents the zeroth order moment for both images.
-There is also a third-order moment, which is expressed in terms of arrows in magenta and blue color to view the skewness along the x and y axes.
+The third-order moment is expressed in terms of arrows in magenta and blue color to view the skewness along the x and y axes.

### 2024-10-02 Phase_II/draft/conclusion.tex
second edit

@@
 \section{Conclusion}
-The challenge of phase retrieval in Intensity Interferometry (II) has been effectively addressed through the application of machine learning techniques, particularly with Generative Adversarial Networks (GANs).
-Our study demonstrates that using a GAN on II data successfully recovers the size, shape, and brightness distribution of a fast-rotating star.
-The evaluation based on image moments, specifically the monopole, second, and third-order moments, supports the effectiveness of the GAN in achieving accurate image reconstruction from a one-night simulation of II using six baselines.
-
+Intensity Interferometry (II), a technique, is emerging after a long gap to overcome the challenges of Amplitude Interferometry on optical wavelength.
+It is rejuvenated with support from advanced facilities at the Imaging Cherenkov Telescope Arrays (ICTAs).
+These telescopes, equipped with large aperture areas and photon detectors capable of resolving signals within a nanosecond, are instrumental in capturing high-resolution images \citep{dravins2013optical}.
+The Major Atmospheric Gamma Imaging Cherenkov Telescope (MAGIC), one of the CTA in the world, is now also being used for II, observing stellar objects with its 17-meter diameter mirror \citep{lorenz2004status}.
+The telescope has already demonstrated the potential of II by measuring and comparing the diameters of individual stars \citep{abe2024performance}.
+Other existing arrays (Very Energetic Radiation Imaging Telescope Array System (VERITAS) and High Energy Stereoscopic System (HESS)) are also making progress as II when gamma-ray observation stops \citep{kieda2021veritas, zmija2022optical}.
+Future observations, made possible by more advanced, sensitive instrumentation and upcoming CTAO, promise to push the boundaries of what we can observe with optical range.
+However, there is a drawback of II in terms of phase loss of signal, capturing only its magnitude via photon correlation.
+Here, the challenge of phase retrieval in Intensity Interferometry (II) has been effectively addressed through the application of machine learning techniques, particularly with conditional Generative Adversarial Networks (cGAN).
+Our study demonstrates that the application of cGAN on II data successfully recovers the size, shape, and brightness distribution of a fast-rotating star.
+The evaluation based on image moments, specifically the monopole, second, and third-order moments, supports the effectiveness of the cGAN in achieving accurate image reconstruction from a one-night simulation of II using six baselines.
 A critical factor in the performance of the reconstruction process is the extent of Fourier plane coverage, which is determined by the number of available telescopes and the total observing time.
@@
 
-This study has not considered the detector efficiencies, which could influence the signal-to-noise ratio (SNR) in practical scenarios.
+While the results of this study demonstrate the significant potential of machine learning, particularly cGAN, for image reconstruction in II, several aspects need further refinement.
+Detector efficiencies, which impact the signal-to-noise ratio (SNR) in real-world scenarios, have yet to be incorporated, and addressing them will be crucial for more accurate SNR estimation.
 Incorporating these efficiencies in future work will be important for providing a more accurate estimate of the SNR and the robustness of the GAN in real-world applications.
-While conditional GANs have proven effective in this study, there are other methods for generating images from image data.
+While cGAN has proven effective in this study, there are other methods for generating images from image data.
 Exploring and comparing alternative methods, as well as adapting the GAN architecture itself, could offer improvements.
@@
 
-In summary, while the current implementation shows strong potential, further exploration and refinement of machine learning models are needed to optimize their application in phase retrieval and image reconstruction in Intensity Interferometry.
+In summary, though cGAN has shown promising results, further testing and improvements are necessary to make the model more robust and reliable in practical applications.
+Overall, this study highlights the potential of machine learning approaches for advancing phase retrieval and high-resolution image reconstruction in II, suggesting exciting future directions in the application of AI to optical astronomy.

### 2024-10-02 Phase_II/draft/intro.tex
second edit

--- 2024-08-09 Phase_II/draft/intro.tex
@@
 Despite these significant achievements, the method did not gain widespread adoption due to the then-required highly sensitive photon detectors and sophisticated data analysis techniques.
-However, advancements in computational methods and modern electronics, which now offer time resolution of detectors in the nanoseconds (ns) to picoseconds (ps) range, have renewed II as a feasible technique for resolving astrophysical objects at visible wavelengths.
+However, advancements in computational methods and modern electronics, which now offer time resolution of detectors in the nanoseconds (ns) range, have renewed II as a feasible technique for resolving astrophysical objects at visible wavelengths.
 Current simulations with ns resolution of photon detectors show that II is effective in achieving high precision measurement of parameters for stellar objects \citep{10.1093/mnras/stab2391, 10.1093/mnras/stac2433}.
-However, a significant drawback of II is the loss of phase information.
-Consequently, a full reconstruction of the brightness distribution of a source with II necessitates phase information.
+Yet, despite these technological advancements, II still faces a significant limitation: the absence of phase information, which is essential for the complete reconstruction of the brightness distribution of stellar sources.
 
@@
 Later \cite{holmes2010two} proposed an alternative method, utilizing the Cauchy-Riemann relations to reconstruct 1-D images and extending this to 2-D images across a range of signal-to-noise (SNR) values.
-This algorithm was applied to simulated data of stellar objects using II, considering existing and forthcoming Imaging Cherenkov Telescope Arrays (IACTs) with a large number of telescopes \citep{nunez2010stellar, nunez2012high, nunez2012imaging}.
+This algorithm was applied to simulated data of stellar objects using II, considering existing and forthcoming Imaging Cherenkov Telescope Arrays (ICTAs) with a large number of telescopes \citep{nunez2010stellar, nunez2012high, nunez2012imaging}.
+Despite these theoretical advances, practical application to actual observational data of stellar objects with II has yet to be achieved.
+There is a need to advance this field by introducing a novel image reconstruction technique.
 
-In this paper, we propose an alternative approach using Generative Adversarial Networks (GANs) \citep{goodfellow2014generative} to reconstruct images of stellar objects using II.
-We consider four Imaging Cherenkov Telescope Arrays (IACTs) located in the Northern Hemisphere and perform a one-night simulation for a fast-rotating star.
-The predicted image using a trained GAN shows promising results for reconstructing the image's shape and size.
-The evaluation of the predicted image is conducted using image moments, demonstrating that the size and shape of the fast-rotating star are reconstructed.
-However, the brightness distribution recovers only at the third-order moment.
+Currently, artificial intelligence (AI) is applied to high-volume data to reduce human computing resources and time effort.
+New analysis techniques using Machine Learning (ML) applications on observed data are playing at the front to reveal the astronomical mystery.
+In radio morphologies, the supervised and unsupervised algorithm is used to distinguish the radio components from the infrared source \citep{wu2019radio, galvin2020cataloguing}.
+Recently, the image reconstruction of the M87 black hole using Generative Adversarial Networks (GANs) has been performed \citep{10.1093/mnras/stad3797}.
+There is also a need to introduce the application of ML to II data, which will aim to overcome the limitations of image reconstruction and high-resolution optical astronomy.
+
+In this paper, we propose an alternative approach for image reconstruction of stellar objects with II using GAN \citep{goodfellow2014generative}.
+We consider four ICTAs and perform a one-night simulation for a fast-rotating star.
+The predicted image by a trained GAN shows promising results for reconstructing the image's shape and size.
+Image moments evaluate the predicted image and demonstrate that the size and shape of the fast-rotating star are reconstructed.
+However, the brightness distribution recovers only up to the third-order moment.
+With the introduction of more telescopes, we can expect even greater precision, especially in recovering higher-order image moments.
+This approach holds great promise, pushing the boundaries of high-resolution optical astronomy and opening up new possibilities for studying stellar objects with remarkable detail.
 
@@
 The second section introduces the GAN formulation and its structure.
-Following the third section details the parameter selection for training the GAN to reconstruct the image.
+The third section details the parameter selection for training the GAN to reconstruct the image.
 After that, the fourth section presents the results of trained GAN visually and using image moments.
-At the end, there is a discussion of the entire result.
+At the end, there is a conclusion of the entire result.

### 2024-10-02 Phase_II/draft/main.tex
second edit

@@
 
-\title{Image reconstruction of stellar objects with Intensity Interferometry using Generative Adversarial Networks}
+\title{Generative AI for Image Reconstruction with Intensity Interferometry: A First Attempt}
 \date{}
@@
 In modern astronomy, the simulation of Intensity Interferometry demonstrates significant advancements in the high-precision resolution of stellar objects at optical wavelengths.
-Despite these achievements, phase retrieval remains challenging due to photon correlation, hence the image reconstruction.
-This paper proposes the application of a conditional Generative Adversarial Network (GAN) to Intensity Interferometry (II) data for high-resolution optical astronomy, aiming to overcome the limitations of traditional image reconstruction methods, as artificial intelligence (AI) techniques are at the forefront of revealing astronomical mysteries by analyzing observed data.
+Despite these achievements, phase retrieval of the signal remains challenging due to photon correlation, hence the image reconstruction.
+Nowadays, artificial intelligence (AI) techniques are at the forefront of revealing astronomical mysteries by analyzing observed data.
+This paper proposes the application of a conditional Generative Adversarial Network (cGAN) to Intensity Interferometry data for high-resolution optical astronomy, aiming to overcome the limitations of traditional image reconstruction methods.
 Here, the cGAN effectively reconstructs the shape, size, and brightness distribution of a fast-rotating star by utilizing sparsely sampled, phase-subtracted Fourier transforms of the star.
 Simulations of II are based on an assembly of four telescopes similar to existing arrays.
-However, the sensitivity of the signal and high resolution are expected to improve with additional baselines.
-It makes the current and future Cherenkov Telescope Array Observatory (CTAO) an ideal candidate for II applications.
+However, the sensitivity of the signal and high resolution are expected to improve with additional baselines, which makes the current and future Cherenkov Telescope Array Observatory (CTAO) an ideal candidate for II applications.
 This approach is highly relevant and innovative, addressing key challenges in phase reconstruction and proposing novel solutions that could revolutionize high-resolution imaging in astronomy.

### 2024-10-16 Phase_II/draft/GAN.tex
..

@@
 \section{Generative Adversarial Networks}
-Generative Adversarial Networks (GANs) were invented by Ian Goodfellow in 2014.
+In 2014, Ian Goodfellow invented Generative Adversarial Networks (GANs).
 The concept is rather simple, as it consists of two competing networks.
@@
 Here, for consistency, the images generated by the generator will be denoted as generated images.
-The second network is the discriminator, which tries to distinguish between the generated image and the real image (ground truth) \citep{goodfellow2014generative}.
+The second network is the discriminator, which tries to distinguish between the generated image (predicted image) and the real image (ground truth) \citep{goodfellow2014generative}.
 As a consequence of training both networks alternately, the generated images eventually become indistinguishable from the real images.
@@
 \end{figure*}
-GAN can be extended to a conditional model \citep{mirza2014conditional}.
+Later, GAN extended its version to a conditional model \citep{mirza2014conditional}.
 In this case, both generator and discriminator receive extra information $y$, such that the value function of the conditional GAN (cGAN) can be expressed as:
@@
 This type of network is shown to be very robust, as it has been applied to several problems.
-Examples include creating colored images from grayscale images, creating images of facades based on architectural labels, changing from day to night in different pictures, and predicting a map based on satellite data.
+Examples include creating colored images from grayscale images based on architectural labels, changing from day to night in different pictures, and predicting a map based on satellite data.
 A longer list of applications is given in \cite{isola2017image}.

### 2024-10-16 Phase_II/draft/II.tex
..

@@
 Eqn.~\ref{eqn:HBT2} carry the information about the source's structure and shape.
-However, the phase information is lost due to the involvement of the absolute value of $V_{12}$.
-In observational astronomy, the correlation is often expressed in terms of the normalized contrast, given by:
+However, it loses the phase information due to the presence of only the absolute value of $V_{12}$.
+In observational astronomy, the correlation in intensity is often expressed in terms of the normalized contrast, given by :
 \begin{equation}
@@
 
-The significance of the signal can be expressed as the signal-to-noise ratio (SNR), which depends on many factors.
-However, most importantly, it is proportional to the absolute value of visibility, which itself depends on the distance between the telescopes \citep{acciari2020optical}
+The significance of the signal is expressed as the signal-to-noise ratio (SNR), which depends on many factors.
+However, most importantly, SNR is proportional to the absolute value of visibility, which itself depends on the distance between the telescopes \citep{acciari2020optical}
 \begin{equation}
@@
 	\includegraphics[width=0.8\linewidth]{fig/ellipse/ellipse6018.jpg}
-	\caption{This figure shows the simulated fast-rotating star. The brightness is highest at the pole, and gravitational darkening is present at the equator.}
+	\caption{This figure shows one of the simulated fast-rotating stars.
+The brightness is highest at the pole and lowest at the equator due to the presence of high-speed rotation of the star.
+This effect is named gravitational darkening in astronomy.}
 	\label{fig:image}
@@
 \subsection{Baseline considerations}
-The measurement of the size of stellar objects through absolute visibility depends on the distance between the telescopes, which is called the baseline $B$. 
+The measurement of the size of stellar objects through absolute visibility depends on the distance between the telescopes, which is called the baseline $B$
 \begin{equation}
-	V_{12}(B) = \frac{c(B)}{c(0)}
+	V_{12}(B) = \frac{c(B)}{c(0)}.
 	\label{eq:angular_size_meas}
@@
 It is the covered observational plane using the baselines shown in Fig.~\ref{fig:teles} on linear and logarithmic scales, respectively.
-However, the upcoming CTAO can promise to greatly expand the observable portion of the visibility plane for stellar objects, offering new insights into the mysteries of the universe.
+However, the instrumentation of existing and upcoming CTAO shows the possibility of covering the maximum observable portion of the visibility plane for stellar objects, offering high resolution to understand the stellar structure and its evolution with time.

### 2024-10-16 Phase_II/draft/ParaGan.tex
..

@@
 Here, we discuss the parameters for the GAN structure, which is trained to reconstruct the image of stellar objects using II.
-Due to the adversarial nature of GAN, where the generator and discriminator compete in a min-max game, careful tuning of key parameters ensures that both networks converge properly.
+Due to the adversarial nature of GAN, where the generator and discriminator compete in a min-max game, careful tuning of key parameters ensures that both networks are in good term to train the model.
 

### 2024-10-16 Phase_II/draft/Result.tex
..

@@
 The left panel shows the signals covered by six baselines, which serve as the input for the generator to train the GAN.
-The first middle panel displays the real image, or ground truth, which the discriminator uses to differentiate between real and generated images from the generator.
+The first, middle panel displays the real image, or ground truth, which the discriminator uses to differentiate between real and generated images from the generator.
 During training, the GAN aims to mimic these ground truth images.
@@
 This difference should be minimized for high-precision image reconstruction with the application of GAN on II.
-The predicted images of Fig.~\ref{fig:GAN} showed positive results, accurately providing visual information about the source's size and shape, as well as the distributed brightness.
-This image reconstruction was achieved using only six baselines.
-However, the results can be further improved by increasing the number of telescopes to cover more (u, v) planes, making the existing and upcoming Cherenkov Telescope Array Observatory (CTAO) an ideal candidate in collaboration with existing CTA.
+The predicted images of Fig.~\ref{fig:GAN} showed positive results.
+It accurately provides visual information about the source's size, shape, and brightness distribution over the surface.
+It is achieved here using only six baselines.
+However, the results can be further improved by increasing the number of telescopes to cover maximum (u, v) planes, making the existing and upcoming Cherenkov Telescope Array Observatory (CTAO) an ideal candidate.
 \subsection{Evaluation of GAN using moments}
@@
 Image moments are statistical properties that provide information about the reconstructed shape, size, and intensity distribution of the objects in the image.
-These moments help quantify key features like the position, orientation, and distribution of brightness in the image, allowing for an objective evaluation of how well the predicted image corresponds to the actual object.
+These moments help to quantify key features like the position, orientation, and distribution of brightness in the image, allowing for an objective evaluation of how well the predicted image corresponds to the actual object.
 We will analyze the consistency and accuracy of the GAN-generated image by comparing its moments to those of the ground truth.
@@
 \subsection{The reconstructed Parameters for object}
-The centroids $(m_x, m_y)$ represent the center of the fast-rotating star and spatial location on the image.
-However, the calculated second-order central moment defines the orientation, semi-major axis, and eccentricity of the source \citep{teague1980image}.
-These parameters fully describe the ellipse that fits the image data based on the moments.
+The centroids $(m_x, m_y)$ represent the center of the fast-rotating star and spatial location on the image only.
+However, the calculated second-order central moment defines the orientation, semi-major axis, and eccentricity with respect to the center of the source \citep{teague1980image}.
+These parameters based on the moments fully describe the two-dimensional ellipse that fits the image data.
 

### 2024-10-16 Phase_II/draft/conclusion.tex
..

@@
 \section{Conclusion}
-Intensity Interferometry (II), a technique, is emerging after a long gap to overcome the challenges of Amplitude Interferometry on optical wavelength.
+Intensity Interferometry (II), a technique, is emerging after a long gap to overcome the challenges of Amplitude Interferometry with optical wavelength range.
 It is rejuvenated with support from advanced facilities at the Imaging Cherenkov Telescope Arrays (ICTAs).
-These telescopes, equipped with large aperture areas and photon detectors capable of resolving signals within a nanosecond, are instrumental in capturing high-resolution images \citep{dravins2013optical}.
+These telescopes are instrumental in capturing high-resolution images equipped with large aperture areas and sensitive photon detectors (capable of resolving signals within a nanosecond) \citep{dravins2013optical}.
 The Major Atmospheric Gamma Imaging Cherenkov Telescope (MAGIC), one of the CTA in the world, is now also being used for II, observing stellar objects with its 17-meter diameter mirror \citep{lorenz2004status}.
@@
 The brightness distribution can likely be reconstructed with even higher precision with a full night of observation using four telescopes.
-Future work could explore different observatory layouts, such as the Southern Cherenkov Telescope Array (CTA) layout, to evaluate the impact on image reconstruction quality.
+Future work could explore different observatory layouts to study the impact on image reconstruction quality, such as the Southern Cherenkov Telescope Array (CTA) with MAGIC.
 
 While the results of this study demonstrate the significant potential of machine learning, particularly cGAN, for image reconstruction in II, several aspects need further refinement.
-Detector efficiencies, which impact the signal-to-noise ratio (SNR) in real-world scenarios, have yet to be incorporated, and addressing them will be crucial for more accurate SNR estimation.
-Incorporating these efficiencies in future work will be important for providing a more accurate estimate of the SNR and the robustness of the GAN in real-world applications.
-While cGAN has proven effective in this study, there are other methods for generating images from image data.
-Exploring and comparing alternative methods, as well as adapting the GAN architecture itself, could offer improvements.
-For instance, different loss functions could be implemented and compared to enhance reconstruction quality.
-Further testing is required to refine the GAN and make it more robust and reliable.
+(1) Detector efficiencies, which impact the signal-to-noise ratio (SNR) of real observational data, have yet to be incorporated.
+It will be crucial to address these challenges for more accurate SNR estimation.
+Incorporating these efficiencies in future work will be important for providing a more accurate estimate of the SNR.
+(2) Exploring and comparing different methods to generate images, which works better than cGAN to reconstruct stellar images with II.
+(3) Different loss functions can be used to check the reconstruction quality.
+So, there are further testing is required to refine the GAN and make it more robust and reliable.
 However, our findings suggest that machine learning is a promising approach for phase reconstruction in II.

### 2024-10-16 Phase_II/draft/intro.tex
..

@@
 
-Intensity Interferometry (II) emerged in the 1970s as a groundbreaking technique for measuring the diameters, orbits, and limb-darkening coefficients of 32 stars in the N-body system.
+Intensity Interferometry (II) emerged in the 1970s as a groundbreaking technique for measuring the diameters, orbits, and limb-darkening coefficients of 32 stars in single/binary star systems.
 Despite these significant achievements, the method did not gain widespread adoption due to the then-required highly sensitive photon detectors and sophisticated data analysis techniques.
-However, advancements in computational methods and modern electronics, which now offer time resolution of detectors in the nanoseconds (ns) range, have renewed II as a feasible technique for resolving astrophysical objects at visible wavelengths.
+However, advancements in computational methods and modern electronics, which now offer time resolution of detectors in the nanoseconds (ns) range, have renewed II as a feasible technique in comparison to the limitation of amplitude interferometry for resolving astrophysical objects at visible wavelengths.
 Current simulations with ns resolution of photon detectors show that II is effective in achieving high precision measurement of parameters for stellar objects \citep{10.1093/mnras/stab2391, 10.1093/mnras/stac2433}.
-Yet, despite these technological advancements, II still faces a significant limitation: the absence of phase information, which is essential for the complete reconstruction of the brightness distribution of stellar sources.
+However, despite these technological advancements, II faces a significant limitation in terms of phase loss and the absence of complete reconstruction of the brightness distribution of stellar sources.
 
@@
 Recently, the image reconstruction of the M87 black hole using Generative Adversarial Networks (GANs) has been performed \citep{10.1093/mnras/stad3797}.
-There is also a need to introduce the application of ML to II data, which will aim to overcome the limitations of image reconstruction and high-resolution optical astronomy.
+There is also a need to introduce the application of ML to II data, which will aim to overcome the limitations of image reconstruction and provide high-resolution optical astronomy.
 
@@
 However, the brightness distribution recovers only up to the third-order moment.
-With the introduction of more telescopes, we can expect even greater precision, especially in recovering higher-order image moments.
-This approach holds great promise, pushing the boundaries of high-resolution optical astronomy and opening up new possibilities for studying stellar objects with remarkable detail.
+We expect even greater precision of image reconstruction by including more telescopes, especially to recover the higher-order image moments.
+It holds great promise, pushing the boundaries of high-resolution optical astronomy and opening up new possibilities for studying stellar objects with remarkable detail.
 

### 2024-10-16 Phase_II/draft/main.tex
..

@@
 \begin{abstract}
-In modern astronomy, the simulation of Intensity Interferometry demonstrates significant advancements in the high-precision resolution of stellar objects at optical wavelengths.
+In modern astronomy, simulation and observation with Intensity Interferometry (II) are showing noteworthy progress with optical wavelengths to achieve high-resolved stellar objects.
 Despite these achievements, phase retrieval of the signal remains challenging due to photon correlation, hence the image reconstruction.
-Nowadays, artificial intelligence (AI) techniques are at the forefront of revealing astronomical mysteries by analyzing observed data.
-This paper proposes the application of a conditional Generative Adversarial Network (cGAN) to Intensity Interferometry data for high-resolution optical astronomy, aiming to overcome the limitations of traditional image reconstruction methods.
+Here, we propose the application of a conditional Generative Adversarial Network (cGAN) to II simulated data to overcome the limitations of traditional image reconstruction methods, as Artificial Intelligence (AI) techniques are at the forefront of revealing astronomical mysteries by analyzing the signal.
 Here, the cGAN effectively reconstructs the shape, size, and brightness distribution of a fast-rotating star by utilizing sparsely sampled, phase-subtracted Fourier transforms of the star.
@@
 However, the sensitivity of the signal and high resolution are expected to improve with additional baselines, which makes the current and future Cherenkov Telescope Array Observatory (CTAO) an ideal candidate for II applications.
-This approach is highly relevant and innovative, addressing key challenges in phase reconstruction and proposing novel solutions that could revolutionize high-resolution imaging in astronomy.
+This approach is highly relevant to the existing image reconstruction technique with II and could revolutionize high-resolution imaging in astronomy.
 \end{abstract}

### 2024-12-09 Phase_II/draft/GAN.tex
modification

@@
 \section{Generative Adversarial Networks}
+
 In 2014, Ian Goodfellow invented Generative Adversarial Networks (GANs).
 The concept is rather simple, as it consists of two competing networks.
-The first network is called a generator and creates new images based on an input image.
-Here, for consistency, the images generated by the generator will be denoted as generated images.
-The second network is the discriminator, which tries to distinguish between the generated image (predicted image) and the real image (ground truth) \citep{goodfellow2014generative}.
+The first network is called a Generator and creates new images based on an input image.
+Here, for consistency, the images generated by the Generator will be denoted as generated images.
+The second network is the Discriminator, which tries to distinguish between the generated image (predicted image) and the real image (ground truth) \cite{goodfellow2014generative}.
 As a consequence of training both networks alternately, the generated images eventually become indistinguishable from the real images.
@@
 
-The goal is now to learn the distribution of the generator $p_g$ over the data $x$.
+The goal is now to learn the distribution of the Generator $p_g$ over the data $x$.
 We have input noise variables $p_z(z)$, as well as the two perceptrons $G(z; \theta_g)$ and $D(x; \theta_d)$ with parameters $\theta_i$.
-$G$ represents a differential function that maps from $z$ to the data space $x$, while $D(x)$ represents the probability that $x$ is from the real data \citep{goodfellow2014generative}.
+$G$ represents a differential function that maps from $z$ to the data space $x$, while $D(x)$ represents the probability that $x$ is from the real data \cite{goodfellow2014generative}.
 The problem can be reformulated as:
@@
 \end{equation}
-where $D^{*}_{G}$ denotes the optimum of the discriminator for a given fixed generator and is expressed as
+where $D^{*}_{G}$ denotes the optimum of the Discriminator for a given fixed Generator and is expressed as
 \begin{equation}
@@
 Furthermore, if both $G$ and $D$ are allowed to reach their optima, $p_g$ converges to $p_{data}$.
-A more detailed discussion of the problem, including proofs, can be found in \citep{goodfellow2014generative}.
+A more detailed discussion of the problem, including proofs, can be found in \cite{goodfellow2014generative}.
 \begin{figure}
@@
 	\end{subfigure}\hfill
-	\caption{Generator and discriminator losses for three different learning rates.
-The upper figure shows the total discriminator loss, and the lower figure shows the total generator loss.
+	\caption{Generator and Discriminator losses for three different learning rates.
+The upper figure shows the total Discriminator loss, and the lower figure shows the total generator loss.
 There is no significant difference, but the highest learning rate might be prone to outliers.
@@
 	\end{subfigure}\hfill
-	\caption{Generator and discriminator losses for three different kernel sizes in the convolutional layers.
+	\caption{Generator and Discriminator losses for three different kernel sizes in the convolutional layers.
 Here, the smallest kernel size has many outliers, while the largest kernel size seems to be the most stable.}
@@
 		\includegraphics[width=\textwidth]{fig/analysis/Plot_Disc_rep_disc_loss.pdf}
-		\caption{Discriminator loss for different discriminator training.}
+		\caption{Discriminator loss for different Discriminator training.}
 		\label{fig:Plot_discrep_discloss}
@@
 		\includegraphics[width=\textwidth]{fig/analysis/Plot_Disc_rep_gen_total_loss.pdf}
-		\caption{Generator losses for different discriminator training.}
+		\caption{Generator losses for different Discriminator training.}
 		\label{fig:Plot_discrep_genloss}
 	\end{subfigure}\hfill
-	\caption{The amount of discriminator training has a high impact on the discriminator score.
-The discriminator repetition indicates the factor by which the discriminator is trained more with respect to the generator.}
+	\caption{The amount of Discriminator training has a high impact on the Discriminator score.
+The Discriminator repetition indicates the factor by which the Discriminator is trained more with respect to the Generator.}
 	\label{fig:Plot_discrep_loss}
@@
 	\caption{The number of telescopes has a very impact on the model performance.
-If there are only two telescopes (1 baseline), both discriminator and generator are not trained smoothly: One gains a big advantage over the other.
+If there are only two telescopes (1 baseline), both Discriminator and Generator are not trained smoothly: One gains a big advantage over the other.
 The result of four telescopes (6 baselines) is a lot better because the loss functions change only slightly with increasing steps.}
@@
 \end{figure*}
-Later, GAN extended its version to a conditional model \citep{mirza2014conditional}.
-In this case, both generator and discriminator receive extra information $y$, such that the value function of the conditional GAN (cGAN) can be expressed as:
+Later, GAN extended its version to a conditional model \cite{mirza2014conditional}.
+In this case, both Generator and Discriminator receive extra information $y$, such that the value function of the conditional GAN (cGAN) is expressed as:
 \begin{equation}
@@
 
-Furthermore, \cite{isola2017image} observed that combining the cGAN given in equation \ref{eq:conditional_GAN} with the traditional L1-loss improves results, as the generator tries to be close to the ground truth.
+Furthermore, \cite{isola2017image} observed that combining the cGAN given in equation \ref{eq:conditional_GAN} with the traditional L1-loss improves results, as the Generator tries to be close to the ground truth.
 Hence, the function that is minimized as:
@@
 \subsection{Generator}
-The used generator in this paper is a common U-Net convolutional network \citep{ronneberger2015u}.
-It consists of a contracting part, reducing the image size, and an expansive part, where the image is enlarged.
-The contracting part consists of repeated application of alternating convolutional layers and rectified linear unit (ReLU) layers.
-The expansion consists of repeated convolution, batch normalization, and ReLU layers.
-The first contracting step also includes a dropout layer \citep{isola2017image}.
+As discussed above, in a GAN, the Generator is responsible for generating fake data; here, the generated images look like real images of a fast-rotating star.
+The Generator used in this paper is a common U-Net convolutional network \cite{ronneberger2015u}, where the spatial dimension of the image is reduced first using downsampling and then enhanced using upsampling, making it U-shape.
+The downsampling process typically consists of convolutional layers followed by a strides operation to skip some pixels of the image.
+Here, the filter is skipping 2 pixels at a time of operation.
+A leaky version of a Rectified Linear Unit is used to activate the neuron in convolutional layers of the downsampling process.
+
+In contrast, only the Rectified Linear Unit is used to activate the neuron in the upsampling process.
+The upsampling process also consists of convolutional layers followed by strides = 2 operations to scale up the image for high resolution.
+However, there is an introduced dropout layer at the beginning of upsampling to avoid over-fitting of the model by the Generator \cite{isola2017image}.
+
+After creating images, the Generator tries to fool the Discriminator into thinking that the generated image is similar to the real image.
+The level of making fools to Discriminator is called GAN loss.
+If the Discriminator does not distinguish between the input image and the real image (i.e., the GAN loss is minimum), the Generator stops creating images, and it is trained.
+However, if the generated image fails to fool the Discriminator, the Generator will again create an image to compare it with the real image.
+There is another loss calculated by the Generator, which is called L1 loss.
+It is defined based on the mean absolute error between the pixels of the real image and the generated image.
+The Generator tries to minimize L1 loss while taking care of GAN loss.
+The balance between GAN loss and L1 loss allows the Generator to generate realistic yet accurate images.
 
 \subsection{Discriminator}
-The discriminator that has been taken here, named PatchGAN, does not work globally but rather classifies single patches as real or fake.
-The overall result is then estimated based on the average.
-The model architecture is as follows: zero padding, convolution, batch-norm, ReLu, zero-padding, and convolution \citep{isola2017image}.
+As discussed before, the Discriminator has the job of classifying the input image by the Generator as real or fake.
+The Discriminator takes a real image from the data set, also called the target image for the Generator.
+It tries to train the Generator to create a perfect image while giving feedback based on the input image.
+Here, the Discriminator that has been taken is PatchGAN \cite{isola2017image}, which does not work globally but rather classifies single patches as real or fake, so it outputs a grid of predictions instead of a single value.
+
+The model architecture of the Discriminator follows the initializer along with inputs (input images and real images).
+After adding Salt-and-Pepper noise to the input image, PatchGAN focuses on reducing the spatial dimensions of images to extract features, making the model focus on smaller regions of the image.
+In this process, a leaky version of a Rectified Linear Unit is introduced to convolutional layers as done in the Generator.
+Later, zero padding adds rows and columns of zeros around the images to prevent loss of spatial information during convolution and extract deeper features from the downsampled output.
+Now, the Discriminator starts classifying the image as to whether each patch of the input is real or fake based on batch normalization, which normalizes activations to stabilize learning.
+Later, it goes through LeakyReLU activation, zero-padding, and convolution again and makes a conclusion about the input image, which the Generator takes as feedback.
+
+The quality of the Discriminator is measured based on how it distinguishes between real and fake images, and it is calculated using Discriminator loss.
+Loss in the Generator helps to train its ability to create better images to fool the Discriminator.
+Similarly, Discriminator loss helps to train its ability to distinguish between the real image from the dataset and the input image from the Generator.
+In another way, it actually trains the Generator indirectly.
+The Discriminator loss is the sum of two losses.
+The first loss is in distinguishing the real image, which measures how close the Discriminator's predictions for real images are to 1.
+The second loss is in distinguishing the fake image, which measures how close the Discriminator's predictions for fake images are to 0.
+The total loss ensures that the Discriminator becomes better at distinguishing real from fake while simultaneously challenging the Generator to produce more realistic images.

### 2024-12-09 Phase_II/draft/II.tex
modification

@@
 \section{Intensity Interferometry with Imaging Cherenkov Telescope Array}
-Recently, Intensity Interferometry (II) has emerged again as an additional tool to resolve stellar objects as it solves some of the key limitations of classical optical interferometry (atmospheric turbulence, length of baseline, and the sensitivity of the optical aperture).
-It is suitable for the high-resolution study of very massive, hot, and short-lived stars, such as OB-type, Wolf-Rayet, and Pulsating stars in N-body systems.
+
 R.
@@
 Twiss first installed the Narrabri Stellar Intensity Interferometer (NSII) in 1974 to resolve the diameter of bright stars at visible wavelengths \citep{brown1954lxxiv, brown1974intensity}.
+After a long gap, Intensity Interferometry (II) has emerged again as an additional tool to resolve stellar objects with high precision levels.
+It solves some of the key limitations of classical optical interferometry (atmospheric turbulence, length of baseline, and the sensitivity of the optical aperture) to reach beyond milli-arc-second.
+II is suitable for the high-resolution study of very massive, hot, and short-lived stars, such as OB-type, Wolf-Rayet, and Pulsating stars in N-body systems.
 Nowadays, Imaging Cherenkov Telescope Arrays (ICTAs), which are primarily used for gamma-ray observations, are at the forefront of implementing II during moonlit nights when it does not detect gamma-ray radiation.
-As a result, detection of intensity correlation and angular size measurements of stars is going on for highly resolved imaging with optical wavelength, particularly using Very Energetic Radiation Imaging Telescope Array Systems (VERITAS), High Energy Stereoscopic Systems (HESS), and Major Atmospheric Gamma Imaging Cherenkov Telescopes (MAGIC) \citep{kieda2022performance, zmija2022optical, abe2024performance}.
+As a result, detection of intensity correlation and angular measurements of stars is going on with optical wavelength, particularly using Very Energetic Radiation Imaging Telescope Array Systems (VERITAS), High Energy Stereoscopic Systems (HESS), and Major Atmospheric Gamma Imaging Cherenkov Telescopes (MAGIC) \citep{kieda2022performance, zmija2022optical, abe2024performance}.
 
-\subsection{The signal for II}\label{sec:signal}
-In a simple case, an II consists of two light collectors, for example, MAGIC-I and MAGIC-II, which are pointed to a star and measure the intensity $I_1(t)$ and $I_2(t)$ respectively \citep{acciari2020optical, dravins2013optical}.
+\subsection{The Signal with Intensity Interferometry}\label{sec:signal}
+In a simple case, an II consists of two light collectors, for example, MAGIC-I and MAGIC-II, which are pointed to a star and measure the intensity $I_1(t)$ and $I_2(t)$ respectively.
 The signals from both detectors are cross-correlated and averaged over time, which results in an equation form
@@
 \end{equation}
-where $\tau$ is the time delay between both telescopes. If the light source is chaotic and randomly polarized, we have:
+where $\tau$ is the time delay between both telescopes \citep{acciari2020optical, dravins2013optical}. If the light source is chaotic and randomly polarized, we have:
 \begin{equation}
@@
 \end{figure}
-\subsection{Baseline considerations}
+
+\subsection{Baseline Considerations}
 The measurement of the size of stellar objects through absolute visibility depends on the distance between the telescopes, which is called the baseline $B$
@@
 The three matrices $R_i$ correspond to the fundamental representation of the SO(3) group \citep{saha2020theory}.
-Fig.~\ref{fig:base} shows the track of six baselines generated from the telescopes (fig.~\ref{fig:teles}) due to Earth's rotation.
+Fig.~\ref{fig:base} shows the track of six baselines generated from the telescopes (Fig.~\ref{fig:teles}) due to Earth's rotation.
 Since every pair of telescopes traces an ellipse in the Fourier plane, the total number of ellipses scales as follows:
@@
 \end{figure}
+
 \subsection{An Object: Fast Rotating Stars}
@@
 This effect was first observed in the fast-rotating star Regulus through interferometric and spectroscopic data from the Center for High Angular Resolution Astronomy (CHARA) Array \citep{mcalister2005first}.
-These stars are crucial for understanding a variety of astrophysical processes and help to understand the stellar evolution, internal structure, and rotational dynamics over time.
+These stars are crucial for understanding a variety of astrophysical processes and help to understand the internal structure, rotational dynamics, and stellar evolution over time.
 
@@
 Fig.~\ref {fig:ft} visualize this statement for the source shown in Fig.~\ref{fig:image} using II on linear and logarithmic scales.
-However, current observational techniques are unable to capture the full signal, and only partial data can be collected with a single night's simulation, which has been shown in Fig.~\ref{fig:ft_base}.
-It is the covered observational plane using the baselines shown in Fig.~\ref{fig:teles} on linear and logarithmic scales, respectively.
+However, current observational techniques are unable to capture the full signal, and only partial data can be collected.
+Fig.~\ref{fig:ft_base} shows the signal on linear and logarithmic scales again for a single night's simulation of II.
+It is the covered observational plane using the six baselines shown in Fig.~\ref{fig:teles}.
 However, the instrumentation of existing and upcoming CTAO shows the possibility of covering the maximum observable portion of the visibility plane for stellar objects, offering high resolution to understand the stellar structure and its evolution with time.

### 2024-12-09 Phase_II/draft/ParaGan.tex
modification

--- 2024-10-02 Phase_II/draft/ParaGan.tex
@@
-\section{The Parameter Analysis for GAN}
+\section{The Parameter for GAN Structure}
+
 \begin{figure*}
@@
 Here, we discuss the parameters for the GAN structure, which is trained to reconstruct the image of stellar objects using II.
-Due to the adversarial nature of GAN, where the generator and discriminator compete in a min-max game, careful tuning of key parameters ensures that both networks converge properly.
+Due to the adversarial nature of GAN, where the Generator and Discriminator compete in a min-max game, careful tuning of key parameters ensures that both networks are in good term to train the model.
 
-\subsection{Data preparation}
+\subsection{Data Preparation}
 First, we simulate fast-rotating stars, which are modeled as oblate spheroids with different radii and oblateness between 0.5 and 1.
@@
 As II does not measure the phase, the absolute value is calculated (shown in Fig.~\ref{fig:ft} on a linear and logarithmic scale for visualization).
-The sparse sampling is also introduced, namely by a pixel-wise multiplication between the absolute valued Fourier transformed image and the sparse sampling map.
-The result is a map in the Fourier plane with several ellipses, also called the sparse sampling map.
-Fig.~\ref{fig:ft_base} shows the sparse sampling for Fig.~\ref{fig:image} as the source with four telescopes (Fig.~\ref{fig:teles}).
+The sparse sampling is also introduced, namely by a pixel-wise multiplication between the absolute valued Fourier transformed image (Fig.~\ref{fig:ft}) and the sparse sampling map (Fig.~\ref{fig:base}).
+The result is a map in the Fourier plane with several ellipses, also called the sparse sampling map (Fig.~\ref{fig:ft_base}).
+It shows the sparse sampling for Fig.~\ref{fig:image} as the source with four telescopes (Fig.~\ref{fig:teles}).
 Finally, the pixels are normalized and converted to 8-bit integers.
@@
 
-\subsection{GAN architecture}
-The GAN used in this work is based on pix2pix \citep{isola2017image}, which uses a cGAN discussed in the last section.
+\subsection{GAN Architecture}
+The GAN used in this work is based on pix2pix, which uses a cGAN discussed in the last section \cite{isola2017image}.
 It is very robust and could already be applied to various problems.
@@
 However, to adapt the pix2pix GAN for the phase retrieval problem, some modifications are necessary.
-The network uses the TensorFlow \citep{abadi2016tensorflow} library, calculations are performed with scipy \citep{virtanen2020scipy}, and plots are drawn with matplotlib \citep{4160265}.
-\begin{figure*}
-	\includegraphics[width=\linewidth]{fig/reconstruction.png}
-	\caption{The elliptical image of ground truth and predicted image by trained GAN.
-The elliptic curve (in red) was drawn using the second-order moment, and cyan dots show the centroids (mx, my) of the images.
-There are two arrows in each image showing the skewness of pixel distribution along the x and y axes (magenta and blue color).}
-	\label{fig:recons}
-\end{figure*}
-\subsection{Hyperparameter tuning}
-The GAN used for this work depends on several parameters, which will be explained here briefly (an in-depth discussion can be found in \citep{murphy2022probabilistic}).
+The network uses the TensorFlow library \cite{abadi2016tensorflow}, calculations are performed with scipy \cite{virtanen2020scipy}, and plots are drawn with matplotlib \cite{4160265}.
+
+\subsection{Hyperparameter Tuning}
+The GAN used for this work depends on several parameters, which will be explained here briefly (an in-depth discussion can be found in \cite{murphy2022probabilistic}).
 
@@
 Small learning rates can lead to underfitting, and large learning rates can make the model unstable.
-It is therefore important to carefully choose the learning rate \citep{murphy2022probabilistic}.
-Fig.~\ref{fig:Plot_learning_rate_loss} shows the effect of the learning rate on both generator and discriminator loss for three different values of it.
+It is therefore important to carefully choose the learning rate \cite{murphy2022probabilistic}.
+Fig.~\ref{fig:Plot_learning_rate_loss} shows the effect of the learning rate on both Generator and Discriminator loss for three different values of it.
 Both loss functions have fewer outliers with decreasing learning rates, which is expected, as there is less change in the models with low learning rates.
@@
 The kernel size does not have a big effect on the loss functions, as shown in Fig.~\ref{fig:Plot_kernel_size_loss}.
-Smaller kernel sizes seem to have more outliers, which means that either generator or discriminator gains an advantage.
+Smaller kernel sizes seem to have more outliers, which means that either Generator or Discriminator gains an advantage.
 Therefore, a kernel size of 5 is preferred.
@@
 The batch size defines the number of images that pass the network simultaneously.
-It is observed that smaller batch sizes can lead to better generalization \citep{prince2023understanding}.
+It is observed that smaller batch sizes can lead to better generalization \cite{prince2023understanding}.
 Fig.~\ref{fig:Plot_batchsize_loss} shows two different batch sizes.
@@
 
-While training GAN, one can give the discriminator an advantage by increasing the number of training steps before returning to the generator training.
+While training GAN, one can give the Discriminator an advantage by increasing the number of training steps before returning to the Generator training.
 It can increase the performance of the model.
-However, it increases the training time as well and leads to a lower discriminator loss score, as shown in Fig.~\ref{fig:Plot_discrep_loss}.
-At the same time, the generator score increases slightly, which should be no surprise.
-Because the generated images did not improve with higher discriminator training, they are usually trained in the same amount as the generator.
+However, it increases the training time as well and leads to a lower Discriminator loss score, as shown in Fig.~\ref{fig:Plot_discrep_loss}.
+At the same time, the Generator score increases slightly, which should be no surprise.
+Because the generated images did not improve with higher Discriminator training, they are usually trained in the same amount as the Generator.
 
@@
 The Fourier plane can be sampled sixfold when using four telescopes in contrast to only two telescopes.
-In the latter case, both the generator and discriminator are not trained smoothly, as seen by the outliers.
+In the latter case, both the Generator and Discriminator are not trained smoothly, as seen by the outliers.
 It is already better with three telescopes and very promising when using four telescopes.

### 2024-12-09 Phase_II/draft/Result.tex
modification

@@
 \section{The Reconstructed Image with GAN}
+
 In this section, we will first discuss phase retrieval using hyperparameters, as mentioned earlier, followed by an analysis where multiple sources are trained simultaneously.
 The best performance for image reconstruction has been observed with a learning rate of $2 \cdot 10^{-4}$, a kernel size of 5x5, and equal noise percentages in original and generated images.
-The batch size selected is 1, and the discriminator-generator receives equal training.
+The batch size selected is 1, and the Discriminator-Generator receives equal training.
+
 \subsection{The Predicted Image with Trained GAN}
@@
 Fig.~\ref{fig:GAN} presents a set of four combined images demonstrating the GAN's performance in reconstructing the shape, size, and brightness distribution of the fast-rotating star using II.
-The left panel shows the signals covered by six baselines, which serve as the input for the generator to train the GAN.
-The first, middle panel displays the real image, or ground truth, which the discriminator uses to differentiate between real and generated images from the generator.
+The left panel shows the signals covered by six baselines, which serve as the input for the Generator to train the GAN.
+The first middle panel displays the real image, or ground truth, which the Discriminator uses to differentiate between real and generated images from the Generator.
 During training, the GAN aims to mimic these ground truth images.
@@
 However, the results can be further improved by increasing the number of telescopes to cover maximum (u, v) planes, making the existing and upcoming Cherenkov Telescope Array Observatory (CTAO) an ideal candidate.
-\subsection{Evaluation of GAN using moments}
+
+\subsection{Evaluation of GAN using Moments}
 The reconstructed images are good enough visually to claim the success of GAN in reconstructing the image using II.
@@
 Fig.~\ref{fig:mom2} and Fig.~\ref{fig:mom3} show the comparison of the x-centroid and y-centroid for 50 predicted images with respect to ground truths, respectively.
-The clustering of centroids in a given scale range for all the results explains that the reconstructed image correctly represents the spatial location of the fast-rotating star in compare with the ground truth.
+The clustering of centroids in a given scale range for all the results explains that the reconstructed image correctly represents the spatial location of the fast-rotating star compared with the ground truth.
 
@@
 
-\subsection{The reconstructed Parameters for object}
+\subsection{The Reconstructed Parameters for Object}
 The centroids $(m_x, m_y)$ represent the center of the fast-rotating star and spatial location on the image only.
@@
 \end{equation}
-Fig.~\ref{fig:recons} shows all zeroth to third order moments only for one ground and predicted image.
-In this figure, there is a red curve for both ground truth and predicted image, which is the representation of all second-order moments in terms of Eqn.~\ref{eqn:orn} to Eqn.~\ref{eqn:eccen} as orientation, axis value, and eccentricity.
-There is a cyan dot point as well, which represents the zeroth order moment for both images.
-The third-order moment is expressed in terms of arrows in magenta and blue color to view the skewness along the x and y axes.
+Eqns.~\ref{eqn:orn}-\ref{eqn:eccen} depending on values explains the elliptical nature of the stellar object (here, fast-rotating star) and provides information on shape and size.
+However, the information about the brightness distribution is gathered using skewness, which can be understood using third and higher-order moments.

### 2024-12-09 Phase_II/draft/conclusion.tex
modification

@@
 It is rejuvenated with support from advanced facilities at the Imaging Cherenkov Telescope Arrays (ICTAs).
-These telescopes are instrumental in capturing high-resolution images equipped with large aperture areas and sensitive photon detectors (capable of resolving signals within a nanosecond) \citep{dravins2013optical}.
-The Major Atmospheric Gamma Imaging Cherenkov Telescope (MAGIC), one of the CTA in the world, is now also being used for II, observing stellar objects with its 17-meter diameter mirror \citep{lorenz2004status}.
-The telescope has already demonstrated the potential of II by measuring and comparing the diameters of individual stars \citep{abe2024performance}.
-Other existing arrays (Very Energetic Radiation Imaging Telescope Array System (VERITAS) and High Energy Stereoscopic System (HESS)) are also making progress as II when gamma-ray observation stops \citep{kieda2021veritas, zmija2022optical}.
+These telescopes are instrumental in capturing high-resolution images equipped with large aperture areas and sensitive photon detectors (capable of resolving signals within a nanosecond) \cite{dravins2013optical}.
+The Major Atmospheric Gamma Imaging Cherenkov Telescope (MAGIC), one of the CTA in the world, is now being used for II, observing stellar objects with its 17-meter diameter mirror \cite{lorenz2004status}.
+The telescope has already demonstrated the potential of II by measuring and comparing the diameters of individual stars \cite{abe2024performance}.
+Other existing arrays (Very Energetic Radiation Imaging Telescope Array System (VERITAS) and High Energy Stereoscopic System (HESS)) are also making progress as II when gamma-ray observation stops \cite{kieda2021veritas, zmija2022optical}.
 Future observations, made possible by more advanced, sensitive instrumentation and upcoming CTAO, promise to push the boundaries of what we can observe with optical range.
 However, there is a drawback of II in terms of phase loss of signal, capturing only its magnitude via photon correlation.
-Here, the challenge of phase retrieval in Intensity Interferometry (II) has been effectively addressed through the application of machine learning techniques, particularly with conditional Generative Adversarial Networks (cGAN).
+Here, the challenge of phase retrieval in II has been effectively addressed through the application of machine learning techniques, particularly with conditional Generative Adversarial Networks (cGAN).
 Our study demonstrates that the application of cGAN on II data successfully recovers the size, shape, and brightness distribution of a fast-rotating star.

### 2024-12-09 Phase_II/draft/intro.tex
modification

@@
 
-Intensity Interferometry (II) emerged in the 1970s as a groundbreaking technique for measuring the diameters, orbits, and limb-darkening coefficients of 32 stars in single/binary star systems.
+Intensity Interferometry (II) emerged in the 1970s as a groundbreaking technique for measuring the diameters, orbits, and limb-darkening coefficients of 32 stars in single/binary/multiple star systems \cite{brown1974intensity}.
 Despite these significant achievements, the method did not gain widespread adoption due to the then-required highly sensitive photon detectors and sophisticated data analysis techniques.
@@
 Despite these theoretical advances, practical application to actual observational data of stellar objects with II has yet to be achieved.
-There is a need to advance this field by introducing a novel image reconstruction technique.
+The introduction of a novel image reconstruction technique with II will advance the field of optical astronomy.
 
-Currently, artificial intelligence (AI) is applied to high-volume data to reduce human computing resources and time effort.
+Currently, Artificial Intelligence (AI) is applied to high-volume data to reduce human computing resources and time effort.
 New analysis techniques using Machine Learning (ML) applications on observed data are playing at the front to reveal the astronomical mystery.
@@
 
-In this paper, we propose an alternative approach for image reconstruction of stellar objects with II using GAN \citep{goodfellow2014generative}.
+In this paper, we propose an alternative approach for image reconstruction of stellar objects with II using conditional GAN (cGAN) \citep{goodfellow2014generative}.
 We consider four ICTAs and perform a one-night simulation for a fast-rotating star.
@@
 However, the brightness distribution recovers only up to the third-order moment.
-We expect even greater precision of image reconstruction by including more telescopes, especially to recover the higher-order image moments.
+We expect even greater precision in image reconstruction by including more telescopes, especially in recovering higher-order image moments.
 It holds great promise, pushing the boundaries of high-resolution optical astronomy and opening up new possibilities for studying stellar objects with remarkable detail.
@@
 The third section details the parameter selection for training the GAN to reconstruct the image.
-After that, the fourth section presents the results of trained GAN visually and using image moments.
+After that, the fourth section presents the results of trained GAN visually using image moments.
 At the end, there is a conclusion of the entire result.

### 2024-12-09 Phase_II/draft/main.tex
modification

@@
 Here, the cGAN effectively reconstructs the shape, size, and brightness distribution of a fast-rotating star by utilizing sparsely sampled, phase-subtracted Fourier transforms of the star.
+This approach is highly relevant to the existing image reconstruction technique with II and could revolutionize high-resolution imaging in astronomy.
 Simulations of II are based on an assembly of four telescopes similar to existing arrays.
-However, the sensitivity of the signal and high resolution are expected to improve with additional baselines, which makes the current and future Cherenkov Telescope Array Observatory (CTAO) an ideal candidate for II applications.
-This approach is highly relevant to the existing image reconstruction technique with II and could revolutionize high-resolution imaging in astronomy.
+However, the sensitivity of the signal and resolution of stellar objects are expected to improve with additional baselines, which makes the current and future Cherenkov Telescope Array Observatory (CTAO) an ideal candidate for II applications.
 \end{abstract}

### 2024-12-09 Phase_II/code/gan_def.py

@@ -137,7 +137,7 @@ class gan_fun():
 
           generated_loss = loss_object(tf.zeros_like(disc_generated_output), disc_generated_output) # loss due to prove that Generator is not producing correct result
 
-          total_disc_loss = real_loss + generated_loss                                   # total loss in Discriminator
+          total_disc_loss = real_loss + generated_loss                                    # total loss in Discriminator
 
           return total_disc_loss
          

### 2025-02-02 Phase_II/draft/GAN.tex
Changes by Sarangi

--- 2024-10-02 Phase_II/draft/GAN.tex
@@
 Here, for consistency, the images generated by the generator will be denoted as generated images.
-The second network is the discriminator, which tries to distinguish between the generated image and the real image (ground truth) \citep{goodfellow2014generative}.
+The second network is the discriminator, which tries to distinguish between the generated image and the real image (ground truth) \cite{goodfellow2014generative}.
 As a consequence of training both networks alternately, the generated images eventually become indistinguishable from the real images.
@@
 We have input noise variables $p_z(z)$, as well as the two perceptrons $G(z; \theta_g)$ and $D(x; \theta_d)$ with parameters $\theta_i$.
-$G$ represents a differential function that maps from $z$ to the data space $x$, while $D(x)$ represents the probability that $x$ is from the real data \citep{goodfellow2014generative}.
+$G$ represents a differential function that maps from $z$ to the data space $x$, while $D(x)$ represents the probability that $x$ is from the real data \cite{goodfellow2014generative}.
 The problem can be reformulated as:
@@
 \end{equation}
-where $D^{*}_{G}$ denotes the optimum of the discriminator for a given fixed generator and is expressed as
+where $D^{*}_{G}$ denotes the optimum of the discriminator for a given fixed generator, shown in equation (\ref{eq:Disc_optimum}).
+It can now be shown that the global optimum of equation (\ref{eq:GAN_reformulated}) is reached if and only if $p_g = p_{data}$.
+Furthermore, if both $G$ and $D$ are allowed to reach their optima, $p_g$ converges to $p_{data}$.
+A more detailed discussion of the problem, including proofs, can be found in \cite{goodfellow2014generative}.
 \begin{equation}
@@
 \end{equation}
-It can now be shown that the global optimum of equation (\ref{eq:GAN_reformulated}) is reached if and only if $p_g = p_{data}$.
-Furthermore, if both $G$ and $D$ are allowed to reach their optima, $p_g$ converges to $p_{data}$.
-A more detailed discussion of the problem, including proofs, can be found in \citep{goodfellow2014generative}.
 \begin{figure}
@@
 \end{figure*}
-GAN can be extended to a conditional model \citep{mirza2014conditional}.
+GANs can be extended to a conditional model \cite{mirza2014conditional}.
 In this case, both generator and discriminator receive extra information $y$, such that the value function of the conditional GAN (cGAN) can be expressed as:
@@
 \end{equation}
-where $\lambda$ = 100 and $L_1(G)$ is given as
+where $\lambda$ = 100 and $L_1(g)$ is given by equation (\ref{eq:l1_loss})
 \begin{equation}
 	\centering
-	L_1(G) = \mathbb{E}_{x,y,z} \left[ ||{y - G(x,z)}||_1 \right]
+	L_1(g) = \mathbb{E}_{x,y,z} \left[ \norm{y - G(x,z)}_1 \right]
 	\label{eq:l1_loss}
@@
 \subsection{Generator}
-The used generator in this paper is a common U-Net convolutional network \citep{ronneberger2015u}.
+The used generator in this paper is a common U-Net convolutional network, described in \cite{ronneberger2015u}.
 It consists of a contracting part, reducing the image size, and an expansive part, where the image is enlarged.
@@
 The expansion consists of repeated convolution, batch normalization, and ReLU layers.
-The first contracting step also includes a dropout layer \citep{isola2017image}.
+The first contracting step also includes a dropout layer \cite{isola2017image}
 
@@
 The overall result is then estimated based on the average.
-The model architecture is as follows: zero padding, convolution, batch-norm, ReLu, zero-padding, and convolution \citep{isola2017image}.
+The model architecture is as follows: zero padding, convolution, batch-norm, ReLu, zero-padding, and convolution \cite{isola2017image}.

### 2025-02-02 Phase_II/draft/II.tex
Changes by Sarangi

--- 2024-10-02 Phase_II/draft/II.tex
@@
-\section{Intensity Interferometry with Imaging Cherenkov Telescope Array}
-Recently, Intensity Interferometry (II) has emerged again as an additional tool to resolve stellar objects as it solves some of the key limitations of classical optical interferometry (atmospheric turbulence, length of baseline, and the sensitivity of the optical aperture).
-It is suitable for the high-resolution study of very massive, hot, and short-lived stars, such as OB-type, Wolf-Rayet, and Pulsating stars in N-body systems.
+\section{Intensity Interferometry (II) with IACT arrays}
 R.
 Hanbury Brown and Robert Q.
-Twiss first installed the Narrabri Stellar Intensity Interferometer (NSII) in 1974 to resolve the diameter of bright stars at visible wavelengths \citep{brown1954lxxiv, brown1974intensity}.
-Nowadays, Imaging Cherenkov Telescope Arrays (ICTAs), which are primarily used for gamma-ray observations, are at the forefront of implementing II during moonlit nights when it does not detect gamma-ray radiation.
-As a result, detection of intensity correlation and angular size measurements of stars is going on for highly resolved imaging with optical wavelength, particularly using Very Energetic Radiation Imaging Telescope Array Systems (VERITAS), High Energy Stereoscopic Systems (HESS), and Major Atmospheric Gamma Imaging Cherenkov Telescopes (MAGIC) \citep{kieda2022performance, zmija2022optical, abe2024performance}.
+Twiss (HBT) carried out the first experiments demonstrating the possibility of measuring angular diameter of stars using Intensity Interferometry (II) in optical wavelengths \citep{HBT56}.
+Subsequently, they also pioneered the theoretical background of II and conducted laboratory experiments \citep{brown1957interferometry,brown1958interferometry},thereby further consolidating II as an alternative method, besides the already established Michelson Interferometry, to measure stars.
+Further, HBT also successfully installed the Narrabri Stellar Intensity Interferometer \textcolor{blue}{during the 1960s-70s and successfully used it to measure the angular diameters of bright stars in the spectral range $\mathrm{O5f}\ -\ \mathrm{F8}$ using visible wavelengths} signals \citep{brown1974intensity}.
+\\\textcolor{blue}
+{However, the available speed and sensitivity of electronics in the 1970s was not favourable for more extensive and larger scale measurement projects using II.}
+
+\textcolor{blue}{Subsequently, during the opening decades of the current century, proposals to use the Imaging Atmospheric Cherenkov Telescope (IACT) facilities for carrying out Stellar Intensity Interferometry (SII) observations were put forth \citep{LeBohec2006, Nunez2010stellar, Nunez2012High, Dravins2013}.
+Such observations, it was suggested, could be carried out during bright moon-lit nights during which $\gamma$-ray observations using upper atmospheric Cherenkov showers were not feasible.
+This idea had the potential of enhancing the scientific output of the existing facilities like VERITAS, MAGIC and HESS.
+Subsequent SII obserations at these facilities providing the proof of concept have been published \citep{abeysekara2020demonstration, Abe2024MAGIC, Zmija2023}.
+}
+
+\textcolor{blue}{In the remaining part of this section, we present a brief conceptual procedure of how an array of Cherenkov telescopes is used to carry out II observations and generate Signal-to-Noise Ratio (SNR) from these observations.}
 
 \subsection{The signal for II}\label{sec:signal}
-In a simple case, an II consists of two light collectors, for example, MAGIC-I and MAGIC-II, which are pointed to a star and measure the intensity $I_1(t)$ and $I_2(t)$ respectively \citep{acciari2020optical, dravins2013optical}.
-The signals from both detectors are cross-correlated and averaged over time, which results in an equation form
+As a simple example, let us consider the pair of IACTs at MAGIC.
+Let us imagine that the two telescopes, namely, MAGIC-I and MAGIC-II are pointed to a star.
+\textcolor{red}{My comment: As our model has 4 hypothetical IACTs and we are not taking any specific properties of the MAGIC telescopes into the calculations or into the model, it would be better to avoid using the specific names of MAGIC facility.This portion can be easily rewritten without the mention of MAGIC.}Let them simultaneously measure the intensity of radiation $I_1(t)$ a  and $I_2(t)$ respectively.
+These signals from the respective detectors are cross-correlated and averaged over time and yield the \textcolor{blue}{second order ($n=2$) correlation of these intensities as}  \citep{acciari2020optical, dravins2013optical}
 \begin{equation}
-	g^{(2)} = \frac{\left\langle I_1(t) \cdot I_2(t + \tau) \right\rangle}{\langle I_1(t) \rangle \cdot \langle I_2(t) \rangle} 
+	g^{(2)}= \frac{\left\langle I_1(t) \cdot I_2(t + \tau) \right\rangle}{\langle I_1(t) \rangle \cdot \langle I_2(t) \rangle} 
 	\label{eqn:HBT}
 \end{equation}
-where $\tau$ is the time delay between both telescopes. If the light source is chaotic and randomly polarized, we have:
+where $\tau$ is the time delay between the telescopes.
+\st{If the light source is chaotic and randomly polarized,}\textcolor{blue}{For a spatially coherent and randomly polarized light, eq.(\ref{eqn:HBT}) reduces to the Siegert relation \citep{acciari2020optical}}
 \begin{equation}
@@
 \end{equation}
-here, $\Delta f$ is the electronic bandwidth, $\Delta \nu$ is the optical bandwidth, and $\Delta f \ll \Delta \nu$ \citep{acciari2020optical}.
-$V_{12}$ is the Fourier transform of the source brightness distribution and is called complex visibility.
-Eqn.~\ref{eqn:HBT2} carry the information about the source's structure and shape.
-However, the phase information is lost due to the involvement of the absolute value of $V_{12}$.
+where, $\Delta f$ is the electronic bandwidth \textcolor{blue}{of the photon detectors (that measure the intensities and typically lie in range $\sim 100 {\mathrm {MHz}}$)} and $\Delta {\mathrm {\nu}}$ is the optical bandwidth \textcolor{blue}{of radiation over which the intensities are measured}\footnote{\textcolor{blue}{Typically, filters with bandwidths in the range $\Delta \lambda \sim 20 nm - 50 nm$ corresponding to $\Delta \nu \sim 10^{15}$ Hz are used.} .
+In eq.(\ref{eqn:HBT2}), $V_{12}$, referred to as the complex visibility fuction, is the Fourier transform of the source brightness distribution and is given by
+\begin{equation}
+\vert V_{12} \vert = 2 \frac{J_1(\pi \ d \ {\theta}/{\lambda})}{\pi\  d \ {\theta}/{\lambda}}
+\label{eqn:absvisib}
+\end{equation}
+with $d$, $\theta$ and $\lambda$ being the baseline, the angular diameter of the star and the optical wavelength of the filter used in observation.
+It is obvious from eq(\ref{eqn:absvisib}) that $\vert V_{12} \vert$ carries the information of the angular diameter of the star.} However, the phase information is lost \st{due to the involvement of the absolute value of $V_{12}$}\textcolor{blue}{as we measure the absolute value $\vert V_{12} \vert$}.
 In observational astronomy, the correlation is often expressed in terms of the normalized contrast, given by:
@@
 
-\subsection{Signal-to-Noise Ratio for Intensity Interferometry}
+\textcolor{red}{Insert text (may be one more paragraph) to extend the expression for $g^{(2)}$ or $c$ to include the signals from more number of baselines.
+This will be important because we are considering a set of 4 IACTs in our model and therefore 6 baselines.}
+
+\subsection{The Signal-to-Noise Ratio for II}
 \begin{figure}
@@
 	\includegraphics[width=\linewidth]{fig/telescope.png}
-	\caption{Configuration of the four Imaging Cherenkov Telescope Array (ICTAs) with similar properties each used to simulate the signal for II.}
+	\caption{The telescope configuration with similar properties each used to simulate the signal for II.}
 	\label{fig:teles}
 \end{figure}
-The main physics channel of ICTAs is the study of Very High Energy gamma rays ($\geq 30$ GeV) originating from particle showers in the atmosphere.
-Telescopes have an array of mirrors, which focus the light onto an array of photo-multiplier tubes (PMTs) \citep{aleksic2016major}.
-Here, Fig.~\ref{fig:teles} shows an arrangement of four ICTAs with similar properties each.
-For the simulation of II, the light of a stellar source is focused on a single PMT, which has a filter in front.
-The purpose of this filter is to efficiently transmit light around mean observational frequency, which protects the PMTs from excessive light.
-It is necessary, as II observations are mainly done during full moon nights when it is too bright for Very High Energy $\gamma$-ray observations.
-The optical signal of the PMTs is transmitted with optical fibers, converted to an electrical signal, and digitized \citep{acciari2020optical}.
-The measurable observable is the Pearson's correlation coefficient:
-\begin{equation}
-	\rho(\tau) = \frac{\left\langle \left( I_1(t) - \left\langle I_1 \right\rangle \right) \cdot \left( I_2(t + \tau) - \left\langle I_2 \right\rangle \right) \right\rangle}{\sqrt{\langle \left( I_1(t) - \langle I_1 \rangle \right)^2 \rangle} \cdot \sqrt{\langle \left( I_2(t) - \langle I_2 \rangle \right) ^2 \rangle}}
-	\label{eqn:pearson}
-\end{equation}
-It must be noted that the calculation of Pearson's correlation coefficient is non-trivial: MAGIC makes use of the convolution theorem for discrete Fourier transforms because it is computationally more efficient.
-Since $I_1$ and $I_2$ are proportional to the direct current of the PMTs ($DC_i$), the normalized contrast can be calculated as
-\begin{equation}
-	c \propto \frac{\rho}{\sqrt{\left(DC_1 \cdot DC_2 \right)}}.
-	\label{eq:norm_contrast2}
-\end{equation}
-One must also correct for a non-constant gain of the PMTs, as well as the moon.
-The latter can be done by measuring the background light with an additional PMT with no mirrors focused on it \citep{acciari2020optical}.
-
-The significance of the signal can be expressed as the signal-to-noise ratio (SNR), which depends on many factors.
-However, most importantly, it is proportional to the absolute value of visibility, which itself depends on the distance between the telescopes \citep{acciari2020optical}
-\begin{equation}
-	SNR = A \cdot \alpha \cdot q \cdot n \cdot \abs{V_{12}}^{2}(d) \cdot \sqrt{b_v} \cdot F^{-1} \cdot \sqrt{\frac{T}{2}} \cdot \sigma.
-	\label{eq:SNR}
-\end{equation}
-Here, $A$ is the total mirror area, $\alpha$ the quantum efficiency of the PMTs, $q$ the quantum efficiency of the optics, $n$ the differential photon flux from the source, and $b_v$ the cross-correlation bandwidth.
-The noise of the PMTs is accounted with $F$, $T$ denotes the observation time, and $\sigma$ is the normalized spectral distribution of the light (including filters) \citep{acciari2020optical}.
-While most of the parameters can be optimized with hardware, the only way to obtain a better SNR is to increase the observation time with a fixed number of telescopes.
 \begin{figure}
@@
 	\includegraphics[width=0.8\linewidth]{fig/ellipse/ellipse6018.jpg}
-	\caption{This figure shows the simulated fast-rotating star. The brightness is highest at the pole, and gravitational darkening is present at the equator.}
+	\caption{This figure shows the simulated fast rotating star. The brightness is highest at the pole and there is gravitational darkening at the equator.}
 	\label{fig:image}
 \end{figure}
+\begin{figure*}
+	\centering
+	\begin{subfigure}{0.5\linewidth}
+		\includegraphics[width=\linewidth]{fig/ft/ft.jpg}
+		\caption{The fourier transform of source.}
+	\end{subfigure}\hfill
+	\begin{subfigure}{0.5\linewidth}
+		\includegraphics[width=\linewidth]{fig/ft/ft_log.jpg}
+		\caption{The logarithmic fourier transform of source.}
+	\end{subfigure}
+	\caption{Absolute value of the two-dimensional Fast Fourier Transform of fig.~\ref{fig:image} measured by Intensity Interferometry, and observation of maximum (u, v) plane with finite number of baselines can be completed with help of earth's rotation.}
+	\label{fig:ft}
+\end{figure*}
+\begin{figure*}
+	\centering
+	\begin{subfigure}{0.5\linewidth}
+		\includegraphics[width=\linewidth]{fig/ft/ft_base.jpg}
+		\caption{The fourier transform with baselines.}
+	\end{subfigure}\hfill
+	\begin{subfigure}{0.5\linewidth}
+		\includegraphics[width=\linewidth]{fig/ft/ft_log_base.jpg}
+		\caption{The logarithmic fourier transform with baselines.}
+	\end{subfigure}
+	\caption{The left panel shows the absolute value of the two-dimensional Fast Fourier Transform of fig.~\ref{fig:image} measured by baselines shown in fig.~\ref{fig:teles}.
+The right panel shows the same on logarithmic scale}
+	\label{fig:ft_base}
+\end{figure*}
+The primary purpose of IACTs is the study of high energy gamma rays (with energy $E\ \geq 30$ GeV) reaching the Earth from cosmic sources, entering the Earth's atmosphere and seeding the Cherenkov showers in the upper atmosphere due to multiple scattering.
+These telescopes have an array of mirrors that focus the light onto a set of photo-multiplier tubes (PMTs) \cite{aleksic2016major}.
+\textcolor{blue}{In the simulation model adopted here, a set of four IACTs with similar properties each are considered.
+The positional configuration of these IACTs is shown in fig.~\ref{fig:teles}.
+The optical signal guided into a PMT is filtered using a spectral filter with chosen mean observational wavelength $\lambda$ and corresponding bandpass $\Delta \lambda$.
+Use of filters helps in not only reducing back ground noise, but in improving the signal quality and the efficiency of the PMTs also.
+Filtering background sky light becomes even more significant in II observations as these observations are carried out around full moon nights.
+Needless to mention that light of the stellar source is focused on the PMT during the II observations.}
+\st{In II observations, the light of a stellar source is focused on a single PMT, which has a filter in front.
+The purpose of this filter is to efficiently transmit light around mean observational frequency, which protects the PMTs from excessive light.
+It is necessary, as II observations are mainly done during full moon nights, where it is too bright for Very High Energy $\gamma$-ray observations.} The optical signal of the PMTs is transmitted through optical fibers, converted to an electrical signal, and digitized \cite{acciari2020optical}.
+The measurable observable is the Pearson's correlation coefficient:
+\begin{equation}
+	\rho(\tau) = \frac{\left\langle \left( I_1(t) - \left\langle I_1 \right\rangle \right) \cdot \left( I_2(t + \tau) - \left\langle I_2 \right\rangle \right) \right\rangle}{\sqrt{\langle \left( I_1(t) - \langle I_1 \rangle \right)^2 \rangle} \cdot \sqrt{\langle \left( I_2(t) - \langle I_2 \rangle \right) ^2 \rangle}}
+	\label{eqn:pearson}
+\end{equation}
+Since $I_1$ and $I_2$ are proportional to the direct current of the PMTs ($DC_i$), the normalized contrast can be calculated as in equation \ref{eq:norm_contrast2}.
+One must also correct for a non-constant gain of the PMTs, as well as the moon.
+The latter can be done by measuring the background light with an additional PMT with no mirrors focused on it \cite{acciari2020optical}.
+\begin{equation}
+	c \propto \frac{\rho}{\sqrt{\left(DC_1 \cdot DC_2 \right)}}
+	\label{eq:norm_contrast2}
+\end{equation}
+It must be noted that the calculation of Pearson's correlation coefficient is non-trivial: MAGIC makes use of the convolution theorem for discrete Fourier transforms because it is computationally more efficient.
+
+The significance of the signal can be expressed as the signal-to-noise ratio (SNR), which depends on many factors.
+However, most importantly, it is proportional to the absolute value of visibility, which itself depends on the distance between the telescopes, shown in equation (\ref{eq:SNR}) \cite{acciari2020optical}.
+\begin{equation}
+	SNR = A \cdot \alpha \cdot q \cdot n \cdot \abs{V_{12}}^{2}(d) \cdot \sqrt{b_v} \cdot F^{-1} \cdot \sqrt{\frac{T}{2}} \cdot \sigma
+	\label{eq:SNR}
+\end{equation}
+here, $A$ is the total mirror area, $\alpha$ the quantum efficiency of the PMTs, $q$ the quantum efficiency of the optics, $n$ the differential photon flux from the source, and $b_v$ the cross-correlation bandwidth.
+The noise of the PMTs is accounted for with $F$, $T$ denotes the observation time, and $\sigma$ is the normalized spectral distribution of the light (including filters) \cite{acciari2020optical}.
+While most of the parameters can be optimized with hardware, the only way to obtain a better SNR is to increase the observation time with fixed telescopes.
+\textcolor{red}{Points to be discussed: 
+\begin{itemize}
+\item{Should/Can the final expression for SNR in eq.(\ref{eq:SNR}) be written in terms of $\rho(\tau)$ of eq.(\ref{eqn:pearson}) or $c$ (\ref{eq:norm_contrast2}) in stead of $\vert V_{12}\vert^2$?}
+\item{It would be better to generalize the eq.(\ref{eq:norm_contrast2}) to include the signals from all the baseline pairs.}
+\end{itemize}}
 \subsection{Baseline considerations}
-The measurement of the size of stellar objects through absolute visibility depends on the distance between the telescopes, which is called the baseline $B$. 
+The measurement of the size of stellar objects through absolute visibility depends on the distance between the telescopes, which is called the baseline $d$. 
 \begin{equation}
-	V_{12}(B) = \frac{c(B)}{c(0)}
+	V_{12}(d) = \frac{c(d)}{c(0)}
 	\label{eq:angular_size_meas}
 \end{equation}
-However, this work needs a good SNR value for high precision of measurement, so the large covered observational plane with telescopes is a necessity for II \citep{acciari2020optical, abeysekara2020demonstration}.
+\textcolor{blue}{For achieving a good SNR with a given telescope configuration, the largest possible observational plane that can be covered is always desirable \citep{acciari2020optical, abeysekara2020demonstration}.}
+\begin{comment}
+{\st{However, this work needs a good SNR value for high precision of measurement, so the large covered observational plane with telescopes is a necessity for II \citep{acciari2020optical, abeysekara2020demonstration}.} }
+\end{comment}
 If the source is at the zenith, the coordinates in the Fourier plane ($u,v$) are given by:
 \begin{equation}
-	(u,v) = \frac{1}{\lambda} (B_N, B_E)
+	(u,v) = \frac{1}{\lambda} (d_N, d_E)
 \end{equation}
-where $B_N$ and $B_E$ are the baselines expressed in north and east coordinates.
-Since not all sources are at the zenith, and the telescopes are stationary, Earth's rotation plays an important role in covering the maximum observational plane through the rotated baselines, which is given as
+where $d_N$ and $d_E$ are the baselines expressed in north and east coordinates. 
+\textcolor{blue}{But not all sources are at the zenith, and the telescopes are stationary and may also have different relative altitudes $d_A$ depending on the available terrain.
+Therefore, the Earth's rotation needs to be factored in for covering the maximum observational plane through the rotated baselines.
+For a given stellar source with declination $\delta$, hour-angle $h$ observed by telescopes at latitude $l$, equation (\ref{eq:baseline_rot}) provides the rotated
+baselines for a given pair of telescopes \citep{dravins2013optical, saha2020theory}
 \begin{equation}
-	\begin{pmatrix} u\\ v\\ w\\ \end{pmatrix} = R_x(\delta) \cdot R_y(h) \cdot R_x(-l) \begin{pmatrix} B_N\\ B_E\\ B_A\\ \end{pmatrix}
+\begin{pmatrix} u\\ v\\ w\\ \end{pmatrix} = R_x(\delta) \cdot R_y(h) \cdot R_x(-l) \begin{pmatrix} d_N\\ d_E\\ d_A\\ \end{pmatrix}
 	\label{eq:baseline_rot}
 \end{equation}
-It traces an ellipse for every pair of telescopes.
-Furthermore, the different altitudes of the telescopes $B_A$ must be considered \citep{dravins2013optical, saha2020theory}.
-Here, $\delta$ is the declination, and $h$ is the hour angle of the stellar source, and $l$ is the latitude of the telescopes.
-The three matrices $R_i$ correspond to the fundamental representation of the SO(3) group \citep{saha2020theory}.
+}
+%\end{comment}
+\begin{comment}
+\st{
+Equation (\ref{eq:baseline_rot}), which traces an ellipse for every pair of telescopes.
+Furthermore, the different altitudes $B_A$ of the telescopes must be considered \cite{dravins2013optical, saha2020theory}.
+\begin{equation}
+	\begin{pmatrix} u\\ v\\ w\\ \end{pmatrix} = R_x(\delta) \cdot R_y(h) \cdot R_x(-l) \begin{pmatrix} d_N\\ d_E\\ d_A\\ \end{pmatrix}
+	\label{eq:baseline_rot}
+\end{equation}
+here, $\delta$ is the declination and $h$ is the hour angle of the stellar source, and $l$ is the latitude of the telescopes.}
+\end{comment}
+The three rotation matrices $R_i$ correspond to the fundamental representation of the SO(3) group \cite{saha2020theory}.
 Fig.~\ref{fig:base} shows the track of six baselines generated from the telescopes (fig.~\ref{fig:teles}) due to Earth's rotation.
@@
 \end{equation}
+where $N_T$ is the number of telescopes considered.
+As the number of baselines increases non-linearly, II benefits greatly from a large number of telescopes.
+The planned Cherenkov Telescope Array (CTA) will cover the maximum observational plane and provide insight into stellar objects with optical wavelengths in the future.
 
-As the number of baselines increases non-linearly, II benefits greatly from a large number of telescopes.
-The existing and upcoming Cherenkov Telescope Array Observatory (CTAO) can promise to cover the maximum observational plane and provide insight into stellar objects with optical wavelengths in the future.
-\begin{figure}
-	\centering
-	\begin{subfigure}{\linewidth}
-		\includegraphics[width=\linewidth]{fig/ft/ft.jpg}
-		\caption{The Fourier transform of the source.}
-	\end{subfigure}\hfill
-	\begin{subfigure}{\linewidth}
-		\includegraphics[width=\linewidth]{fig/ft/ft_log.jpg}
-		\caption{The logarithmic Fourier transform of the source.}
-	\end{subfigure}
-	\caption{Absolute value of the two-dimensional Fast Fourier Transform of Fig.~\ref{fig:image} on linear and logarithmic scales.
-Observation of the maximum (u, v) plane with a finite number of baselines can be completed with the help of Earth's rotation.}
-	\label{fig:ft}
-\end{figure}
-\begin{figure}
-	\centering
-	\begin{subfigure}{\linewidth}
-		\includegraphics[width=\linewidth]{fig/ft/ft_base.jpg}
-		\caption{The Fourier transform with baselines.}
-	\end{subfigure}\hfill
-	\begin{subfigure}{\linewidth}
-		\includegraphics[width=\linewidth]{fig/ft/ft_log_base.jpg}
-		\caption{The logarithmic Fourier transform with baselines.}
-	\end{subfigure}
-	\caption{The upper panel shows the absolute value of the two-dimensional Fast Fourier Transform of Fig.~\ref{fig:image} measured by baselines shown in Fig.~\ref{fig:teles} on a linear scale, and the lower panel shows the same on a logarithmic scale.}
-	\label{fig:ft_base}
-\end{figure}
 \subsection{An Object: Fast Rotating Stars}
-In our work, we simulate a single fast-rotating star to test image reconstruction with II in intersection with the Generative Adversarial Networks (GAN).
-Fast rotation causes stars to take on an oblate shape, flattening at the poles and bulging at the equator due to the existence of stronger centrifugal force \citep{von1924radiative, 1999A&A...347..185M}.
-Fig.~\ref{fig:image} shows one of the simulations of a fast-rotating star, where the star takes on an elliptical shape with brightness distributed across the object.
-The brightness is maximum at the poles and minimum at the equator, a phenomenon known as gravity darkening \citep{lucy1967gravity}.
-This effect was first observed in the fast-rotating star Regulus through interferometric and spectroscopic data from the Center for High Angular Resolution Astronomy (CHARA) Array \citep{mcalister2005first}.
-These stars are crucial for understanding a variety of astrophysical processes and help to understand the stellar evolution, internal structure, and rotational dynamics over time.
+In our work presented here, we simulate a single fast-rotating star to test image reconstruction using a GAN.
+Fast rotation causes stars to take on an oblate shape, flattening at the poles and bulging at the equator due to the existence of stronger centrifugal force \cite{von1924radiative, 1999A&A...347..185M}.
+Fig.~\ref{fig:image} shows one of the simulations of such a fast-rotating star, \st{where the star takes on an elliptical shape} with brightness distributed across its surface.
+The brightness is at its maximum at the poles and minimum at the equator, a phenomenon known as gravity darkening \cite{lucy1967gravity}.
+This effect has been observed first through the interferometric and spectroscopic data from the CHARA Array for the fast-rotating star Regulus \cite{mcalister2005first}.
+Fast-rotating stars are crucial for understanding various astrophysical processes, including stellar evolution, structure, and \textcolor{red}{dynamics(???
+Can we be more elaborate here?)} over time.
 
-Intensity Interferometry (II) detects the photon from the stellar objects, and the correlation of it results in squared visibility (explained in subsection.\ref{sec:signal}).
+Intensity Interferometry measures/counts photons arriving at the telescopes from the stellar object.
+The correlation of these photon arrivals at the telescopes results in squared visibility (explained in subsection.\ref{sec:signal}).
 According to Van Cittert Zernike's theorem, this signal is the Fourier transform of brightness distribution in the sky.
-Fig.~\ref {fig:ft} visualize this statement for the source shown in Fig.~\ref{fig:image} using II on linear and logarithmic scales.
-However, current observational techniques are unable to capture the full signal, and only partial data can be collected with a single night's simulation, which has been shown in Fig.~\ref{fig:ft_base}.
-It is the covered observational plane using the baselines shown in Fig.~\ref{fig:teles} on linear and logarithmic scales, respectively.
-However, the upcoming CTAO can promise to greatly expand the observable portion of the visibility plane for stellar objects, offering new insights into the mysteries of the universe.
+Fig.~\ref {fig:ft} shows represents the Fourier Transform of the source shown in fig.~\ref{fig:image} using II on linear and logarithmic scale.
+\sout
+{However, we do not have an existing technique to observe the complete signals, and we could capture some parts of it only with a one-night simulation, which has been shown in fig.~\ref{fig:ft_base}.
+It is the covered observational plane using the baselines shown in fig.~\ref{fig:teles}.
+However, the upcoming CTA promises to cover the maximum observational plane for stellar objects.}
+\textcolor{blue}{In order to observe a real stellar source in the sky, however, we would need to receive photons from each point on the surface of the source.
+This would require infinite number of baselines observing the source over a long enough duration.
+This demand is obviously not feasible.
+We have finite number of baselines corresponding to the finite number $N_T$ of telescopes at our disposal and finitely budgeted observation schedule.
+Therefore, as a pilot, what we have attempted in this work is to simulate the II observation of a sky source over one night duration.
+Using this finite amount of signal of one night's observation, we have attempted to train a Generative Adversarial Network (GAN) to construct the image of the source.}
+
+\textcolor{red}{My comments: Suppose we do more simulations with say 8 and 16 telescopes covering the effective ground area, but obviously with 28 and 120 baselines respectively.
+We can then, perhaps, evolve/suggest some kind of measure (or scale) of quality in resultant image reconstruction with number of telescopes.
+May be some form of ratios of the SNRs would provide a good comparison.
+{\bf How much more computationally expensive would it become?}}

### 2025-02-02 Phase_II/draft/Result.tex
Changes by Sarangi

--- 2024-10-02 Phase_II/draft/Result.tex
@@
 The left panel shows the signals covered by six baselines, which serve as the input for the generator to train the GAN.
-The first middle panel displays the real image, or ground truth, which the discriminator uses to differentiate between real and generated images from the generator.
-During training, the GAN aims to mimic these ground truth images.
+The first, middle panel displays the real image, or ground truth, which the discriminator uses to differentiate between real and generated images from the generator.
+During training, the GAN aims to mimic this ground truth.
 The second middle panel depicts the reconstructed image, or predicted image, produced by the trained GAN.
@@
 The right panel shows the difference between the ground truth and the predicted image.
-This difference should be minimized for high-precision image reconstruction with the application of GAN on II.
-The predicted images of Fig.~\ref{fig:GAN} showed positive results, accurately providing visual information about the source's size and shape, as well as the distributed brightness.
+This difference should be minimized for high-precision image reconstruction with application of GAN on II.
+So, the predicted images of fig.~\ref{fig:GAN} showed positive results, accurately providing visual information about the source's size and shape, as well as the distributed brightness.
 This image reconstruction was achieved using only six baselines.
-However, the results can be further improved by increasing the number of telescopes to cover more (u, v) planes, making the existing and upcoming Cherenkov Telescope Array Observatory (CTAO) an ideal candidate in collaboration with existing CTA.
+However, the results can be further improved by increasing the number of telescopes to cover more (u, v) planes.
 \subsection{Evaluation of GAN using moments}
-The reconstructed images are good enough visually to claim the success of GAN in reconstructing the image using II.
-However, there is a need for statistical evaluation of this predicted image to guarantee success.
-So, we use image moments as a statistical method.
-Image moments are statistical properties that provide information about the reconstructed shape, size, and intensity distribution of the objects in the image.
-These moments help quantify key features like the position, orientation, and distribution of brightness in the image, allowing for an objective evaluation of how well the predicted image corresponds to the actual object.
-We will analyze the consistency and accuracy of the GAN-generated image by comparing its moments to those of the ground truth.
-It provides a reliable framework for evaluating reconstruction quality, as image moments highlight the subtle differences in geometric and intensity properties that might not be visually apparent.
+After the success of GAN in reconstructing the image using II, there is a need for evaluation of this result.
+Here, we use the image moments for this work.
+Image moments are statistical properties that provide information about the shape, size, and intensity distribution of the objects in the image.
+So, we evaluate images generated by the GAN with the moments to ensure the accuracy and precision of the predicted image.
 
@@
 
-The zeroth order raw moment called the monopole is the total intensity of an image.
+The zeroth order raw moment, which is the total intensity of an image and is called the monopole.
 It sums up all the pixel values across the image, providing an overall intensity value.
 So, the study of monopole provides the total flux of fast-rotating stars here.
-According to eqn.~\ref{eqn:Mom}, the monopole of an image is calculated as
+According to eqn.~\ref{eqn:Mom}, the monopole of a image is calculated as
 \begin{equation}
@@
 \end{equation}
-Fig.~\ref{fig:mom1} shows the monopole for 50 different reconstructed images.
+The left figure (fig.~\ref{fig:mom1}) in fig.~\ref{fig:cen} shows the monopole for 50 different reconstructed images.
 It shows the linear behavior for the monopole between the ground truth (the real image) along the x-axis and the predicted image (reconstructed image) along the y-axis, which is obvious for different shape-size sources.
@@
 It ensures that the predicted image has the approximately correct total brightness (the flux) compared to the ground truth.
-However, monopole does not explain the position, shape, size, and brightness distribution of fast-rotating stars; there is a need for higher-order moments.
+However, monopole does not explain the shape, size, and brightness distribution of fast-rotating stars.
+So, we need higher-order moments.
 
-The center of mass for the fast-rotating star or any other stellar object is calculated using the centroid (x-centroid and y-centroid).
-It represents the spatial position of the image and is calculated using first-order raw moment and monopole.
-The formulation of centroid along the x and y directions is
+The center of mass for the fast-rotating star or any other stellar object is calculated using the centroid (in x and y directions).
+These centroids are given in terms of first-order raw moment and monopole as
 \begin{equation}
@@
 \end{equation}
-Fig.~\ref{fig:mom2} and Fig.~\ref{fig:mom3} show the comparison of the x-centroid and y-centroid for 50 predicted images with respect to ground truths, respectively.
-The clustering of centroids in a given scale range for all the results explains that the reconstructed image correctly represents the spatial location of the fast-rotating star in compare with the ground truth.
+Fig.~\ref{fig:mom2} and fig.~\ref{fig:mom3} show the comparison of centroid along the x and y axis for 50 predicted images with respect to ground truths.
+The clustering of centroids in a given scale range for all the results explains that the reconstructed image correctly represents the spatial location of the fast-rotating star.
 
-Further, these calculated centroids will help to study the shape, size, and brightness distribution of fast-rotating stars in terms of higher-order image moments.
+Now, these centroids will help to study the shape, size, and brightness distribution of fast-rotating stars in terms of higher-order image moments.
 For that, the central moment of an image is calculated according to
 \begin{equation}
-	\mu_{pq} = \frac{1}{M_{00}}\sum_{x} \sum_{y} (x - m_x)^p (y - m_y)^q I(x, y).
+	\mu_{pq} = \frac{1}{M_{00}}\sum_{x} \sum_{y} (x - m_x)^p (y - m_y)^q I(x, y)
 \end{equation}
-The sum of $p$ and $q$ defines the order of the central moment.
 
-The second order central moment ($\mu_{11}, \mu_{20}, \mu_{02}$) has been shown in Fig.~\ref{fig:struc}, which is used to study the structure of a fast-rotating star along the line of sight of observation (explain in upcoming subsection).
+The second order moment ($\mu_{11}, \mu_{20}, \mu_{02}$) has been shown in fig.~\ref{fig:struc}, which is used to study the structure of a fast-rotating star along the line of sight of observation (explain in upcoming subsection).
 All these three plots explain the linear relation of second-order moments again as for monopole and show the success of the application of GAN to reconstruct the image with II.
 
-The information on brightness distribution is gathered using the skewness of the image by calculating third-order central moment ($\mu_{30}, \mu_{03}, \mu_{21}, \mu_{12}$) of images.
+The information on brightness distribution can be gathered using the skewness of the image, and for that, there is a need for third order ($\mu_{30}, \mu_{03}, \mu_{21}, \mu_{12}$) central moment of images.
 Fig.~\ref{fig:moments} shows all third-order moments for the ground truth and reconstructed image.
-The skewness along the x and y axis ($\mu_{30}, \mu_{03}$) to test the GAN for II are acceptable, which can be seen in Fig.~\ref{fig:mom7} and Fig.~\ref{fig:mom8}, where a linear relation exists between ground truth and predicted image.
-However, the remaining higher moments $(\mu_{21}, \mu_{12})$ shown in Fig.~\ref{fig:mom9} and Fig.~\ref{fig:mom10} are not in good terms specially $\mu_{12}$.
-Further improvement is possible and needs to be studied.
+The skewness along the x and y axis ($\mu_{30}, \mu_{03}$) to test the GAN for II are acceptable, which can be seen in fig.~\ref{fig:mom7} and fig.~\ref{fig:mom8} where a linear relation exists between ground truth and predicted image.
+However, the remaining higher moments $(\mu_{21}, \mu_{12})$ shown in fig.~\ref{fig:mom9} and fig.~\ref{fig:mom10} are not in good terms specially $\mu_{12}$.
 
 \subsection{The reconstructed Parameters for object}
-The centroids $(m_x, m_y)$ represent the center of the fast-rotating star and spatial location on the image.
+The centroids $(m-x, m_y)$ represents the center of the fast-rotating star.
 However, the calculated second-order central moment defines the orientation, semi-major axis, and eccentricity of the source \citep{teague1980image}.
@@
 
-The orientation of a fast-rotating star along the line of sight is defined in terms of second-order central moments as
+The orientation along the line of sight is defined as
 \begin{equation}
@@
 \end{equation}
-The semi-major and semi-minor axis of the stellar object will be calculated with the help of second-order central moment again and denoted as a and b here, respectively
+The semi-major and semi-minor axis will be calculated according to
 \begin{equation}
@@
 \end{equation}
-With the help of the axis value, the eccentricity of the fast-rotating star is calculated as
+So, the eccentricity of the fast-rotating star in terms of axis value is 
 \begin{equation}
@@
 Fig.~\ref{fig:recons} shows all zeroth to third order moments only for one ground and predicted image.
-In this figure, there is a red curve for both ground truth and predicted image, which is the representation of all second-order moments in terms of Eqn.~\ref{eqn:orn} to Eqn.~\ref{eqn:eccen} as orientation, axis value, and eccentricity.
+In this figure, there is a red curve for both ground truth and predicted image which is the representation of all second-order moments in terms of eqn.~\ref{eqn:orn} to eqn.~\ref{eqn:eccen} as orientation, axis value, and eccentricity.
 There is a cyan dot point as well, which represents the zeroth order moment for both images.
-The third-order moment is expressed in terms of arrows in magenta and blue color to view the skewness along the x and y axes.
+There is also a third-order moment, which is expressed in terms of arrows in magenta and blue color to view the skewness along the x and y axes.

### 2025-02-02 Phase_II/draft/conclusion.tex
Changes by Sarangi

--- 2024-10-02 Phase_II/draft/conclusion.tex
@@
 \section{Conclusion}
-Intensity Interferometry (II), a technique, is emerging after a long gap to overcome the challenges of Amplitude Interferometry on optical wavelength.
-It is rejuvenated with support from advanced facilities at the Imaging Cherenkov Telescope Arrays (ICTAs).
-These telescopes, equipped with large aperture areas and photon detectors capable of resolving signals within a nanosecond, are instrumental in capturing high-resolution images \citep{dravins2013optical}.
-The Major Atmospheric Gamma Imaging Cherenkov Telescope (MAGIC), one of the CTA in the world, is now also being used for II, observing stellar objects with its 17-meter diameter mirror \citep{lorenz2004status}.
-The telescope has already demonstrated the potential of II by measuring and comparing the diameters of individual stars \citep{abe2024performance}.
-Other existing arrays (Very Energetic Radiation Imaging Telescope Array System (VERITAS) and High Energy Stereoscopic System (HESS)) are also making progress as II when gamma-ray observation stops \citep{kieda2021veritas, zmija2022optical}.
-Future observations, made possible by more advanced, sensitive instrumentation and upcoming CTAO, promise to push the boundaries of what we can observe with optical range.
-However, there is a drawback of II in terms of phase loss of signal, capturing only its magnitude via photon correlation.
-Here, the challenge of phase retrieval in Intensity Interferometry (II) has been effectively addressed through the application of machine learning techniques, particularly with conditional Generative Adversarial Networks (cGAN).
-Our study demonstrates that the application of cGAN on II data successfully recovers the size, shape, and brightness distribution of a fast-rotating star.
-The evaluation based on image moments, specifically the monopole, second, and third-order moments, supports the effectiveness of the cGAN in achieving accurate image reconstruction from a one-night simulation of II using six baselines.
+The challenge of phase retrieval in Intensity Interferometry (II) has been effectively addressed through the application of machine learning techniques, particularly with Generative Adversarial Networks (GANs).
+Our study demonstrates that using a GAN on II data successfully recovers the size, shape, and brightness distribution of a fast-rotating star.
+The evaluation based on image moments, specifically the monopole, second, and third-order moments, supports the effectiveness of the GAN in achieving accurate image reconstruction from a one-night observation using six baselines.
+
 A critical factor in the performance of the reconstruction process is the extent of Fourier plane coverage, which is determined by the number of available telescopes and the total observing time.
@@
 
-While the results of this study demonstrate the significant potential of machine learning, particularly cGAN, for image reconstruction in II, several aspects need further refinement.
-Detector efficiencies, which impact the signal-to-noise ratio (SNR) in real-world scenarios, have yet to be incorporated, and addressing them will be crucial for more accurate SNR estimation.
+This study has not considered the detector efficiencies, which could influence the signal-to-noise ratio (SNR) in practical scenarios.
 Incorporating these efficiencies in future work will be important for providing a more accurate estimate of the SNR and the robustness of the GAN in real-world applications.
-While cGAN has proven effective in this study, there are other methods for generating images from image data.
+
+While conditional GANs have proven effective in this study, there are other methods for generating images from image data.
 Exploring and comparing alternative methods, as well as adapting the GAN architecture itself, could offer improvements.
-For instance, different loss functions could be implemented and compared to enhance reconstruction quality.
+For instance, different loss functions could be implemented and compared to potentially enhance reconstruction quality.
 Further testing is required to refine the GAN and make it more robust and reliable.
@@
 
-In summary, though cGAN has shown promising results, further testing and improvements are necessary to make the model more robust and reliable in practical applications.
-Overall, this study highlights the potential of machine learning approaches for advancing phase retrieval and high-resolution image reconstruction in II, suggesting exciting future directions in the application of AI to optical astronomy.
+In summary, while the current implementation shows strong potential, further exploration and refinement of machine learning models are needed to optimize their application in phase retrieval and image reconstruction in Intensity Interferometry.

### 2025-02-02 Phase_II/draft/intro.tex
Changes by Sarangi

--- 2024-10-02 Phase_II/draft/intro.tex
@@
 
-Intensity Interferometry (II) emerged in the 1970s as a groundbreaking technique for measuring the diameters, orbits, and limb-darkening coefficients of 32 stars in the N-body system.
-Despite these significant achievements, the method did not gain widespread adoption due to the then-required highly sensitive photon detectors and sophisticated data analysis techniques.
-However, advancements in computational methods and modern electronics, which now offer time resolution of detectors in the nanoseconds (ns) range, have renewed II as a feasible technique for resolving astrophysical objects at visible wavelengths.
-Current simulations with ns resolution of photon detectors show that II is effective in achieving high precision measurement of parameters for stellar objects \citep{10.1093/mnras/stab2391, 10.1093/mnras/stac2433}.
-Yet, despite these technological advancements, II still faces a significant limitation: the absence of phase information, which is essential for the complete reconstruction of the brightness distribution of stellar sources.
+Intensity Interferometry (II) \textcolor{blue}{was first reported by Hanbury Brown and Twiss (HBT) during the 1950s \citep{brown1954lxxiv, HBT56} as a \textquotedblleft new type of interferometry\textquotedblright \ to measure stellar parameters such as angular diameter, orbits, limb darkening coefficients etc.
+Later theoretical results reported by
+\cite{brown1957interferometry, brown1958interferometry}, 
+and those of \cite{glauber1963quantum} and 
+\cite{MandelWolf1995, Hecht2002} demonstrated the deeper 
+physical properties of photon correlations that lay at the 
+core of II and also laid the foundation of Quantum Optics.}
+By the 1970s, \st{as a groundbreaking} \textcolor{blue}
+{with the results of stellar parameter measurements of 32 stars 
+in single and multistar systems, 
+carried out by Hanbury Brown and his collaborators \citep{hanbury1974angular} at the historic Narrabri Stellar Intensity Interferometer (NSII), Australia,  
+II had emerged as an alternative technique 
+for measuring stellar parameters.}\st{diameters, orbits, and limb-darkening 
+coefficients of 32 stars the N-body system.} Despite these significant achievements,
+the method did not gain 
+widespread adoption \textcolor{blue}{during several following decades due to unavailability of} the required 
+sensitive photon detectors and sophisticated data analysis 
+\textcolor{blue}{devices}\st{techniques}. 
+However, \textcolor{blue}{subsequent} advancements in computational 
+methods and in modern electronics, which currently offer time resolution of detectors in the nanoseconds (ns) to picoseconds (ps) range, have renewed 
+II as a feasible technique for resolving astrophysical objects at visible wavelengths. Recent 
+ simulations deploying ns-resolution photon detectors show that II 
+ \st{is} \textcolor{blue}{could be} effective 
+ in achieving high precision measurement of parameters for stellar objects 
+ \citep{10.1093/mnras/stab2391, 10.1093/mnras/stac2433}.
 
-Several theoretical and computational approaches to phase reconstruction with II have been proposed.
-\cite{gamo1963triple} introduced the concept of triple-intensity correlation, which \cite{goldberger1963use} further applied in an experiment to observe scattered particles in microscopic systems.
-Sato conducted experiments to measure the diameter and phase of asymmetrical objects, suggesting that triple correlation could extend II to image stellar bodies \citep{sato1978imaging, sato1979computer, sato1981adaptive}.
-Despite its potential, the sensitivity of the signal to noise poses a significant challenge for this approach.
+In addition to measurement of physical parameters of star systems, a fundamental motivation of optical astronomy is to obtain the sky intensity distribution of the source using the information observed on the ground.
+In the context of II, the task is to construct the image of the source from the intensity correlations observed by a set of pairs of telescopes (light buckets) on the ground.
+\textcolor{blue}{However, with the basic observable of II being the electromagnetic field intensity, and not the field strength},
+ a significant aspect of \textcolor{blue}{this method} is the loss of phase information. \st{Consequently, a} A full 
+ reconstruction of the brightness distribution of a source with II 
+ necessitates phase information. Therefoere the task is to reconstruct the phase of the signal.
 
-Later \cite{holmes2010two} proposed an alternative method, utilizing the Cauchy-Riemann relations to reconstruct 1-D images and extending this to 2-D images across a range of signal-to-noise (SNR) values.
-This algorithm was applied to simulated data of stellar objects using II, considering existing and forthcoming Imaging Cherenkov Telescope Arrays (ICTAs) with a large number of telescopes \citep{nunez2010stellar, nunez2012high, nunez2012imaging}.
-Despite these theoretical advances, practical application to actual observational data of stellar objects with II has yet to be achieved.
-There is a need to advance this field by introducing a novel image reconstruction technique.
+Several theoretical and computational approaches to phase reconstruction 
+with II have been proposed. \cite{gamo1963triple} introduced the concept 
+of triple-intensity correlation, which \cite{goldberger1963use} further 
+applied in an experiment to observe scattered particles in microscopic systems. 
+Sato conducted experiments to measure the diameter and phase of asymmetrical 
+objects, suggesting that triple correlation could extend II to image stellar 
+bodies \citep{sato1978imaging, sato1979computer, sato1981adaptive}. \textcolor{blue}{However, achieving a good signal-to-noise ratio (SNR) still poses a significant challenge for this approach.}
 
-Currently, artificial intelligence (AI) is applied to high-volume data to reduce human computing resources and time effort.
-New analysis techniques using Machine Learning (ML) applications on observed data are playing at the front to reveal the astronomical mystery.
-In radio morphologies, the supervised and unsupervised algorithm is used to distinguish the radio components from the infrared source \citep{wu2019radio, galvin2020cataloguing}.
-Recently, the image reconstruction of the M87 black hole using Generative Adversarial Networks (GANs) has been performed \citep{10.1093/mnras/stad3797}.
-There is also a need to introduce the application of ML to II data, which will aim to overcome the limitations of image reconstruction and high-resolution optical astronomy.
+Gerchberg and Saxton suggested an iterative method \cite{GerchbergSaxton1972}to determine the phase of from the image and diffraction plane pictures.
+This method relies on good initial estimates and may struggle with slow convergence issues otherwise.
+Fienup suggested a Hybrid Input-Output algorithm that introduced feedback mechanisms to improve convergence rate and robustness, particularly in noisy environments.
 
-In this paper, we propose an alternative approach for image reconstruction of stellar objects with II using GAN \citep{goodfellow2014generative}.
-We consider four ICTAs and perform a one-night simulation for a fast-rotating star.
-The predicted image by a trained GAN shows promising results for reconstructing the image's shape and size.
-Image moments evaluate the predicted image and demonstrate that the size and shape of the fast-rotating star are reconstructed.
-However, the brightness distribution recovers only up to the third-order moment.
-With the introduction of more telescopes, we can expect even greater precision, especially in recovering higher-order image moments.
-This approach holds great promise, pushing the boundaries of high-resolution optical astronomy and opening up new possibilities for studying stellar objects with remarkable detail.
+Later \cite{holmes2010two} proposed an alternative method, utilizing the 
+Cauchy-Riemann relations to reconstruct 1-D images and extending this to 
+2-D images across a range of signal-to-noise (SNR) values. This algorithm 
+was applied to simulated data of stellar objects using II, considering 
+existing and forthcoming Imaging Cherenkov Telescope Arrays (IACTs) with 
+a large number of telescopes 
+\citep{nunez2010stellar, nunez2012high, nunez2012imaging}. This method faces challenge of computational complexity in attempting to generalize to higher dimensions.
 
-This paper is organized as follows: The first section discusses Intensity Interferometry following its signal and noise for fast-rotating stars along the Earth's rotation.
-The second section introduces the GAN formulation and its structure.
-The third section details the parameter selection for training the GAN to reconstruct the image.
-After that, the fourth section presents the results of trained GAN visually and using image moments.
-At the end, there is a conclusion of the entire result.
+Li etal suggested a flexible iterative Regularization method \citep{Li2014} of incorporating prior information (e.g., sparsity, smoothness, or non-negativity), reducing the ill-posedness of the phase retrieval problem.
+This method is more robust against noise and stabilizes the solution against artefacts and spurious solutions.
+This method faces challenges of choice of regularization parameter, computational complexity and sensitivity to initial guess.
+
+The Transport-of-Intensity Equation (TIE) method, a non-interferometric technique and first suggested by Teague \citep{Teague1983} relates the intensity variations along the optical axis and phase of the optical fields.
+It enabled phase retrieval from intensity measurements at multiple planes.
+Zhang et al suggested a method \citep{Zhang2020} of obtaining a \textquotedblleft universal solution \textquotedblright to TIE using \textquotedblleft maximum intensity assumption \textquotedblleft, hence converting the TIE into a Poisson equation and then by solving it iteratively.
+Recent work of Kirisits et al \citep{Kirisits2024} have explored hybrid methods combining TIE with other equations, such as the Transport of Phase Equation (TPE).
+These approaches leverage the strengths of both equations to improve phase retrieval accuracy.
+This method has universal applicability in the sense that it works for arbitrarily shaped apertures, handles non-uniform illumination and inhomogeneous boundary conditions.
+This method guarantees convergence although the speed of convergence is dependent on initial guess quality.
+The final results are dependent on boundary conditions.
+
+\textcolor{red}{With non-linearlity built into its grains, neural networks and deep learning were obvious choice to look for as an option to use.
+There have been these works..
+involving deep learning, GAN.........{\bf Reference and brief description of other pieces of work using NN and Deep Learning to be inserted here!!}}
+
+In this paper, we propose an alternative approach using Generative 
+Adversarial Networks (GANs) \citep{goodfellow2014generative} to reconstruct 
+images of stellar objects using II. We consider four Imaging Cherenkov 
+Telescope Arrays (IACTs) located in the Northern Hemisphere and perform 
+a one-night simulation for a fast-rotating star. The predicted image using 
+a trained GAN shows promising results for reconstructing the image's shape and 
+size.The evaluation of the predicted image is conducted using image moments, 
+demonstrating that the size and shape of the fast-rotating star are 
+reconstructed. However, the brightness distribution recovers only at the 
+third-order moment.
+
+This paper is organized as follows: The first section discusses 
+Intensity Interferometry following its signal and noise for fast-rotating 
+stars along the Earth's rotation. The second section introduces the GAN 
+formulation and its structure. Following the third section details the 
+parameter selection for training the GAN to reconstruct the image. 
+After that, the fourth section presents the results of trained GAN visually 
+and using image moments. At the end, there is a discussion of the entire result.

### 2025-02-02 Phase_II/draft/main.tex
Changes by Sarangi

--- 2024-10-16 Phase_II/draft/main.tex
@@
 \usepackage{amsfonts} % For \mathbb
+%%%%%
+\usepackage{color}
+%\usepackage[normalem]{ulem}
+\usepackage{soul}
+\usepackage{ulem}
+\usepackage{comment}
 
@@
 
-\title{Generative AI for Image Reconstruction with Intensity Interferometry: A First Attempt}
+\title{Image reconstruction of stellar objects with Intensity Interferometry using Generative Adversarial Networks}
 \date{}
@@
 \begin{abstract}
-In modern astronomy, simulation and observation with Intensity Interferometry (II) are showing noteworthy progress with optical wavelengths to achieve high-resolved stellar objects.
-Despite these achievements, phase retrieval of the signal remains challenging due to photon correlation, hence the image reconstruction.
-Here, we propose the application of a conditional Generative Adversarial Network (cGAN) to II simulated data to overcome the limitations of traditional image reconstruction methods, as Artificial Intelligence (AI) techniques are at the forefront of revealing astronomical mysteries by analyzing the signal.
-Here, the cGAN effectively reconstructs the shape, size, and brightness distribution of a fast-rotating star by utilizing sparsely sampled, phase-subtracted Fourier transforms of the star.
-Simulations of II are based on an assembly of four telescopes similar to existing arrays.
-However, the sensitivity of the signal and high resolution are expected to improve with additional baselines, which makes the current and future Cherenkov Telescope Array Observatory (CTAO) an ideal candidate for II applications.
-This approach is highly relevant to the existing image reconstruction technique with II and could revolutionize high-resolution imaging in astronomy.
+In current astronomy, the simulation of Intensity Interferometry is demonstrating significant advancements in the high-precision resolution of stellar objects at optical wavelengths.
+Despite these achievements, phase retrieval remains challenging due to photon correlation.
+This paper proposes the application of a conditional Generative Adversarial Network (GAN) to address this issue of image reconstruction with Intensity Interferometry.
+Here, the GAN effectively reconstructs the shape, size, and brightness distribution of a fast-rotating star by utilizing sparsely sampled, phase-subtracted Fourier transforms of the star.
+This innovative approach promises to enhance the capabilities of Intensity Interferometry for image reconstruction in addition to estimating the parameters with high precision in astronomical observations.
 \end{abstract}
@@
 \bibliographystyle{mnras}
-\bibliography{refs.bib}
+\bibliography{refs}
 

### 2025-02-02 Phase_II/draft/II.tex
changes in bib file

@@
 
-\textcolor{blue}{Subsequently, during the opening decades of the current century, proposals to use the Imaging Atmospheric Cherenkov Telescope (IACT) facilities for carrying out Stellar Intensity Interferometry (SII) observations were put forth \citep{LeBohec2006, Nunez2010stellar, Nunez2012High, Dravins2013}.
+\textcolor{blue}{Subsequently, during the opening decades of the current century, proposals to use the Imaging Atmospheric Cherenkov Telescope (IACT) facilities for carrying out Stellar Intensity Interferometry (SII) observations were put forth \citep{LeBohec2006, nunez2010stellar, nunez2012high, Dravins2013}.
 Such observations, it was suggested, could be carried out during bright moon-lit nights during which $\gamma$-ray observations using upper atmospheric Cherenkov showers were not feasible.

### 2025-02-12 Phase_II/draft/II.tex
II

@@
 \subsection{The signal for II}\label{sec:signal}
-As a simple example, let us consider the pair of IACTs at MAGIC.
-Let us imagine that the two telescopes, namely, MAGIC-I and MAGIC-II are pointed to a star.
-\textcolor{red}{My comment: As our model has 4 hypothetical IACTs and we are not taking any specific properties of the MAGIC telescopes into the calculations or into the model, it would be better to avoid using the specific names of MAGIC facility.This portion can be easily rewritten without the mention of MAGIC.}Let them simultaneously measure the intensity of radiation $I_1(t)$ a  and $I_2(t)$ respectively.
+As a simple example, let us consider the pair of IACTs.
+Let us imagine that the two telescopes are pointed to a star.
+Let them simultaneously measure the intensity of radiation $I_1(t)$ a  and $I_2(t)$ respectively.
 These signals from the respective detectors are cross-correlated and averaged over time and yield the \textcolor{blue}{second order ($n=2$) correlation of these intensities as}  \citep{acciari2020optical, dravins2013optical}
@@
 \end{equation}
-where, $\Delta f$ is the electronic bandwidth \textcolor{blue}{of the photon detectors (that measure the intensities and typically lie in range $\sim 100 {\mathrm {MHz}}$)} and $\Delta {\mathrm {\nu}}$ is the optical bandwidth \textcolor{blue}{of radiation over which the intensities are measured}\footnote{\textcolor{blue}{Typically, filters with bandwidths in the range $\Delta \lambda \sim 20 nm - 50 nm$ corresponding to $\Delta \nu \sim 10^{15}$ Hz are used.} .
-In eq.(\ref{eqn:HBT2}), $V_{12}$, referred to as the complex visibility fuction, is the Fourier transform of the source brightness distribution and is given by
+where, $\Delta f$ is the electronic bandwidth \textcolor{blue}{of the photon detectors (that measure the intensities and typically lie in range $\sim 100 {\mathrm {MHz}}$)} and $\Delta {\mathrm {\nu}}$ is the optical bandwidth of radiation over which the intensities are measured.\footnote{\textcolor{blue}{Typically, filters with bandwidths in the range $\Delta \lambda \sim 20 nm - 50 nm$ corresponding to $\Delta \nu \sim 10^{15}$ Hz are used.}} In eq.(\ref{eqn:HBT2}), $V_{12}$, referred to as the complex visibility fuction, is the Fourier transform of the source brightness distribution and is given by
 \begin{equation}
-\vert V_{12} \vert = 2 \frac{J_1(\pi \ d \ {\theta}/{\lambda})}{\pi\  d \ {\theta}/{\lambda}}
+ V_{12} = 2 \frac{J_1(2 \pi d \theta)}{(2 \pi d \theta)}
 \label{eqn:absvisib}
 \end{equation}
-with $d$, $\theta$ and $\lambda$ being the baseline, the angular diameter of the star and the optical wavelength of the filter used in observation.
-It is obvious from eq(\ref{eqn:absvisib}) that $\vert V_{12} \vert$ carries the information of the angular diameter of the star.} However, the phase information is lost \st{due to the involvement of the absolute value of $V_{12}$}\textcolor{blue}{as we measure the absolute value $\vert V_{12} \vert$}.
+where $\theta$ is the angular diameter of the star and d is the radial coordinate in the usual interferometric $(u , v) = (x/\lambda, y/\lambda)$ plane with the optical wavelength $\lambda$ of the filter used in observation.
+It is obvious from eqn(\ref{eqn:absvisib}) that $V_{12}$ carries the information of the angular diameter of the star.
+However, the phase information is lost \st{due to the involvement of the absolute value of $V_{12}$}\textcolor{blue}{as we measure the absolute value $\vert V_{12} \vert^2$}.
 In observational astronomy, the correlation is often expressed in terms of the normalized contrast, given by:
@@
 where, $\left\langle I_1 \right\rangle$ and $\left\langle I_2 \right\rangle$ are the mean intensity from two telescopes.
+So, the signal measured by electronic bandwidth  $\Delta f$ of photon detector of II in the optical bandwidth of observational radiation $\Delta {\mathrm {\nu}}$ is
+\begin{equation}
+	c = g^{(2)} - 1 = \frac{\Delta f}{\Delta \nu} \abs{V_{12}}^2
+	\label{eq:signal}
+\end{equation}
+$\abs{V_{12}}^2$ is a function of baseline $d = \sqrt{u^2 + v^2}$ on observational plane. So the strength of the signal is increased using large number of baselines.
 
@@
 Needless to mention that light of the stellar source is focused on the PMT during the II observations.}
-\st{In II observations, the light of a stellar source is focused on a single PMT, which has a filter in front.
-The purpose of this filter is to efficiently transmit light around mean observational frequency, which protects the PMTs from excessive light.
-It is necessary, as II observations are mainly done during full moon nights, where it is too bright for Very High Energy $\gamma$-ray observations.} The optical signal of the PMTs is transmitted through optical fibers, converted to an electrical signal, and digitized \cite{acciari2020optical}.
-The measurable observable is the Pearson's correlation coefficient:
-\begin{equation}
-	\rho(\tau) = \frac{\left\langle \left( I_1(t) - \left\langle I_1 \right\rangle \right) \cdot \left( I_2(t + \tau) - \left\langle I_2 \right\rangle \right) \right\rangle}{\sqrt{\langle \left( I_1(t) - \langle I_1 \rangle \right)^2 \rangle} \cdot \sqrt{\langle \left( I_2(t) - \langle I_2 \rangle \right) ^2 \rangle}}
-	\label{eqn:pearson}
-\end{equation}
-Since $I_1$ and $I_2$ are proportional to the direct current of the PMTs ($DC_i$), the normalized contrast can be calculated as in equation \ref{eq:norm_contrast2}.
-One must also correct for a non-constant gain of the PMTs, as well as the moon.
-The latter can be done by measuring the background light with an additional PMT with no mirrors focused on it \cite{acciari2020optical}.
-\begin{equation}
-	c \propto \frac{\rho}{\sqrt{\left(DC_1 \cdot DC_2 \right)}}
-	\label{eq:norm_contrast2}
-\end{equation}
-It must be noted that the calculation of Pearson's correlation coefficient is non-trivial: MAGIC makes use of the convolution theorem for discrete Fourier transforms because it is computationally more efficient.
 
 The significance of the signal can be expressed as the signal-to-noise ratio (SNR), which depends on many factors.
-However, most importantly, it is proportional to the absolute value of visibility, which itself depends on the distance between the telescopes, shown in equation (\ref{eq:SNR}) \cite{acciari2020optical}.
+However, most importantly, it does not depend on optical bandwidth $\Delta {\mathrm {\nu}}$ of radiation for two telescope correlation.
+The explanation of independence of SNR from  $\Delta {\mathrm {\nu}}$ is given in the end of subsection 4.1 of \cite{10.1093/mnras/stab2391}.
 \begin{equation}
-	SNR = A \cdot \alpha \cdot q \cdot n \cdot \abs{V_{12}}^{2}(d) \cdot \sqrt{b_v} \cdot F^{-1} \cdot \sqrt{\frac{T}{2}} \cdot \sigma
+	SNR = A \cdot \alpha \cdot q \cdot n \cdot F^{-1} \cdot \sigma \cdot \sqrt{\frac{T \Delta f}{2}} \cdot \abs{V_{12}}^{2}
 	\label{eq:SNR}
 \end{equation}
-here, $A$ is the total mirror area, $\alpha$ the quantum efficiency of the PMTs, $q$ the quantum efficiency of the optics, $n$ the differential photon flux from the source, and $b_v$ the cross-correlation bandwidth.
-The noise of the PMTs is accounted for with $F$, $T$ denotes the observation time, and $\sigma$ is the normalized spectral distribution of the light (including filters) \cite{acciari2020optical}.
-While most of the parameters can be optimized with hardware, the only way to obtain a better SNR is to increase the observation time with fixed telescopes.
+here, $A$ is the total mirror area, $\alpha$ the quantum efficiency of the PMTs, $q$ the quantum efficiency of the remaining optics, and $n$ the differential photon flux from the source.
+The excess noise factor of the PMTs is accounted with $F$, $T$ denotes the observation time, and $\sigma$ is the normalized spectral distribution of the light (including filters) \cite{acciari2020optical}.
+The signal (S) and noise (N) can be understand using eqns.\ref{eq:signal} and \ref{eq:SNR} as
+\begin{equation}
+	S = \frac{\Delta f}{\Delta \nu} \abs{V_{12}}^2
+\end{equation}
+and
+\begin{equation}
+	N = (A \cdot \alpha \cdot q \cdot n \cdot F \cdot \sigma \cdot \Delta \nu)^{-1}\sqrt{\frac{2 \Delta f}{T}}
+\end{equation}
+While most of the parameters can be optimized with hardware, the only way to obtain a better SNR is to increase the observation time T with fixed telescopes.
+
 \textcolor{red}{Points to be discussed: 
@@
 \begin{equation}
-	(u,v) = \frac{1}{\lambda} (d_N, d_E)
+	(u,v) = \frac{1}{\lambda} (d_E, d_N)
 \end{equation}
-where $d_N$ and $d_E$ are the baselines expressed in north and east coordinates. 
+where $d_E$ and $d_N$ are the baselines expressed in north and east coordinates. 
 \textcolor{blue}{But not all sources are at the zenith, and the telescopes are stationary and may also have different relative altitudes $d_A$ depending on the available terrain.
@@
 \begin{equation}
-\begin{pmatrix} u\\ v\\ w\\ \end{pmatrix} = R_x(\delta) \cdot R_y(h) \cdot R_x(-l) \begin{pmatrix} d_N\\ d_E\\ d_A\\ \end{pmatrix}
+\begin{pmatrix} u\\ v\\ w\\ \end{pmatrix} = R_x(\delta) \cdot R_y(h) \cdot R_x(-l) \begin{pmatrix} d_E \\ d_N \\ d_A \\ \end{pmatrix}
 	\label{eq:baseline_rot}

### 2025-02-21 Phase_II/draft/GAN.tex
modification

--- 2024-12-09 Phase_II/draft/GAN.tex
@@
 \section{Generative Adversarial Networks}
-
 In 2014, Ian Goodfellow invented Generative Adversarial Networks (GANs).
@@
 \end{equation}
-where $D^{*}_{G}$ denotes the optimum of the Discriminator for a given fixed Generator and is expressed as
+where $D^{*}_{G}$ denotes the optimum of the discriminator for a given fixed generator, shown in equation (\ref{eq:Disc_optimum}).
+It can now be shown that the global optimum of equation (\ref{eq:GAN_reformulated}) is reached if and only if $p_g = p_{data}$.
+Furthermore, if both $G$ and $D$ are allowed to reach their optima, $p_g$ converges to $p_{data}$.
+A more detailed discussion of the problem, including proofs, can be found in \cite{goodfellow2014generative}.
 \begin{equation}
@@
 \end{equation}
-It can now be shown that the global optimum of equation (\ref{eq:GAN_reformulated}) is reached if and only if $p_g = p_{data}$.
-Furthermore, if both $G$ and $D$ are allowed to reach their optima, $p_g$ converges to $p_{data}$.
-A more detailed discussion of the problem, including proofs, can be found in \cite{goodfellow2014generative}.
 \begin{figure}
@@
 	\end{subfigure}\hfill
-	\caption{Generator and Discriminator losses for three different learning rates.
-The upper figure shows the total Discriminator loss, and the lower figure shows the total generator loss.
+	\caption{Generator and discriminator losses for three different learning rates.
+The upper figure shows the total discriminator loss, and the lower figure shows the total generator loss.
 There is no significant difference, but the highest learning rate might be prone to outliers.
@@
 	\end{subfigure}\hfill
-	\caption{Generator and Discriminator losses for three different kernel sizes in the convolutional layers.
+	\caption{Generator and discriminator losses for three different kernel sizes in the convolutional layers.
 Here, the smallest kernel size has many outliers, while the largest kernel size seems to be the most stable.}
@@
 \end{figure*}
+
 Later, GAN extended its version to a conditional model \cite{mirza2014conditional}.

### 2025-02-21 Phase_II/draft/ParaGan.tex
modification

@@
 Due to the adversarial nature of GAN, where the Generator and Discriminator compete in a min-max game, careful tuning of key parameters ensures that both networks are in good term to train the model.
-
 \subsection{Data Preparation}

### 2025-02-21 Phase_II/draft/Result.tex
modification

--- 2024-12-09 Phase_II/draft/Result.tex
@@
 \section{The Reconstructed Image with GAN}
-
 In this section, we will first discuss phase retrieval using hyperparameters, as mentioned earlier, followed by an analysis where multiple sources are trained simultaneously.
@@
 
-\subsection{The Reconstructed Parameters for Object}
+\subsection{The reconstructed Parameters for object}
 The centroids $(m_x, m_y)$ represent the center of the fast-rotating star and spatial location on the image only.

### 2025-02-21 Phase_II/draft/conclusion.tex
modification

--- 2024-12-09 Phase_II/draft/conclusion.tex
@@
 However, our findings suggest that machine learning is a promising approach for phase reconstruction in II.
-
-In summary, though cGAN has shown promising results, further testing and improvements are necessary to make the model more robust and reliable in practical applications.
-Overall, this study highlights the potential of machine learning approaches for advancing phase retrieval and high-resolution image reconstruction in II, suggesting exciting future directions in the application of AI to optical astronomy.

### 2025-03-18 Phase_II/draft/GAN.tex
edit by Prof. Sarangi

--- 2025-02-02 Phase_II/draft/GAN.tex
@@
 \section{Generative Adversarial Networks}
-Generative Adversarial Networks (GANs) were invented by Ian Goodfellow in 2014.
-The concept is rather simple, as it consists of two competing networks.
-The first network is called a generator and creates new images based on an input image.
-Here, for consistency, the images generated by the generator will be denoted as generated images.
-The second network is the discriminator, which tries to distinguish between the generated image and the real image (ground truth) \cite{goodfellow2014generative}.
-As a consequence of training both networks alternately, the generated images eventually become indistinguishable from the real images.
-It is nothing more than a two-player min-max game, a famous problem in game theory.
-GAN was initially proposed in the formulation form as:
+In 2014, Ian Goodfellow introduced Generative Adversarial Networks (GANs).
+The underlying concept is straightforward: it involves two competing networks.
+The first network, known as the Generator, produces new images based on an input image.
+For consistency, images produced by the Generator will be referred to as generated images.
+The second network, the Discriminator, attempts to distinguish between the generated image (predicted image) and the real image (ground truth) \citep{goodfellow2014generative}.
+
+Through the alternating training of these networks, the generated images gradually become indistinguishable from the real images.
+Essentially, this process constitutes a two-player min-max game — a classic problem in game theory.
+The original formulation of GANs is given by:
 \begin{equation}
@@
 \end{equation}
-here, $V(D, G)$ is the value function of the min-max game.
+where $V(D, G)$ denotes the value function of the min-max game.
 
-The goal is now to learn the distribution of the generator $p_g$ over the data $x$.
-We have input noise variables $p_z(z)$, as well as the two perceptrons $G(z; \theta_g)$ and $D(x; \theta_d)$ with parameters $\theta_i$.
-$G$ represents a differential function that maps from $z$ to the data space $x$, while $D(x)$ represents the probability that $x$ is from the real data \cite{goodfellow2014generative}.
+The objective is to learn the Generator's distribution, \(p_G\), over the data \(x\).
+We begin with input noise variables \(p_z(z)\) and employ two perceptrons, \(G(z; \theta_G)\) and \(D(x; \theta_D)\), parameterized by \(\theta_i\) with \(i = G \ \mathrm{or}\ D\) respectively.
+Here, \(G(z)\) is a differentiable function that maps \(z\) to the data space \(x\), while \(D(x)\) represents the probability that \(x\) originates from real data \cite{goodfellow2014generative}.
 The problem can be reformulated as:
@@
 \end{equation}
-where $D^{*}_{G}$ denotes the optimum of the discriminator for a given fixed generator, shown in equation (\ref{eq:Disc_optimum}).
-It can now be shown that the global optimum of equation (\ref{eq:GAN_reformulated}) is reached if and only if $p_g = p_{data}$.
-Furthermore, if both $G$ and $D$ are allowed to reach their optima, $p_g$ converges to $p_{data}$.
-A more detailed discussion of the problem, including proofs, can be found in \cite{goodfellow2014generative}.
+where \(D^{*}_{G}\) denotes the optimum of the discriminator for a given fixed generator, as shown in equation (\ref{eq:Disc_optimum}).
+It can be demonstrated that the global optimum of equation (\ref{eq:GAN_reformulated}) is achieved if and only if \(p_G = p_{data}\).
+Furthermore, if both \(G\) and \(D\) are allowed to reach their respective optima, then \(p_G\) converges to \(p_{data}\).
+A more comprehensive discussion of the problem, including proofs, is provided in \citep{goodfellow2014generative}.
 \begin{equation}
@@
 \end{figure*}
-GANs can be extended to a conditional model \cite{mirza2014conditional}.
-In this case, both generator and discriminator receive extra information $y$, such that the value function of the conditional GAN (cGAN) can be expressed as:
+
+Subsequently, the GAN framework was extended to a conditional model \cite{mirza2014conditional}.
+In this formulation, both the Generator and the Discriminator receive additional information \(y\), and the value function of the conditional GAN (cGAN) is expressed as:
 \begin{equation}
@@
 
-Furthermore, \cite{isola2017image} observed that combining the cGAN given in equation \ref{eq:conditional_GAN} with the traditional L1-loss improves results, as the generator tries to be close to the ground truth.
-Hence, the function that is minimized as:
+Furthermore, \cite{isola2017image} observed that combining the cGAN from equation \ref{eq:conditional_GAN} with the traditional L1 loss improves the results, as the Generator is encouraged to produce outputs closer to the ground truth.
+Hence, the function that is minimized is:
 \begin{equation}
@@
 \end{equation}
-where $\lambda$ = 100 and $L_1(g)$ is given by equation (\ref{eq:l1_loss})
+where $\lambda$ = 100 and $L_1(G)$ is given as
 \begin{equation}
 	\centering
-	L_1(g) = \mathbb{E}_{x,y,z} \left[ \norm{y - G(x,z)}_1 \right]
+	L_1(G) = \mathbb{E}_{x,y,z} \left[ ||{y - G(x,z)}||_1 \right]
 	\label{eq:l1_loss}
@@
 
-This type of network is shown to be very robust, as it has been applied to several problems.
-Examples include creating colored images from grayscale images, creating images of facades based on architectural labels, changing from day to night in different pictures, and predicting a map based on satellite data.
-A longer list of applications is given in \cite{isola2017image}.
+This type of network has demonstrated remarkable robustness across a variety of applications.
+For example, it can generate colored images from grayscale inputs based on architectural labels, transform images from day to night, and even predict maps from satellite data.
+A more extensive list of applications is provided in \cite{isola2017image}.
 
 \subsection{Generator}
-The used generator in this paper is a common U-Net convolutional network, described in \cite{ronneberger2015u}.
-It consists of a contracting part, reducing the image size, and an expansive part, where the image is enlarged.
-The contracting part consists of repeated application of alternating convolutional layers and rectified linear unit (ReLU) layers.
-The expansion consists of repeated convolution, batch normalization, and ReLU layers.
-The first contracting step also includes a dropout layer \cite{isola2017image}
+As discussed above, in a GAN the Generator is responsible for producing synthetic data—in this case, images that resemble those of a fast-rotating star.
+In this work, the Generator is implemented as a U-Net convolutional network \cite{ronneberger2015u}.
+In such architectures, the image's spatial resolution is first reduced through downsampling and then restored via upsampling, resulting in a U-shaped structure.
+The downsampling process typically involves convolutional layers followed by a strided operation (with a stride of 2) to effectively subsample the image, and a leaky version of the Rectified Linear Unit (ReLU) is employed as the activation function.
+
+In contrast, the upsampling process uses only the standard Rectified Linear Unit (ReLU) for neuron activation.
+This stage also comprises convolutional layers followed by operations with a stride of 2 to upscale the image to a higher resolution.
+Additionally, a dropout layer is introduced at the beginning of the upsampling phase to mitigate overfitting of the Generator model \cite{isola2017image}.
+
+After generating images, the Generator aims to deceive the Discriminator into classifying the generated images as real.
+The extent to which the Generator succeeds in this deception is quantified by the GAN loss.
+When the Discriminator is unable to distinguish between the generated and real images (i.e., when the GAN loss is minimized), the Generator is considered to have reached an optimal state.
+Conversely, if the generated image fails to fool the Discriminator, the Generator produces a new image for further comparison with the real image.
+Additionally, the Generator's performance is evaluated using another metric known as the L1 loss, which is defined as the mean absolute error between the pixels of the real image and those of the generated image.
+Balancing the minimization of both the GAN loss and the L1 loss enables the Generator to produce images that are not only realistic but also faithful to the input data.
 
 \subsection{Discriminator}
-The discriminator that has been taken here, named PatchGAN, does not work globally but rather classifies single patches as real or fake.
-The overall result is then estimated based on the average.
-The model architecture is as follows: zero padding, convolution, batch-norm, ReLu, zero-padding, and convolution \cite{isola2017image}.
+As discussed earlier, the Discriminator is tasked with classifying the images produced by the Generator as either real or fake.
+It takes a real image from the dataset (often referred to as the target image for the Generator) and provides feedback to guide the Generator toward producing more accurate images.
+In this work, the PatchGAN model \cite{isola2017image} is employed as the Discriminator.
+Unlike a traditional global classifier, PatchGAN evaluates individual patches of the image, outputting a grid of predictions rather than a single scalar value.
+
+The Discriminator’s architecture begins with an initializer that accepts both the input (generated) images and the corresponding real images.
+Initially, Salt-and-Pepper noise is added to the input images.
+PatchGAN then reduces the spatial dimensions of the images to extract localized features, ensuring the model focuses on smaller regions.
+In this downsampling stage, a leaky version of the Rectified Linear Unit (LeakyReLU) is applied in the convolutional layers, similar to the approach used in the Generator.
+
+Subsequently, zero padding is applied—adding rows and columns of zeros around the images—to prevent the loss of spatial information during convolution and to facilitate the extraction of deeper features from the downsampled output.
+Following this, batch normalization is employed to stabilize learning by normalizing activations, and the Discriminator begins classifying each patch as real or fake.
+This is followed by additional layers involving LeakyReLU activation, zero padding, and convolution, culminating in a final prediction that the Generator uses as feedback.
+
+The effectiveness of the Discriminator is measured by its ability to distinguish between real and fake images, quantified through the Discriminator loss.
+This loss is composed of two parts: one that measures how accurately the Discriminator identifies real images (by comparing predictions to a target value of 1) and another that assesses how accurately it identifies fake images (by comparing predictions to a target value of 0).
+Together, these loss components ensure that the Discriminator improves its classification performance, which in turn challenges the Generator to produce increasingly realistic images.

### 2025-03-18 Phase_II/draft/II.tex
edit by Prof. Sarangi

@@
 Hanbury Brown and Robert Q.
-Twiss (HBT) carried out the first experiments demonstrating the possibility of measuring angular diameter of stars using Intensity Interferometry (II) in optical wavelengths \citep{HBT56}.
-Subsequently, they also pioneered the theoretical background of II and conducted laboratory experiments \citep{brown1957interferometry,brown1958interferometry},thereby further consolidating II as an alternative method, besides the already established Michelson Interferometry, to measure stars.
-Further, HBT also successfully installed the Narrabri Stellar Intensity Interferometer \textcolor{blue}{during the 1960s-70s and successfully used it to measure the angular diameters of bright stars in the spectral range $\mathrm{O5f}\ -\ \mathrm{F8}$ using visible wavelengths} signals \citep{brown1974intensity}.
-\\\textcolor{blue}
-{However, the available speed and sensitivity of electronics in the 1970s was not favourable for more extensive and larger scale measurement projects using II.}
+Twiss (HBT) carried out the first experiments demonstrating the feasibility of measuring the angular diameters of stars using Intensity Interferometry (II) in optical wavelengths \citep{HBT56}.
+Subsequently, they pioneered the theoretical framework of II and conducted laboratory experiments \citep{brown1957interferometry,brown1958interferometry}, further establishing II as an alternative method to the already established Michelson Interferometry for stellar measurements.
+Furthermore, HBT installed the Narrabri Stellar Intensity Interferometer during the 1960s–70s and used it to measure the angular diameters of bright stars in the spectral range $\mathrm{O5f}\ -\ \mathrm{F8}$ using visible wavelength signals \citep{brown1974intensity}.
+However, the speed and sensitivity of electronics available in the 1970s were not sufficient for more extensive and large-scale II measurement projects.
 
-\textcolor{blue}{Subsequently, during the opening decades of the current century, proposals to use the Imaging Atmospheric Cherenkov Telescope (IACT) facilities for carrying out Stellar Intensity Interferometry (SII) observations were put forth \citep{LeBohec2006, nunez2010stellar, nunez2012high, Dravins2013}.
-Such observations, it was suggested, could be carried out during bright moon-lit nights during which $\gamma$-ray observations using upper atmospheric Cherenkov showers were not feasible.
-This idea had the potential of enhancing the scientific output of the existing facilities like VERITAS, MAGIC and HESS.
-Subsequent SII obserations at these facilities providing the proof of concept have been published \citep{abeysekara2020demonstration, Abe2024MAGIC, Zmija2023}.
-}
+In the early decades of the current century, proposals emerged to utilize Imaging Atmospheric Cherenkov Telescope (IACT) facilities for conducting Stellar Intensity Interferometry (SII) observations \citep{LeBohec2006, nunez2010stellar, nunez2012high, Dravins2013}.
+It was suggested that such observations could be carried out during bright, moonlit nights when $\gamma$-ray observations based on upper atmospheric Cherenkov showers were not feasible.
+This approach had the potential to enhance the scientific output of existing facilities such as VERITAS, MAGIC, and HESS.
+Subsequent SII observations at these facilities, providing proof of concept, have been published \citep{abeysekara2020demonstration, Abe2024MAGIC, Zmija2023}.
 
-\textcolor{blue}{In the remaining part of this section, we present a brief conceptual procedure of how an array of Cherenkov telescopes is used to carry out II observations and generate Signal-to-Noise Ratio (SNR) from these observations.}
+The remainder of this section presents a brief conceptual overview of how an array of Cherenkov telescopes is used to perform II observations and derive the Signal-to-Noise Ratio (SNR) from these measurements.
 
 \subsection{The signal for II}\label{sec:signal}
-As a simple example, let us consider the pair of IACTs.
-Let us imagine that the two telescopes are pointed to a star.
-Let them simultaneously measure the intensity of radiation $I_1(t)$ a  and $I_2(t)$ respectively.
-These signals from the respective detectors are cross-correlated and averaged over time and yield the \textcolor{blue}{second order ($n=2$) correlation of these intensities as}  \citep{acciari2020optical, dravins2013optical}
+As a simple example, let us consider a pair of IACTs pointed at a star.
+Suppose the two telescopes simultaneously measure the intensity of radiation $I_1(t)$ and $I_2(t)$, respectively.
+The signals from these detectors are cross-correlated and averaged over time, yielding the second order ($n=2$) correlation of these intensities as \citep{acciari2020optical, dravins2013optical}
 \begin{equation}
@@
 \end{equation}
-where $\tau$ is the time delay between the telescopes.
-\st{If the light source is chaotic and randomly polarized,}\textcolor{blue}{For a spatially coherent and randomly polarized light, eq.(\ref{eqn:HBT}) reduces to the Siegert relation \citep{acciari2020optical}}
+where $\tau$ is the time delay between the telescopes. For spatially coherent and randomly polarized light, eq.(\ref{eqn:HBT}) reduces to the Siegert relation \citep{acciari2020optical}.
 \begin{equation}
@@
 \end{equation}
-where, $\Delta f$ is the electronic bandwidth \textcolor{blue}{of the photon detectors (that measure the intensities and typically lie in range $\sim 100 {\mathrm {MHz}}$)} and $\Delta {\mathrm {\nu}}$ is the optical bandwidth of radiation over which the intensities are measured.\footnote{\textcolor{blue}{Typically, filters with bandwidths in the range $\Delta \lambda \sim 20 nm - 50 nm$ corresponding to $\Delta \nu \sim 10^{15}$ Hz are used.}} In eq.(\ref{eqn:HBT2}), $V_{12}$, referred to as the complex visibility fuction, is the Fourier transform of the source brightness distribution and is given by
+where $\Delta f$ is the electronic bandwidth of the photon detectors (which measure the intensities and typically operate in the range $\sim 100 {\mathrm {MHz}}$) and $\Delta {\mathrm {\nu}}$ is the optical bandwidth of the radiation over which the intensities are measured.\footnote{Typically, filters with bandwidths in the range $\Delta \lambda \sim 20,\mathrm{nm} - 50,\mathrm{nm}$, corresponding to $\Delta \nu \sim 10^{15}$ Hz, are used.} In eq.(\ref{eqn:HBT2}), $V_{12}$, referred to as the complex visibility function, is the Fourier transform of the source brightness distribution and is given by
 \begin{equation}
@@
 \end{equation}
-where $\theta$ is the angular diameter of the star and d is the radial coordinate in the usual interferometric $(u , v) = (x/\lambda, y/\lambda)$ plane with the optical wavelength $\lambda$ of the filter used in observation.
-It is obvious from eqn(\ref{eqn:absvisib}) that $V_{12}$ carries the information of the angular diameter of the star.
-However, the phase information is lost \st{due to the involvement of the absolute value of $V_{12}$}\textcolor{blue}{as we measure the absolute value $\vert V_{12} \vert^2$}.
+where $\theta$ is the angular diameter of the star and $d$ is the radial coordinate in the conventional interferometric $(u , v) = (x/\lambda, y/\lambda)$ plane, with $\lambda$ representing the optical wavelength of the filter used for observation.
+It is evident from eqn(\ref{eqn:absvisib}) that $V_{12}$ contains information about the star's angular diameter.
+However, the phase information is lost since we measure only the absolute value $\vert V_{12} \vert^2$.
 In observational astronomy, the correlation is often expressed in terms of the normalized contrast, given by:
@@
 \end{equation}
-where, $\left\langle I_1 \right\rangle$ and $\left\langle I_2 \right\rangle$ are the mean intensity from two telescopes.
-So, the signal measured by electronic bandwidth  $\Delta f$ of photon detector of II in the optical bandwidth of observational radiation $\Delta {\mathrm {\nu}}$ is
+where, $\left\langle I_1 \right\rangle$ and $\left\langle I_2 \right\rangle$ denote the mean intensities from the two telescopes.
+Therefore, the signal measured by the photon detector in II, operating with an electronic bandwidth $\Delta f$ within the optical bandwidth $\Delta {\mathrm {\nu}}$ of the observational radiation, is
 \begin{equation}
@@
 \end{equation}
-$\abs{V_{12}}^2$ is a function of baseline $d = \sqrt{u^2 + v^2}$ on observational plane. So the strength of the signal is increased using large number of baselines.
+$\abs{V_{12}}^2$ is a function of baseline $d = \sqrt{u^2 + v^2}$ on observational plane. Consequently, the strength of the signal is enhanced by employing a large number of baselines.
 
-\textcolor{red}{Insert text (may be one more paragraph) to extend the expression for $g^{(2)}$ or $c$ to include the signals from more number of baselines.
-This will be important because we are considering a set of 4 IACTs in our model and therefore 6 baselines.}
+%%%%%%%%%%%%%%My commnets (Block-1 of 4) starts here%%%%
+\textcolor{red}{Considering a set of 4 IACTs in our model, there are 6 unique baselines available for measurement.
+Consequently, the overall correlation, denoted as $g^{(2)}$ (or equivalently, the normalized contrast $c$), can be extended to incorporate the signals from all these baselines.
+For example, if $c_{ij}$ represents the correlation measured between telescope $i$ and telescope $j$, the total correlation can be expressed as an average over the 6 baselines:}
+\begin{equation}
+g^{(2)} = \frac{1}{6}\sum_{i<j} c_{ij}
+\end{equation}
+\textcolor{red}{Alternatively, if the signal contributions from each baseline are weighted by a factor $w_{ij}$ to account for differences in baseline length or noise characteristics, the overall correlation can be written as:}
+\begin{equation}
+g^{(2)} = \frac{1}{6}\frac{\sum_{i<j} w_{ij} c_{ij}}{\sum_{i<j} w_{ij}}
+\end{equation}
+\textcolor{red}{This averaging process not only increases the effective signal strength by combining data from multiple baselines, but also improves the overall signal-to-noise ratio, thereby enhancing the reliability of the reconstructed image.
+The redundancy provided by the additional baselines helps mitigate the impact of noise and systematic errors, leading to a more robust determination of the source's brightness distribution.
+}
+%%%%%%%%%%%%My comments Block-1 of 4) ends here%%%%%%%%%%
 
@@
 \end{figure*}
-The primary purpose of IACTs is the study of high energy gamma rays (with energy $E\ \geq 30$ GeV) reaching the Earth from cosmic sources, entering the Earth's atmosphere and seeding the Cherenkov showers in the upper atmosphere due to multiple scattering.
-These telescopes have an array of mirrors that focus the light onto a set of photo-multiplier tubes (PMTs) \cite{aleksic2016major}.
-\textcolor{blue}{In the simulation model adopted here, a set of four IACTs with similar properties each are considered.
+The primary purpose of IACTs is to study high-energy gamma rays (with energy $E\ \geq 30$ GeV) arriving from cosmic sources, entering the Earth's atmosphere, and initiating Cherenkov showers in the upper atmosphere due to multiple scattering.
+These telescopes feature an array of mirrors that focus light onto a set of photo-multiplier tubes (PMTs) \cite{aleksic2016major}.
+In the simulation model adopted here, we consider a set of four IACTs, each with similar properties.
 The positional configuration of these IACTs is shown in fig.~\ref{fig:teles}.
-The optical signal guided into a PMT is filtered using a spectral filter with chosen mean observational wavelength $\lambda$ and corresponding bandpass $\Delta \lambda$.
-Use of filters helps in not only reducing back ground noise, but in improving the signal quality and the efficiency of the PMTs also.
-Filtering background sky light becomes even more significant in II observations as these observations are carried out around full moon nights.
-Needless to mention that light of the stellar source is focused on the PMT during the II observations.}
+The optical signal directed to a PMT is filtered using a spectral filter with a chosen mean observational wavelength $\lambda$ and corresponding bandpass $\Delta \lambda$.
+The use of filters not only reduces background noise but also improves the signal quality and the efficiency of the PMTs.
+Filtering background skylight becomes even more significant in II observations, as these are carried out during full moon nights.
+It is important to note that the light from the stellar source is focused on the PMT during II observations.
 
-The significance of the signal can be expressed as the signal-to-noise ratio (SNR), which depends on many factors.
-However, most importantly, it does not depend on optical bandwidth $\Delta {\mathrm {\nu}}$ of radiation for two telescope correlation.
-The explanation of independence of SNR from  $\Delta {\mathrm {\nu}}$ is given in the end of subsection 4.1 of \cite{10.1093/mnras/stab2391}.
+The significance of the signal can be expressed in terms of the signal-to-noise ratio (SNR), which depends on many factors.
+However, most importantly, it does not depend on the optical bandwidth $\Delta {\mathrm {\nu}}$ of the radiation for a two-telescope correlation.
+The explanation for the independence of the SNR from $\Delta {\mathrm {\nu}}$ is provided at the end of subsection 4.1 of \cite{10.1093/mnras/stab2391}.
 \begin{equation}
@@
 \end{equation}
-here, $A$ is the total mirror area, $\alpha$ the quantum efficiency of the PMTs, $q$ the quantum efficiency of the remaining optics, and $n$ the differential photon flux from the source.
-The excess noise factor of the PMTs is accounted with $F$, $T$ denotes the observation time, and $\sigma$ is the normalized spectral distribution of the light (including filters) \cite{acciari2020optical}.
-The signal (S) and noise (N) can be understand using eqns.\ref{eq:signal} and \ref{eq:SNR} as
+Here, $A$ is the total mirror area, $\alpha$ is the quantum efficiency of the PMTs, $q$ is the quantum efficiency of the remaining optics, and $n$ is the differential photon flux from the source.
+The excess noise factor of the PMTs is represented by $F$, $T$ denotes the observation time, and $\sigma$ is the normalized spectral distribution of the light (including filters) \cite{acciari2020optical}.
+The signal (S) and noise (N) can be understood using eqns.\ref{eq:signal} and \ref{eq:SNR} as:
 \begin{equation}
@@
 \begin{equation}
-	N = (A \cdot \alpha \cdot q \cdot n \cdot F \cdot \sigma \cdot \Delta \nu)^{-1}\sqrt{\frac{2 \Delta f}{T}}
+	N = (A \cdot \alpha \cdot q \cdot n \cdot F \cdot \sigma \cdot \Delta \nu)^{-1}\sqrt{\frac{2 \Delta f}{T}}.
 \end{equation}
-While most of the parameters can be optimized with hardware, the only way to obtain a better SNR is to increase the observation time T with fixed telescopes.
+While most of the parameters can be optimized with hardware, the only way to achieve a better SNR with fixed telescopes is to increase the observation time $T$.
 
+%%%%%%%%%%%%%%%%My Comment Text (Block 2 of 4) begins%%%%%%%%%
 \textcolor{red}{Points to be discussed: 
@@
 \end{itemize}}
+%%%%%%%%%%%%%%%%%My Comments Text (Block 2 of 4 ends here)%%%%
+
 \subsection{Baseline considerations}
-The measurement of the size of stellar objects through absolute visibility depends on the distance between the telescopes, which is called the baseline $d$. 
+The measurement of the size of stellar objects via absolute visibility depends on the distance between the telescopes, known as the baseline $d$.
 \begin{equation}
@@
 \end{equation}
-\textcolor{blue}{For achieving a good SNR with a given telescope configuration, the largest possible observational plane that can be covered is always desirable \citep{acciari2020optical, abeysekara2020demonstration}.}
-\begin{comment}
-{\st{However, this work needs a good SNR value for high precision of measurement, so the large covered observational plane with telescopes is a necessity for II \citep{acciari2020optical, abeysekara2020demonstration}.} }
-\end{comment}
+For achieving a good SNR with a given telescope configuration, covering the largest possible observational plane is always desirable \citep{acciari2020optical, abeysekara2020demonstration}.
 If the source is at the zenith, the coordinates in the Fourier plane ($u,v$) are given by:
@@
 \end{equation}
-where $d_E$ and $d_N$ are the baselines expressed in north and east coordinates. 
-\textcolor{blue}{But not all sources are at the zenith, and the telescopes are stationary and may also have different relative altitudes $d_A$ depending on the available terrain.
-Therefore, the Earth's rotation needs to be factored in for covering the maximum observational plane through the rotated baselines.
-For a given stellar source with declination $\delta$, hour-angle $h$ observed by telescopes at latitude $l$, equation (\ref{eq:baseline_rot}) provides the rotated
-baselines for a given pair of telescopes \citep{dravins2013optical, saha2020theory}
+where $d_E$ and $d_N$ are the baselines expressed in east and north coordinates.
+However, not all sources are at the zenith, and the telescopes are stationary and may also have different relative altitudes $d_A$ depending on the available terrain.
+Therefore, the Earth's rotation must be taken into account to cover the maximum observational plane using rotated baselines.
+For a given stellar source with declination $\delta$ and hour-angle $h$, as observed by telescopes at latitude $l$, equation (\ref{eq:baseline_rot}) provides the rotated baselines for a given pair of telescopes \citep{dravins2013optical, saha2020theory}.
 \begin{equation}
@@
 \end{equation}
-}
-%\end{comment}
-\begin{comment}
-\st{
-Equation (\ref{eq:baseline_rot}), which traces an ellipse for every pair of telescopes.
-Furthermore, the different altitudes $B_A$ of the telescopes must be considered \cite{dravins2013optical, saha2020theory}.
-\begin{equation}
-	\begin{pmatrix} u\\ v\\ w\\ \end{pmatrix} = R_x(\delta) \cdot R_y(h) \cdot R_x(-l) \begin{pmatrix} d_N\\ d_E\\ d_A\\ \end{pmatrix}
-	\label{eq:baseline_rot}
-\end{equation}
-here, $\delta$ is the declination and $h$ is the hour angle of the stellar source, and $l$ is the latitude of the telescopes.}
-\end{comment}
+
 The three rotation matrices $R_i$ correspond to the fundamental representation of the SO(3) group \cite{saha2020theory}.
-Fig.~\ref{fig:base} shows the track of six baselines generated from the telescopes (fig.~\ref{fig:teles}) due to Earth's rotation.
+Fig.\ref{fig:base} shows the track of six baselines generated from the telescopes (fig.\ref{fig:teles}) due to Earth's rotation.
 Since every pair of telescopes traces an ellipse in the Fourier plane, the total number of ellipses scales as follows:
@@
 where $N_T$ is the number of telescopes considered.
-As the number of baselines increases non-linearly, II benefits greatly from a large number of telescopes.
+As the number of baselines increases non-linearly, Intensity Interferometry (II) benefits greatly from a large number of telescopes.
 The planned Cherenkov Telescope Array (CTA) will cover the maximum observational plane and provide insight into stellar objects with optical wavelengths in the future.
 
-\subsection{An Object: Fast Rotating Stars}
+\subsection{A Fast Rotating Star: The Object in Our Instance}
 In our work presented here, we simulate a single fast-rotating star to test image reconstruction using a GAN.
-Fast rotation causes stars to take on an oblate shape, flattening at the poles and bulging at the equator due to the existence of stronger centrifugal force \cite{von1924radiative, 1999A&A...347..185M}.
-Fig.~\ref{fig:image} shows one of the simulations of such a fast-rotating star, \st{where the star takes on an elliptical shape} with brightness distributed across its surface.
-The brightness is at its maximum at the poles and minimum at the equator, a phenomenon known as gravity darkening \cite{lucy1967gravity}.
-This effect has been observed first through the interferometric and spectroscopic data from the CHARA Array for the fast-rotating star Regulus \cite{mcalister2005first}.
-Fast-rotating stars are crucial for understanding various astrophysical processes, including stellar evolution, structure, and \textcolor{red}{dynamics(???
-Can we be more elaborate here?)} over time.
+Fast rotation causes stars to adopt an oblate shape, flattening at the poles and bulging at the equator due to the stronger centrifugal force \cite{von1924radiative, 1999A&A...347..185M}.
+Fig.~\ref{fig:image} shows one of the simulations of such a fast-rotating star, with brightness distributed across its surface.
+The brightness is highest at the poles and lowest at the equator, a phenomenon known as gravity darkening \cite{lucy1967gravity}.
+This effect was first observed through interferometric and spectroscopic data from the CHARA Array for the fast-rotating star Regulus \cite{mcalister2005first}.
+Fast-rotating stars are crucial for understanding various astrophysical processes, including stellar evolution, internal structure, and dynamical behavior over time.
 
-Intensity Interferometry measures/counts photons arriving at the telescopes from the stellar object.
-The correlation of these photon arrivals at the telescopes results in squared visibility (explained in subsection.\ref{sec:signal}).
-According to Van Cittert Zernike's theorem, this signal is the Fourier transform of brightness distribution in the sky.
-Fig.~\ref {fig:ft} shows represents the Fourier Transform of the source shown in fig.~\ref{fig:image} using II on linear and logarithmic scale.
-\sout
-{However, we do not have an existing technique to observe the complete signals, and we could capture some parts of it only with a one-night simulation, which has been shown in fig.~\ref{fig:ft_base}.
-It is the covered observational plane using the baselines shown in fig.~\ref{fig:teles}.
-However, the upcoming CTA promises to cover the maximum observational plane for stellar objects.}
-\textcolor{blue}{In order to observe a real stellar source in the sky, however, we would need to receive photons from each point on the surface of the source.
-This would require infinite number of baselines observing the source over a long enough duration.
-This demand is obviously not feasible.
-We have finite number of baselines corresponding to the finite number $N_T$ of telescopes at our disposal and finitely budgeted observation schedule.
-Therefore, as a pilot, what we have attempted in this work is to simulate the II observation of a sky source over one night duration.
-Using this finite amount of signal of one night's observation, we have attempted to train a Generative Adversarial Network (GAN) to construct the image of the source.}
+Intensity Interferometry measures (or counts) the photons arriving at the telescopes from the stellar object.
+The correlation of these photon arrivals at the telescopes yields the squared visibility (explained in subsection.\ref{sec:signal}).
+According to Van Cittert Zernike's theorem, this signal is the Fourier transform of the brightness distribution in the sky.
+Fig.\ref{fig:ft} represents the Fourier Transform of the source shown in fig.\ref{fig:image} using II, displayed on both linear and logarithmic scales.
+In order to observe a real stellar source, however, one would need to receive photons from every point on the surface of the source, which would require an infinite number of baselines observing the source over a sufficiently long duration—an obviously unfeasible demand.
+In practice, we have a finite number of baselines corresponding to the finite number $N_T$ of telescopes at our disposal and a limited observation schedule.
+Therefore, as a pilot, we have simulated the II observation of a sky source over one night's duration.
+Using this finite amount of signal from one night's observation, we have trained a Generative Adversarial Network (GAN) to construct the image of the source.
 
-\textcolor{red}{My comments: Suppose we do more simulations with say 8 and 16 telescopes covering the effective ground area, but obviously with 28 and 120 baselines respectively.
+%%%%%%%%%%%%%%%%%%%My comments (Block 4 of 4) starts%%%%%%%%%%
+\textcolor{red}{My comments: Suppose we do more simulations with say 8 and 16 telescopes covering the same effective ground area, but obviously with more (28 and 120 to be exact) baselines respectively.
 We can then, perhaps, evolve/suggest some kind of measure (or scale) of quality in resultant image reconstruction with number of telescopes.
@@
 {\bf How much more computationally expensive would it become?}}
+%%%%%%%%%%%%%%%%%%My comments (Block 4 of 4) end here%%%%%%%%%

### 2025-03-18 Phase_II/draft/Result.tex
edit by Prof. Sarangi

--- 2024-12-09 Phase_II/draft/Result.tex
@@
 \section{The Reconstructed Image with GAN}
-
-In this section, we will first discuss phase retrieval using hyperparameters, as mentioned earlier, followed by an analysis where multiple sources are trained simultaneously.
-The best performance for image reconstruction has been observed with a learning rate of $2 \cdot 10^{-4}$, a kernel size of 5x5, and equal noise percentages in original and generated images.
-The batch size selected is 1, and the Discriminator-Generator receives equal training.
+In this section, we begin by discussing phase retrieval using hyperparameters, as mentioned earlier, followed by an analysis in which multiple sources are trained simultaneously.
+The best performance for image reconstruction has been observed with a learning rate of \(2 \cdot 10^{-4}\), a kernel size of 5×5, and equal noise percentages applied to both the original and generated images.
+A batch size of 1 is used, and equal training is provided to both the Discriminator and the Generator.
 
 \subsection{The Predicted Image with Trained GAN}
-The success of the GAN in training the model for Intensity Interferometry to reconstruct images of fast-rotating stars is demonstrated in Fig.~\ref{fig:GAN}.
-The GAN was trained on training datasets for 60,000 steps.
-After training, the GAN was tested on different validation datasets, producing predicted images of a fast-rotating star.
-Fig.~\ref{fig:GAN} presents a set of four combined images demonstrating the GAN's performance in reconstructing the shape, size, and brightness distribution of the fast-rotating star using II.
-The left panel shows the signals covered by six baselines, which serve as the input for the Generator to train the GAN.
-The first middle panel displays the real image, or ground truth, which the Discriminator uses to differentiate between real and generated images from the Generator.
-During training, the GAN aims to mimic these ground truth images.
-The second middle panel depicts the reconstructed image, or predicted image, produced by the trained GAN.
-This panel illustrates the success of the GAN in image reconstruction using II.
-The right panel shows the difference between the ground truth and the predicted image.
-This difference should be minimized for high-precision image reconstruction with the application of GAN on II.
-The predicted images of Fig.~\ref{fig:GAN} showed positive results.
-It accurately provides visual information about the source's size, shape, and brightness distribution over the surface.
-It is achieved here using only six baselines.
-However, the results can be further improved by increasing the number of telescopes to cover maximum (u, v) planes, making the existing and upcoming Cherenkov Telescope Array Observatory (CTAO) an ideal candidate.
-
+Figure~\ref{fig:GAN} demonstrates the success of the GAN in training a model for Intensity Interferometry (II) to reconstruct images of fast-rotating stars.
+The GAN was trained on the training datasets for 60,000 steps and subsequently tested on various validation datasets to produce predicted images of a fast-rotating star.
+In Fig.~\ref{fig:GAN}, four combined images illustrate the GAN's performance in reconstructing the star’s shape, size, and brightness distribution using II.
+\begin{itemize}
+\item{The left panel shows the signals collected from six baselines, which serve as the input for the Generator during training.}
+\item{The first middle panel displays the real image, or ground truth, which the Discriminator uses to distinguish between real images and those generated by the Generator.
+During training, the GAN aims to replicate these ground truth images.}
+\item{The second middle panel presents the reconstructed, or predicted, image produced by the trained GAN, highlighting its success in image reconstruction.}
+\item{The right panel shows the difference between the ground truth and the predicted image, with a smaller difference indicating higher precision in image reconstruction.}
+\end{itemize}
+The predicted images in Fig.~\ref{fig:GAN} yield positive results, accurately conveying visual information about the source's size, shape, and brightness distribution across its surface using only six baselines.
+However, further improvements can be achieved by increasing the number of telescopes to maximize coverage of the (u, v) plane, making the existing and upcoming Cherenkov Telescope Array Observatory (CTAO) an ideal candidate for this approach.
 \subsection{Evaluation of GAN using Moments}
-The reconstructed images are good enough visually to claim the success of GAN in reconstructing the image using II.
-However, there is a need for statistical evaluation of this predicted image to guarantee success.
-So, we use image moments as a statistical method.
-Image moments are statistical properties that provide information about the reconstructed shape, size, and intensity distribution of the objects in the image.
-These moments help to quantify key features like the position, orientation, and distribution of brightness in the image, allowing for an objective evaluation of how well the predicted image corresponds to the actual object.
-We will analyze the consistency and accuracy of the GAN-generated image by comparing its moments to those of the ground truth.
-It provides a reliable framework for evaluating reconstruction quality, as image moments highlight the subtle differences in geometric and intensity properties that might not be visually apparent.
+The reconstructed images are visually compelling, demonstrating the GAN's effectiveness in using II to reconstruct images.
+However, visual assessment alone is insufficient; statistical evaluation is necessary to rigorously validate the results.
+To achieve this, we employ image moments as a statistical method.
+Image moments capture key properties of the reconstructed objects—such as shape, size, and intensity distribution—by quantifying features like position, orientation, and brightness distribution.
+By comparing the moments of the GAN-generated images to those of the ground truth, we can objectively assess the consistency and accuracy of the reconstruction.
+This approach provides a reliable framework for evaluating reconstruction quality, as image moments can reveal subtle differences in geometric and intensity properties that might not be apparent through visual inspection alone.
 
@@
 
-The zeroth order raw moment called the monopole is the total intensity of an image.
-It sums up all the pixel values across the image, providing an overall intensity value.
-So, the study of monopole provides the total flux of fast-rotating stars here.
-According to eqn.~\ref{eqn:Mom}, the monopole of an image is calculated as
+The zeroth order raw moment, known as the monopole, represents the total intensity of an image.
+It is computed by summing all pixel values across the image, yielding an overall intensity measure.
+In this context, analyzing the monopole provides the total flux of fast-rotating stars.
+According to eqn.~\ref{eqn:Mom}, the monopole of an image is calculated as:
 \begin{equation}
@@
 \end{equation}
-Fig.~\ref{fig:mom1} shows the monopole for 50 different reconstructed images.
-It shows the linear behavior for the monopole between the ground truth (the real image) along the x-axis and the predicted image (reconstructed image) along the y-axis, which is obvious for different shape-size sources.
-This result explains the similarity between the total intensity of both images.
-It ensures that the predicted image has the approximately correct total brightness (the flux) compared to the ground truth.
-However, monopole does not explain the position, shape, size, and brightness distribution of fast-rotating stars; there is a need for higher-order moments.
-
+Figure~\ref{fig:mom1} displays the monopole values for 50 reconstructed images.
+The plot reveals a linear relationship between the monopole of the ground truth (real image) on the x-axis and that of the predicted (reconstructed) image on the y-axis, consistent across sources of varying shapes and sizes.
+This linearity confirms that the predicted images have an overall intensity (flux) that closely matches the ground truth.
+However, while the monopole effectively represents the total brightness, it does not provide information about the position, shape, size, or detailed brightness distribution of the fast-rotating stars.
+For these aspects, higher-order moments are necessary.
+%%%%%%%%%%%%%%This is original %%%%%%%%%%%%%%%%%%%%%
+%To be decided%%%%%%%
 The center of mass for the fast-rotating star or any other stellar object is calculated using the centroid (x-centroid and y-centroid).
@@
 The clustering of centroids in a given scale range for all the results explains that the reconstructed image correctly represents the spatial location of the fast-rotating star compared with the ground truth.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Further, these calculated centroids will help to study the shape, size, and brightness distribution of fast-rotating stars in terms of higher-order image moments.
-For that, the central moment of an image is calculated according to
+%%%%%%%%%%This portion is generated by ChatGPT%%%%%%%%%%
+%%%%To be decided depending on Nitu's reply%%%%
+
+The center of mass of a fast-rotating star, or any stellar object, is determined by its centroid, which provides the x and y coordinates representing the spatial position of the image.
+This centroid is computed using the first-order raw moments in conjunction with the monopole (the zeroth-order moment).
+The formulations for the centroid along the x and y directions are given by:
+\begin{eqnarray}
+&&x_c = \frac{M_{10}}{M_{00}} = \frac{\sum_{x,y} x \cdot I(x,y)}{\sum_{x,y} I(x,y)} \nonumber \\
+&&y_c = \frac{M_{01}}{M_{00}} = \frac{\sum_{x,y} y \cdot I(x,y)}{\sum_{x,y} I(x,y)}
+\end{eqnarray}
+Here, \(I(x,y)\) represents the intensity at pixel \((x,y)\), \(M_{00}\) is the monopole (total intensity), and \(M_{10}\) and \(M_{01}\) are the first-order raw moments along the x and y axes, respectively.
+This formulation accurately captures the spatial center of mass of the stellar object in the image.
+
+Fig.~\ref{fig:mom2} and Fig.~\ref{fig:mom3} compare the centroids ($x_{c}$, $y_{c}$)of 50 predicted images with their corresponding ground truths, respectively.
+The clustering of centroids within a specific scale range across all results indicates that the reconstructed images accurately represent the spatial location of the fast-rotating star relative to the ground truth.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Furthermore, these calculated centroids are instrumental in analyzing the shape, size, and brightness distribution of fast-rotating stars using higher-order image moments.
+To this end, the central moment of an image is calculated according to:
 \begin{equation}
-	\mu_{pq} = \frac{1}{M_{00}}\sum_{x} \sum_{y} (x - m_x)^p (y - m_y)^q I(x, y).
+	\mu_{pq} = \frac{1}{M_{00}}\sum_{x} \sum_{y} (x - x_c)^p (y - y_c)^q I(x, y).
 \end{equation}
-The sum of $p$ and $q$ defines the order of the central moment.
+The sum of \(p\) and \(q\) defines the order of the central moment.
 
-The second order central moment ($\mu_{11}, \mu_{20}, \mu_{02}$) has been shown in Fig.~\ref{fig:struc}, which is used to study the structure of a fast-rotating star along the line of sight of observation (explain in upcoming subsection).
-All these three plots explain the linear relation of second-order moments again as for monopole and show the success of the application of GAN to reconstruct the image with II.
+Figure~\ref{fig:struc} presents the second-order central moments (\(\mu_{11}, \mu_{20}, \mu_{02}\)), which are used to study the structure of a fast-rotating star along the line of sight (as explained in the upcoming subsection).
+All three plots demonstrate a linear relationship in the second-order moments, similar to the monopole, thereby confirming the success of applying the GAN to reconstruct images with II.
 
-The information on brightness distribution is gathered using the skewness of the image by calculating third-order central moment ($\mu_{30}, \mu_{03}, \mu_{21}, \mu_{12}$) of images.
-Fig.~\ref{fig:moments} shows all third-order moments for the ground truth and reconstructed image.
-The skewness along the x and y axis ($\mu_{30}, \mu_{03}$) to test the GAN for II are acceptable, which can be seen in Fig.~\ref{fig:mom7} and Fig.~\ref{fig:mom8}, where a linear relation exists between ground truth and predicted image.
-However, the remaining higher moments $(\mu_{21}, \mu_{12})$ shown in Fig.~\ref{fig:mom9} and Fig.~\ref{fig:mom10} are not in good terms specially $\mu_{12}$.
-Further improvement is possible and needs to be studied.
+The brightness distribution is characterized by the skewness of the image, which is quantified by calculating the third-order central moments (\(\mu_{30}, \mu_{03}, \mu_{21}, \mu_{12}\)).
+Figure~\ref{fig:moments} presents all third-order moments for both the ground truth and the reconstructed image.
+The skewness along the x and y axes (\(\mu_{30}\) and \(\mu_{03}\)) appears acceptable, as shown in Fig.~\ref{fig:mom7} and Fig.~\ref{fig:mom8}, where a linear relationship exists between the ground truth and predicted images.
+However, the other higher-order moments (\(\mu_{21}\) and \(\mu_{12}\))—particularly \(\mu_{12}\), as depicted in Fig.~\ref{fig:mom9} and Fig.~\ref{fig:mom10}—do not align as well.
+This indicates that further improvement is possible and should be investigated.
 
-\subsection{The Reconstructed Parameters for Object}
-The centroids $(m_x, m_y)$ represent the center of the fast-rotating star and spatial location on the image only.
-However, the calculated second-order central moment defines the orientation, semi-major axis, and eccentricity with respect to the center of the source \citep{teague1980image}.
-These parameters based on the moments fully describe the two-dimensional ellipse that fits the image data.
+\subsection{The reconstructed Parameters for object}
+The centroids \((x_c, y_c)\) indicate only the center of the fast-rotating star and its spatial location in the image.
+In contrast, the second-order central moments determine the orientation, semi-major axis, and eccentricity relative to the source's center \citep{teague1980image}.
+These moment-based parameters fully describe the two-dimensional ellipse that fits the image data.
 
@@
 \end{equation}
-The semi-major and semi-minor axis of the stellar object will be calculated with the help of second-order central moment again and denoted as a and b here, respectively
+The semi-major and semi-minor axes of the stellar object are computed using the second-order central moments and are denoted as \(a\) and \(b\), respectively.
 \begin{equation}
@@
 \end{equation}
-With the help of the axis value, the eccentricity of the fast-rotating star is calculated as
+Using the calculated axis values, the eccentricity of the fast-rotating star is determined as:
 \begin{equation}
@@
 \end{equation}
-Eqns.~\ref{eqn:orn}-\ref{eqn:eccen} depending on values explains the elliptical nature of the stellar object (here, fast-rotating star) and provides information on shape and size.
-However, the information about the brightness distribution is gathered using skewness, which can be understood using third and higher-order moments.
+Equations~\ref{eqn:orn}-\ref{eqn:eccen} describe the elliptical nature of the stellar object (in this case, a fast-rotating star) and provide information on its shape and size, depending on the computed values.
+In contrast, the brightness distribution is characterized by skewness, which is quantified using third and higher-order moments.

### 2025-03-18 Phase_II/draft/intro.tex
edit by Prof. Sarangi

--- 2024-10-16 Phase_II/draft/intro.tex
@@
 
-Intensity Interferometry (II) emerged in the 1970s as a groundbreaking technique for measuring the diameters, orbits, and limb-darkening coefficients of 32 stars in single/binary star systems.
-Despite these significant achievements, the method did not gain widespread adoption due to the then-required highly sensitive photon detectors and sophisticated data analysis techniques.
-However, advancements in computational methods and modern electronics, which now offer time resolution of detectors in the nanoseconds (ns) range, have renewed II as a feasible technique in comparison to the limitation of amplitude interferometry for resolving astrophysical objects at visible wavelengths.
-Current simulations with ns resolution of photon detectors show that II is effective in achieving high precision measurement of parameters for stellar objects \citep{10.1093/mnras/stab2391, 10.1093/mnras/stac2433}.
-However, despite these technological advancements, II faces a significant limitation in terms of phase loss and the absence of complete reconstruction of the brightness distribution of stellar sources.
+Intensity Interferometry (II) was first reported by Hanbury Brown and Twiss (HBT) during the 1950s \citep{brown1954lxxiv, HBT56} as a \textquotedblleft new type of interferometry\textquotedblright\ to measure stellar parameters such as angular diameter, orbits, and limb darkening coefficients.
+Later, theoretical results reported by \cite{brown1957interferometry, brown1958interferometry}, along with those of \cite{glauber1963quantum} and \cite{MandelWolf1995, Hecht2002}, demonstrated the deeper physical properties of photon correlations that lie at the core of II and laid the foundation for Quantum Optics.
 
-Several theoretical and computational approaches to phase reconstruction with II have been proposed.
-\cite{gamo1963triple} introduced the concept of triple-intensity correlation, which \cite{goldberger1963use} further applied in an experiment to observe scattered particles in microscopic systems.
+By the 1970s, with stellar parameter measurements of 32 stars in single and multiple star systems conducted by Hanbury Brown and his collaborators \citep{hanbury1974angular} at the historic Narrabri Stellar Intensity Interferometer (NSII) in Australia, II had emerged as an alternative technique for measuring stellar parameters.
+Despite these significant achievements, the method did not gain widespread adoption in the ensuing decades, primarily due to the unavailability of sensitive photon detectors and advanced data analysis equipment.
+
+However, subsequent advancements in computational methods and modern electronics—which now provide detectors with time resolutions in the nanosecond (ns) to picosecond (ps) range—have revived II as a feasible technique for resolving astrophysical objects at visible wavelengths.
+Recent advancements in photon detectors show that II could be effective in achieving high-precision measurements of parameters for stellar objects \citep{10.1093/mnras/stab2391, 10.1093/mnras/stac2433}.
+
+Beyond measuring the physical parameters of star systems, a fundamental goal of optical astronomy is to determine the sky intensity distribution of a source from ground-based observations.
+In the context of II, this involves reconstructing the source's image from the intensity correlations recorded by pairs of telescopes (light buckets) on the ground.
+However, because the primary observable in II is the electromagnetic field intensity rather than the field strength, a significant drawback of this method is the loss of phase information.
+Since a complete reconstruction of a source's brightness distribution requires phase information, the challenge is to recover the phase of the signal.
+
+Several theoretical and computational approaches for phase reconstruction with II have been proposed.
+\cite{gamo1963triple} introduced the concept of triple-intensity correlation, which Goldberger subsequently applied \cite{goldberger1963use} in an experiment to observe scattered particles in microscopic systems.
 Sato conducted experiments to measure the diameter and phase of asymmetrical objects, suggesting that triple correlation could extend II to image stellar bodies \citep{sato1978imaging, sato1979computer, sato1981adaptive}.
-Despite its potential, the sensitivity of the signal to noise poses a significant challenge for this approach.
+However, achieving a satisfactory signal-to-noise ratio (SNR) remained a significant challenge for this approach.
 
-Later \cite{holmes2010two} proposed an alternative method, utilizing the Cauchy-Riemann relations to reconstruct 1-D images and extending this to 2-D images across a range of signal-to-noise (SNR) values.
-This algorithm was applied to simulated data of stellar objects using II, considering existing and forthcoming Imaging Cherenkov Telescope Arrays (ICTAs) with a large number of telescopes \citep{nunez2010stellar, nunez2012high, nunez2012imaging}.
-Despite these theoretical advances, practical application to actual observational data of stellar objects with II has yet to be achieved.
-There is a need to advance this field by introducing a novel image reconstruction technique.
+Gerchberg and Saxton suggested an iterative method \citep{GerchbergSaxton1972} to determine the phase from the image and diffraction plane pictures.
+This method relies on accurate initial estimates and may struggle with slow convergence otherwise.
+Fienup \citep{Fienup1982} introduced a Hybrid Input-Output algorithm that incorporates feedback mechanisms to improve convergence rate and robustness, particularly in noisy environments.
 
-Currently, artificial intelligence (AI) is applied to high-volume data to reduce human computing resources and time effort.
-New analysis techniques using Machine Learning (ML) applications on observed data are playing at the front to reveal the astronomical mystery.
-In radio morphologies, the supervised and unsupervised algorithm is used to distinguish the radio components from the infrared source \citep{wu2019radio, galvin2020cataloguing}.
-Recently, the image reconstruction of the M87 black hole using Generative Adversarial Networks (GANs) has been performed \citep{10.1093/mnras/stad3797}.
-There is also a need to introduce the application of ML to II data, which will aim to overcome the limitations of image reconstruction and provide high-resolution optical astronomy.
+Later, \cite{holmes2010two} proposed an alternative method that utilizes the Cauchy-Riemann relations to reconstruct 1-D images and extends the approach to 2-D images across a range of signal-to-noise (SNR) values.
+This algorithm was applied to simulated data of stellar objects using II, considering both existing and forthcoming Imaging Cherenkov Telescope Arrays (IACTs) with a large number of telescopes \citep{nunez2010stellar, nunez2012high, nunez2012imaging}.
+However, this method faces challenges related to computational complexity when attempting to generalize to higher dimensions.
 
-In this paper, we propose an alternative approach for image reconstruction of stellar objects with II using GAN \citep{goodfellow2014generative}.
-We consider four ICTAs and perform a one-night simulation for a fast-rotating star.
-The predicted image by a trained GAN shows promising results for reconstructing the image's shape and size.
-Image moments evaluate the predicted image and demonstrate that the size and shape of the fast-rotating star are reconstructed.
-However, the brightness distribution recovers only up to the third-order moment.
-We expect even greater precision of image reconstruction by including more telescopes, especially to recover the higher-order image moments.
-It holds great promise, pushing the boundaries of high-resolution optical astronomy and opening up new possibilities for studying stellar objects with remarkable detail.
+Li et al.
+suggested a flexible iterative Regularization method \citep{Li2014} that incorporates prior information (e.g., sparsity, smoothness, or non-negativity) to reduce the ill-posedness of the phase retrieval problem.
+This method is more robust against noise and stabilizes the solution against artefacts and spurious solutions.
+Nevertheless, it faces challenges regarding the choice of the regularization parameter, computational complexity, and sensitivity to the initial guess.
 
-This paper is organized as follows: The first section discusses Intensity Interferometry following its signal and noise for fast-rotating stars along the Earth's rotation.
+The Transport-of-Intensity Equation (TIE) method is a non-interferometric technique first proposed by Teague \citep{Teague1983} that relates the intensity variations along the optical axis to the phase of the optical fields.
+This method enables phase retrieval from intensity measurements taken at multiple planes.
+Zhang et al.
+\citep{Zhang2020} proposed a method to obtain a \textquotedblleft universal solution\textquotedblright\ to the TIE by employing a \textquotedblleft maximum intensity assumption\textquotedblright, thereby converting the TIE into a Poisson equation which is then solved iteratively.
+More recently, Kirisits et al.
+\citep{Kirisits2024} explored hybrid methods that combine the TIE with other equations, such as the Transport of Phase Equation (TPE).
+These approaches leverage the strengths of both equations to improve phase retrieval accuracy.
+This method is universally applicable, as it works for arbitrarily shaped apertures, handles non-uniform illumination, and accommodates inhomogeneous boundary conditions.
+It guarantees convergence, although the speed of convergence depends on the quality of the initial guess, and the final results are influenced by the boundary conditions.
+
+\textcolor{magenta}{With non-linearity built into their architecture, artificial neural networks (ANNs) empowered by deep learning methods have become an obvious choice for exploring the task of reconstructing images of stellar objects from ground-based observations.
+Convolutional Neural Networks (CNNs), with their specialized architecture for processing two-dimensional datasets, are a natural choice for image processing tasks.
+In astronomical image reconstruction projects, a common challenge is that the ground-truth data are often noisy, incomplete, or both.
+Therefore, the CNN architectures and deep learning methods employed must be capable of reliably learning both the global context of the training dataset and the local features within it.
+Among the various CNN architectures, U-Net models \citep{ronneberger2015u} have proven successful in such tasks.}
+
+\textcolor{magenta}{Furthermore, given that achieving a high signal-to-noise ratio (SNR) is often challenging in astronomical datasets, it is immensely beneficial if additional data can be generated using the available information from the observed sky density distribution and ground-based observations (II data, in our case) of the sources under investigation.
+Generative Adversarial Networks (GANs), introduced by Ian Goodfellow et al.
+\citep{goodfellow2014generative}, have been successful in data augmentation tasks.
+Conditional GAN (cGAN) architectures, proposed by Mirza \& Osindero \citep{mirza2014conditional} and applied to a wide variety of datasets by Isola et al.
+\citep{isola2017image}, leverage additional information about the images in the training datasets and have demonstrated remarkable robustness in image recovery across diverse data types.}
+
+\textcolor{magenta}{In the astrophysical context, Schawinski et al.
+\cite{schawinski2017galaxypics} employed a cGAN model to recover features—such as spiral arms, central bulges, and disk structures—of galaxies from noise-affected images.
+Mustafa et al.
+\citep{mustafa2019cosmogan} developed and customized a Deep Convolutional GAN, dubbed \textquotedblleft CosmoGAN\textquotedblright, capable of generating high-fidelity weak-lensing convergence maps of the dark matter distribution that statistically reproduce real weak lensing structures.
+Coccomini et al.
+\citep{coccomini2021lightweightgan} have successfully generated credible images of planets, nebulae, and galaxies using \textquotedblleft lightweight\textquotedblright\ and \textquotedblleft physics-uninformed\textquotedblright\ GANs to produce synthetic images of celestial bodies.
+They also generated a \textquotedblleft Hubble Deep Field-inspired\textquotedblright\ wide-view simulation of the universe.
+}
+
+In this paper, we propose a conditional Generative Adversarial Network (cGAN) model \citep{isola2017image} to reconstruct images of fast-rotating stars using their simulated Intensity Interferograms and simulated sky-intensity distributions as input data for training, testing, and validation.
+We consider four Imaging Cherenkov Telescope Arrays (IACTs) located in the Northern Hemisphere and perform a one-night simulation of a fast-rotating star.
+The image predicted by the trained GAN shows promising results in reconstructing the star’s shape and size.
+The evaluation, conducted using image moments, demonstrates that the size and shape are successfully recovered, although the brightness distribution is reconstructed only at the third-order moment.
+
+This paper is organized as follows.
+The first section discusses Intensity Interferometry, focusing on its signal and noise characteristics for fast-rotating stars along the Earth’s rotation.
 The second section introduces the GAN formulation and its structure.
-The third section details the parameter selection for training the GAN to reconstruct the image.
-After that, the fourth section presents the results of trained GAN visually and using image moments.
-At the end, there is a conclusion of the entire result.
+The third section details the parameter selection for training the GAN for image reconstruction.
+The fourth section presents the results of the trained GAN both visually and via image moments.
+Finally, the paper concludes with a discussion of the overall results.

### 2025-03-20 Phase_II/draft/II.tex
edit by Prof. Sarangi

@@
 $\abs{V_{12}}^2$ is a function of baseline $d = \sqrt{u^2 + v^2}$ on observational plane. Consequently, the strength of the signal is enhanced by employing a large number of baselines.
-
-%%%%%%%%%%%%%%My commnets (Block-1 of 4) starts here%%%%
-\textcolor{red}{Considering a set of 4 IACTs in our model, there are 6 unique baselines available for measurement.
-Consequently, the overall correlation, denoted as $g^{(2)}$ (or equivalently, the normalized contrast $c$), can be extended to incorporate the signals from all these baselines.
-For example, if $c_{ij}$ represents the correlation measured between telescope $i$ and telescope $j$, the total correlation can be expressed as an average over the 6 baselines:}
-\begin{equation}
-g^{(2)} = \frac{1}{6}\sum_{i<j} c_{ij}
-\end{equation}
-\textcolor{red}{Alternatively, if the signal contributions from each baseline are weighted by a factor $w_{ij}$ to account for differences in baseline length or noise characteristics, the overall correlation can be written as:}
-\begin{equation}
-g^{(2)} = \frac{1}{6}\frac{\sum_{i<j} w_{ij} c_{ij}}{\sum_{i<j} w_{ij}}
-\end{equation}
-\textcolor{red}{This averaging process not only increases the effective signal strength by combining data from multiple baselines, but also improves the overall signal-to-noise ratio, thereby enhancing the reliability of the reconstructed image.
-The redundancy provided by the additional baselines helps mitigate the impact of noise and systematic errors, leading to a more robust determination of the source's brightness distribution.
-}
-%%%%%%%%%%%%My comments Block-1 of 4) ends here%%%%%%%%%%
 
@@
 
-%%%%%%%%%%%%%%%%My Comment Text (Block 2 of 4) begins%%%%%%%%%
-\textcolor{red}{Points to be discussed: 
-\begin{itemize}
-\item{Should/Can the final expression for SNR in eq.(\ref{eq:SNR}) be written in terms of $\rho(\tau)$ of eq.(\ref{eqn:pearson}) or $c$ (\ref{eq:norm_contrast2}) in stead of $\vert V_{12}\vert^2$?}
-\item{It would be better to generalize the eq.(\ref{eq:norm_contrast2}) to include the signals from all the baseline pairs.}
-\end{itemize}}
-%%%%%%%%%%%%%%%%%My Comments Text (Block 2 of 4 ends here)%%%%
-
 \subsection{Baseline considerations}
@@
 Using this finite amount of signal from one night's observation, we have trained a Generative Adversarial Network (GAN) to construct the image of the source.
-
-%%%%%%%%%%%%%%%%%%%My comments (Block 4 of 4) starts%%%%%%%%%%
-\textcolor{red}{My comments: Suppose we do more simulations with say 8 and 16 telescopes covering the same effective ground area, but obviously with more (28 and 120 to be exact) baselines respectively.
-We can then, perhaps, evolve/suggest some kind of measure (or scale) of quality in resultant image reconstruction with number of telescopes.
-May be some form of ratios of the SNRs would provide a good comparison.
-{\bf How much more computationally expensive would it become?}}
-%%%%%%%%%%%%%%%%%%My comments (Block 4 of 4) end here%%%%%%%%%

### 2025-03-20 Phase_II/draft/intro.tex
edit by Prof. Sarangi

@@
 
-\textcolor{magenta}{With non-linearity built into their architecture, artificial neural networks (ANNs) empowered by deep learning methods have become an obvious choice for exploring the task of reconstructing images of stellar objects from ground-based observations.
+With non-linearity built into their architecture, artificial neural networks (ANNs) empowered by deep learning methods have become an obvious choice for exploring the task of reconstructing images of stellar objects from ground-based observations.
 Convolutional Neural Networks (CNNs), with their specialized architecture for processing two-dimensional datasets, are a natural choice for image processing tasks.
@@
 Therefore, the CNN architectures and deep learning methods employed must be capable of reliably learning both the global context of the training dataset and the local features within it.
-Among the various CNN architectures, U-Net models \citep{ronneberger2015u} have proven successful in such tasks.}
+Among the various CNN architectures, U-Net models \citep{ronneberger2015u} have proven successful in such tasks.
 
-\textcolor{magenta}{Furthermore, given that achieving a high signal-to-noise ratio (SNR) is often challenging in astronomical datasets, it is immensely beneficial if additional data can be generated using the available information from the observed sky density distribution and ground-based observations (II data, in our case) of the sources under investigation.
+Furthermore, given that achieving a high signal-to-noise ratio (SNR) is often challenging in astronomical datasets, it is immensely beneficial if additional data can be generated using the available information from the observed sky density distribution and ground-based observations (II data, in our case) of the sources under investigation.
 Generative Adversarial Networks (GANs), introduced by Ian Goodfellow et al.
@@
 Conditional GAN (cGAN) architectures, proposed by Mirza \& Osindero \citep{mirza2014conditional} and applied to a wide variety of datasets by Isola et al.
-\citep{isola2017image}, leverage additional information about the images in the training datasets and have demonstrated remarkable robustness in image recovery across diverse data types.}
+\citep{isola2017image}, leverage additional information about the images in the training datasets and have demonstrated remarkable robustness in image recovery across diverse data types.
 
-\textcolor{magenta}{In the astrophysical context, Schawinski et al.
+In the astrophysical context, Schawinski et al.
 \cite{schawinski2017galaxypics} employed a cGAN model to recover features—such as spiral arms, central bulges, and disk structures—of galaxies from noise-affected images.
@@
 They also generated a \textquotedblleft Hubble Deep Field-inspired\textquotedblright\ wide-view simulation of the universe.
-}
 

### 2025-03-20 Phase_II/draft/main.tex
edit by Prof. Sarangi

@@
 \begin{abstract}
-In current astronomy, the simulation of Intensity Interferometry is demonstrating significant advancements in the high-precision resolution of stellar objects at optical wavelengths.
-Despite these achievements, phase retrieval remains challenging due to photon correlation.
-This paper proposes the application of a conditional Generative Adversarial Network (GAN) to address this issue of image reconstruction with Intensity Interferometry.
-Here, the GAN effectively reconstructs the shape, size, and brightness distribution of a fast-rotating star by utilizing sparsely sampled, phase-subtracted Fourier transforms of the star.
-This innovative approach promises to enhance the capabilities of Intensity Interferometry for image reconstruction in addition to estimating the parameters with high precision in astronomical observations.
+In modern astronomy, simulations of Intensity Interferometry are making significant strides in achieving high-precision resolution of stellar objects at optical wavelengths.
+Despite these advancements, phase retrieval remains a major challenge due to the nature of photon correlation.
+This paper explores the application of a conditional Generative Adversarial Network (GAN) to tackle the problem of image reconstruction in Intensity Interferometry.
+The proposed GAN-based approach effectively reconstructs the shape, size, and brightness distribution of a fast-rotating star by leveraging sparsely sampled, phase-subtracted Fourier transforms of the source.
+This method not only enhances the image reconstruction capabilities of Intensity Interferometry but also enables precise parameter estimation in astronomical observations.
 \end{abstract}

### 2025-04-29 Phase_II/draft/II.tex
edits

@@
 Suppose the two telescopes simultaneously measure the intensity of radiation $I_1(t)$ and $I_2(t)$, respectively.
-The signals from these detectors are cross-correlated and averaged over time, yielding the second order ($n=2$) correlation of these intensities as \citep{acciari2020optical, dravins2013optical}
+The signals from these detectors are cross-correlated and averaged over time, yielding the second order ($n=2$) correlation of these intensities as \citep[cf.~][]{acciari2020optical, dravins2013optical}
 \begin{equation}
@@
 \end{equation}
-where $\tau$ is the time delay between the telescopes. For spatially coherent and randomly polarized light, eq.(\ref{eqn:HBT}) reduces to the Siegert relation \citep{acciari2020optical}.
+where $\tau$ is the time delay between the telescopes.
+For spatially coherent and randomly polarized light, eq.~(\ref{eqn:HBT}) reduces to the relation \citep[sometimes called the Siegert relation, see e.g.~][]{acciari2020optical}.
 \begin{equation}
@@
 \end{equation}
-where $\Delta f$ is the electronic bandwidth of the photon detectors (which measure the intensities and typically operate in the range $\sim 100 {\mathrm {MHz}}$) and $\Delta {\mathrm {\nu}}$ is the optical bandwidth of the radiation over which the intensities are measured.\footnote{Typically, filters with bandwidths in the range $\Delta \lambda \sim 20,\mathrm{nm} - 50,\mathrm{nm}$, corresponding to $\Delta \nu \sim 10^{15}$ Hz, are used.} In eq.(\ref{eqn:HBT2}), $V_{12}$, referred to as the complex visibility function, is the Fourier transform of the source brightness distribution and is given by
+where $\Delta f$ is the electronic bandwidth of the photon detectors (which measure the intensities.
+Values of $\Delta\nu\sim 1\,\mathrm{THz}$ and $\Delta f \sim 1\,\mathrm{GHz}$ are typical of recent work.
+In eq.~(\ref{eqn:HBT2}), $V_{12}$, referred to as the complex visibility function, is the Fourier transform of the source brightness distribution.
+For a uniform disk it is given by
 \begin{equation}
@@
 where $\theta$ is the angular diameter of the star and $d$ is the radial coordinate in the conventional interferometric $(u , v) = (x/\lambda, y/\lambda)$ plane, with $\lambda$ representing the optical wavelength of the filter used for observation.
-It is evident from eqn(\ref{eqn:absvisib}) that $V_{12}$ contains information about the star's angular diameter.
+It is evident from eq.~(\ref{eqn:absvisib}) that $V_{12}$ contains information about the star's angular diameter.
 However, the phase information is lost since we measure only the absolute value $\vert V_{12} \vert^2$.
@@
 Therefore, the Earth's rotation must be taken into account to cover the maximum observational plane using rotated baselines.
-For a given stellar source with declination $\delta$ and hour-angle $h$, as observed by telescopes at latitude $l$, equation (\ref{eq:baseline_rot}) provides the rotated baselines for a given pair of telescopes \citep{dravins2013optical, saha2020theory}.
+For a given stellar source with declination $\delta$ and hour-angle $h$, as observed by telescopes at latitude $l$, equation (\ref{eq:baseline_rot}) provides the rotated baselines for a given pair of telescopes \citep[see e.g., eqs.~8--10 from][]{2020MNRAS.498.4577B}.
 \begin{equation}
@@
 
-The three rotation matrices $R_i$ correspond to the fundamental representation of the SO(3) group \cite{saha2020theory}.
 Fig.\ref{fig:base} shows the track of six baselines generated from the telescopes (fig.\ref{fig:teles}) due to Earth's rotation.

### 2025-04-29 Phase_II/draft/conclusion.tex
edits

--- 2025-02-02 Phase_II/draft/conclusion.tex
@@
 \section{Conclusion}
-The challenge of phase retrieval in Intensity Interferometry (II) has been effectively addressed through the application of machine learning techniques, particularly with Generative Adversarial Networks (GANs).
-Our study demonstrates that using a GAN on II data successfully recovers the size, shape, and brightness distribution of a fast-rotating star.
-The evaluation based on image moments, specifically the monopole, second, and third-order moments, supports the effectiveness of the GAN in achieving accurate image reconstruction from a one-night observation using six baselines.
 
-A critical factor in the performance of the reconstruction process is the extent of Fourier plane coverage, which is determined by the number of available telescopes and the total observing time.
-The brightness distribution can likely be reconstructed with even higher precision with a full night of observation using four telescopes.
-Future work could explore different observatory layouts, such as the Southern Cherenkov Telescope Array (CTA) layout, to evaluate the impact on image reconstruction quality.
+However, II faces a significant drawback: it captures only the magnitude of the signal via photon correlation, resulting in a loss of phase information.
+This challenge of phase retrieval in II has been effectively addressed through machine learning techniques, particularly with conditional Generative Adversarial Networks (cGAN).
+Our study demonstrates that applying cGAN to II data successfully recovers the size, shape, and brightness distribution of a fast-rotating star.
+Evaluations based on image moments—specifically, the monopole, second, and third-order moments—support the effectiveness of cGAN in achieving accurate image reconstruction from a one-night simulation of II using six baselines.
+A critical factor in the reconstruction process is the extent of Fourier plane coverage, which depends on the number of available telescopes and the total observing time.
+With a full night of observation using four telescopes, the brightness distribution could be reconstructed with even greater precision.
+Future work might explore different observatory layouts to assess their impact on image reconstruction quality, such as integrating the Southern Cherenkov Telescope Array (CTA) with MAGIC.
 
-This study has not considered the detector efficiencies, which could influence the signal-to-noise ratio (SNR) in practical scenarios.
-Incorporating these efficiencies in future work will be important for providing a more accurate estimate of the SNR and the robustness of the GAN in real-world applications.
-
-While conditional GANs have proven effective in this study, there are other methods for generating images from image data.
-Exploring and comparing alternative methods, as well as adapting the GAN architecture itself, could offer improvements.
-For instance, different loss functions could be implemented and compared to potentially enhance reconstruction quality.
-Further testing is required to refine the GAN and make it more robust and reliable.
-However, our findings suggest that machine learning is a promising approach for phase reconstruction in II.
-
-In summary, while the current implementation shows strong potential, further exploration and refinement of machine learning models are needed to optimize their application in phase retrieval and image reconstruction in Intensity Interferometry.
+While the results of this study highlight the significant potential of machine learning—particularly cGAN—for image reconstruction in II, several aspects require further refinement.
+First, detector efficiencies, which impact the signal-to-noise ratio (SNR) of actual observational data, have not yet been incorporated; addressing these factors will be crucial for more accurate SNR estimation.
+Second, exploring and comparing alternative methods for image generation could reveal approaches that outperform cGAN in reconstructing stellar images with II.
+Third, experimenting with different loss functions could provide additional insights into reconstruction quality.
+Although further testing is needed to refine the GAN and enhance its robustness and reliability, our findings suggest that machine learning is a promising approach for phase reconstruction in II.

### 2025-04-29 Phase_II/draft/intro.tex
edits

@@
 
-Gerchberg and Saxton suggested an iterative method \citep{GerchbergSaxton1972} to determine the phase from the image and diffraction plane pictures.
+\cite{GerchbergSaxton1972} suggested an iterative method to determine the phase from the image and diffraction plane pictures.
 This method relies on accurate initial estimates and may struggle with slow convergence otherwise.
-Fienup \citep{Fienup1982} introduced a Hybrid Input-Output algorithm that incorporates feedback mechanisms to improve convergence rate and robustness, particularly in noisy environments.
+\citep{Fienup1982} introduced a Hybrid Input-Output algorithm that incorporates feedback mechanisms to improve convergence rate and robustness, particularly in noisy environments.
 
@@
 
-Li et al.
-suggested a flexible iterative Regularization method \citep{Li2014} that incorporates prior information (e.g., sparsity, smoothness, or non-negativity) to reduce the ill-posedness of the phase retrieval problem.
+\cite{Li2014} suggested a flexible iterative Regularization method that incorporates prior information (e.g., sparsity, smoothness, or non-negativity) to reduce the ill-posedness of the phase retrieval problem.
 This method is more robust against noise and stabilizes the solution against artefacts and spurious solutions.
@@
 
-The Transport-of-Intensity Equation (TIE) method is a non-interferometric technique first proposed by Teague \citep{Teague1983} that relates the intensity variations along the optical axis to the phase of the optical fields.
+The Transport-of-Intensity Equation (TIE) method is a non-interferometric technique first proposed by \cite{Teague1983} that relates the intensity variations along the optical axis to the phase of the optical fields.
 This method enables phase retrieval from intensity measurements taken at multiple planes.
-Zhang et al.
-\citep{Zhang2020} proposed a method to obtain a \textquotedblleft universal solution\textquotedblright\ to the TIE by employing a \textquotedblleft maximum intensity assumption\textquotedblright, thereby converting the TIE into a Poisson equation which is then solved iteratively.
-More recently, Kirisits et al.
-\citep{Kirisits2024} explored hybrid methods that combine the TIE with other equations, such as the Transport of Phase Equation (TPE).
+\cite{Zhang2020} proposed a method to obtain a \textquotedblleft universal solution\textquotedblright\ to the TIE by employing a \textquotedblleft maximum intensity assumption\textquotedblright, thereby converting the TIE into a Poisson equation which is then solved iteratively.
+More recently, \cite{Kirisits2024} explored hybrid methods that combine the TIE with other equations, such as the Transport of Phase Equation (TPE).
 These approaches leverage the strengths of both equations to improve phase retrieval accuracy.
@@
 Furthermore, given that achieving a high signal-to-noise ratio (SNR) is often challenging in astronomical datasets, it is immensely beneficial if additional data can be generated using the available information from the observed sky density distribution and ground-based observations (II data, in our case) of the sources under investigation.
-Generative Adversarial Networks (GANs), introduced by Ian Goodfellow et al.
-\citep{goodfellow2014generative}, have been successful in data augmentation tasks.
-Conditional GAN (cGAN) architectures, proposed by Mirza \& Osindero \citep{mirza2014conditional} and applied to a wide variety of datasets by Isola et al.
-\citep{isola2017image}, leverage additional information about the images in the training datasets and have demonstrated remarkable robustness in image recovery across diverse data types.
+Generative Adversarial Networks (GANs), introduced by \cite{goodfellow2014generative}, have been successful in data augmentation tasks.
+Conditional GAN (cGAN) architectures, proposed by \cite{mirza2014conditional} and applied to a wide variety of datasets by \cite{isola2017image}, leverage additional information about the images in the training datasets and have demonstrated remarkable robustness in image recovery across diverse data types.
 
@@
 \cite{schawinski2017galaxypics} employed a cGAN model to recover features—such as spiral arms, central bulges, and disk structures—of galaxies from noise-affected images.
-Mustafa et al.
-\citep{mustafa2019cosmogan} developed and customized a Deep Convolutional GAN, dubbed \textquotedblleft CosmoGAN\textquotedblright, capable of generating high-fidelity weak-lensing convergence maps of the dark matter distribution that statistically reproduce real weak lensing structures.
-Coccomini et al.
-\citep{coccomini2021lightweightgan} have successfully generated credible images of planets, nebulae, and galaxies using \textquotedblleft lightweight\textquotedblright\ and \textquotedblleft physics-uninformed\textquotedblright\ GANs to produce synthetic images of celestial bodies.
+\cite{mustafa2019cosmogan} developed and customized a Deep Convolutional GAN, dubbed \textquotedblleft CosmoGAN\textquotedblright, capable of generating high-fidelity weak-lensing convergence maps of the dark matter distribution that statistically reproduce real weak lensing structures.
+\cite{coccomini2021lightweightgan} have successfully generated credible images of planets, nebulae, and galaxies using \textquotedblleft lightweight\textquotedblright\ and \textquotedblleft physics-uninformed\textquotedblright\ GANs to produce synthetic images of celestial bodies.
 They also generated a \textquotedblleft Hubble Deep Field-inspired\textquotedblright\ wide-view simulation of the universe.

### 2025-04-29 Phase_II/draft/GAN.tex
edits

@@
 \section{Generative Adversarial Networks}
-In 2014, Ian Goodfellow introduced Generative Adversarial Networks (GANs).
+Generative Adversarial Networks (GANs) were introduced by \citep{goodfellow2014generative}.
 The underlying concept is straightforward: it involves two competing networks.
 The first network, known as the Generator, produces new images based on an input image.
-For consistency, images produced by the Generator will be referred to as generated images.
-The second network, the Discriminator, attempts to distinguish between the generated image (predicted image) and the real image (ground truth) \citep{goodfellow2014generative}.
+These will be referred to as generated images.
+The second network, the Discriminator, attempts to distinguish between the generated image (predicted image) and the real image (ground truth).
 
 Through the alternating training of these networks, the generated images gradually become indistinguishable from the real images.
-Essentially, this process constitutes a two-player min-max game — a classic problem in game theory.
+Essentially, this process constitutes a two-player min-max game --- a classic problem in game theory.
 The original formulation of GANs is given by:
@@
 We begin with input noise variables \(p_z(z)\) and employ two perceptrons, \(G(z; \theta_G)\) and \(D(x; \theta_D)\), parameterized by \(\theta_i\) with \(i = G \ \mathrm{or}\ D\) respectively.
-Here, \(G(z)\) is a differentiable function that maps \(z\) to the data space \(x\), while \(D(x)\) represents the probability that \(x\) originates from real data \cite{goodfellow2014generative}.
+Here, \(G(z)\) is a differentiable function that maps \(z\) to the data space \(x\), while \(D(x)\) represents the probability that \(x\) originates from real data.
 The problem can be reformulated as:
@@
 Furthermore, if both \(G\) and \(D\) are allowed to reach their respective optima, then \(p_G\) converges to \(p_{data}\).
-A more comprehensive discussion of the problem, including proofs, is provided in \citep{goodfellow2014generative}.
+A more comprehensive discussion of the problem, including proofs, is provided in \cite{goodfellow2014generative}.
 \begin{equation}
@@
 
-Subsequently, the GAN framework was extended to a conditional model \cite{mirza2014conditional}.
-In this formulation, both the Generator and the Discriminator receive additional information \(y\), and the value function of the conditional GAN (cGAN) is expressed as:
+Subsequently, the GAN framework was extended to a conditional model \citep{mirza2014conditional}.
+In this formulation, both the Generator and the Discriminator receive additional information $y$, and the value function of the conditional GAN (cGAN) is expressed as:
 \begin{equation}
@@
 
-Furthermore, \cite{isola2017image} observed that combining the cGAN from equation \ref{eq:conditional_GAN} with the traditional L1 loss improves the results, as the Generator is encouraged to produce outputs closer to the ground truth.
+\cite{isola2017image} further observed that combining the cGAN from equation \ref{eq:conditional_GAN} with the traditional L1 loss improves the results, as the Generator is encouraged to produce outputs closer to the ground truth.
 Hence, the function that is minimized is:
@@
 As discussed above, in a GAN the Generator is responsible for producing synthetic data—in this case, images that resemble those of a fast-rotating star.
-In this work, the Generator is implemented as a U-Net convolutional network \cite{ronneberger2015u}.
+In this work, the Generator is implemented as a U-Net convolutional network \citep{ronneberger2015u}.
 In such architectures, the image's spatial resolution is first reduced through downsampling and then restored via upsampling, resulting in a U-shaped structure.

### 2025-04-29 Phase_II/draft/II.tex
edits

@@
 \section{Intensity Interferometry (II) with IACT arrays}
-R.
-Hanbury Brown and Robert Q.
-Twiss (HBT) carried out the first experiments demonstrating the feasibility of measuring the angular diameters of stars using Intensity Interferometry (II) in optical wavelengths \citep{HBT56}.
-Subsequently, they pioneered the theoretical framework of II and conducted laboratory experiments \citep{brown1957interferometry,brown1958interferometry}, further establishing II as an alternative method to the already established Michelson Interferometry for stellar measurements.
-Furthermore, HBT installed the Narrabri Stellar Intensity Interferometer during the 1960s–70s and used it to measure the angular diameters of bright stars in the spectral range $\mathrm{O5f}\ -\ \mathrm{F8}$ using visible wavelength signals \citep{brown1974intensity}.
-However, the speed and sensitivity of electronics available in the 1970s were not sufficient for more extensive and large-scale II measurement projects.
 
-In the early decades of the current century, proposals emerged to utilize Imaging Atmospheric Cherenkov Telescope (IACT) facilities for conducting Stellar Intensity Interferometry (SII) observations \citep{LeBohec2006, nunez2010stellar, nunez2012high, Dravins2013}.
-It was suggested that such observations could be carried out during bright, moonlit nights when $\gamma$-ray observations based on upper atmospheric Cherenkov showers were not feasible.
-This approach had the potential to enhance the scientific output of existing facilities such as VERITAS, MAGIC, and HESS.
-Subsequent SII observations at these facilities, providing proof of concept, have been published \citep{abeysekara2020demonstration, Abe2024MAGIC, Zmija2023}.
-
-The remainder of this section presents a brief conceptual overview of how an array of Cherenkov telescopes is used to perform II observations and derive the Signal-to-Noise Ratio (SNR) from these measurements.
+This section presents a brief conceptual overview of how an array of telescopes is used to perform II observations, and explains the Signal-to-Noise Ratio (SNR) from these measurements.
 
@@
 Suppose the two telescopes simultaneously measure the intensity of radiation $I_1(t)$ and $I_2(t)$, respectively.
-The signals from these detectors are cross-correlated and averaged over time, yielding the second order ($n=2$) correlation of these intensities as \citep[cf.~][]{acciari2020optical, dravins2013optical}
+The signals from these detectors are cross-correlated and averaged over time, yielding the second order ($n=2$) correlation of these intensities as \citep[cf.][]{acciari2020optical, dravins2013optical}
 \begin{equation}
@@
 where $\tau$ is the time delay between the telescopes.
-For spatially coherent and randomly polarized light, eq.~(\ref{eqn:HBT}) reduces to the relation \citep[sometimes called the Siegert relation, see e.g.~][]{acciari2020optical}.
+For spatially coherent and randomly polarized light, eq.~(\ref{eqn:HBT}) reduces to the relation \citep[sometimes called the Siegert relation, see e.g.,][]{acciari2020optical}.
 \begin{equation}
@@
 \begin{equation}
- V_{12} = 2 \frac{J_1(2 \pi d \theta)}{(2 \pi d \theta)}
+ V_{12} = 2 \frac{J_1(\pi\theta_D b)}{(\pi\theta_D b)}
 \label{eqn:absvisib}
 \end{equation}
-where $\theta$ is the angular diameter of the star and $d$ is the radial coordinate in the conventional interferometric $(u , v) = (x/\lambda, y/\lambda)$ plane, with $\lambda$ representing the optical wavelength of the filter used for observation.
+where $\theta_D$ is the angular diameter of the star and $b$ is the radial coordinate in the conventional interferometric $(u , v) = (x/\lambda, y/\lambda)$ plane, with $\lambda$ representing the optical wavelength of the filter used for observation.
 It is evident from eq.~(\ref{eqn:absvisib}) that $V_{12}$ contains information about the star's angular diameter.
@@
 However, most importantly, it does not depend on the optical bandwidth $\Delta {\mathrm {\nu}}$ of the radiation for a two-telescope correlation.
-The explanation for the independence of the SNR from $\Delta {\mathrm {\nu}}$ is provided at the end of subsection 4.1 of \cite{10.1093/mnras/stab2391}.
+The explanation for the independence of the SNR from $\Delta {\mathrm {\nu}}$ is provided in several works \citep[e.g.,][subsection 4.1 of][]{10.1093/mnras/stab2391}.
+The Signal-to-Noise is given by
 \begin{equation}
@@
 \end{equation}
-Here, $A$ is the total mirror area, $\alpha$ is the quantum efficiency of the PMTs, $q$ is the quantum efficiency of the remaining optics, and $n$ is the differential photon flux from the source.
-The excess noise factor of the PMTs is represented by $F$, $T$ denotes the observation time, and $\sigma$ is the normalized spectral distribution of the light (including filters) \cite{acciari2020optical}.
+Here, $A$ is the total mirror area, $\alpha$ is the quantum efficiency of the PMTs, $q$ is the throughput of the remaining optics, and $n$ is the differential photon flux from the source.
+The excess noise factor of the PMTs is represented by $F$, $T$ denotes the observation time, and $\sigma$ is the normalized spectral distribution of the light (including filters) \citep[e.g.,][]{acciari2020optical}.
 The signal (S) and noise (N) can be understood using eqns.\ref{eq:signal} and \ref{eq:SNR} as:
@@
 \end{equation}
-For achieving a good SNR with a given telescope configuration, covering the largest possible observational plane is always desirable \citep{acciari2020optical, abeysekara2020demonstration}.
+For achieving a good SNR with a given telescope configuration, covering as much as possible of the interferometric plane is always desirable.
 If the source is at the zenith, the coordinates in the Fourier plane ($u,v$) are given by:
@@
 
-Fig.\ref{fig:base} shows the track of six baselines generated from the telescopes (fig.\ref{fig:teles}) due to Earth's rotation.
-Since every pair of telescopes traces an ellipse in the Fourier plane, the total number of ellipses scales as follows:
+Fig.~\ref{fig:base} shows the track of six baselines generated from the telescopes (Fig.~\ref{fig:teles}) due to the Earth's rotation.
+Since every pair of telescopes traces an ellipse in the Fourier plane, the total number of ellipses scales as
 \begin{equation}
 	\label{eq:N_telescopes}
-	\mathcal{N} = \frac{N_T \cdot (N_T -1)}{2}
+	\mathcal{N} = \tfrac12 N_T \cdot (N_T -1)
 \end{equation}
@@
 
-\subsection{A Fast Rotating Star: The Object in Our Instance}
+\subsection{Fast Rotating Stars: The Objects Considered}
 In our work presented here, we simulate a single fast-rotating star to test image reconstruction using a GAN.
-Fast rotation causes stars to adopt an oblate shape, flattening at the poles and bulging at the equator due to the stronger centrifugal force \cite{von1924radiative, 1999A&A...347..185M}.
+Fast rotation causes stars to adopt an oblate shape, flattening at the poles and bulging at the equator due to the stronger centrifugal force \citep[e.g.,][]{von1924radiative, 1999A&A...347..185M}.
 Fig.~\ref{fig:image} shows one of the simulations of such a fast-rotating star, with brightness distributed across its surface.
-The brightness is highest at the poles and lowest at the equator, a phenomenon known as gravity darkening \cite{lucy1967gravity}.
+The brightness is highest at the poles and lowest at the equator, a phenomenon known as gravity darkening \citep{lucy1967gravity}.
 This effect was first observed through interferometric and spectroscopic data from the CHARA Array for the fast-rotating star Regulus \cite{mcalister2005first}.
@@
 
-Intensity Interferometry measures (or counts) the photons arriving at the telescopes from the stellar object.
-The correlation of these photon arrivals at the telescopes yields the squared visibility (explained in subsection.\ref{sec:signal}).
-According to Van Cittert Zernike's theorem, this signal is the Fourier transform of the brightness distribution in the sky.
-Fig.\ref{fig:ft} represents the Fourier Transform of the source shown in fig.\ref{fig:image} using II, displayed on both linear and logarithmic scales.
-In order to observe a real stellar source, however, one would need to receive photons from every point on the surface of the source, which would require an infinite number of baselines observing the source over a sufficiently long duration—an obviously unfeasible demand.
-In practice, we have a finite number of baselines corresponding to the finite number $N_T$ of telescopes at our disposal and a limited observation schedule.
-Therefore, as a pilot, we have simulated the II observation of a sky source over one night's duration.
+Intensity Interferometry counts the photons arriving at the telescopes from the stellar object.
+The correlation of these photon arrivals at the telescopes yields the squared visibility (explained in subsection~\ref{sec:signal}).
+This signal is the Fourier transform of the brightness distribution in the sky.
+Fig.\ref{fig:ft} represents the Fourier Transform of the source shown in Fig.~\ref{fig:image} using II, displayed on both linear and logarithmic scales.
+In practice, only a small part of this information is available, because one has a finite number of baselines corresponding to the finite number $N_T$ of telescopes at our disposal and a limited observation schedule.
+Therefore, we have simulated the II observation of a sky source over one night.
 Using this finite amount of signal from one night's observation, we have trained a Generative Adversarial Network (GAN) to construct the image of the source.

### 2025-04-29 Phase_II/draft/Result.tex
edits

@@
-\section{The Reconstructed Image with GAN}
+\section{Images Reconstructed by the GAN}
 In this section, we begin by discussing phase retrieval using hyperparameters, as mentioned earlier, followed by an analysis in which multiple sources are trained simultaneously.
@@
 
-\subsection{The Predicted Image with Trained GAN}
+\subsection{Predicted Image from the Trained GAN}
 Figure~\ref{fig:GAN} demonstrates the success of the GAN in training a model for Intensity Interferometry (II) to reconstruct images of fast-rotating stars.
@@
 The predicted images in Fig.~\ref{fig:GAN} yield positive results, accurately conveying visual information about the source's size, shape, and brightness distribution across its surface using only six baselines.
-However, further improvements can be achieved by increasing the number of telescopes to maximize coverage of the (u, v) plane, making the existing and upcoming Cherenkov Telescope Array Observatory (CTAO) an ideal candidate for this approach.
+However, further improvements can be achieved by increasing the number of telescopes to maximize coverage of the $(u, v)$ plane, making the existing and upcoming Cherenkov Telescope Array Observatory (CTAO) an ideal candidate for this approach.
 \subsection{Evaluation of GAN using Moments}
@@
 
-The zeroth order raw moment, known as the monopole, represents the total intensity of an image.
+The zeroth order raw moment, or monopole, represents the total intensity of an image.
 It is computed by summing all pixel values across the image, yielding an overall intensity measure.

### 2025-04-29 Phase_II/draft/intro.tex
edits

@@
 Intensity Interferometry (II) was first reported by Hanbury Brown and Twiss (HBT) during the 1950s \citep{brown1954lxxiv, HBT56} as a \textquotedblleft new type of interferometry\textquotedblright\ to measure stellar parameters such as angular diameter, orbits, and limb darkening coefficients.
-Later, theoretical results reported by \cite{brown1957interferometry, brown1958interferometry}, along with those of \cite{glauber1963quantum} and \cite{MandelWolf1995, Hecht2002}, demonstrated the deeper physical properties of photon correlations that lie at the core of II and laid the foundation for Quantum Optics.
+Later, theoretical results reported by \cite{brown1957interferometry, brown1958interferometry}, along with those of \cite{glauber1963quantum} and others, demonstrated the deeper physical properties of photon correlations that lie at the core of II and laid the foundation for Quantum Optics \cite[for textbook treatments see][]{MandelWolf1995, Hecht2002}.
 
-By the 1970s, with stellar parameter measurements of 32 stars in single and multiple star systems conducted by Hanbury Brown and his collaborators \citep{hanbury1974angular} at the historic Narrabri Stellar Intensity Interferometer (NSII) in Australia, II had emerged as an alternative technique for measuring stellar parameters.
+By the 1970s, with stellar parameter measurements of 32 stars in single and multiple star systems conducted by Hanbury Brown and his collaborators \citep{hanbury1974angular} at the historic Narrabri Stellar Intensity Interferometer (NSII) in Australia, II had emerged as an alternative to the already established technique of Michelson Interferometry for measuring stellar parameters.
 Despite these significant achievements, the method did not gain widespread adoption in the ensuing decades, primarily due to the unavailability of sensitive photon detectors and advanced data analysis equipment.
 
-However, subsequent advancements in computational methods and modern electronics—which now provide detectors with time resolutions in the nanosecond (ns) to picosecond (ps) range—have revived II as a feasible technique for resolving astrophysical objects at visible wavelengths.
-Recent advancements in photon detectors show that II could be effective in achieving high-precision measurements of parameters for stellar objects \citep{10.1093/mnras/stab2391, 10.1093/mnras/stac2433}.
+More recently, proposals emerged to utilize Imaging Atmospheric Cherenkov Telescope (IACT) facilities for conducting II observations of stars \citep{LeBohec2006, nunez2010stellar, nunez2012high, Dravins2013}.
+It was suggested that such observations could be carried out during bright, moonlit nights when $\gamma$-ray observations based on upper atmospheric Cherenkov showers were not feasible.
+This approach had the potential to enhance the scientific output of existing facilities such as VERITAS, MAGIC, and HESS.
+Subsequent SII observations at these facilities are now appearing \citep{abeysekara2020demonstration, Abe2024MAGIC, Zmija2023}.
+Simulations \citep[e.g.,][]{10.1093/mnras/stab2391, 10.1093/mnras/stac2433} have argued that recent advancements in photon detectors could be effective in achieving high-precision measurements of parameters for stellar objects
 
@@
 Several theoretical and computational approaches for phase reconstruction with II have been proposed.
-\cite{gamo1963triple} introduced the concept of triple-intensity correlation, which Goldberger subsequently applied \cite{goldberger1963use} in an experiment to observe scattered particles in microscopic systems.
+\cite{gamo1963triple} introduced the concept of triple-intensity correlation, which \cite{goldberger1963use} subsequently applied in an experiment to observe scattered particles in microscopic systems.
 Sato conducted experiments to measure the diameter and phase of asymmetrical objects, suggesting that triple correlation could extend II to image stellar bodies \citep{sato1978imaging, sato1979computer, sato1981adaptive}.
@@
 This method relies on accurate initial estimates and may struggle with slow convergence otherwise.
-\citep{Fienup1982} introduced a Hybrid Input-Output algorithm that incorporates feedback mechanisms to improve convergence rate and robustness, particularly in noisy environments.
+\cite{Fienup1982} introduced a Hybrid Input-Output algorithm that incorporates feedback mechanisms to improve convergence rate and robustness, particularly in noisy environments.
 
@@
 
-With non-linearity built into their architecture, artificial neural networks (ANNs) empowered by deep learning methods have become an obvious choice for exploring the task of reconstructing images of stellar objects from ground-based observations.
+With non-linearity built into their architecture, artificial neural networks (ANNs) empowered by deep learning methods are promising for exploring the task of reconstructing images of stellar objects from ground-based observations.
 Convolutional Neural Networks (CNNs), with their specialized architecture for processing two-dimensional datasets, are a natural choice for image processing tasks.
@@
 
-In the astrophysical context, Schawinski et al.
-\cite{schawinski2017galaxypics} employed a cGAN model to recover features—such as spiral arms, central bulges, and disk structures—of galaxies from noise-affected images.
+In the astrophysical context, \cite{schawinski2017galaxypics} employed a cGAN model to recover features—such as spiral arms, central bulges, and disk structures—of galaxies from noise-affected images.
 \cite{mustafa2019cosmogan} developed and customized a Deep Convolutional GAN, dubbed \textquotedblleft CosmoGAN\textquotedblright, capable of generating high-fidelity weak-lensing convergence maps of the dark matter distribution that statistically reproduce real weak lensing structures.
@@
 In this paper, we propose a conditional Generative Adversarial Network (cGAN) model \citep{isola2017image} to reconstruct images of fast-rotating stars using their simulated Intensity Interferograms and simulated sky-intensity distributions as input data for training, testing, and validation.
-We consider four Imaging Cherenkov Telescope Arrays (IACTs) located in the Northern Hemisphere and perform a one-night simulation of a fast-rotating star.
+We consider four Imaging Cherenkov Telescope Arrays (IACTs) and simulation observation of a fast-rotating star.
 The image predicted by the trained GAN shows promising results in reconstructing the star’s shape and size.
-The evaluation, conducted using image moments, demonstrates that the size and shape are successfully recovered, although the brightness distribution is reconstructed only at the third-order moment.
+The reconstructed brightness distributions are then assessed using moments.
 
 This paper is organized as follows.
-The first section discusses Intensity Interferometry, focusing on its signal and noise characteristics for fast-rotating stars along the Earth’s rotation.
-The second section introduces the GAN formulation and its structure.
-The third section details the parameter selection for training the GAN for image reconstruction.
-The fourth section presents the results of the trained GAN both visually and via image moments.
+The next section discusses Intensity Interferometry, focusing on its signal and noise characteristics for fast-rotating stars along the Earth’s rotation.
+The following section introduces the GAN formulation and its structure.
+The fourth section details the parameter selection for training the GAN for image reconstruction.
+The fifth section presents the results of the trained GAN both visually and via image moments.
 Finally, the paper concludes with a discussion of the overall results.

### 2025-04-30 Phase_II/draft/conclusion.tex
edits

@@
 
-However, II faces a significant drawback: it captures only the magnitude of the signal via photon correlation, resulting in a loss of phase information.
-This challenge of phase retrieval in II has been effectively addressed through machine learning techniques, particularly with conditional Generative Adversarial Networks (cGAN).
+Intensity Interferometry (II) is re-emerging as a promising technique to overcome the challenges associated with Michelson Interferometry in the optical wavelength range.
+However, compared to radio-interferometry II faces a significant drawback: photon correlation captures only the magnitude of the interferometric signal, resulting in a loss of phase information.
+
+This work addresses the challenge of phase retrieval in II using a machine-learning technique, specifically a conditional Generative Adversarial Networks (cGAN).
 Our study demonstrates that applying cGAN to II data successfully recovers the size, shape, and brightness distribution of a fast-rotating star.
-Evaluations based on image moments—specifically, the monopole, second, and third-order moments—support the effectiveness of cGAN in achieving accurate image reconstruction from a one-night simulation of II using six baselines.
-A critical factor in the reconstruction process is the extent of Fourier plane coverage, which depends on the number of available telescopes and the total observing time.
-With a full night of observation using four telescopes, the brightness distribution could be reconstructed with even greater precision.
-Future work might explore different observatory layouts to assess their impact on image reconstruction quality, such as integrating the Southern Cherenkov Telescope Array (CTA) with MAGIC.
+Evaluations based on image moments—specifically, the monopole, second, and third-order moments—support the effectiveness of cGAN in achieving accurate image reconstruction from a simulation of II from a single site with four telescopes.
 
-While the results of this study highlight the significant potential of machine learning—particularly cGAN—for image reconstruction in II, several aspects require further refinement.
-First, detector efficiencies, which impact the signal-to-noise ratio (SNR) of actual observational data, have not yet been incorporated; addressing these factors will be crucial for more accurate SNR estimation.
-Second, exploring and comparing alternative methods for image generation could reveal approaches that outperform cGAN in reconstructing stellar images with II.
-Third, experimenting with different loss functions could provide additional insights into reconstruction quality.
+While the results of this study highlight the significant potential of machine learning, and in particular cGAN, for image reconstruction in II, several aspects require further refinement.
+First, an important factor in the reconstruction process is the extent of Fourier plane coverage, which depends on the number of available telescopes and the total observing time.
+With more than four telescopes, more complicated systems could be reconstructed.
+Future work might explore different observatory layouts to assess their impact on image reconstruction quality.
+Second, detector efficiencies, which impact the signal-to-noise ratio (SNR) of actual observational data, have not yet been incorporated; addressing these factors will be crucial for more accurate SNR estimation.
+Third, exploring and comparing alternative methods for image generation could reveal approaches that outperform cGAN in reconstructing stellar images with II.
+Fourth, experimenting with different loss functions could provide additional insights into reconstruction quality.
 Although further testing is needed to refine the GAN and enhance its robustness and reliability, our findings suggest that machine learning is a promising approach for phase reconstruction in II.

### 2025-04-30 Phase_II/draft/main.tex
edits

@@
 
-\title{Image reconstruction of stellar objects with Intensity Interferometry using Generative Adversarial Networks}
+\title{Generative AI for image reconstruction in Intensity Interferometry: a first attempt}
 \date{}
@@
 \begin{abstract}
-In modern astronomy, simulations of Intensity Interferometry are making significant strides in achieving high-precision resolution of stellar objects at optical wavelengths.
+In the last few years Intensity Interferometry has made significant strides in achieving high-precision resolution of stellar objects at optical wavelengths.
 Despite these advancements, phase retrieval remains a major challenge due to the nature of photon correlation.
-This paper explores the application of a conditional Generative Adversarial Network (GAN) to tackle the problem of image reconstruction in Intensity Interferometry.
-The proposed GAN-based approach effectively reconstructs the shape, size, and brightness distribution of a fast-rotating star by leveraging sparsely sampled, phase-subtracted Fourier transforms of the source.
-This method not only enhances the image reconstruction capabilities of Intensity Interferometry but also enables precise parameter estimation in astronomical observations.
+This paper explores the application of a conditional Generative Adversarial Network (cGAN) to tackle the problem of image reconstruction in Intensity Interferometry.
+This approach successfully reconstructs the shape, size, and brightness distribution of a fast-rotating star from sparsely sampled, spatial power spectrum of the source, corresponding to II with four telescopes.
+Although this particular example could also be addressed using parameter fitting, the results suggest that with larger arrays much more complicated systems could be reconstructed by applying machine-learning techniques to II.
 \end{abstract}

### 2025-04-30 Phase_II/draft/conclusion.tex
edits

@@
 
-Intensity Interferometry (II) is re-emerging as a promising technique to overcome the challenges associated with Michelson Interferometry in the optical wavelength range.
+Intensity Interferometry (II) is re-emerging as a promising technique to overcome the challenges of very long baseline interferometry in the optical wavelength range.
 However, compared to radio-interferometry II faces a significant drawback: photon correlation captures only the magnitude of the interferometric signal, resulting in a loss of phase information.

### 2025-05-07 Phase_II/draft/conclusion.tex
edits

@@
 Intensity Interferometry (II) is re-emerging as a promising technique to overcome the challenges of very long baseline interferometry in the optical wavelength range.
-However, compared to radio-interferometry II faces a significant drawback: photon correlation captures only the magnitude of the interferometric signal, resulting in a loss of phase information.
+However, compared to radio-interferometry, optical interferometry faces an important hurdle: photon correlation captures only the magnitude of the interferometric signal, resulting in a loss of phase information.
 

### 2025-05-07 Phase_II/draft/main.tex
authors

@@
 
+\author[Rai et al.]{Km Nitu Rai,$^{1,2}$ Yuri van der Burg,$^{3}$ Soumen Basak,$^{1}$ Prasenjit Saha,$^{3}$ and
+	Subrata Sarangi$^{4}$ \\ \\
+	$^{1}$School of Physics, Indian Institute of Science Education and Research Thiruvananthapuram, Maruthamala PO,
+	Vithura,\\ Thiruvananthapuram 695551, Kerala, India \\
+	$^{2}$Aryabhatta Research Institute of Observational Sciences, Manora Peak, Nainital 263129, India. \\
+	$^{3}$Physik-Institut, University of Zurich, Winterthurerstrasse 190, 8057 Zurich, Switzerland \\
+	$^{4}$School of Applied Sciences, Centurion University of Technology and Management, Odisha-752050, India.}
+
 \begin{document}

### 2025-05-14 Phase_II/draft/II.tex
edits

@@
 However, most importantly, it does not depend on the optical bandwidth $\Delta {\mathrm {\nu}}$ of the radiation for a two-telescope correlation.
-The explanation for the independence of the SNR from $\Delta {\mathrm {\nu}}$ is provided in several works \citep[e.g.,][subsection 4.1 of][]{10.1093/mnras/stab2391}.
+The explanation for the independence of the SNR from $\Delta {\mathrm {\nu}}$ is provided in several works \citep[e.g., subsection 4.1 of][]{10.1093/mnras/stab2391}.
 The Signal-to-Noise is given by

### 2025-05-28 Phase_II/draft/prev/ParaGan.tex
sync with overleaf today

\section{The Parameter for GAN Structure}

\begin{figure*}
	\centering
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/testing_image/image_0.png}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/testing_image/image_16.png}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/testing_image/image_35.png}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/testing_image/image_38.png}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/testing_image/image_42.png}
	\end{subfigure}
	\begin{subfigure}{\linewidth}
		\includegraphics[width=\linewidth]{fig/testing_image/image_47.png}
	\end{subfigure}
	\caption{This set of figures shows the result of GAN for II. The left panels are signals using six baselines, which work as input for GAN. The first middle panel is the real image, also called ground truth, and GAN tries to mimic it during the training. The second middle panel is the reconstructed image, also called the predicted image, with trained GAN, and the end panel is the difference between the ground truth and the predicted image.}
	\label{fig:GAN}
\end{figure*}
Here, we discuss the parameters of the GAN architecture used for reconstructing images of stellar objects using II. Given the adversarial nature of GANs—where the Generator and Discriminator engage in a min-max game—careful tuning of key parameters is critical to ensure that both networks are well-balanced for effective training.

\subsection{Data Preparation}
First, we simulate fast-rotating stars, modeling them as oblate spheroids with varying radii and an oblateness ranging between 0.5 and 1. We also consider different viewing angles, assuming a linear dependence for the effect of gravity darkening. The traced ellipses result from integrating over the source's hour angle. For hyperparameter tuning and comparing different telescopes, the total hour angle is set to approximately 11.5 hours. Finally, the ellipses are plotted, converted into grayscale images, resized, and stored as raw arrays to facilitate further analysis.
\begin{figure*}
	\centering
	\begin{subfigure}{0.33\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom0.png}
		\caption{The monopole.}
		\label{fig:mom1}
	\end{subfigure}\hfill
	\begin{subfigure}{0.33\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom1.png}
		\caption{The centroids along x direction.}
		\label{fig:mom2}
	\end{subfigure}\hfill
	\begin{subfigure}{0.33\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom2.png}
		\caption{The centroids along y direction.}
		\label{fig:mom3}
	\end{subfigure}\hfill
	\caption{This set of figures shows the comparison of monopole, x-centroid, and y-centroid for ground truth and predicted images generated by trained GAN.}
	\label{fig:cen}
\end{figure*}
\begin{figure*}
	\centering
	\begin{subfigure}{0.33\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom3.png}
		\caption{The 2nd order moment $\mu_{11}$.}
		\label{fig:mom4}
	\end{subfigure}\hfill
	\begin{subfigure}{0.33\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom4.png}
		\caption{The 2nd order moment $\mu_{20}$.}
		\label{fig:mom5}
	\end{subfigure}\hfill
	\begin{subfigure}{0.33\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom5.png}
		\caption{The 2nd order moment $\mu_{02}$.}
		\label{fig:mom6}
	\end{subfigure}\hfill
	\caption{The second-order central moments provide information about the size and shape of stellar objects. This set of figures shows all the second-order central moments for ground truth and predicted images generated by trained GAN.}
	\label{fig:struc}
\end{figure*}
\begin{figure*}
	\centering
	\begin{subfigure}{0.50\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom6.png}
		\caption{The 3rd order moment $\mu_{30}$.}
		\label{fig:mom7}
	\end{subfigure}\hfill
	\begin{subfigure}{0.50\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom7.png}
		\caption{The 3rd order moment $\mu_{03}$.}
		\label{fig:mom8}
	\end{subfigure}\hfill
	\begin{subfigure}{0.50\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom8.png}
		\caption{The 3rd order moment $\mu_{21}$.}
		\label{fig:mom9}
	\end{subfigure}\hfill
	\begin{subfigure}{0.50\linewidth}
		\includegraphics[width=\linewidth]{fig/moments/mom9.png}
		\caption{The 3rd order moment $\mu_{12}$.}
		\label{fig:mom10}
	\end{subfigure}\hfill
	\caption{This set of figures shows all the 3rd-order central moments for ground truth and predicted images generated by trained GAN. It calculates the skewness and evaluates the brightness distribution of images.}
	\label{fig:moments}
\end{figure*}

First, Salt and Pepper noise is introduced at a rate of \(\alpha\) (usually 0.5\%). Then, the images are resized and their mean is subtracted. A two-dimensional Fast Fourier Transform, along with a Fourier shift, is applied, yielding a complex number for each pixel. Since II does not measure phase, the absolute value is calculated (as shown in Fig.~\ref{fig:ft} on both linear and logarithmic scales for visualization).

Next, sparse sampling is introduced via pixel-wise multiplication between the absolute-valued Fourier-transformed image (Fig.~\ref{fig:ft}) and the sparse sampling map (Fig.~\ref{fig:base}). The result is a map in the Fourier plane featuring several ellipses, which is also referred to as the sparse sampling map (Fig.~\ref{fig:ft_base}). This map represents the sparse sampling for Fig.~\ref{fig:image}, corresponding to the source observed with four telescopes (Fig.~\ref{fig:teles}).

Finally, the pixels are normalized and converted to 8-bit integers. This image represents the sparsely sampled complex visibility as it can be measured with II. The image shown in Fig.~\ref{fig:ft_base} serves as the input for the GAN, which also requires the corresponding ground truth image. Consequently, the simulated stars are resized using the same algorithm and converted to 8-bit integers to reduce bias. The GAN must have access to the ground truth corresponding to each input image; therefore, the input and ground truth images are merged side-by-side (as shown in Fig.~\ref{fig:GANinput}) and used to train the GAN. This procedure is applied to all simulated stars, with 10\% used as test data, 10\% as validation data, and the remaining 80\% as training data.

\subsection{GAN Architecture}
The GAN used in this work is based on pix2pix, which utilizes a conditional GAN (cGAN) as discussed in the previous section \cite{isola2017image}. This architecture is highly robust and has already been applied to various problems. For instance, the TensorFlow tutorials\footnote{\url{https://www.tensorflow.org/tutorials/generative/pix2pix}} demonstrate its application to a dataset of architectural facades. However, to adapt the pix2pix GAN for the phase retrieval problem, some modifications are necessary. The network is implemented using the TensorFlow library \cite{abadi2016tensorflow}, calculations are performed with scipy \cite{virtanen2020scipy}, and plots are generated with matplotlib \cite{4160265}.

\subsection{Hyperparameter Tuning}
The GAN used in this work depends on several parameters, which are explained briefly below (for a more in-depth discussion, see \cite{murphy2022probabilistic}).

The learning rate of the optimizer determines how much the model updates its parameters with each iteration. A learning rate that is too small may lead to underfitting, while one that is too large can render the model unstable. Therefore, selecting an appropriate learning rate is crucial \cite{murphy2022probabilistic}. Figure~\ref{fig:Plot_learning_rate_loss} illustrates the effect of different learning rates on both the Generator and Discriminator losses. As expected, lower learning rates result in fewer outliers in the loss functions, indicating more stable updates. Although all models eventually stabilize at a similar level, lower learning rates are preferred.

The kernel size refers to the dimensions of the convolutional kernel used in the network, determining how many pixels are combined to produce a new pixel. A larger kernel size can capture features spanning several pixels, but it may also incorporate unrelated features. As shown in Figure~\ref{fig:Plot_kernel_size_loss}, the kernel size does not have a significant impact on the loss functions; however, smaller kernel sizes tend to produce more outliers, suggesting that either the Generator or Discriminator may gain an advantage. Therefore, a kernel size of 5 is preferred.

The amount of noise is controlled by two parameters, \(\alpha\) and \(\beta\), which indicate the percentage of pixels altered to either black or white—hence the term Salt and Pepper noise. Here, \(\alpha\) is applied to the real image, while \(\beta\) is applied to the generated image. Different ratios \(\frac{\alpha}{\beta}\) can lead to varying model performance; however, our results indicate that distinct noise rates do not significantly affect the loss functions. Figure~\ref{fig:Plot_noise_loss} shows the loss functions for smaller images (64 × 64), and due to the negligible impact, this analysis was not repeated for larger images.

The batch size defines the number of images processed simultaneously by the network. Smaller batch sizes have been observed to improve generalization \cite{prince2023understanding}. As illustrated in Figure~\ref{fig:Plot_batchsize_loss}, processing two images at once results in fewer outliers. However, because a larger batch size significantly increases training time, a batch size of 1 is used.

When training GANs, one strategy to potentially boost performance is to give the Discriminator an advantage by increasing its number of training steps before returning to the Generator's training. While this can lower the Discriminator loss—as shown in Figure~\ref{fig:Plot_discrep_loss}—it also increases training time and leads to a slight rise in the Generator loss. Since the generated images do not noticeably improve with additional Discriminator training, both networks are typically trained with the same number of steps.

Finally, the degree of sparse sampling can be varied to provide the model with access to more pixels. Increasing the number of telescopes results in more baselines and, consequently, more available pixels. Figure~\ref{fig:Plot_telescopes_loss} shows the loss functions for different numbers of telescopes. There is a significant disparity in performance, partly because the relationship between telescopes and baselines is not linear. For example, the Fourier plane can be sampled sixfold when using four telescopes compared to using only two. In the case of two telescopes, both the Generator and Discriminator exhibit less smooth training, as indicated by the outliers. Performance improves with three telescopes and becomes very promising with four. Overall, the degree of sparse sampling appears to have the most pronounced effect of all the hyperparameters.

### 2025-05-28 Phase_II/draft/prev/conclusion.tex
sync with overleaf today

\section{Conclusion}
Intensity Interferometry (II) is re-emerging as a promising technique to overcome the challenges associated with Amplitude Interferometry in the optical wavelength range. This resurgence is bolstered by advanced facilities at Imaging Cherenkov Telescope Arrays (ICTAs), which capture high-resolution images using large apertures and sensitive photon detectors capable of resolving signals on the nanosecond timescale \cite{dravins2013optical}. The Major Atmospheric Gamma Imaging Cherenkov Telescope (MAGIC), one of the world's leading CTAs, is now being employed for II, observing stellar objects with its 17-meter diameter mirror \cite{lorenz2004status}. MAGIC has already demonstrated the potential of II by measuring and comparing the diameters of individual stars \cite{abe2024performance}. Other existing arrays, such as the Very Energetic Radiation Imaging Telescope Array System (VERITAS) and the High Energy Stereoscopic System (HESS), are also advancing their II capabilities during periods when gamma-ray observations are not in progress \cite{kieda2021veritas, zmija2022optical}. Future observations, enabled by more advanced and sensitive instrumentation as well as the upcoming CTAO, promise to extend the boundaries of optical observations further.

However, II faces a significant drawback: it captures only the magnitude of the signal via photon correlation, resulting in a loss of phase information. This challenge of phase retrieval in II has been effectively addressed through machine learning techniques, particularly with conditional Generative Adversarial Networks (cGAN). Our study demonstrates that applying cGAN to II data successfully recovers the size, shape, and brightness distribution of a fast-rotating star. Evaluations based on image moments—specifically, the monopole, second, and third-order moments—support the effectiveness of cGAN in achieving accurate image reconstruction from a one-night simulation of II using six baselines. A critical factor in the reconstruction process is the extent of Fourier plane coverage, which depends on the number of available telescopes and the total observing time. With a full night of observation using four telescopes, the brightness distribution could be reconstructed with even greater precision. Future work might explore different observatory layouts to assess their impact on image reconstruction quality, such as integrating the Southern Cherenkov Telescope Array (CTA) with MAGIC.

While the results of this study highlight the significant potential of machine learning—particularly cGAN—for image reconstruction in II, several aspects require further refinement. First, detector efficiencies, which impact the signal-to-noise ratio (SNR) of actual observational data, have not yet been incorporated; addressing these factors will be crucial for more accurate SNR estimation. Second, exploring and comparing alternative methods for image generation could reveal approaches that outperform cGAN in reconstructing stellar images with II. Third, experimenting with different loss functions could provide additional insights into reconstruction quality. Although further testing is needed to refine the GAN and enhance its robustness and reliability, our findings suggest that machine learning is a promising approach for phase reconstruction in II.

### 2025-06-05 Phase_II/code/generate_baseline.py
baseline

@@ -10,21 +10,23 @@ obs = observe()
 vb = vary_base()
 
 # observation time for Intensity Interferometry
-start = [2460311.20167, 2460312.20167, 2460313.20167]   # (Jan 1-3, 2024, 7pm)
-end = [2460311.70833, 2460312.70833, 2460313.70833]     # (Jan 2-4, 2024, 5am)
+start = [2460311.20167]#, 2460312.20167, 2460313.20167, 2460314.20167, 2460315.20167]   # (Jan 1-5, 2024, 7pm)
+end = [2460311.70833]#, 2460312.70833, 2460313.70833, 2460314.70833, 2460315.70833]     # (Jan 2-6, 2024, 5am)
 step = obs.obslen(start, end, 0.0104167)
 jd = obs.julday(start, end, step)
 
 # telescope position, name, baseline name and baseline length
-# position of telescope on earth, Hanle Ladhakh
-la = vb.raddeg(32, 46, 48) 
-lo = vb.raddeg(78, 58, 35)
+# the position of Veritas Observatory
+la = vb.raddeg(31, 40, 30) 
+lo = vb.raddeg(110, 57, 7)
 
 # coordinates for telescope
 x = np.linspace(-60, 150, 500)
 y = np.linspace(-60, 80, 500)
 Tname = ['T1', 'T2', 'T3', 'T4'] 
 Tpos = [135 - 15j, 40 - 50j, 30 + 60j, -40 + 10j]
+ang = np.exp(0.1j)
+Tpos = [ang*x for x in Tpos]
 fname = 'telescope.png'
 ap.telescope(Tpos, Tname, fname, x, y, 6)
 
@@ -34,9 +36,9 @@ x = np.real(base)
 y = np.imag(base)
 z = 1e-6
 
-# position of source Polaris (assumed) in sky coordinate
-r = vb.radhr(2, 31, 49.09)
-de = vb.raddeg(89, 15, 50.8)
+# a single star at the position of source Spica
+r = vb.radhr(13, 25, 11.579)
+de = vb.raddeg(-11, 9, 40.75)
 
 # variational baseline according to the earth rotation
 vb.ps_para(lat=la, lon=lo, rac=r, dec=de)
@@ -52,16 +54,21 @@ zt = distance[:,2]           # baseline in up
 
 # plot the covered (u,v) plane with baselines
 plt.close()
-plt.rcParams.update({'font.size': 14})
[…]

### 2025-06-05 Phase_II/code/ellipse.py
colorbar

@@ -88,7 +88,7 @@ class ellipsoid():
                   fms = '%7.1e'
               else:
                   fms = '%' + '.%i' % ip + 'f'
-          plt.colorbar(cs) #,format=fms)
+          #plt.colorbar(cs) #,format=fms)
           #plt.axis('off')
           if title:
              plt.title(title)

### 2025-06-05 Phase_II/code/gan_def_test.py

@@ -23,14 +23,12 @@ sample_input, sample_real = fn.load('train/ellipse1541.jpg')                    
 generator = mfn.Generator()
 tf.keras.utils.plot_model(generator, to_file='testing_image/generator.png', show_shapes=True, dpi=64) # structure of Generator according to the neuron
 
-
 gen_output = generator(sample_input[tf.newaxis, ...], training=True)                                  # test the Generator to generate image using input signal (visibility) 
 plt.imshow(gen_output[0, ...])
 plt.savefig('testing_image/gen.png')
 
 discriminator = mfn.Discriminator()
 tf.keras.utils.plot_model(discriminator, to_file='testing_image/discriminator.png', show_shapes=True, dpi=64) # structure of Discriminator according to the neuron
-
 
 disc_out = discriminator([sample_input[tf.newaxis, :], gen_output], training=False)                   # test the discrimator to predict the image (result) based on signal and generated imgae as input.
 plt.imshow(disc_out[0, ..., -1], vmin=-10, vmax=10, cmap='RdBu_r')

### 2025-06-05 Phase_II/code/generate_baseline.py

@@ -52,22 +52,22 @@ yt = distance[:,1]           # baselines in north direction
 zt = distance[:,2]           # baseline in up
 
 
-# plot the covered (u,v) plane with baselines
+# plot the covered (u,v) plane with baselines (comment out the lines for the visualizations of baseline only)
 plt.close()
 plt.rcParams.update({'font.size': 15})
 plt.rcParams["figure.figsize"] = [12,8]
 plt.rcParams["font.weight"] = "bold"
 plt.rcParams["axes.labelweight"] = "bold"
 st = np.cumsum(step)
-color = ['cornflowerblue', 'orange', 'cyan', 'olive', 'red', 'purple']
+#color = ['cornflowerblue', 'orange', 'cyan', 'olive', 'red', 'purple']
 for k in range(0, len(xt), 1):
-    plt.plot(xt[k,:], yt[k,:], 'o', markeredgecolor='blue', markersize=6, markeredgewidth=1.5, color=color[k], )
+    plt.plot(xt[k,:], yt[k,:], '.', color='black')#, 'o', markeredgecolor='blue', markersize=6, markeredgewidth=1.5, color=color[k], )
     
-#plt.axis('off')
+plt.axis('off')
 plt.gca().set_aspect('equal')
-plt.xlabel('Along East in meter')
-plt.ylabel('Along North in meter')
-plt.title('The covered observational (u, v) plane', fontweight='bold')
+#plt.xlabel('Along East in meter')
+#plt.ylabel('Along North in meter')
+#plt.title('The covered observational (u, v) plane', fontweight='bold')
 plt.savefig('base/baseline.png')#, bbox_inches='tight', pad_inches=0, dpi=500)
 
 

### 2025-06-05 Phase_II/code/generate_image.py

@@ -19,13 +19,27 @@ for r in rad:
            i += 0.07
         if (i == 0) or (i == np.pi):
            ellipse = ep.ellip(sx, sy, r, i, 0, 1)
-           plt.imsave('ellip_image/ellipse' + str(pic) + '.jpg', ellipse)
-           np.save('ellip_npy/ellipse' + str(pic) + '.npy', ellipse)
+           img = plt.imshow(ellipse)
+           plt.colorbar(img) 
+           plt.axis('off')
+           plt.savefig(f'ellip_image/ellipse{pic}.jpg')
+           plt.close()
+           np.save(f'ellip_npy/ellipse{pic}.npy', ellipse)
            pic += 1
+           #plt.imsave('ellip_image/ellipse' + str(pic) + '.jpg', ellipse)
+           #np.save('ellip_npy/ellipse' + str(pic) + '.npy', ellipse)
+           #pic += 1
         else:
            for p in pa:
                for s in sq:
                    ellipse = ep.ellip(sx, sy, r, i, p, s)
-                   plt.imsave('ellip_image/ellipse' + str(pic) + '.jpg', ellipse)
-                   np.save('ellip_npy/ellipse' + str(pic) + '.npy', ellipse)
+                   img = plt.imshow(ellipse)
+                   plt.colorbar(img) 
+                   plt.axis('off')
+                   plt.savefig(f'ellip_image/ellipse{pic}.jpg')
+                   plt.close()
+                   np.save(f'ellip_npy/ellipse{pic}.npy', ellipse)
                    pic += 1
+                   #plt.imsave('ellip_image/ellipse' + str(pic) + '.jpg', ellipse)
+                   #np.save('ellip_npy/ellipse' + str(pic) + '.npy', ellipse)
+                   #pic += 1

### 2025-06-05 Phase_II/code/main_def_test.py

@@ -10,40 +10,58 @@ fn.para(img_size=128)
 
 # check the signal on observational plane and captured one using baseline of a stellar object
 base = np.load("base_npy/base.npy") 
-train_image = np.load("ellip_npy/ellipse6018.npy")
+train_image = np.load("ellip_npy/ellipse1612.npy")
 train_image = cv2.resize(train_image, dsize=(128, 128), interpolation=cv2.INTER_AREA)
 print('base shape', np.shape(base))
 print('image shape', np.shape(train_image))
 fft = np.abs(fft.fftshift(fft.fft2(fft.fftshift(train_image))))
 # the signal on observational plane
-plt.imshow(fft)
+img = plt.imshow(fft)
+plt.colorbar(img)
 plt.gca().set_aspect('equal')
 plt.axis('off')
 plt.savefig('ft/ft.jpg')
 #plt.show()
 
-plt.imshow(np.log(fft))
+plt.close()
+img1 = plt.imshow(np.log(fft))
+plt.colorbar(img1)
 plt.gca().set_aspect('equal')
 plt.axis('off')
 plt.savefig('ft/ft_log.jpg')
 #plt.show()
 
-'''
+plt.close()
 # the signal captured with baseline on observational plane
 output = np.multiply(fft, base) 
-plt.imshow(output)
+img2 = plt.imshow(output)
+plt.colorbar(img2)
+plt.gca().set_aspect('equal')
+plt.axis('off')
+plt.savefig('ft/ft_base.jpg')
 plt.show()
 
+plt.close()
+# the signal captured with baseline on log observational plane
+img3 = plt.imshow(np.log10(output+1e-7))
+plt.colorbar(img3)
+plt.gca().set_aspect('equal')
+plt.axis('off')
+plt.savefig('ft/ft_log_base.jpg')
+plt.show()
+
+'''
+plt.close()
 # The full fourier transformation on ground of stellar object and the captured one with baselines
 plt.subplot(1,2,1)
 plt.imshow(fft)
 plt.subplot(1,2,2)
 plt.imshow(output)
-plt.show()
+#plt.show()
 
 
 # check the spliting of image (sky and observational) is working
-sample_input, sample_real = fn.load('train/ellipse1693.jpg')                         # load the image to be trained in float32 tensor
+sample_input, sample_real = fn.load('train/ellipse1612.jpg')                         # load the image to be trained in float32 tensor
 print(np.shape(sample_input))
 pic = 0
 for i in [sample_input, sample_real]:

### 2025-06-05 Phase_II/code/generate_pspec.py
fig6

@@ -45,11 +45,33 @@ for filename in os.listdir(path_in):
     image_name = filename[:-4]                                                                        # save or display images > use cv2 instead of matplotlib, this always saves as (64,64,4)
     if save_images:
             if counter < 150:
-               cv2.imwrite('val/' + image_name + '.jpg', combined_image)
+               im = plt.imshow(combined_image, cmap='gray')
+               plt.colorbar(shrink=0.55)
+               plt.gca().set_aspect('equal')
+               plt.axis('off')
+               plt.savefig('val/' + image_name + '.jpg')
+               plt.clf()
+               plt.close()
+               #cv2.imwrite('val/' + image_name + '.jpg', combined_image)
             elif (counter >= 150) and (counter < 300):
-               cv2.imwrite('test/' + image_name + '.jpg', combined_image)
+               im = plt.imshow(combined_image, cmap='gray')
+               plt.colorbar(shrink=0.55)
+               plt.gca().set_aspect('equal')
+               plt.axis('off')
+               #plt.show()
+               plt.savefig('test/' + image_name + '.jpg')
+               plt.clf()
+               plt.close()
+               #cv2.imwrite('test/' + image_name + '.jpg', combined_image)
             else:
-               cv2.imwrite('train/' + image_name + '.jpg', combined_image)
+               im = plt.imshow(combined_image, cmap='gray')
+               plt.colorbar(shrink=0.55)
+               plt.gca().set_aspect('equal')
+               plt.axis('off')
+               plt.savefig('train/' + image_name + '.jpg')
+               plt.clf()
+               plt.close()
+               #cv2.imwrite('train/' + image_name + '.jpg', combined_image)
 
     else:
             plt.imshow(ground_truth)

### 2025-07-16 Phase_II/draft/GAN.tex
edits

@@
 \section{Generative Adversarial Networks}
-Generative Adversarial Networks (GANs) were introduced by \citep{goodfellow2014generative}.
+Generative Adversarial Networks (GANs) were introduced by \cite{goodfellow2014generative}.
 The underlying concept is straightforward: it involves two competing networks.
@@
 	\begin{aligned}
-		\min_{G} \max_{D} V(D, G) &= \mathbb{E}_{x \sim p_{data}(x)} \left[ \log D(x) \right] \\
+		\min_{G} \max_{D} V(D, G) &= \mathbb{E}_{x \sim p_{\rm data}(x)} \left[ \log D(x) \right] \\
 		&+ \mathbb{E}_{z \sim p_{z}(z)} \left[ \log \left( 1-D(G(z)) \right) \right]
@@
 	\begin{aligned}
-		\max_{D} V(G, D) &= \mathbb{E}_{x \sim p_{data}} \left[ \log D^{*}_{G}(x) \right] \\ 
+		\max_{D} V(G, D) &= \mathbb{E}_{x \sim p_{\rm data}} \left[ \log D^{*}_{G}(x) \right] \\ 
 		&+ \mathbb{E}_{x \sim p_{g}} \left[ \log \left( 1 - D^{*}_{G}(x) \right) \right]
@@
 where \(D^{*}_{G}\) denotes the optimum of the discriminator for a given fixed generator, as shown in equation (\ref{eq:Disc_optimum}).
-It can be demonstrated that the global optimum of equation (\ref{eq:GAN_reformulated}) is achieved if and only if \(p_G = p_{data}\).
-Furthermore, if both \(G\) and \(D\) are allowed to reach their respective optima, then \(p_G\) converges to \(p_{data}\).
+It can be demonstrated that the global optimum of equation (\ref{eq:GAN_reformulated}) is achieved if and only if \(p_G = p_{\rm data}\).
+Furthermore, if both \(G\) and \(D\) are allowed to reach their respective optima, then \(p_G\) converges to \(p_{\rm data}\).
 A more comprehensive discussion of the problem, including proofs, is provided in \cite{goodfellow2014generative}.
@@
 	\centering
-	D^*_G(x) = \frac{p_{data}(x)}{p_{data}(x) + p_g(g)}
+	D^*_G(x) = \frac{p_{\rm data}(x)}{p_{\rm data}(x) + p_g(g)}
 	\label{eq:Disc_optimum}
@@
 	\centering
-	\includegraphics[width=\linewidth]{fig/ellipsoid_0.jpg}
+	\includegraphics[width=\linewidth]{fig/ellipse1612.jpg}
 	\caption{Merged image, which includes the original and the sparsely sampled Fourier plane. It is exactly what the GAN receives. }
@@
 	\begin{aligned}
-		V(D, G) &= \mathbb{E}_{x \sim p_{data}(x)} \left[ \log D(x|y) \right] \\
+		V(D, G) &= \mathbb{E}_{x \sim p_{\rm data}(x)} \left[ \log D(x|y) \right] \\
 		&+ \mathbb{E}_{z \sim p_{z}(z)} \left[ \log \left( 1-D(G(z|y) \right) \right]
@@
 \end{equation}
-
-\cite{isola2017image} further observed that combining the cGAN from equation \ref{eq:conditional_GAN} with the traditional L1 loss improves the results, as the Generator is encouraged to produce outputs closer to the ground truth.
+\cite{isola2017image} further observed that combining the cGAN from Eq.~\eqref{eq:conditional_GAN} with the traditional L1 loss improves the results, as the Generator is encouraged to produce outputs closer to the ground truth.
 Hence, the function that is minimized is:
@@
 \end{equation}
-where $\lambda$ = 100 and $L_1(G)$ is given as
+with the choice $\lambda = 100$ and
 \begin{equation}
@@
 \end{equation}
-
 This type of network has demonstrated remarkable robustness across a variety of applications.
@@
 This stage also comprises convolutional layers followed by operations with a stride of 2 to upscale the image to a higher resolution.
-Additionally, a dropout layer is introduced at the beginning of the upsampling phase to mitigate overfitting of the Generator model \cite{isola2017image}.
+Additionally, a dropout layer is introduced at the beginning of the upsampling phase to mitigate overfitting of the Generator model \citep{isola2017image}.
 
@@
 It takes a real image from the dataset (often referred to as the target image for the Generator) and provides feedback to guide the Generator toward producing more accurate images.
-In this work, the PatchGAN model \cite{isola2017image} is employed as the Discriminator.
+In this work, the PatchGAN model \citep{isola2017image} is employed as the Discriminator.
 Unlike a traditional global classifier, PatchGAN evaluates individual patches of the image, outputting a grid of predictions rather than a single scalar value.

### 2025-07-16 Phase_II/draft/II.tex
colorbar
edits

@@
 Suppose the two telescopes simultaneously measure the intensity of radiation $I_1(t)$ and $I_2(t)$, respectively.
-The signals from these detectors are cross-correlated and averaged over time, yielding the second order ($n=2$) correlation of these intensities as \citep[cf.][]{acciari2020optical, dravins2013optical}
+The signals from these detectors are cross-correlated and averaged over time, yielding the second order ($n=2$) correlation of these intensities as \citep[cf.][]{acciari2020optical, 2013APh....43..331D}
 \begin{equation}
@@
 \end{equation}
-where $\Delta f$ is the electronic bandwidth of the photon detectors (which measure the intensities.
+where $\Delta f$ is the electronic bandwidth of the photon detectors which measure the intensities.
 Values of $\Delta\nu\sim 1\,\mathrm{THz}$ and $\Delta f \sim 1\,\mathrm{GHz}$ are typical of recent work.
@@
 	\centering
-	\includegraphics[width=0.8\linewidth]{fig/ellipse/ellipse6018.jpg}
+	\includegraphics[width=\linewidth]{fig/ellipse/ellipse1612.jpg}
 	\caption{This figure shows the simulated fast rotating star. The brightness is highest at the pole and there is gravitational darkening at the equator.}
@@
 		\includegraphics[width=\linewidth]{fig/ft/ft.jpg}
-		\caption{The fourier transform of source.}
+		\caption{The signal (absolute value of the Fourier transform of the source).}
 	\end{subfigure}\hfill
@@
 		\includegraphics[width=\linewidth]{fig/ft/ft_log.jpg}
-		\caption{The logarithmic fourier transform of source.}
+		\caption{The logarithm of the signal.}
 	\end{subfigure}
-	\caption{Absolute value of the two-dimensional Fast Fourier Transform of fig.~\ref{fig:image} measured by Intensity Interferometry, and observation of maximum (u, v) plane with finite number of baselines can be completed with help of earth's rotation.}
+	\caption{Absolute value of the two-dimensional Fast Fourier Transform of Fig.~\ref{fig:image} measured by Intensity Interferometry, and observation of maximum $(u, v)$ plane with the assumed telescope separations can be completed with the help of Earth rotation.}
 	\label{fig:ft}
@@
 		\includegraphics[width=\linewidth]{fig/ft/ft_base.jpg}
-		\caption{The fourier transform with baselines.}
+		\caption{The signal as samples by the baselines.}
 	\end{subfigure}\hfill
@@
 		\includegraphics[width=\linewidth]{fig/ft/ft_log_base.jpg}
-		\caption{The logarithmic fourier transform with baselines.}
+		\caption{The logarithmic signal as sampled by the baselines.}
 	\end{subfigure}
@@
 The primary purpose of IACTs is to study high-energy gamma rays (with energy $E\ \geq 30$ GeV) arriving from cosmic sources, entering the Earth's atmosphere, and initiating Cherenkov showers in the upper atmosphere due to multiple scattering.
-These telescopes feature an array of mirrors that focus light onto a set of photo-multiplier tubes (PMTs) \cite{aleksic2016major}.
+These telescopes feature an array of mirrors that focus light onto a set of photo-multiplier tubes \citep[PMTs, see e.g.,][]{aleksic2016major}.
 In the simulation model adopted here, we consider a set of four IACTs, each with similar properties.
-The positional configuration of these IACTs is shown in fig.~\ref{fig:teles}.
+The positional configuration of these IACTs is shown in Fig.~\ref{fig:teles}.
 The optical signal directed to a PMT is filtered using a spectral filter with a chosen mean observational wavelength $\lambda$ and corresponding bandpass $\Delta \lambda$.
@@
 \begin{equation}
-	V_{12}(d) = \frac{c(d)}{c(0)}
+	|V_{12}(d)|^2 = \frac{c(d)}{c(0)}
 	\label{eq:angular_size_meas}
@@
 where $d_E$ and $d_N$ are the baselines expressed in east and north coordinates.
-However, not all sources are at the zenith, and the telescopes are stationary and may also have different relative altitudes $d_A$ depending on the available terrain.
+However, of course sources can be anywhere on the sky, and the telescopes are stationary and may also have different relative altitudes $d_A$ depending on the available terrain.
 Therefore, the Earth's rotation must be taken into account to cover the maximum observational plane using rotated baselines.
@@
 As the number of baselines increases non-linearly, Intensity Interferometry (II) benefits greatly from a large number of telescopes.
-The planned Cherenkov Telescope Array (CTA) will cover the maximum observational plane and provide insight into stellar objects with optical wavelengths in the future.
+The CTAO can offer many more baselines --- \cite{2013APh....43..331D} considered the telescope configurations then being considered, and all provided dense coverage of the interferometric plane.
 
@@
 Fast rotation causes stars to adopt an oblate shape, flattening at the poles and bulging at the equator due to the stronger centrifugal force \citep[e.g.,][]{von1924radiative, 1999A&A...347..185M}.
-Fig.~\ref{fig:image} shows one of the simulations of such a fast-rotating star, with brightness distributed across its surface.
+Fig.~\ref{fig:image} shows a fictitious image qualitatively representing a fast-rotating star, with brightness distributed across its surface.
 The brightness is highest at the poles and lowest at the equator, a phenomenon known as gravity darkening \citep{lucy1967gravity}.
 This effect was first observed through interferometric and spectroscopic data from the CHARA Array for the fast-rotating star Regulus \cite{mcalister2005first}.
-Fast-rotating stars are crucial for understanding various astrophysical processes, including stellar evolution, internal structure, and dynamical behavior over time.
+Fast-rotating stars are important test cases for understanding various astrophysical processes, including stellar evolution, internal structure, and dynamical behavior over time.
 
 Intensity Interferometry counts the photons arriving at the telescopes from the stellar object.
-The correlation of these photon arrivals at the telescopes yields the squared visibility (explained in subsection~\ref{sec:signal}).
-This signal is the Fourier transform of the brightness distribution in the sky.
-Fig.\ref{fig:ft} represents the Fourier Transform of the source shown in Fig.~\ref{fig:image} using II, displayed on both linear and logarithmic scales.
+The correlation of these photon arrivals at the telescopes yields the squared visibility Eq.~\eqref{eq:angular_size_meas}, as explained in subsection~\ref{sec:signal}.
+Fig.\ref{fig:ft} shows the signal from the source shown in Fig.~\ref{fig:image} using II, displayed on both linear and logarithmic scales.
 In practice, only a small part of this information is available, because one has a finite number of baselines corresponding to the finite number $N_T$ of telescopes at our disposal and a limited observation schedule.
-Therefore, we have simulated the II observation of a sky source over one night.
-Using this finite amount of signal from one night's observation, we have trained a Generative Adversarial Network (GAN) to construct the image of the source.
+Therefore, we have simulated the II observation of a sky source by four telescopes (correlated in pairs) over one night.
+Using this modest amount of signal from one night's observation, we have trained a cGAN to construct the image of the source.

### 2025-07-16 Phase_II/draft/ParaGan.tex
edits

@@
-\section{The Parameter for GAN Structure}
+\section{Network Parameters}
 
@@
 	\end{subfigure}
-	\caption{This set of figures shows the result of GAN for II.
+	\caption{Examples results of GAN for II.
 The left panels are signals using six baselines, which work as input for GAN.
@@
 \end{figure*}
-Here, we discuss the parameters for the GAN structure, which is trained to reconstruct the image of stellar objects using II.
-Due to the adversarial nature of GAN, where the Generator and Discriminator compete in a min-max game, careful tuning of key parameters ensures that both networks are in good term to train the model.
+Here, we discuss the parameters of the GAN architecture used for reconstructing images of stellar objects using II.
+Given the adversarial nature of GANs—where the Generator and Discriminator engage in a min-max game—careful tuning of key parameters is critical to ensure that both networks are well-balanced for effective training.
+
 \subsection{Data Preparation}
-First, we simulate fast-rotating stars, which are modeled as oblate spheroids with different radii and oblateness between 0.5 and 1.
-Different viewed angles have also been considered, with the effect of gravity darkening being linear dependence.
-The traced ellipses arise when integrating over the hour angle of the source.
-For the hyperparameter tuning and comparison of different telescopes, the total hour angle is about 11.5 hours.
-The ellipses are plotted and converted into grayscale images, resized, and stored as pure arrays to simplify further analysis.
+First, we simulate fast-rotating stars, modeling them as oblate spheroids with varying radii and an oblateness ranging between 0.5 and 1.
+We also consider different viewing angles, assuming a linear dependence for the effect of gravity darkening.
+The traced ellipses result from integrating over the source's hour angle.
+For hyperparameter tuning and comparing different telescopes, the total observing duration is set to approximately 11.5 hours.
+Finally, the ellipses are plotted, converted into grayscale images, resized, and stored as raw arrays to facilitate further analysis.
 \begin{figure*}
@@
 
-First, Salt and Pepper noise is introduced at a rate of $\alpha$ (usually 0.5\%).
-Then, the images are resized, and the mean is subtracted.
-A two-dimensional Fast Fourier Transform, as well as a Fourier shift, is applied, which yields a complex number of every pixel.
-As II does not measure the phase, the absolute value is calculated (shown in Fig.~\ref{fig:ft} on a linear and logarithmic scale for visualization).
-The sparse sampling is also introduced, namely by a pixel-wise multiplication between the absolute valued Fourier transformed image (Fig.~\ref{fig:ft}) and the sparse sampling map (Fig.~\ref{fig:base}).
-The result is a map in the Fourier plane with several ellipses, also called the sparse sampling map (Fig.~\ref{fig:ft_base}).
-It shows the sparse sampling for Fig.~\ref{fig:image} as the source with four telescopes (Fig.~\ref{fig:teles}).
+First, Salt and Pepper noise is introduced at a rate of \(\alpha\) (usually 0.5\%).
+Then, the images are resized and their mean is subtracted.
+A two-dimensional Fast Fourier Transform, along with a Fourier shift, is applied, yielding a complex number for each pixel.
+Since II does not measure phase, the absolute value is calculated (as shown in Fig.~\ref{fig:ft} on both linear and logarithmic scales for visualization).
+
+Next, sparse sampling is introduced via pixel-wise multiplication between the absolute-valued Fourier-transformed image (Fig.~\ref{fig:ft}) and the sparse sampling map (Fig.~\ref{fig:base}).
+The result is a map in the Fourier plane featuring several ellipses, which is also referred to as the sparse sampling map (Fig.~\ref{fig:ft_base}).
+This map represents the sparse sampling for Fig.~\ref{fig:image}, corresponding to the source observed with four telescopes (Fig.~\ref{fig:teles}).
+
 Finally, the pixels are normalized and converted to 8-bit integers.
-This image represents the sparsely sampled complex visibility, as it can be measured with II.
-The image shown in Fig.~\ref{fig:ft_base} is the input image for the GAN, which also requires the ground truth image.
-So, the simulated stars are also resized using the same algorithm and converted to 8-bit integers to reduce the bias.
-The GAN must know the ground truth corresponding to an input image.
-Hence, they are merged side-by-side, shown in Fig.~\ref{fig:GANinput}, and used as input to train the GAN.
-This procedure is conducted for all the simulated stars, with 10\% acting as test data, 10\% as validation data, and the remaining 80\% as training data.
+This image represents the sparsely sampled phaseless visibility as it can be measured with II.
+The image shown in Fig.~\ref{fig:ft_base} serves as the input for the GAN, which also requires the corresponding ground truth image.
+Consequently, the simulated stars are resized using the same algorithm and converted to 8-bit integers to reduce bias.
+The GAN must have access to the ground truth corresponding to each input image; therefore, the input and ground truth images are merged side-by-side (as shown in Fig.~\ref{fig:GANinput}) and used to train the GAN.
+This procedure is applied to all simulated stars, with 10\% used as test data, 10\% as validation data, and the remaining 80\% as training data.
 
 \subsection{GAN Architecture}
-The GAN used in this work is based on pix2pix, which uses a cGAN discussed in the last section \cite{isola2017image}.
-It is very robust and could already be applied to various problems.
-An example can be found in the TensorFlow tutorials\footnote{\url{https://www.tensorflow.org/tutorials/generative/pix2pix}}, where it is applied to a data set of architectural facades.
+The GAN used in this work is based on pix2pix, which utilizes a conditional GAN (cGAN) as discussed in the previous section \citep{isola2017image}.
+This architecture is highly robust and has already been applied to various problems.
+For instance, the TensorFlow tutorials\footnote{\url{https://www.tensorflow.org/tutorials/generative/pix2pix}} demonstrate its application to a dataset of architectural facades.
 However, to adapt the pix2pix GAN for the phase retrieval problem, some modifications are necessary.
-The network uses the TensorFlow library \cite{abadi2016tensorflow}, calculations are performed with scipy \cite{virtanen2020scipy}, and plots are drawn with matplotlib \cite{4160265}.
+The network is implemented using the TensorFlow library \citep{abadi2016tensorflow}, calculations are performed with scipy \citep{virtanen2020scipy}, and plots are generated with matplotlib \citep{4160265}.
 
 \subsection{Hyperparameter Tuning}
-The GAN used for this work depends on several parameters, which will be explained here briefly (an in-depth discussion can be found in \cite{murphy2022probabilistic}).
+The GAN used in this work depends on several parameters, which are explained briefly below \citep[for a more in-depth discussion, see][]{murphy2022probabilistic}.
 
-The learning rate of the optimizer is a measure of how much the model changes per iteration.
-Small learning rates can lead to underfitting, and large learning rates can make the model unstable.
-It is therefore important to carefully choose the learning rate \cite{murphy2022probabilistic}.
-Fig.~\ref{fig:Plot_learning_rate_loss} shows the effect of the learning rate on both Generator and Discriminator loss for three different values of it.
-Both loss functions have fewer outliers with decreasing learning rates, which is expected, as there is less change in the models with low learning rates.
-Even though all models stabilize at the same level, low learning rates are preferred.
+The learning rate of the optimizer determines how much the model updates its parameters with each iteration.
+A learning rate that is too small may lead to underfitting, while one that is too large can render the model unstable.
+Therefore, selecting an appropriate learning rate is crucial \citep{murphy2022probabilistic}.
+Fig.~\ref{fig:Plot_learning_rate_loss} illustrates the effect of different learning rates on both the Generator and Discriminator losses.
+As expected, lower learning rates result in fewer outliers in the loss functions, indicating more stable updates.
+Although all models eventually stabilize at a similar level, lower learning rates are preferred.
 
-The kernel size is the size of the kernel in the convolutional layer.
-It determines the amount of pixels that are linearly combined into a new pixel.
-A large kernel size allows one to catch features that are a few pixels away, but it also means that unrelated features might be introduced.
-The kernel size does not have a big effect on the loss functions, as shown in Fig.~\ref{fig:Plot_kernel_size_loss}.
-Smaller kernel sizes seem to have more outliers, which means that either Generator or Discriminator gains an advantage.
+The kernel size refers to the dimensions of the convolutional kernel used in the network, determining how many pixels are combined to produce a new pixel.
+A larger kernel size can capture features spanning several pixels, but it may also incorporate unrelated features.
+As shown in Fig.~\ref{fig:Plot_kernel_size_loss}, the kernel size does not have a significant impact on the loss functions; however, smaller kernel sizes tend to produce more outliers, suggesting that either the Generator or Discriminator may gain an advantage.
 Therefore, a kernel size of 5 is preferred.
 
-The amount of noise is reflected by the two parameters $\alpha$ and $\beta$.
-Both indicate the percentage of pixels that change to either black or white, hence the name Salt and Pepper noise, where $\alpha$ is introduced in the real image, $\beta$ in the generated image.
-Different ratios $\frac{\alpha}{\beta}$ can lead to different model performances.
-There is no significant difference between distinct noise rates introduced in the images.
-Fig.~\ref{fig:Plot_noise_loss} shows the loss functions on smaller images (64 x 64).
-As there is no effect, it was not necessary to repeat this analysis for larger images.
+The amount of noise is controlled by two parameters, \(\alpha\) and \(\beta\), which indicate the percentage of pixels altered to either black or white—hence the term Salt and Pepper noise.
+Here, \(\alpha\) is applied to the real image, while \(\beta\) is applied to the generated image.
+Different ratios \(\frac{\alpha}{\beta}\) can lead to varying model performance; however, our results indicate that distinct noise rates do not significantly affect the loss functions.
+Figure~\ref{fig:Plot_noise_loss} shows the loss functions for smaller images ($64 \times 64$), and due to the negligible impact, this analysis was not repeated for larger images.
 
-The batch size defines the number of images that pass the network simultaneously.
-It is observed that smaller batch sizes can lead to better generalization \cite{prince2023understanding}.
-Fig.~\ref{fig:Plot_batchsize_loss} shows two different batch sizes.
-Here, when two images are processed simultaneously, there are fewer outliers, but since it increases the training time heavily, a batch size of 1 is used.
+The batch size defines the number of images processed simultaneously by the network.
+Smaller batch sizes have been observed to improve generalization \citep{prince2023understanding}.
+As illustrated in Fig.~\ref{fig:Plot_batchsize_loss}, processing two images at once results in fewer outliers.
+However, because a larger batch size significantly increases training time, a batch size of 1 is used.
 
-While training GAN, one can give the Discriminator an advantage by increasing the number of training steps before returning to the Generator training.
-It can increase the performance of the model.
-However, it increases the training time as well and leads to a lower Discriminator loss score, as shown in Fig.~\ref{fig:Plot_discrep_loss}.
-At the same time, the Generator score increases slightly, which should be no surprise.
-Because the generated images did not improve with higher Discriminator training, they are usually trained in the same amount as the Generator.
+When training GANs, one strategy to potentially boost performance is to give the Discriminator an advantage by increasing its number of training steps before returning to the Generator's training.
+While this can lower the Discriminator loss—as shown in Fig.~\ref{fig:Plot_discrep_loss}—it also increases training time and leads to a slight rise in the Generator loss.
+Since the generated images do not noticeably improve with additional Discriminator training, both networks are typically trained with the same number of steps.
 
-Finally, the amount of sparse sampling can be varied, giving the model access to more pixels.
-More telescopes automatically lead to more baselines and, hence, more pixels that are available.
+Finally, the degree of sparse sampling can be varied to provide the model with access to more pixels.
+Increasing the number of telescopes results in more baselines and, consequently, more available pixels.
 Fig.~\ref{fig:Plot_telescopes_loss} shows the loss functions for different numbers of telescopes.
-There is a huge disparity, which can partly be explained by the fact that the relation between telescopes and baselines is not linear.
-The Fourier plane can be sampled sixfold when using four telescopes in contrast to only two telescopes.
-In the latter case, both the Generator and Discriminator are not trained smoothly, as seen by the outliers.
-It is already better with three telescopes and very promising when using four telescopes.
-The degree of sparse sampling seems to have the biggest effect of all hyperparameters.
+There is a significant disparity in performance, partly because the relationship between telescopes and baselines is not linear.
+For example, the Fourier plane can be sampled along six tracks when using four telescopes, as compared to only one tracks if using only two telescopes.
+In the case of two telescopes, both the Generator and Discriminator exhibit less smooth training, as indicated by the outliers.
+Performance improves with three telescopes and becomes very promising with four.
+Overall, the degree of sparse sampling appears to have the most pronounced effect of all the hyperparameters.

### 2025-07-16 Phase_II/draft/Result.tex
edits

@@
 \subsection{Predicted Image from the Trained GAN}
-Figure~\ref{fig:GAN} demonstrates the success of the GAN in training a model for Intensity Interferometry (II) to reconstruct images of fast-rotating stars.
+Fig.~\ref{fig:GAN} demonstrates the success of the GAN in training a model for Intensity Interferometry (II) to reconstruct images of fast-rotating stars.
 The GAN was trained on the training datasets for 60,000 steps and subsequently tested on various validation datasets to produce predicted images of a fast-rotating star.
@@
 \end{itemize}
-The predicted images in Fig.~\ref{fig:GAN} yield positive results, accurately conveying visual information about the source's size, shape, and brightness distribution across its surface using only six baselines.
-However, further improvements can be achieved by increasing the number of telescopes to maximize coverage of the $(u, v)$ plane, making the existing and upcoming Cherenkov Telescope Array Observatory (CTAO) an ideal candidate for this approach.
+The predicted images in Fig.~\ref{fig:GAN} yield encouraging results, accurately conveying visual information about the source's size, shape, and brightness distribution across its surface using only six baselines.
+However, further improvements can be achieved by increasing the number of telescopes to maximize coverage of the $(u, v)$ plane, making the existing and upcoming CTAO an ideal candidate for this approach.
 \subsection{Evaluation of GAN using Moments}
 The reconstructed images are visually compelling, demonstrating the GAN's effectiveness in using II to reconstruct images.
-However, visual assessment alone is insufficient; statistical evaluation is necessary to rigorously validate the results.
+However, visual assessment alone is insufficient; statistical evaluation is necessary to validate the results.
 To achieve this, we employ image moments as a statistical method.
@@
 
-The raw moment $M_{ij}$ of an image I(x, y) is defined as \citep{hu1962visual}
+The raw moment $M_{ij}$ of an image $I(x, y)$ is defined as \citep{hu1962visual}
 \begin{equation}
@@
 \end{equation}
-
 The zeroth order raw moment, or monopole, represents the total intensity of an image.
@@
 In this context, analyzing the monopole provides the total flux of fast-rotating stars.
-According to eqn.~\ref{eqn:Mom}, the monopole of an image is calculated as:
+According to Eq.~\eqref{eqn:Mom}, the monopole of an image is calculated as:
 \begin{equation}
@@
 Figure~\ref{fig:mom1} displays the monopole values for 50 reconstructed images.
-The plot reveals a linear relationship between the monopole of the ground truth (real image) on the x-axis and that of the predicted (reconstructed) image on the y-axis, consistent across sources of varying shapes and sizes.
+The plot reveals a linear relationship between the monopole of the ground truth (real image) on the $x$-axis and that of the predicted (reconstructed) image on the $y$-axis, consistent across sources of varying shapes and sizes.
 This linearity confirms that the predicted images have an overall intensity (flux) that closely matches the ground truth.
@@
 %To be decided%%%%%%%
-The center of mass for the fast-rotating star or any other stellar object is calculated using the centroid (x-centroid and y-centroid).
+The center of mass for the fast-rotating star or any other stellar object is calculated using the centroid ($x$-centroid and $y$-centroid).
 It represents the spatial position of the image and is calculated using first-order raw moment and monopole.
-The formulation of centroid along the x and y directions is
+The formulation of centroid along the $x$ and $y$ directions is
 \begin{equation}
@@
 \end{equation}
-Fig.~\ref{fig:mom2} and Fig.~\ref{fig:mom3} show the comparison of the x-centroid and y-centroid for 50 predicted images with respect to ground truths, respectively.
+Fig.~\ref{fig:mom2} and Fig.~\ref{fig:mom3} show the comparison of the $x$-centroid and $y$-centroid for 50 predicted images with respect to ground truths, respectively.
 The clustering of centroids in a given scale range for all the results explains that the reconstructed image correctly represents the spatial location of the fast-rotating star compared with the ground truth.
@@
 
-The center of mass of a fast-rotating star, or any stellar object, is determined by its centroid, which provides the x and y coordinates representing the spatial position of the image.
+The center of mass of a fast-rotating star, or any stellar object, is determined by its centroid, which provides the $x$ and $y$ coordinates representing the spatial position of the image.
 This centroid is computed using the first-order raw moments in conjunction with the monopole (the zeroth-order moment).
-The formulations for the centroid along the x and y directions are given by:
+The formulations for the centroid along the $x$ and $y$ directions are given by:
 \begin{eqnarray}
@@
 \end{eqnarray}
-Here, \(I(x,y)\) represents the intensity at pixel \((x,y)\), \(M_{00}\) is the monopole (total intensity), and \(M_{10}\) and \(M_{01}\) are the first-order raw moments along the x and y axes, respectively.
+Here, \(I(x,y)\) represents the intensity at pixel \((x,y)\), \(M_{00}\) is the monopole (total intensity), and \(M_{10}\) and \(M_{01}\) are the first-order raw moments along the $x$ and $y$ axes, respectively.
 This formulation accurately captures the spatial center of mass of the stellar object in the image.
 
-Fig.~\ref{fig:mom2} and Fig.~\ref{fig:mom3} compare the centroids ($x_{c}$, $y_{c}$)of 50 predicted images with their corresponding ground truths, respectively.
+Fig.~\ref{fig:mom2} and Fig.~\ref{fig:mom3} compare the centroids ($x_{c}$, $y_{c}$) of 50 predicted images with their corresponding ground truths, respectively.
 The clustering of centroids within a specific scale range across all results indicates that the reconstructed images accurately represent the spatial location of the fast-rotating star relative to the ground truth.
@@
 
-Figure~\ref{fig:struc} presents the second-order central moments (\(\mu_{11}, \mu_{20}, \mu_{02}\)), which are used to study the structure of a fast-rotating star along the line of sight (as explained in the upcoming subsection).
+Fig.~\ref{fig:struc} presents the second-order central moments (\(\mu_{11}, \mu_{20}, \mu_{02}\)), which are used to study the structure of a fast-rotating star along the line of sight (as explained in the upcoming subsection).
 All three plots demonstrate a linear relationship in the second-order moments, similar to the monopole, thereby confirming the success of applying the GAN to reconstruct images with II.
@@
 The brightness distribution is characterized by the skewness of the image, which is quantified by calculating the third-order central moments (\(\mu_{30}, \mu_{03}, \mu_{21}, \mu_{12}\)).
-Figure~\ref{fig:moments} presents all third-order moments for both the ground truth and the reconstructed image.
-The skewness along the x and y axes (\(\mu_{30}\) and \(\mu_{03}\)) appears acceptable, as shown in Fig.~\ref{fig:mom7} and Fig.~\ref{fig:mom8}, where a linear relationship exists between the ground truth and predicted images.
+Fig.~\ref{fig:moments} presents all third-order moments for both the ground truth and the reconstructed image.
+The skewness along the $x$ and $y$ axes (\(\mu_{30}\) and \(\mu_{03}\)) appears acceptable, as shown in Fig.~\ref{fig:mom7} and Fig.~\ref{fig:mom8}, where a linear relationship exists between the ground truth and predicted images.
 However, the other higher-order moments (\(\mu_{21}\) and \(\mu_{12}\))—particularly \(\mu_{12}\), as depicted in Fig.~\ref{fig:mom9} and Fig.~\ref{fig:mom10}—do not align as well.
@@
 \begin{equation}
-	\theta = \frac{1}{2}\arctan \big(\frac{2\mu_{11}}{\mu_{20} - \mu_{02}}\big).
+	\theta = \tfrac{1}{2}\arctan \left(\frac{2\mu_{11}}{\mu_{20} - \mu_{02}}\right).
 	\label{eqn:orn}
@@
 \end{equation}
-Equations~\ref{eqn:orn}-\ref{eqn:eccen} describe the elliptical nature of the stellar object (in this case, a fast-rotating star) and provide information on its shape and size, depending on the computed values.
+Eqs.~\ref{eqn:orn}-\ref{eqn:eccen} describe the elliptical nature of the stellar object (in this case, a fast-rotating star) and provide information on its shape and size, depending on the computed values.
 In contrast, the brightness distribution is characterized by skewness, which is quantified using third and higher-order moments.

### 2025-07-16 Phase_II/draft/conclusion.tex
edits

@@
 
-This work addresses the challenge of phase retrieval in II using a machine-learning technique, specifically a conditional Generative Adversarial Networks (cGAN).
-Our study demonstrates that applying cGAN to II data successfully recovers the size, shape, and brightness distribution of a fast-rotating star.
+This work addresses the challenge of phase retrieval in II using a machine-learning technique, specifically a conditional Generative Adversarial Network (cGAN).
+Our study demonstrates that applying a cGAN to II data successfully recovers the size, shape, and brightness distribution of a fast-rotating star.
 Evaluations based on image moments—specifically, the monopole, second, and third-order moments—support the effectiveness of cGAN in achieving accurate image reconstruction from a simulation of II from a single site with four telescopes.

### 2025-07-16 Phase_II/draft/intro.tex
edits

@@
 
-More recently, proposals emerged to utilize Imaging Atmospheric Cherenkov Telescope (IACT) facilities for conducting II observations of stars \citep{LeBohec2006, nunez2010stellar, nunez2012high, Dravins2013}.
+More recently, proposals emerged to utilize Imaging Atmospheric Cherenkov Telescope (IACT) facilities for conducting II observations of stars \citep{LeBohec2006, nunez2010stellar, nunez2012high, 2013APh....43..331D}.
 It was suggested that such observations could be carried out during bright, moonlit nights when $\gamma$-ray observations based on upper atmospheric Cherenkov showers were not feasible.
-This approach had the potential to enhance the scientific output of existing facilities such as VERITAS, MAGIC, and HESS.
-Subsequent SII observations at these facilities are now appearing \citep{abeysekara2020demonstration, Abe2024MAGIC, Zmija2023}.
+This approach has the potential to enhance the scientific output of existing IACT facilities, and especially of the upcoming Cherenkov Telescope Array (CTAO).
+SII observations at VERITAS, MAGIC, and HESS are now appearing
+\citep[e.g.,][]{2024ApJ...966...28A,2024MNRAS.529.4387A,2025MNRAS.537.2334V}
 Simulations \citep[e.g.,][]{10.1093/mnras/stab2391, 10.1093/mnras/stac2433} have argued that recent advancements in photon detectors could be effective in achieving high-precision measurements of parameters for stellar objects
 
-Beyond measuring the physical parameters of star systems, a fundamental goal of optical astronomy is to determine the sky intensity distribution of a source from ground-based observations.
+Beyond measuring stellar diameters and other parameters of star systems, a fundamental goal of optical astronomy is to image stellar systems at high angular resolution.
 In the context of II, this involves reconstructing the source's image from the intensity correlations recorded by pairs of telescopes (light buckets) on the ground.
-However, because the primary observable in II is the electromagnetic field intensity rather than the field strength, a significant drawback of this method is the loss of phase information.
+However, because the primary observable in II is the electromagnetic field intensity rather than the field amplitude, the phase of the interferometric signal is lost.
 Since a complete reconstruction of a source's brightness distribution requires phase information, the challenge is to recover the phase of the signal.
@@
 Convolutional Neural Networks (CNNs), with their specialized architecture for processing two-dimensional datasets, are a natural choice for image processing tasks.
-In astronomical image reconstruction projects, a common challenge is that the ground-truth data are often noisy, incomplete, or both.
+In astronomical image reconstruction projects, a common challenge is that the interferometric data are typically undersampled as well as noisy.
 Therefore, the CNN architectures and deep learning methods employed must be capable of reliably learning both the global context of the training dataset and the local features within it.
@@
 
-In the astrophysical context, \cite{schawinski2017galaxypics} employed a cGAN model to recover features—such as spiral arms, central bulges, and disk structures—of galaxies from noise-affected images.
+In the astrophysical context, \cite{schawinski2017galaxypics} employed a GAN model to recover features—such as spiral arms, central bulges, and disk structures—of galaxies from noise-affected images.
 \cite{mustafa2019cosmogan} developed and customized a Deep Convolutional GAN, dubbed \textquotedblleft CosmoGAN\textquotedblright, capable of generating high-fidelity weak-lensing convergence maps of the dark matter distribution that statistically reproduce real weak lensing structures.
@@
 
-In this paper, we propose a conditional Generative Adversarial Network (cGAN) model \citep{isola2017image} to reconstruct images of fast-rotating stars using their simulated Intensity Interferograms and simulated sky-intensity distributions as input data for training, testing, and validation.
+In this paper, we propose a conditional Generative Adversarial Network (cGAN) model \citep[following][]{isola2017image} to reconstruct images of fast-rotating stars using their simulated Intensity Interferograms and simulated sky-intensity distributions as input data for training, testing, and validation.
 We consider four Imaging Cherenkov Telescope Arrays (IACTs) and simulation observation of a fast-rotating star.

### 2025-07-16 Phase_II/draft/prev/main.tex
colorbar
edits

--- 2025-04-30 Phase_II/draft/main.tex
@@
 
+\author[Rai et al.]{Km Nitu Rai,$^{1,2}$ Yuri van der Burg,$^{3}$ Soumen Basak,$^{1}$ Prasenjit Saha,$^{3}$ and
+	Subrata Sarangi$^{4,5}$ \\ \\
+	$^{1}$School of Physics, Indian Institute of Science Education and Research Thiruvananthapuram, Maruthamala PO,
+	Vithura,\\ Thiruvananthapuram 695551, Kerala, India \\
+	$^{2}$Aryabhatta Research Institute of Observational Sciences, Manora Peak, Nainital 263129, India. \\
+	$^{3}$Physik-Institut, University of Zurich, Winterthurerstrasse 190, 8057 Zurich, Switzerland \\
+	$^{4}$School of Applied Sciences, Centurion University of Technology and Management, Odisha-752050, India. \\
+    $^5$ Visiting Associate, Inter-University Centre for Astronomy and Astrophysics, Post Bag 4, Ganeshkhind, Pune 411 007,\\ Maharashtra, India.}
+
 \begin{document}

### 2025-07-17 Phase_II/draft/ParaGan.tex
article

@@
 	\label{fig:cen}
-\end{figure*}
-\begin{figure*}
-	\centering
-	\begin{subfigure}{0.33\linewidth}
-		\includegraphics[width=\linewidth]{fig/moments/mom3.png}
-		\caption{The 2nd order moment $\mu_{11}$.}
-		\label{fig:mom4}
-	\end{subfigure}\hfill
-	\begin{subfigure}{0.33\linewidth}
-		\includegraphics[width=\linewidth]{fig/moments/mom4.png}
-		\caption{The 2nd order moment $\mu_{20}$.}
-		\label{fig:mom5}
-	\end{subfigure}\hfill
-	\begin{subfigure}{0.33\linewidth}
-		\includegraphics[width=\linewidth]{fig/moments/mom5.png}
-		\caption{The 2nd order moment $\mu_{02}$.}
-		\label{fig:mom6}
-	\end{subfigure}\hfill
-	\caption{The second-order central moments provide information about the size and shape of stellar objects.
-This set of figures shows all the second-order central moments for ground truth and predicted images generated by trained GAN.}
-	\label{fig:struc}
-\end{figure*}
-\begin{figure*}
-	\centering
-	\begin{subfigure}{0.50\linewidth}
-		\includegraphics[width=\linewidth]{fig/moments/mom6.png}
-		\caption{The 3rd order moment $\mu_{30}$.}
-		\label{fig:mom7}
-	\end{subfigure}\hfill
-	\begin{subfigure}{0.50\linewidth}
-		\includegraphics[width=\linewidth]{fig/moments/mom7.png}
-		\caption{The 3rd order moment $\mu_{03}$.}
-		\label{fig:mom8}
-	\end{subfigure}\hfill
-	\begin{subfigure}{0.50\linewidth}
-		\includegraphics[width=\linewidth]{fig/moments/mom8.png}
-		\caption{The 3rd order moment $\mu_{21}$.}
-		\label{fig:mom9}
-	\end{subfigure}\hfill
-	\begin{subfigure}{0.50\linewidth}
-		\includegraphics[width=\linewidth]{fig/moments/mom9.png}
-		\caption{The 3rd order moment $\mu_{12}$.}
-		\label{fig:mom10}
-	\end{subfigure}\hfill
-	\caption{This set of figures shows all the 3rd-order central moments for ground truth and predicted images generated by trained GAN.
-It calculates the skewness and evaluates the brightness distribution of images.}
-	\label{fig:moments}
 \end{figure*}

### 2025-07-17 Phase_II/draft/Result.tex
article

@@
 
+\begin{figure*}
+	\centering
+	\begin{subfigure}{0.33\linewidth}
+		\includegraphics[width=\linewidth]{fig/moments/mom3.png}
+		\caption{The 2nd order moment $\mu_{11}$.}
+		\label{fig:mom4}
+	\end{subfigure}\hfill
+	\begin{subfigure}{0.33\linewidth}
+		\includegraphics[width=\linewidth]{fig/moments/mom4.png}
+		\caption{The 2nd order moment $\mu_{20}$.}
+		\label{fig:mom5}
+	\end{subfigure}\hfill
+	\begin{subfigure}{0.33\linewidth}
+		\includegraphics[width=\linewidth]{fig/moments/mom5.png}
+		\caption{The 2nd order moment $\mu_{02}$.}
+		\label{fig:mom6}
+	\end{subfigure}\hfill
+	\caption{The second-order central moments provide information about the size and shape of stellar objects.
+This set of figures shows all the second-order central moments for ground truth and predicted images generated by trained GAN.}
+	\label{fig:struc}
+\end{figure*}
+\begin{figure*}
+	\centering
+	\begin{subfigure}{0.50\linewidth}
+		\includegraphics[width=\linewidth]{fig/moments/mom6.png}
+		\caption{The 3rd order moment $\mu_{30}$.}
+		\label{fig:mom7}
+	\end{subfigure}\hfill
+	\begin{subfigure}{0.50\linewidth}
+		\includegraphics[width=\linewidth]{fig/moments/mom7.png}
+		\caption{The 3rd order moment $\mu_{03}$.}
+		\label{fig:mom8}
+	\end{subfigure}\hfill
+	\begin{subfigure}{0.50\linewidth}
+		\includegraphics[width=\linewidth]{fig/moments/mom8.png}
+		\caption{The 3rd order moment $\mu_{21}$.}
+		\label{fig:mom9}
+	\end{subfigure}\hfill
+	\begin{subfigure}{0.50\linewidth}
+		\includegraphics[width=\linewidth]{fig/moments/mom9.png}
+		\caption{The 3rd order moment $\mu_{12}$.}
+		\label{fig:mom10}
+	\end{subfigure}\hfill
+	\caption{This set of figures shows all the 3rd-order central moments for ground truth and predicted images generated by trained GAN.
+It calculates the skewness and evaluates the brightness distribution of images.}
+	\label{fig:moments}
+\end{figure*}
 \subsection{The reconstructed Parameters for object}

### 2025-07-17 Phase_II/draft/intro.tex
article

@@
 It was suggested that such observations could be carried out during bright, moonlit nights when $\gamma$-ray observations based on upper atmospheric Cherenkov showers were not feasible.
-This approach has the potential to enhance the scientific output of existing IACT facilities, and especially of the upcoming Cherenkov Telescope Array (CTAO).
-SII observations at VERITAS, MAGIC, and HESS are now appearing
-\citep[e.g.,][]{2024ApJ...966...28A,2024MNRAS.529.4387A,2025MNRAS.537.2334V}
-Simulations \citep[e.g.,][]{10.1093/mnras/stab2391, 10.1093/mnras/stac2433} have argued that recent advancements in photon detectors could be effective in achieving high-precision measurements of parameters for stellar objects
+This approach has the potential to enhance the scientific output of existing IACT facilities, and especially of the upcoming Cherenkov Telescope Array Observatory (CTAO).
+SII observations at VERITAS, MAGIC, and HESS are now appearing \citep[e.g.,][]{2024ApJ...966...28A,2024MNRAS.529.4387A,2025MNRAS.537.2334V}.
+Simulations \citep[e.g.,][]{10.1093/mnras/stab2391, 10.1093/mnras/stac2433} have argued that recent advancements in photon detectors could be effective in achieving high-precision measurements of parameters for stellar objects.
 

### 2025-07-17 Phase_II/draft/main.tex
article

--- 2025-04-30 Phase_II/draft/main.tex
@@
-\documentclass[fleqn,usenatbib,twocolumn]{mnras}
-\usepackage[utf8]{inputenc}
+\documentclass[fleqn,usenatbib,twocolumn, 11pt]{article}
+\usepackage[english]{babel}
+\usepackage[left=0.8in, right=0.8in, bottom=0.8in, top=0.8in]{geometry}
 \usepackage{graphicx}
-\usepackage{mathtools}
-\usepackage{siunitx}
-\usepackage{enumerate}
 \usepackage{caption,subcaption}
-\usepackage{comment}
-\captionsetup{compatibility=false}
-\usepackage{animate}
+\usepackage{charter}
 \usepackage{amsmath} % For \text and many other math symbols
@@
 \usepackage{amsfonts} % For \mathbb
-%%%%%
-\usepackage{color}
-%\usepackage[normalem]{ulem}
-\usepackage{soul}
-\usepackage{ulem}
-\usepackage{comment}
+\usepackage{xcolor}
+\usepackage{wrapfig}
+\usepackage[colorlinks=true, allcolors=blue]{hyperref}
+\usepackage{siunitx}
+\usepackage[numbers]{natbib}
+\usepackage{authblk}
+\usepackage[normalem]{ulem}
 
+\newcommand{\mias}{$\SI{}{\micro{\rm as}}$}
+
+% set the space between references
+\setlength{\bibsep}{3pt}
 \newcommand{\abs}[1]{\left|#1\right|}
@@
 
-\title{Generative AI for image reconstruction in Intensity Interferometry: a first attempt}
+\title{Radial Pulsations in Polaris: A Secondary Science Application of Cherenkov Telescopes via Intensity Interferometry}
 \date{}
+
+\author[Rai et al.]{Km Nitu Rai,$^{1,2}$, Yuri van der Burg$^{3}$, Soumen Basak$^{1}$, Prasenjit Saha,$^{3}$ and
+	Subrata Sarangi$^{4,5}$ \\
+
+	\textit{
+	$^{1}$School of Physics, Indian Institute of Science Education and Research Thiruvananthapuram, Maruthamala PO, Vithura, Thiruvananthapuram 695551, Kerala, India.} \\
+	\textit{
+	$^{2}$Aryabhatta Research Institute of Observational Sciences, Manora Peak, Nainital 263129, India.} \\
+	\textit{
+	$^{3}$Physik-Institut, University of Zurich, Winterthurerstrasse 190, 8057 Zurich, Switzerland.} \\
+	\textit{
+	$^{4}$School of Applied Sciences, Centurion University of Technology and Management, Odisha-752050, India.} \\
+	\textit{
+	$^5$ Visiting Associate, Inter-University Centre for Astronomy and Astrophysics, Post Bag 4, Ganeshkhind, Pune 411 007, Maharashtra, India.}}
 
@@
 	\maketitle
-
 \begin{abstract}
@@
 
-\bibliographystyle{mnras}
+\bibliographystyle{apsrev4-1}
 \bibliography{refs}

### 2025-07-17 Phase_II/draft/GAN.tex
article
rearrange

@@
 \section{Generative Adversarial Networks}
+\begin{figure*}[hbt]
+	\centering
+	\begin{subfigure}{0.5\linewidth}
+		\centering
+		\includegraphics[width=\textwidth]{fig/analysis/Plot_learning_rate_disc_loss.pdf}
+		\caption{Discriminator loss for three different learning rates. }
+		\label{fig:Plot_learning_rate_discloss}
+	\end{subfigure}\hfill
+	\begin{subfigure}{0.5\linewidth}
+		\centering
+		\includegraphics[width=\textwidth]{fig/analysis/Plot_learning_rate_gen_total_loss.pdf}
+		\caption{Total generator loss for different learning rates (eqn. (\ref{eq:total_gen_loss})).}
+		\label{fig:Plot_learning_rate_genloss}
+	\end{subfigure}\hfill
+	\caption{Generator and discriminator losses for three different learning rates.
+The left figure shows the total discriminator loss, and the right figure shows the total generator loss.
+There is no significant difference, but the highest learning rate might be prone to outliers.
+}
+	\label{fig:Plot_learning_rate_loss}
+\end{figure*}
 Generative Adversarial Networks (GANs) were introduced by \cite{goodfellow2014generative}.
@@
 \end{equation}
-\begin{figure}
+\begin{figure*}[hbt]
 	\centering
-	\includegraphics[width=\linewidth]{fig/ellipse1612.jpg}
-	\caption{Merged image, which includes the original and the sparsely sampled Fourier plane. It is exactly what the GAN receives. }
-	\label{fig:GANinput}
-\end{figure}
-\begin{figure}
-	\centering
-	\begin{subfigure}{\linewidth}
-		\centering
-		\includegraphics[width=\textwidth]{fig/analysis/Plot_learning_rate_disc_loss.pdf}
-		\caption{Discriminator loss for three different learning rates. }
-		\label{fig:Plot_learning_rate_discloss}
-	\end{subfigure}\hfill
-	\begin{subfigure}{\linewidth}
-		\centering
-		\includegraphics[width=\textwidth]{fig/analysis/Plot_learning_rate_gen_total_loss.pdf}
-		\caption{Total generator loss for different learning rates (eqn. (\ref{eq:total_gen_loss})).}
-		\label{fig:Plot_learning_rate_genloss}
-	\end{subfigure}\hfill
-	\caption{Generator and discriminator losses for three different learning rates.
-The upper figure shows the total discriminator loss, and the lower figure shows the total generator loss.
-There is no significant difference, but the highest learning rate might be prone to outliers.
-}
-	\label{fig:Plot_learning_rate_loss}
-\end{figure}
-\begin{figure}
-	\centering
-	\begin{subfigure}{\linewidth}
+	\begin{subfigure}{0.5\linewidth}
 		\centering
@@
 	\end{subfigure}\hfill
-	\begin{subfigure}{\linewidth}
+	\begin{subfigure}{0.5\linewidth}
 		\centering
@@
 	\label{fig:Plot_kernel_size_loss}
-\end{figure}
-\begin{figure*}
+\end{figure*}
+\begin{figure*}[hbt]
 	\centering
@@
 \end{figure*}
-\begin{figure*}
+\begin{figure*}[hbt]
 	\centering

### 2025-07-17 Phase_II/draft/II.tex
article
rearrange

@@
 \section{Intensity Interferometry (II) with IACT arrays}
-
+\begin{figure}[hbt]
+	\centering
+	\includegraphics[width=\linewidth]{fig/baseline.png}
+	\caption{The tracking of baselines with four telescopes arranged in fig.~\ref{fig:teles} for one night of observation.}
+	\label{fig:base}
+\end{figure}
+\begin{figure}[hbt]
+	\centering
+	\includegraphics[width=\linewidth]{fig/ellipse/ellipse1612.jpg}
+	\caption{This figure shows the simulated fast rotating star. The brightness is highest at the pole and there is gravitational darkening at the equator.}
+	\label{fig:image}
+\end{figure}
+\begin{figure*}[hbt]
+	\centering
+	\begin{subfigure}{0.5\linewidth}
+		\includegraphics[width=\linewidth]{fig/ft/ft.jpg}
+		\caption{The signal (absolute value of the Fourier transform of the source).}
+	\end{subfigure}\hfill
+	\begin{subfigure}{0.5\linewidth}
+		\includegraphics[width=\linewidth]{fig/ft/ft_log.jpg}
+		\caption{The logarithm of the signal.}
+	\end{subfigure}
+	\caption{Absolute value of the two-dimensional Fast Fourier Transform of Fig.~\ref{fig:image} measured by Intensity Interferometry, and observation of maximum $(u, v)$ plane with the assumed telescope separations can be completed with the help of Earth rotation.}
+	\label{fig:ft}
+\end{figure*}
 This section presents a brief conceptual overview of how an array of telescopes is used to perform II observations, and explains the Signal-to-Noise Ratio (SNR) from these measurements.
-
+\begin{figure*}[hbt]
+	\centering
+	\begin{subfigure}{0.5\linewidth}
+		\includegraphics[width=\linewidth]{fig/ft/ft_base.jpg}
+		\caption{The signal as samples by the baselines.}
+	\end{subfigure}\hfill
+	\begin{subfigure}{0.5\linewidth}
+		\includegraphics[width=\linewidth]{fig/ft/ft_log_base.jpg}
+		\caption{The logarithmic signal as sampled by the baselines.}
+	\end{subfigure}
+	\caption{The left panel shows the absolute value of the two-dimensional Fast Fourier Transform of fig.~\ref{fig:image} measured by baselines shown in fig.~\ref{fig:teles}.
+The right panel shows the same on logarithmic scale}
+	\label{fig:ft_base}
+\end{figure*}
 \subsection{The signal for II}\label{sec:signal}
@@
 \subsection{The Signal-to-Noise Ratio for II}
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{fig/telescope.png}
-	\caption{The telescope configuration with similar properties each used to simulate the signal for II.}
-	\label{fig:teles}
-\end{figure}
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{fig/baseline.png}
-	\caption{The tracking of baselines with four telescopes arranged in fig.~\ref{fig:teles} for one night of observation.}
-	\label{fig:base}
-\end{figure}
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{fig/ellipse/ellipse1612.jpg}
-	\caption{This figure shows the simulated fast rotating star. The brightness is highest at the pole and there is gravitational darkening at the equator.}
-	\label{fig:image}
-\end{figure}
-\begin{figure*}
-	\centering
-	\begin{subfigure}{0.5\linewidth}
-		\includegraphics[width=\linewidth]{fig/ft/ft.jpg}
-		\caption{The signal (absolute value of the Fourier transform of the source).}
-	\end{subfigure}\hfill
-	\begin{subfigure}{0.5\linewidth}
-		\includegraphics[width=\linewidth]{fig/ft/ft_log.jpg}
-		\caption{The logarithm of the signal.}
-	\end{subfigure}
-	\caption{Absolute value of the two-dimensional Fast Fourier Transform of Fig.~\ref{fig:image} measured by Intensity Interferometry, and observation of maximum $(u, v)$ plane with the assumed telescope separations can be completed with the help of Earth rotation.}
-	\label{fig:ft}
-\end{figure*}
-\begin{figure*}
-	\centering
-	\begin{subfigure}{0.5\linewidth}
-		\includegraphics[width=\linewidth]{fig/ft/ft_base.jpg}
-		\caption{The signal as samples by the baselines.}
-	\end{subfigure}\hfill
-	\begin{subfigure}{0.5\linewidth}
-		\includegraphics[width=\linewidth]{fig/ft/ft_log_base.jpg}
-		\caption{The logarithmic signal as sampled by the baselines.}
-	\end{subfigure}
-	\caption{The left panel shows the absolute value of the two-dimensional Fast Fourier Transform of fig.~\ref{fig:image} measured by baselines shown in fig.~\ref{fig:teles}.
-The right panel shows the same on logarithmic scale}
-	\label{fig:ft_base}
-\end{figure*}
 The primary purpose of IACTs is to study high-energy gamma rays (with energy $E\ \geq 30$ GeV) arriving from cosmic sources, entering the Earth's atmosphere, and initiating Cherenkov showers in the upper atmosphere due to multiple scattering.
@@
 Using this modest amount of signal from one night's observation, we have trained a cGAN to construct the image of the source.
+\begin{figure}[hbt]
+	\centering
+	\includegraphics[width=\linewidth]{fig/ellipse1612.jpg}
+	\caption{Merged image, which includes the original and the sparsely sampled Fourier plane. It is exactly what the GAN receives. }
+	\label{fig:GANinput}
+\end{figure}

### 2025-07-17 Phase_II/draft/GAN.tex
temporary

@@
 \begin{figure*}[hbt]
-	\centering
-	\begin{subfigure}{0.5\linewidth}
-		\centering
-		\includegraphics[width=\textwidth]{fig/analysis/Plot_learning_rate_disc_loss.pdf}
-		\caption{Discriminator loss for three different learning rates. }
-		\label{fig:Plot_learning_rate_discloss}
-	\end{subfigure}\hfill
-	\begin{subfigure}{0.5\linewidth}
-		\centering
-		\includegraphics[width=\textwidth]{fig/analysis/Plot_learning_rate_gen_total_loss.pdf}
+	%\centering
+	%\begin{subfigure}{0.5\linewidth}
+	\includegraphics[width=.49\textwidth]{fig/analysis/Plot_learning_rate_disc_loss.pdf}\hfil
+	%\caption{Discriminator loss for three different learning rates. }
+	%	\label{fig:Plot_learning_rate_discloss}
+	%\end{subfigure}\hfill
+	%\begin{subfigure}{0.5\linewidth}
+	\includegraphics[width=.49\textwidth]{fig/analysis/Plot_learning_rate_gen_total_loss.pdf}
 		\caption{Total generator loss for different learning rates (eqn. (\ref{eq:total_gen_loss})).}
-		\label{fig:Plot_learning_rate_genloss}
-	\end{subfigure}\hfill
+	%	\label{fig:Plot_learning_rate_genloss}
+	%\end{subfigure}\hfill
 	\caption{Generator and discriminator losses for three different learning rates.
@@
 \begin{figure*}[hbt]
-	\centering
-	\begin{subfigure}{0.5\linewidth}
-		\centering
-		\includegraphics[width=\textwidth]{fig/analysis/Plot_Kernel_size_disc_loss.pdf}
-		\caption{Discriminator loss for three different kernel sizes. }
-		\label{fig:Plot_kernel_size_discloss}
-	\end{subfigure}\hfill
-	\begin{subfigure}{0.5\linewidth}
-		\centering
-		\includegraphics[width=\textwidth]{fig/analysis/Plot_Kernel_size_gen_total_loss.pdf}
-		\caption{Total generator loss for three different kernel sizes.}
-		\label{fig:Plot_kernel_size_genloss}
-	\end{subfigure}\hfill
+  %\begin{subfigure}{0.5\linewidth}
+  \includegraphics[width=.49\textwidth]{fig/analysis/Plot_Kernel_size_disc_loss.pdf}
+  %\caption{Discriminator loss for three different kernel sizes. }
+  %\label{fig:Plot_kernel_size_discloss}
+  %\end{subfigure}\hfill
+  %\begin{subfigure}{0.5\linewidth}
+  \includegraphics[width=.49\textwidth]{fig/analysis/Plot_Kernel_size_gen_total_loss.pdf}
+  %\caption{Total generator loss for three different kernel sizes.}
+  %\label{fig:Plot_kernel_size_genloss}
+  %\end{subfigure}\hfill
   \caption{Generator and discriminator losses for three different kernel sizes in the convolutional layers.
@@
 \begin{figure*}[hbt]
-	\centering
-	\begin{subfigure}{0.5\linewidth}
-		\centering
-		\includegraphics[width=\textwidth]{fig/analysis/Plot_noise_factor_disc_loss.pdf}
-		\caption{Discriminator loss for different noise percentages.}
-		\label{fig:Plot_noise_discloss}
-	\end{subfigure}\hfill
-	\begin{subfigure}{0.5\linewidth}
-		\centering
-		\includegraphics[width=\textwidth]{fig/analysis/Plot_noise_factor_gen_total_loss.pdf}
-		\caption{Generator losses for different noise percentages.}
-		\label{fig:Plot_noise_genloss}
-	\end{subfigure}\hfill
+  %\begin{subfigure}{0.5\linewidth}
+  \includegraphics[width=.49\textwidth]{fig/analysis/Plot_noise_factor_disc_loss.pdf}
+  %\caption{Discriminator loss for different noise percentages.}
+  %\label{fig:Plot_noise_discloss}
+  %\end{subfigure}\hfill
+  %\begin{subfigure}{0.5\linewidth}
+  %\centering
+  \includegraphics[width=.49\textwidth]{fig/analysis/Plot_noise_factor_gen_total_loss.pdf}
+  %\caption{Generator losses for different noise percentages.}
+  %\label{fig:Plot_noise_genloss}
+  %\end{subfigure}\hfill
   \caption{Effect of the Salt and Pepper noise introduced in the images.
@@
 \begin{figure*}[hbt]
-	\centering
-	\begin{subfigure}{0.5\linewidth}
-		\centering
-		\includegraphics[width=\textwidth]{fig/analysis/Plot_Batchsize_disc_loss.pdf}
-		\caption{Discriminator loss for different batch sizes.}
-		\label{fig:Plot_batchsize_discloss}
-	\end{subfigure}\hfill
-	\begin{subfigure}{0.5\linewidth}
-		\centering
-		\includegraphics[width=\textwidth]{fig/analysis/Plot_Batchsize_gen_total_loss.pdf}
-		\caption{Generator losses for different batch sizes.}
-		\label{fig:Plot_batchsize_genloss}
-	\end{subfigure}\hfill
+  %\begin{subfigure}{0.5\linewidth}
+  \includegraphics[width=.49\textwidth]{fig/analysis/Plot_Batchsize_disc_loss.pdf}\hfill
+  %\caption{Discriminator loss for different batch sizes.}
+  %\label{fig:Plot_batchsize_discloss}
+  %\end{subfigure}\hfill
+  %\begin{subfigure}{0.5\linewidth}
+  \includegraphics[width=.49\textwidth]{fig/analysis/Plot_Batchsize_gen_total_loss.pdf}
+  %\caption{Generator losses for different batch sizes.}
+  %\label{fig:Plot_batchsize_genloss}
+  %\end{subfigure}\hfill
   \caption{Loss functions for two different batch sizes. Large batch sizes seem to be more robust, but they also increase training time significantly. }
@@
 \begin{figure*}[hbt]
-	\centering
-	\begin{subfigure}{0.5\linewidth}
-		\centering
-		\includegraphics[width=\textwidth]{fig/analysis/Plot_Disc_rep_disc_loss.pdf}
-		\caption{Discriminator loss for different Discriminator training.}
-		\label{fig:Plot_discrep_discloss}
-	\end{subfigure}\hfill
-	\begin{subfigure}{0.5\linewidth}
-		\centering
-		\includegraphics[width=\textwidth]{fig/analysis/Plot_Disc_rep_gen_total_loss.pdf}
-		\caption{Generator losses for different Discriminator training.}
-		\label{fig:Plot_discrep_genloss}
-	\end{subfigure}\hfill
+  %\begin{subfigure}{0.5\linewidth}
+  \includegraphics[width=.49\textwidth]{fig/analysis/Plot_Disc_rep_disc_loss.pdf}\hfil
+  %\caption{Discriminator loss for different Discriminator training.}
+  %\label{fig:Plot_discrep_discloss}
+  %\end{subfigure}\hfill
+  %\begin{subfigure}{0.5\linewidth}
+  \includegraphics[width=.49\textwidth]{fig/analysis/Plot_Disc_rep_gen_total_loss.pdf}
+  %\caption{Generator losses for different Discriminator training.}
+  %\label{fig:Plot_discrep_genloss}
+  %\end{subfigure}\hfill
   \caption{The amount of Discriminator training has a high impact on the Discriminator score.
@@
 \begin{figure*}[hbt]
-	\centering
-	\begin{subfigure}{0.5\linewidth}
-		\centering
-		\includegraphics[width=\textwidth]{fig/analysis/Plot_N_telescopes_disc_loss.pdf}
-		\caption{Discriminator loss for different amounts of telescopes.}
-		\label{fig:Plot_telescopes_discloss}
-	\end{subfigure}\hfill
-	\begin{subfigure}{0.5\linewidth}
-		\centering
-		\includegraphics[width=\textwidth]{fig/analysis/Plot_N_telescopes_gen_total_loss.pdf}
-		\caption{Generator loss for different amount of telescopes.}
-		\label{fig:Plot_telescopes_genloss}
-	\end{subfigure}\hfill
+  %\begin{subfigure}{0.5\linewidth}
+  \includegraphics[width=.49\textwidth]{fig/analysis/Plot_N_telescopes_disc_loss.pdf}\hfil
+  %\caption{Discriminator loss for different amounts of telescopes.}
+  %\label{fig:Plot_telescopes_discloss}
+  %\end{subfigure}\hfill
+  %\begin{subfigure}{0.5\linewidth}
+  \includegraphics[width=\textwidth]{fig/analysis/Plot_N_telescopes_gen_total_loss.pdf}\hfil
+  %\caption{Generator loss for different amount of telescopes.}
+  %\label{fig:Plot_telescopes_genloss}
+  %\end{subfigure}\hfill
   \caption{The number of telescopes has a very impact on the model performance.

### 2025-07-17 Phase_II/draft/II.tex
temporary

@@
 \begin{figure*}[hbt]
-	\centering
-	\begin{subfigure}{0.5\linewidth}
-		\includegraphics[width=\linewidth]{fig/ft/ft.jpg}
-		\caption{The signal (absolute value of the Fourier transform of the source).}
-	\end{subfigure}\hfill
-	\begin{subfigure}{0.5\linewidth}
-		\includegraphics[width=\linewidth]{fig/ft/ft_log.jpg}
-		\caption{The logarithm of the signal.}
-	\end{subfigure}
-	\caption{Absolute value of the two-dimensional Fast Fourier Transform of Fig.~\ref{fig:image} measured by Intensity Interferometry, and observation of maximum $(u, v)$ plane with the assumed telescope separations can be completed with the help of Earth rotation.}
+	%\begin{subfigure}{0.5\linewidth}
+		\includegraphics[width=.49\linewidth]{fig/ft/ft.jpg}\hfil
+	%\caption{The signal (absolute value of the Fourier transform of the source).}
+	%\end{subfigure}\hfill
+	%\begin{subfigure}{0.5\linewidth}
+		\includegraphics[width=.49\linewidth]{fig/ft/ft_log.jpg}
+		%\caption{The logarithm of the signal.}
+	%\end{subfigure}
+	\caption{Absolute value of the two-dimensional Fast Fourier Transform of Fig.~\ref{fig:image} measured by Intensity Interferometry in the $(u, v)$ plane.
+\textit{Left.}~Signal on a linear scale.
+\text{Right}.~Signal on a logarithmic scale.}
 	\label{fig:ft}
@@
 \begin{figure*}[hbt]
-	\centering
-	\begin{subfigure}{0.5\linewidth}
-		\includegraphics[width=\linewidth]{fig/ft/ft_base.jpg}
-		\caption{The signal as samples by the baselines.}
-	\end{subfigure}\hfill
-	\begin{subfigure}{0.5\linewidth}
-		\includegraphics[width=\linewidth]{fig/ft/ft_log_base.jpg}
-		\caption{The logarithmic signal as sampled by the baselines.}
-	\end{subfigure}
+	%\centering
+	%\begin{subfigure}{0.5\linewidth}
+		\includegraphics[width=.49\linewidth]{fig/ft/ft_base.jpg}\hfil
+		%\caption{The signal as samples by the baselines.}
+	%\end{subfigure}\hfill
+	%\begin{subfigure}{0.5\linewidth}
+		\includegraphics[width=.49\linewidth]{fig/ft/ft_log_base.jpg}
+		%\caption{The logarithmic signal as sampled by the baselines.}
+	%\end{subfigure}
 	\caption{The left panel shows the absolute value of the two-dimensional Fast Fourier Transform of fig.~\ref{fig:image} measured by baselines shown in fig.~\ref{fig:teles}.

### 2025-07-17 Phase_II/draft/Result.tex
rearrange
temporary

--- 2025-07-16 Phase_II/draft/Result.tex
@@
 However, further improvements can be achieved by increasing the number of telescopes to maximize coverage of the $(u, v)$ plane, making the existing and upcoming CTAO an ideal candidate for this approach.
+
 \subsection{Evaluation of GAN using Moments}
@@
 
+\begin{figure*}
+  %\begin{subfigure}{0.33\linewidth}
+  \includegraphics[width=.32\linewidth]{fig/moments/mom3.png}\hfil
+  %\caption{The 2nd order moment $\mu_{11}$.}
+  %\label{fig:mom4}
+  %\end{subfigure}\hfill
+  %\begin{subfigure}{0.33\linewidth}
+  \includegraphics[width=.32\linewidth]{fig/moments/mom4.png}\hfil
+  %\caption{The 2nd order moment $\mu_{20}$.}
+  %\label{fig:mom5}
+  %\end{subfigure}\hfill
+  %\begin{subfigure}{0.33\linewidth}
+  \includegraphics[width=.32\linewidth]{fig/moments/mom5.png}
+  %\caption{The 2nd order moment $\mu_{02}$.}
+  %\label{fig:mom6}
+  %\end{subfigure}\hfill
+  \caption{The second-order central moments provide information about the size and shape of stellar objects.
+Shown here are all the second-order central moments for ground truth and predicted images generated by the trained GAN.
+From left to right these are $\mu_{11},\mu_{20},\mu_{02}$.}
+	\label{fig:struc}
+\end{figure*}
+\begin{figure*}
+  %\begin{subfigure}{0.50\linewidth}
+  \includegraphics[width=.49\linewidth]{fig/moments/mom6.png}\hfil
+  %\caption{The 3rd order moment $\mu_{30}$.}
+  %\label{fig:mom7}
+  %\end{subfigure}\hfill
+  %\begin{subfigure}{0.50\linewidth}
+  \includegraphics[width=.49\linewidth]{fig/moments/mom7.png}
+  %\caption{The 3rd order moment $\mu_{03}$.}
+  %\label{fig:mom8}
+  %\end{subfigure}\hfill
+  %\begin{subfigure}{0.50\linewidth}
+  \includegraphics[width=.49\linewidth]{fig/moments/mom8.png}
+  %\caption{The 3rd order moment $\mu_{21}$.}
+  %\label{fig:mom9}
+  %\end{subfigure}\hfill
+  %\begin{subfigure}{0.50\linewidth}
+  \includegraphics[width=.49\linewidth]{fig/moments/mom9.png}
+  %\caption{The 3rd order moment $\mu_{12}$.}
+  %\label{fig:mom10}
+  %\end{subfigure}\hfill
+  \caption{Shown here are all the third-order central moments for
+    ground truth and predicted images generated by the trained GAN.
+    They represent the skewness of the brightness distributions.  The
+    panels in reading order show
+    $\mu_{30},\mu_{03},\mu_{21},\mu_{12}$.}
+  \label{fig:moments}
+\end{figure*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2025-07-17 Phase_II/draft/main.tex
rearrange
temporary

--- 2025-04-30 Phase_II/draft/main.tex
@@
-\documentclass[fleqn,usenatbib,twocolumn]{mnras}
-\usepackage[utf8]{inputenc}
-\usepackage{graphicx}
-\usepackage{mathtools}
-\usepackage{siunitx}
-\usepackage{enumerate}
-\usepackage{caption,subcaption}
-\usepackage{comment}
-\captionsetup{compatibility=false}
-\usepackage{animate}
-\usepackage{amsmath} % For \text and many other math symbols
-\usepackage{amssymb} % For \mathbb
-\usepackage{amsfonts} % For \mathbb
-%%%%%
-\usepackage{color}
-%\usepackage[normalem]{ulem}
-\usepackage{soul}
-\usepackage{ulem}
-\usepackage{comment}
+\documentclass[twocolumn]{emulateapj}
 
+\usepackage{amsmath}
+
+\newcommand{\mias}{$\SI{}{\micro{\rm as}}$}
 \newcommand{\abs}[1]{\left|#1\right|}
@@
 
-\title{Generative AI for image reconstruction in Intensity Interferometry: a first attempt}
-\date{}
+\begin{document}
 
-\begin{document}
-\maketitle
+\title{Generative AI for image reconstruction\\ in Intensity Interferometry: a first attempt}
+
+\author{Km Nitu Rai,$^{1,2}$, Yuri van der Burg$^{3}$, Soumen
+  Basak$^{1}$, Prasenjit Saha,$^{3}$ and Subrata Sarangi$^{4,5}$}
+
+\affiliation{$^{1}$School of Physics, Indian Institute of Science
+  Education and Research Thiruvananthapuram, Maruthamala PO, Vithura,
+  Thiruvananthapuram 695551, Kerala, India.}
+
+\affiliation{$^{2}$Aryabhatta Research Institute of Observational Sciences, Manora Peak, Nainital 263129, India.}
+
+\affiliation{$^{3}$Physik-Institut, University of Zurich,
+  Winterthurerstrasse 190, 8057 Zurich, Switzerland.}
+
+\affiliation{$^{4}$School of Applied Sciences, Centurion University of
+  Technology and Management, Odisha-752050, India.}
+
+\affiliation{$^5$ Visiting Associate, Inter-University Centre for Astronomy and Astrophysics, Post Bag 4, Ganeshkhind, Pune 411 007, Maharashtra, India.}
 
@@
 \end{abstract}
+
+\maketitle
+
 \input{intro}
@@
 
-\bibliographystyle{mnras}
+\bibliographystyle{aa}
 \bibliography{refs}

### 2025-07-17 Phase_II/draft/Result.tex
..
Para and result

@@
 
+\begin{figure*}
+	\includegraphics[width=.32\linewidth]{fig/moments/mom0.png}\hfil
+	\includegraphics[width=.32\linewidth]{fig/moments/mom1.png}\hfil
+	\includegraphics[width=.32\linewidth]{fig/moments/mom2.png}\hfil
+	\caption{This set of figures shows the comparison of monopole, x-centroid, and y-centroid for ground truth and predicted images generated by trained GAN.}
+	\label{fig:cen}
+\end{figure*}
 \subsection{Evaluation of GAN using Moments}
@@
 \end{equation}
-Figure~\ref{fig:mom1} displays the monopole values for 50 reconstructed images.
+The left figure of Fig.~\ref{fig:cen} displays the monopole values for 50 reconstructed images.
 The plot reveals a linear relationship between the monopole of the ground truth (real image) on the $x$-axis and that of the predicted (reconstructed) image on the $y$-axis, consistent across sources of varying shapes and sizes.
@@
 For these aspects, higher-order moments are necessary.
-%%%%%%%%%%%%%%This is original %%%%%%%%%%%%%%%%%%%%%
-%To be decided%%%%%%%
+
 The center of mass for the fast-rotating star or any other stellar object is calculated using the centroid ($x$-centroid and $y$-centroid).
@@
 \end{equation}
-Fig.~\ref{fig:mom2} and Fig.~\ref{fig:mom3} show the comparison of the $x$-centroid and $y$-centroid for 50 predicted images with respect to ground truths, respectively.
+The middle and right figure of Fig.~\ref{fig:cen} show the comparison of the $x$-centroid and $y$-centroid for 50 predicted images with respect to ground truths, respectively.
 The clustering of centroids in a given scale range for all the results explains that the reconstructed image correctly represents the spatial location of the fast-rotating star compared with the ground truth.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%This portion is generated by ChatGPT%%%%%%%%%%
-%%%%To be decided depending on Nitu's reply%%%%
 
@@
 
-Fig.~\ref{fig:mom2} and Fig.~\ref{fig:mom3} compare the centroids ($x_{c}$, $y_{c}$) of 50 predicted images with their corresponding ground truths, respectively.
+The middle and right panel of Fig.~\ref{fig:cen} compare the centroids ($x_{c}$, $y_{c}$) of 50 predicted images with their corresponding ground truths, respectively.
 The clustering of centroids within a specific scale range across all results indicates that the reconstructed images accurately represent the spatial location of the fast-rotating star relative to the ground truth.
@@
 \begin{figure*}
-  %\begin{subfigure}{0.33\linewidth}
   \includegraphics[width=.32\linewidth]{fig/moments/mom3.png}\hfil
-  %\caption{The 2nd order moment $\mu_{11}$.}
-  %\label{fig:mom4}
-  %\end{subfigure}\hfill
-  %\begin{subfigure}{0.33\linewidth}
   \includegraphics[width=.32\linewidth]{fig/moments/mom4.png}\hfil
-  %\caption{The 2nd order moment $\mu_{20}$.}
-  %\label{fig:mom5}
-  %\end{subfigure}\hfill
-  %\begin{subfigure}{0.33\linewidth}
-  \includegraphics[width=.32\linewidth]{fig/moments/mom5.png}
-  %\caption{The 2nd order moment $\mu_{02}$.}
-  %\label{fig:mom6}
-  %\end{subfigure}\hfill
+  \includegraphics[width=.32\linewidth]{fig/moments/mom5.png}\hfil
   \caption{The second-order central moments provide information about the size and shape of stellar objects.
@@
 \begin{figure*}
-  %\begin{subfigure}{0.50\linewidth}
   \includegraphics[width=.49\linewidth]{fig/moments/mom6.png}\hfil
-  %\caption{The 3rd order moment $\mu_{30}$.}
-  %\label{fig:mom7}
-  %\end{subfigure}\hfill
-  %\begin{subfigure}{0.50\linewidth}
-  \includegraphics[width=.49\linewidth]{fig/moments/mom7.png}
-  %\caption{The 3rd order moment $\mu_{03}$.}
-  %\label{fig:mom8}
-  %\end{subfigure}\hfill
-  %\begin{subfigure}{0.50\linewidth}
-  \includegraphics[width=.49\linewidth]{fig/moments/mom8.png}
-  %\caption{The 3rd order moment $\mu_{21}$.}
-  %\label{fig:mom9}
-  %\end{subfigure}\hfill
-  %\begin{subfigure}{0.50\linewidth}
-  \includegraphics[width=.49\linewidth]{fig/moments/mom9.png}
-  %\caption{The 3rd order moment $\mu_{12}$.}
-  %\label{fig:mom10}
-  %\end{subfigure}\hfill
+  \includegraphics[width=.49\linewidth]{fig/moments/mom7.png}\hfil
+  \includegraphics[width=.49\linewidth]{fig/moments/mom8.png}\hfil
+  \includegraphics[width=.49\linewidth]{fig/moments/mom9.png}\hfil
   \caption{Shown here are all the third-order central moments for
@@
 Fig.~\ref{fig:moments} presents all third-order moments for both the ground truth and the reconstructed image.
-The skewness along the $x$ and $y$ axes (\(\mu_{30}\) and \(\mu_{03}\)) appears acceptable, as shown in Fig.~\ref{fig:mom7} and Fig.~\ref{fig:mom8}, where a linear relationship exists between the ground truth and predicted images.
-However, the other higher-order moments (\(\mu_{21}\) and \(\mu_{12}\))—particularly \(\mu_{12}\), as depicted in Fig.~\ref{fig:mom9} and Fig.~\ref{fig:mom10}—do not align as well.
+The skewness along the $x$ and $y$ axes (\(\mu_{30}\) and \(\mu_{03}\)) appears acceptable, as shown in both upper panel of Fig.~\ref{fig:moments}, where a linear relationship exists between the ground truth and predicted images.
+However, the other higher-order moments (\(\mu_{21}\) and \(\mu_{12}\))—particularly \(\mu_{12}\), as depicted in both lower panel of Fig.~\ref{fig:moments}—do not align as well.
 This indicates that further improvement is possible and should be investigated.

### 2025-07-17 Phase_II/draft/GAN.tex
figure
..
edits

@@
 \section{Generative Adversarial Networks}
-\begin{figure*}[hbt]
+\begin{figure*}
 	%\centering
@@
 	\includegraphics[width=.49\textwidth]{fig/analysis/Plot_learning_rate_gen_total_loss.pdf}
-		\caption{Total generator loss for different learning rates (eqn. (\ref{eq:total_gen_loss})).}
+		%\caption{Total generator loss for different learning rates (eqn. (\ref{eq:total_gen_loss})).}
 	%	\label{fig:Plot_learning_rate_genloss}
 	%\end{subfigure}\hfill
-	\caption{Generator and discriminator losses for three different learning rates.
-The left figure shows the total discriminator loss, and the right figure shows the total generator loss.
-There is no significant difference, but the highest learning rate might be prone to outliers.
-}
+	\caption{Discriminator and Generator losses for three different learning rates.
+The left panel shows the total discriminator loss, and the right figure shows the total generator loss (Eq.~\ref{eq:total_gen_loss}).
+There is no significant difference, but the highest learning rate might be prone to outliers.}
 	\label{fig:Plot_learning_rate_loss}
@@
 \end{equation}
-\begin{figure*}[hbt]
+\begin{figure*}
   %\begin{subfigure}{0.5\linewidth}
@@
   %\end{subfigure}\hfill
-  \caption{Generator and discriminator losses for three different kernel sizes in the convolutional layers.
+  \caption{Generator and discriminator losses (left and right panels respectively) for three different kernel sizes in the convolutional layers.
 Here, the smallest kernel size has many outliers, while the largest kernel size seems to be the most stable.}
@@
 \end{figure*}
-\begin{figure*}[hbt]
+\begin{figure*}
   %\begin{subfigure}{0.5\linewidth}
@@
   %\end{subfigure}\hfill
-  \caption{The amount of Discriminator training has a high impact on the Discriminator score.
+  \caption{The left panel shows the Discriminator loss for different Discriminator training, while the right panel shows the Generator losses for different Discriminator training.
+The amount of Discriminator training has a high impact on the Discriminator score.
 The Discriminator repetition indicates the factor by which the Discriminator is trained more with respect to the Generator.}
@@
   %\begin{subfigure}{0.5\linewidth}
-  \includegraphics[width=\textwidth]{fig/analysis/Plot_N_telescopes_gen_total_loss.pdf}\hfil
+  \includegraphics[width=0.49\textwidth]{fig/analysis/Plot_N_telescopes_gen_total_loss.pdf}\hfil
   %\caption{Generator loss for different amount of telescopes.}
@@
   %\end{subfigure}\hfill
-  \caption{The number of telescopes has a very impact on the model performance.
+  \caption{Discriminator loss (left panel) and Generator loss (right panel) for different numbers of telescopes.
+The number of telescopes has a very impact on the model performance.
 If there are only two telescopes (1 baseline), both Discriminator and Generator are not trained smoothly: One gains a big advantage over the other.

### 2025-07-17 Phase_II/draft/II.tex
..
edits

@@
 \section{Intensity Interferometry (II) with IACT arrays}
-\begin{figure}[hbt]
-	\centering
+\begin{figure}
   \includegraphics[width=\linewidth]{fig/baseline.png}
@@
 \begin{figure}[hbt]
-	\centering
   \includegraphics[width=\linewidth]{fig/ellipse/ellipse1612.jpg}
@@
 \end{figure}
-\begin{figure*}[hbt]
+\begin{figure*}
 	%\begin{subfigure}{0.5\linewidth}
@@
 This section presents a brief conceptual overview of how an array of telescopes is used to perform II observations, and explains the Signal-to-Noise Ratio (SNR) from these measurements.
-\begin{figure*}[hbt]
+\begin{figure*}
 	%\centering
@@
 	%\end{subfigure}
-	\caption{The left panel shows the absolute value of the two-dimensional Fast Fourier Transform of fig.~\ref{fig:image} measured by baselines shown in fig.~\ref{fig:teles}.
+  \caption{The left panel shows the absolute value of the two-dimensional Fast Fourier Transform of Fig.~\ref{fig:image} measured by baselines shown in Fig.~\ref{fig:teles}.
 The right panel shows the same on logarithmic scale}
@@
 where $\tau$ is the time delay between the telescopes.
-For spatially coherent and randomly polarized light, eq.~(\ref{eqn:HBT}) reduces to the relation \citep[sometimes called the Siegert relation, see e.g.,][]{acciari2020optical}.
+For spatially coherent and randomly polarized light, Eq.~\eqref{eqn:HBT} reduces to the relation \citep[sometimes called the Siegert relation, see e.g.,][]{acciari2020optical}.
 \begin{equation}
@@
 Values of $\Delta\nu\sim 1\,\mathrm{THz}$ and $\Delta f \sim 1\,\mathrm{GHz}$ are typical of recent work.
-In eq.~(\ref{eqn:HBT2}), $V_{12}$, referred to as the complex visibility function, is the Fourier transform of the source brightness distribution.
+In Eq.~\eqref{eqn:HBT2}, $V_{12}$, referred to as the complex visibility function, is the Fourier transform of the source brightness distribution.
 For a uniform disk it is given by
@@
 where $\theta_D$ is the angular diameter of the star and $b$ is the radial coordinate in the conventional interferometric $(u , v) = (x/\lambda, y/\lambda)$ plane, with $\lambda$ representing the optical wavelength of the filter used for observation.
-It is evident from eq.~(\ref{eqn:absvisib}) that $V_{12}$ contains information about the star's angular diameter.
+It is evident from Eq.~\eqref{eqn:absvisib} that $V_{12}$ contains information about the star's angular diameter.
 However, the phase information is lost since we measure only the absolute value $\vert V_{12} \vert^2$.
@@
 The correlation of these photon arrivals at the telescopes yields the squared visibility Eq.~\eqref{eq:angular_size_meas}, as explained in subsection~\ref{sec:signal}.
-Fig.\ref{fig:ft} shows the signal from the source shown in Fig.~\ref{fig:image} using II, displayed on both linear and logarithmic scales.
+Fig.~\ref{fig:ft} shows the signal from the source shown in Fig.~\ref{fig:image} using II, displayed on both linear and logarithmic scales.
 In practice, only a small part of this information is available, because one has a finite number of baselines corresponding to the finite number $N_T$ of telescopes at our disposal and a limited observation schedule.
@@
 Using this modest amount of signal from one night's observation, we have trained a cGAN to construct the image of the source.
-\begin{figure}[hbt]
-	\centering
+\begin{figure}
   \includegraphics[width=\linewidth]{fig/ellipse1612.jpg}
-	\caption{Merged image, which includes the original and the sparsely sampled Fourier plane. It is exactly what the GAN receives. }
+  \caption{Merged image, which includes the original and the sparsely sampled Fourier plane. It is exactly what the GAN receives.}
   \label{fig:GANinput}

### 2025-07-21 Phase_II/code/aperture.py
normalized figure

@@ -112,3 +112,4 @@ class aper():
               base.append(i[1] - i[0])
           return tel, base 
 
+

### 2025-07-21 Phase_II/code/gan_def.py

@@ -282,22 +282,22 @@ class gan_fun():
           Fitting the training data with test data.
           """
           
-          example_input, example_target = next(iter(test_ds.take(1)))                          # Unpacking a dataset (input signal and ground truth) with iterating and next to test the model
+          example_input, example_target = next(iter(test_ds.take(1)))                           # Unpacking a dataset (input signal and ground truth) with iterating and next to test the model
           start = time.time()
         
           #generator = self.Generator()                                                         # Generator model
           #discriminator = self.Discriminator()                                                 # Discriminator model
-          generator_optimizer = tf.keras.optimizers.Adam(self.learning_rate, beta_1 = 0.5)     # Generator Optimizer using the Adam algorithm
-          discriminator_optimizer = tf.keras.optimizers.Adam(self.learning_rate, beta_1 = 0.5) # Discriminator Optimizer using the Adam algorithm   
+          generator_optimizer = tf.keras.optimizers.Adam(self.learning_rate, beta_1 = 0.5)      # Generator Optimizer using the Adam algorithm
+          discriminator_optimizer = tf.keras.optimizers.Adam(self.learning_rate, beta_1 = 0.5)  # Discriminator Optimizer using the Adam algorithm   
                  
           checkpoint_dir = "models/models/ellipsoids_run8.15_a0.005_b0.005_discrep1_itk_bs1_lr2em4_teles4_addedlayers_filtersize5_MS/" # name of the folder and file to save the summary
           
           checkpoint_prefix = os.path.join(checkpoint_dir, "ckpt")
           checkpoint = tf.train.Checkpoint(generator_optimizer=generator_optimizer,
-                                           discriminator_optimizer=discriminator_optimizer,    # A Checkpoint object can be constructed to save either
-                                           generator=model1, discriminator=model2)   # a single or group of trackable objects to a checkpoint file.
+                                           discriminator_optimizer=discriminator_optimizer,     # A Checkpoint object can be constructed to save either
+                                           generator=model1, discriminator=model2)              # a single or group of trackable objects to a checkpoint file.
           counter = 0
-          for step, (input_image, target) in train_ds.repeat().take(steps).enumerate():        # Unpacking a dataset (input signal and ground truth) with iterating and next to train the model
+          for step, (input_image, target) in train_ds.repeat().take(steps).enumerate():         # Unpacking a dataset (input signal and ground truth) with iterating and next to train the model
               if (step) % 1000 == 0:
                  display.clear_output(wait=True)
  
@@ -310,7 +310,7 @@ class gan_fun():
[…]

### 2025-07-21 Phase_II/code/generate_baseline.py

@@ -79,5 +79,3 @@ mask = np.where(mask < 1, 1, 0).astype(np.float32)                              
 mask = cv2.resize(mask, dsize=(image_size, image_size), interpolation=cv2.INTER_AREA) # gives the best results
 mask = np.where(mask > 0, 1, 0)
 np.save("base_npy/base", mask)                                                        # Save mask as numpy array
-
-

### 2025-07-21 Phase_II/code/generate_pspec.py

@@ -38,7 +38,9 @@ for filename in os.listdir(path_in):
     
     # the images are on float ([0,1]), but cv2 requires integer ([0, 255]):
     img_fft_norm = cv2.convertScaleAbs(img_fft_norm, alpha=(255.0))
+    img_fft_norm = img_fft_norm/img_fft_norm.max()
     ground_truth = cv2.convertScaleAbs(ground_truth, alpha=(255.0))
+    ground_truth = ground_truth/ground_truth.max()
     
     combined_image = ps.add_image(ground_truth, img_fft_norm)                                         # combine ground truth and input image (power spectrum)
     

### 2025-07-21 Phase_II/code/main_def_test.py

@@ -16,24 +16,26 @@ print('base shape', np.shape(base))
 print('image shape', np.shape(train_image))
 fft = np.abs(fft.fftshift(fft.fft2(fft.fftshift(train_image))))
 # the signal on observational plane
-img = plt.imshow(fft)
+fft1 = fft/fft.max()
+img = plt.imshow(fft1)
 plt.colorbar(img)
 plt.gca().set_aspect('equal')
 plt.axis('off')
 plt.savefig('ft/ft.jpg')
-#plt.show()
+plt.show()
 
 plt.close()
-img1 = plt.imshow(np.log(fft))
+img1 = plt.imshow(np.log(fft1))
 plt.colorbar(img1)
 plt.gca().set_aspect('equal')
 plt.axis('off')
 plt.savefig('ft/ft_log.jpg')
-#plt.show()
+plt.show()
 
 plt.close()
 # the signal captured with baseline on observational plane
 output = np.multiply(fft, base) 
+output = output/output.max()
 img2 = plt.imshow(output)
 plt.colorbar(img2)
 plt.gca().set_aspect('equal')

### 2025-07-21 Phase_II/code/main_def_test.py
last commit with normalized colorbar

@@ -52,6 +52,7 @@ plt.axis('off')
 plt.savefig('ft/ft_log_base.jpg')
 plt.show()
 
+
 '''
 plt.close()
 # The full fourier transformation on ground of stellar object and the captured one with baselines

### 2025-07-30 Phase_II/draft/ParaGan.tex
rearrange
temporary
..
Para and result
fig13

@@
 \section{Network Parameters}
-
 \begin{figure*}
 	\centering
-	\begin{subfigure}{\linewidth}
-		\includegraphics[width=\linewidth]{fig/testing_image/image_0.png}
-	\end{subfigure}
-	\begin{subfigure}{\linewidth}
-		\includegraphics[width=\linewidth]{fig/testing_image/image_16.png}
-	\end{subfigure}
-	\begin{subfigure}{\linewidth}
-		\includegraphics[width=\linewidth]{fig/testing_image/image_35.png}
-	\end{subfigure}
-	\begin{subfigure}{\linewidth}
-		\includegraphics[width=\linewidth]{fig/testing_image/image_38.png}
-	\end{subfigure}
-	\begin{subfigure}{\linewidth}
+	\includegraphics[width=\linewidth]{fig/testing_image/image_3.png}
+	\includegraphics[width=\linewidth]{fig/testing_image/image_14.png}
+	\includegraphics[width=\linewidth]{fig/testing_image/image_5.png}
+	\includegraphics[width=\linewidth]{fig/testing_image/image_6.png}
+	\includegraphics[width=\linewidth]{fig/testing_image/image_13.png}
 	\includegraphics[width=\linewidth]{fig/testing_image/image_42.png}
-	\end{subfigure}
-	\begin{subfigure}{\linewidth}
-		\includegraphics[width=\linewidth]{fig/testing_image/image_47.png}
-	\end{subfigure}
 \caption{Examples results of GAN for II.
@@
 Finally, the ellipses are plotted, converted into grayscale images, resized, and stored as raw arrays to facilitate further analysis.
-\begin{figure*}
-	\centering
-	\begin{subfigure}{0.33\linewidth}
-		\includegraphics[width=\linewidth]{fig/moments/mom0.png}
-		\caption{The monopole.}
-		\label{fig:mom1}
-	\end{subfigure}\hfill
-	\begin{subfigure}{0.33\linewidth}
-		\includegraphics[width=\linewidth]{fig/moments/mom1.png}
-		\caption{The centroids along x direction.}
-		\label{fig:mom2}
-	\end{subfigure}\hfill
-	\begin{subfigure}{0.33\linewidth}
-		\includegraphics[width=\linewidth]{fig/moments/mom2.png}
-		\caption{The centroids along y direction.}
-		\label{fig:mom3}
-	\end{subfigure}\hfill
-	\caption{This set of figures shows the comparison of monopole, x-centroid, and y-centroid for ground truth and predicted images generated by trained GAN.}
-	\label{fig:cen}
-\end{figure*}
 

### 2025-07-30 Phase_II/code/gan_def.py

@@ -149,7 +149,7 @@ class gan_fun():
           Output : Either predicted image or its 180 rotation depending on mean square error
           """       
            
-          prediction = prediction*0.5 + 0.5
+          prediction = prediction
           prediction_rot = prediction[0, ::-1, ::-1, 0]                                   # 180 degree rotated image
           prediction = prediction[0, :, :, 0]                                             # predicted image
           groundtruth = groundtruth[0, :, :, 0]                                           # ground image
@@ -211,6 +211,8 @@ class gan_fun():
               plt.subplot(1, N_images, i+1)
               plt.title(title[i])
               plt.imshow(display_list[i]*0.5 + 0.5)                                       # Getting the pixel values in the [0, 1] range to plot:
+              plt.colorbar(shrink=0.85)
+              plt.gca().set_aspect('equal')
               plt.axis('off')
               
           # Save the plots

### 2025-07-30 Phase_II/code/gan_def_test.py

@@ -12,7 +12,7 @@ fn = main_fun()
 mfn = gan_fun()
 
 fn.para(img_size=128)
-mfn.gan_para(LAMBDA=100, OUTPUT_CHANNELS = 1, filtersize = 5, beta = 0.005, learning_rate = 2e-4, disc_train_iterations = 2)
+mfn.gan_para(LAMBDA=100, OUTPUT_CHANNELS = 1, filtersize = 5, beta = 0.005, learning_rate = 2e-4, disc_train_iterations = 1)
 BATCH_SIZE = 1                                                                                        #  The batch_size parameter specifies the number of samples that will be used in each iteration.
 BUFFER_SIZE = 1400
 
@@ -26,6 +26,7 @@ tf.keras.utils.plot_model(generator, to_file='testing_image/generator.png', show
 gen_output = generator(sample_input[tf.newaxis, ...], training=True)                                  # test the Generator to generate image using input signal (visibility) 
 plt.imshow(gen_output[0, ...])
 plt.savefig('testing_image/gen.png')
+plt.show()
 
 discriminator = mfn.Discriminator()
 tf.keras.utils.plot_model(discriminator, to_file='testing_image/discriminator.png', show_shapes=True, dpi=64) # structure of Discriminator according to the neuron
@@ -34,11 +35,12 @@ disc_out = discriminator([sample_input[tf.newaxis, :], gen_output], training=Fal
 plt.imshow(disc_out[0, ..., -1], vmin=-10, vmax=10, cmap='RdBu_r')
 plt.colorbar()
 plt.savefig('testing_image/disc.png')
+plt.show()
 
 # Plots four images based on the model: Input, Ground truth, Prediction, and (optionally) difference in the predicted image and ground truth (if show_diff = True). 
 example_input = sample_input[tf.newaxis, :]
 example_target = sample_real[tf.newaxis, :]
-#mfn.generate_images(generator, example_input, example_target)
+mfn.generate_images(generator, example_input, example_target)
 
 # check the helper function with train and test dataset
 train_dataset = tf.data.Dataset.list_files(str('train/*.jpg'))                              # To create a dataset of all files matching a pattern
@@ -53,7 +55,7 @@ except tf.errors.InvalidArgumentError:
 test_dataset = test_dataset.map(fn.load_image_test)
 test_dataset = test_dataset.batch(BATCH_SIZE)
 
[…]

### 2025-07-30 Phase_II/code/generate_pspec.py

@@ -38,15 +38,16 @@ for filename in os.listdir(path_in):
     
     # the images are on float ([0,1]), but cv2 requires integer ([0, 255]):
     img_fft_norm = cv2.convertScaleAbs(img_fft_norm, alpha=(255.0))
-    img_fft_norm = img_fft_norm/img_fft_norm.max()
+    #img_fft_norm = img_fft_norm/img_fft_norm.max()
     ground_truth = cv2.convertScaleAbs(ground_truth, alpha=(255.0))
-    ground_truth = ground_truth/ground_truth.max()
+    #ground_truth = ground_truth/ground_truth.max()
     
     combined_image = ps.add_image(ground_truth, img_fft_norm)                                         # combine ground truth and input image (power spectrum)
     
     image_name = filename[:-4]                                                                        # save or display images > use cv2 instead of matplotlib, this always saves as (64,64,4)
     if save_images:
             if counter < 150:
+               '''
                im = plt.imshow(combined_image, cmap='gray')
                plt.colorbar(shrink=0.55)
                plt.gca().set_aspect('equal')
@@ -54,8 +55,10 @@ for filename in os.listdir(path_in):
                plt.savefig('val/' + image_name + '.jpg')
                plt.clf()
                plt.close()
-               #cv2.imwrite('val/' + image_name + '.jpg', combined_image)
+               '''
+               cv2.imwrite('val/' + image_name + '.jpg', combined_image)
             elif (counter >= 150) and (counter < 300):
+               '''
                im = plt.imshow(combined_image, cmap='gray')
                plt.colorbar(shrink=0.55)
                plt.gca().set_aspect('equal')
@@ -64,8 +67,10 @@ for filename in os.listdir(path_in):
                plt.savefig('test/' + image_name + '.jpg')
                plt.clf()
                plt.close()
-               #cv2.imwrite('test/' + image_name + '.jpg', combined_image)
+               '''
+               cv2.imwrite('test/' + image_name + '.jpg', combined_image)
             else:
+               '''
                im = plt.imshow(combined_image, cmap='gray')
                plt.colorbar(shrink=0.55)
                plt.gca().set_aspect('equal')
@@ -73,7 +78,8 @@ for filename in os.listdir(path_in):
                plt.savefig('train/' + image_name + '.jpg')
                plt.clf()
                plt.close()
-               #cv2.imwrite('train/' + image_name + '.jpg', combined_image)
+               '''
[…]

### 2025-07-30 Phase_II/code/main_def_test.py

@@ -53,7 +53,7 @@ plt.savefig('ft/ft_log_base.jpg')
 plt.show()
 
 
-'''
+
 plt.close()
 # The full fourier transformation on ground of stellar object and the captured one with baselines
 plt.subplot(1,2,1)
@@ -105,4 +105,4 @@ print('down sampling result of an input image, observed signal', down_result.sha
 up_model = fn.upsample(3, 4, apply_dropout=True)
 up_result = up_model(down_result)
 print('up sampling result of down sampled image', up_result.shape)
-'''
+

### 2025-07-31 Phase_II/draft/GAN.tex
final draft

@@
 \begin{figure*}
-	%\centering
-	%\begin{subfigure}{0.5\linewidth}
 	\includegraphics[width=.49\textwidth]{fig/analysis/Plot_learning_rate_disc_loss.pdf}\hfil
-	%\caption{Discriminator loss for three different learning rates. }
-	%	\label{fig:Plot_learning_rate_discloss}
-	%\end{subfigure}\hfill
-	%\begin{subfigure}{0.5\linewidth}
 	\includegraphics[width=.49\textwidth]{fig/analysis/Plot_learning_rate_gen_total_loss.pdf}
-		%\caption{Total generator loss for different learning rates (eqn. (\ref{eq:total_gen_loss})).}
-	%	\label{fig:Plot_learning_rate_genloss}
-	%\end{subfigure}\hfill
 	\caption{Discriminator and Generator losses for three different learning rates.
-The left panel shows the total discriminator loss, and the right figure shows the total generator loss (Eq.~\ref{eq:total_gen_loss}).
-There is no significant difference, but the highest learning rate might be prone to outliers.}
+The left panel and the right panel show the total discriminator loss and the total generator loss (Eq.~\ref{eq:total_gen_loss}) respectively.
+There is no significant difference, but these figures indicate that higher learning rates might render the training prone to outliers.}
 	\label{fig:Plot_learning_rate_loss}
+\end{figure*}
+\begin{figure*}
+	\includegraphics[width=.49\textwidth]{fig/analysis/Plot_Kernel_size_disc_loss.pdf}
+	\includegraphics[width=.49\textwidth]{fig/analysis/Plot_Kernel_size_gen_total_loss.pdf}
+	\caption{Discriminator and Generator losses (left and right panels respectively) for three different kernel sizes in the convolutional layers.
+Here, the smallest kernel size has many outliers, while the largest kernel size seems to be the most stable.}
+	\label{fig:Plot_kernel_size_loss}
+\end{figure*}
+\begin{figure*}
+	\includegraphics[width=.49\textwidth]{fig/analysis/Plot_noise_factor_disc_loss.pdf}
+	\includegraphics[width=.49\textwidth]{fig/analysis/Plot_noise_factor_gen_total_loss.pdf}
+	\caption{Effect of the Salt (alpha) and Pepper (beta) noise (explained in the text) introduced into the images.
+There is no significant effect of the alpha/beta ratio.
+These results are from training on $64\times64$-pixel images.}
+	\label{fig:Plot_noise_loss}
+\end{figure*}
+\begin{figure*}
+	\includegraphics[width=.49\textwidth]{fig/analysis/Plot_Batchsize_disc_loss.pdf}\hfill
+	\includegraphics[width=.49\textwidth]{fig/analysis/Plot_Batchsize_gen_total_loss.pdf}
+	\caption{Loss functions for two different batch sizes. Large batch sizes seem to make the training more robust, but also increase training time significantly. }
+	\label{fig:Plot_batchsize_loss}
+\end{figure*}
+\begin{figure*}
+	\includegraphics[width=.49\textwidth]{fig/analysis/Plot_Disc_rep_disc_loss.pdf}\hfil
+	\includegraphics[width=.49\textwidth]{fig/analysis/Plot_Disc_rep_gen_total_loss.pdf}
+	\caption{The number of episodes of Discriminator training per every episode of Generator training (termed Discriminator repetition or Disc.
+rep.), understandably, has a higher impact on the Discriminator loss than on the Generator loss.
+The left and the right panel show this effect on the Discriminator loss and the Generator loss respectively.}
+	\label{fig:Plot_discrep_loss}
+\end{figure*}
+\begin{figure*}
+	\includegraphics[width=.49\textwidth]{fig/analysis/Plot_N_telescopes_disc_loss.pdf}\hfil
+	\includegraphics[width=0.49\textwidth]{fig/analysis/Plot_N_telescopes_gen_total_loss.pdf}\hfil
+	\caption{Discriminator loss (left panel) and Generator loss (right panel) for different numbers of telescopes.
+The number of telescopes has a very significant impact on the model performance.
+If there are only two telescopes (1 baseline), both Discriminator and Generator are not trained smoothly: One gains a big advantage over the other.
+The result of four telescopes (6 baselines) is a lot better because the loss functions change only slightly with increasing steps.}
+	\label{fig:Plot_telescopes_loss}
 \end{figure*}
@@
 		\max_{D} V(G, D) &= \mathbb{E}_{x \sim p_{\rm data}} \left[ \log D^{*}_{G}(x) \right] \\ 
-		&+ \mathbb{E}_{x \sim p_{g}} \left[ \log \left( 1 - D^{*}_{G}(x) \right) \right]
+		&+ \mathbb{E}_{x \sim p_{G}} \left[ \log \left( 1 - D^{*}_{G}(x) \right) \right]
 	\end{aligned}
@@
 	\centering
-	D^*_G(x) = \frac{p_{\rm data}(x)}{p_{\rm data}(x) + p_g(g)}
+	D^*_G(x) = \frac{p_{\rm data}(x)}{p_{\rm data}(x) + p_G(g)}
 	\label{eq:Disc_optimum}
 \end{equation}
-\begin{figure*}
-  %\begin{subfigure}{0.5\linewidth}
-  \includegraphics[width=.49\textwidth]{fig/analysis/Plot_Kernel_size_disc_loss.pdf}
-  %\caption{Discriminator loss for three different kernel sizes. }
-  %\label{fig:Plot_kernel_size_discloss}
-  %\end{subfigure}\hfill
-  %\begin{subfigure}{0.5\linewidth}
-  \includegraphics[width=.49\textwidth]{fig/analysis/Plot_Kernel_size_gen_total_loss.pdf}
-  %\caption{Total generator loss for three different kernel sizes.}
-  %\label{fig:Plot_kernel_size_genloss}
-  %\end{subfigure}\hfill
-  \caption{Generator and discriminator losses (left and right panels respectively) for three different kernel sizes in the convolutional layers.
-Here, the smallest kernel size has many outliers, while the largest kernel size seems to be the most stable.}
-	\label{fig:Plot_kernel_size_loss}
-\end{figure*}
-\begin{figure*}
-  %\begin{subfigure}{0.5\linewidth}
-  \includegraphics[width=.49\textwidth]{fig/analysis/Plot_noise_factor_disc_loss.pdf}
-  %\caption{Discriminator loss for different noise percentages.}
-  %\label{fig:Plot_noise_discloss}
-  %\end{subfigure}\hfill
-  %\begin{subfigure}{0.5\linewidth}
-  %\centering
-  \includegraphics[width=.49\textwidth]{fig/analysis/Plot_noise_factor_gen_total_loss.pdf}
-  %\caption{Generator losses for different noise percentages.}
-  %\label{fig:Plot_noise_genloss}
-  %\end{subfigure}\hfill
-  \caption{Effect of the Salt and Pepper noise introduced in the images.
-Different ratios between $\alpha$ and $\beta$ are shown.
-There is no significant effect.
-Please note that these results are from training on 64-pixel images.}
-	\label{fig:Plot_noise_loss}
-\end{figure*}
-\begin{figure*}
-  %\begin{subfigure}{0.5\linewidth}
-  \includegraphics[width=.49\textwidth]{fig/analysis/Plot_Batchsize_disc_loss.pdf}\hfill
-  %\caption{Discriminator loss for different batch sizes.}
-  %\label{fig:Plot_batchsize_discloss}
-  %\end{subfigure}\hfill
-  %\begin{subfigure}{0.5\linewidth}
-  \includegraphics[width=.49\textwidth]{fig/analysis/Plot_Batchsize_gen_total_loss.pdf}
-  %\caption{Generator losses for different batch sizes.}
-  %\label{fig:Plot_batchsize_genloss}
-  %\end{subfigure}\hfill
-  \caption{Loss functions for two different batch sizes. Large batch sizes seem to be more robust, but they also increase training time significantly. }
-	\label{fig:Plot_batchsize_loss}
-\end{figure*}
-\begin{figure*}
-  %\begin{subfigure}{0.5\linewidth}
-  \includegraphics[width=.49\textwidth]{fig/analysis/Plot_Disc_rep_disc_loss.pdf}\hfil
-  %\caption{Discriminator loss for different Discriminator training.}
-  %\label{fig:Plot_discrep_discloss}
-  %\end{subfigure}\hfill
-  %\begin{subfigure}{0.5\linewidth}
-  \includegraphics[width=.49\textwidth]{fig/analysis/Plot_Disc_rep_gen_total_loss.pdf}
-  %\caption{Generator losses for different Discriminator training.}
-  %\label{fig:Plot_discrep_genloss}
-  %\end{subfigure}\hfill
-  \caption{The left panel shows the Discriminator loss for different Discriminator training, while the right panel shows the Generator losses for different Discriminator training.
-The amount of Discriminator training has a high impact on the Discriminator score.
-The Discriminator repetition indicates the factor by which the Discriminator is trained more with respect to the Generator.}
-	\label{fig:Plot_discrep_loss}
-\end{figure*}
-\begin{figure*}
-  %\begin{subfigure}{0.5\linewidth}
-  \includegraphics[width=.49\textwidth]{fig/analysis/Plot_N_telescopes_disc_loss.pdf}\hfil
-  %\caption{Discriminator loss for different amounts of telescopes.}
-  %\label{fig:Plot_telescopes_discloss}
-  %\end{subfigure}\hfill
-  %\begin{subfigure}{0.5\linewidth}
-  \includegraphics[width=0.49\textwidth]{fig/analysis/Plot_N_telescopes_gen_total_loss.pdf}\hfil
-  %\caption{Generator loss for different amount of telescopes.}
-  %\label{fig:Plot_telescopes_genloss}
-  %\end{subfigure}\hfill
-  \caption{Discriminator loss (left panel) and Generator loss (right panel) for different numbers of telescopes.
-The number of telescopes has a very impact on the model performance.
-If there are only two telescopes (1 baseline), both Discriminator and Generator are not trained smoothly: One gains a big advantage over the other.
-The result of four telescopes (6 baselines) is a lot better because the loss functions change only slightly with increasing steps.}
-	\label{fig:Plot_telescopes_loss}
-\end{figure*}
 
@@
 In such architectures, the image's spatial resolution is first reduced through downsampling and then restored via upsampling, resulting in a U-shaped structure.
-The downsampling process typically involves convolutional layers followed by a strided operation (with a stride of 2) to effectively subsample the image, and a leaky version of the Rectified Linear Unit (ReLU) is employed as the activation function.
+The downsampling process typically involves convolutional layers followed by a strided operation (with a stride of 2) to effectively subsample the image, and a leaky version of the Rectified Linear Unit (LeakyReLU) is employed as the activation function.
 
@@
 \subsection{Discriminator}
-As discussed earlier, the Discriminator is tasked with classifying the images produced by the Generator as either real or fake.
+The Discriminator is tasked with classifying the images produced by the Generator as either real or fake.
 It takes a real image from the dataset (often referred to as the target image for the Generator) and provides feedback to guide the Generator toward producing more accurate images.

### 2025-07-31 Phase_II/draft/ParaGan.tex
final draft

--- 2025-07-17 Phase_II/draft/ParaGan.tex
@@
 \section{Network Parameters}
-
 \begin{figure*}
 	\centering
-	\begin{subfigure}{\linewidth}
 	\includegraphics[width=\linewidth]{fig/testing_image/image_0.png}
-	\end{subfigure}
-	\begin{subfigure}{\linewidth}
 	\includegraphics[width=\linewidth]{fig/testing_image/image_16.png}
-	\end{subfigure}
-	\begin{subfigure}{\linewidth}
 	\includegraphics[width=\linewidth]{fig/testing_image/image_35.png}
-	\end{subfigure}
-	\begin{subfigure}{\linewidth}
 	\includegraphics[width=\linewidth]{fig/testing_image/image_38.png}
-	\end{subfigure}
-	\begin{subfigure}{\linewidth}
 	\includegraphics[width=\linewidth]{fig/testing_image/image_42.png}
-	\end{subfigure}
-	\begin{subfigure}{\linewidth}
 	\includegraphics[width=\linewidth]{fig/testing_image/image_47.png}
-	\end{subfigure}
-	\caption{Examples results of GAN for II.
-The left panels are signals using six baselines, which work as input for GAN.
-The first middle panel is the real image, also called ground truth, and GAN tries to mimic it during the training.
-The second middle panel is the reconstructed image, also called the predicted image, with trained GAN, and the end panel is the difference between the ground truth and the predicted image.}
+\caption{Example results of image reconstruction using the GAN model along with the II observations simulated in this work.
+Each row in this figure represents the results for a hypothetical fast-rotating star.
+Going from left to right in each row, the first panel represents the simulated $(u,v)$ plane II signals obtained using the six baselines (of Fig.\ref{fig:ft_base}).
+This image is presented, as the input, to the trained GAN to produce a predicted image.
+The second panel is the real image of the star, also called the ground truth.
+The third panel is the reconstructed image, or the predicted image, produced by the trained GAN model .
+The fourth and the last panel is the difference between the ground truth and the predicted image in the $(u,v)$ plane.
+The uniform background color in the difference panel suggests that the network is picking up white noise from the $(u,v)$ plane.
+}
 	\label{fig:GAN}
@@
 \subsection{Data Preparation}
-First, we simulate fast-rotating stars, modeling them as oblate spheroids with varying radii and an oblateness ranging between 0.5 and 1.
+First, we simulate fast-rotating stars, modelling them as oblate spheroids with varying radii and an oblateness ranging between 0.5 and 1.
 We also consider different viewing angles, assuming a linear dependence for the effect of gravity darkening.
@@
 Finally, the ellipses are plotted, converted into grayscale images, resized, and stored as raw arrays to facilitate further analysis.
-\begin{figure*}
-	\centering
-	\begin{subfigure}{0.33\linewidth}
-		\includegraphics[width=\linewidth]{fig/moments/mom0.png}
-		\caption{The monopole.}
-		\label{fig:mom1}
-	\end{subfigure}\hfill
-	\begin{subfigure}{0.33\linewidth}
-		\includegraphics[width=\linewidth]{fig/moments/mom1.png}
-		\caption{The centroids along x direction.}
-		\label{fig:mom2}
-	\end{subfigure}\hfill
-	\begin{subfigure}{0.33\linewidth}
-		\includegraphics[width=\linewidth]{fig/moments/mom2.png}
-		\caption{The centroids along y direction.}
-		\label{fig:mom3}
-	\end{subfigure}\hfill
-	\caption{This set of figures shows the comparison of monopole, x-centroid, and y-centroid for ground truth and predicted images generated by trained GAN.}
-	\label{fig:cen}
-\end{figure*}
 
-First, Salt and Pepper noise is introduced at a rate of \(\alpha\) (usually 0.5\%).
+Next, Salt and Pepper noise is introduced usually at a rate of 0.5\%.
 Then, the images are resized and their mean is subtracted.
@@
 The result is a map in the Fourier plane featuring several ellipses, which is also referred to as the sparse sampling map (Fig.~\ref{fig:ft_base}).
-This map represents the sparse sampling for Fig.~\ref{fig:image}, corresponding to the source observed with four telescopes (Fig.~\ref{fig:teles}).
+This map represents the sparse sampling of the signal space (Fig.~\ref{fig:ft}) corresponding to the source (Fig.~\ref{fig:image}) observed with four telescopes (Fig.~\ref{fig:teles}).
 
@@
 
-The amount of noise is controlled by two parameters, \(\alpha\) and \(\beta\), which indicate the percentage of pixels altered to either black or white—hence the term Salt and Pepper noise.
-Here, \(\alpha\) is applied to the real image, while \(\beta\) is applied to the generated image.
-Different ratios \(\frac{\alpha}{\beta}\) can lead to varying model performance; however, our results indicate that distinct noise rates do not significantly affect the loss functions.
+The amount of noise is controlled by two parameters, ``alpha" and ``beta", which indicate the percentage of pixels altered to either white or black — hence the term Salt and Pepper noise.
+Here, ``alpha" is applied to the real image, while ``beta" is applied to the generated image.
+Different ratios (``alpha/beta") can lead to varying model performance; however, our results indicate that distinct noise rates do not significantly affect the loss functions.
 Figure~\ref{fig:Plot_noise_loss} shows the loss functions for smaller images ($64 \times 64$), and due to the negligible impact, this analysis was not repeated for larger images.
@@
 There is a significant disparity in performance, partly because the relationship between telescopes and baselines is not linear.
-For example, the Fourier plane can be sampled along six tracks when using four telescopes, as compared to only one tracks if using only two telescopes.
+For example, the Fourier plane can be sampled along six tracks when using four telescopes, as compared to only one track if using only two telescopes.
 In the case of two telescopes, both the Generator and Discriminator exhibit less smooth training, as indicated by the outliers.

### 2025-07-31 Phase_II/draft/intro.tex
rearrange
..
final draft

@@
 
-More recently, proposals emerged to utilize Imaging Atmospheric Cherenkov Telescope (IACT) facilities for conducting II observations of stars \citep{LeBohec2006, nunez2010stellar, nunez2012high, 2013APh....43..331D}.
-It was suggested that such observations could be carried out during bright, moonlit nights when $\gamma$-ray observations based on upper atmospheric Cherenkov showers were not feasible.
+More recently, proposals to utilize Imaging Atmospheric Cherenkov Telescope (IACT) facilities for conducting II observations of stars have emerged\citep{LeBohec2006, nunez2010stellar, nunez2012high, 2013APh....43..331D}.
+It has been demonstrated that such observations could be carried out during bright, moonlit nights when $\gamma$-ray observations based on upper atmospheric Cherenkov showers were not feasible.
 This approach has the potential to enhance the scientific output of existing IACT facilities, and especially of the upcoming Cherenkov Telescope Array Observatory (CTAO).
-SII observations at VERITAS, MAGIC, and HESS are now appearing \citep[e.g.,][]{2024ApJ...966...28A,2024MNRAS.529.4387A,2025MNRAS.537.2334V}.
+SII observations at VERITAS, MAGIC, and HESS are now being reported \citep[e.g.,][]{2024ApJ...966...28A,2024MNRAS.529.4387A,2025MNRAS.537.2334V}.
 Simulations \citep[e.g.,][]{10.1093/mnras/stab2391, 10.1093/mnras/stac2433} have argued that recent advancements in photon detectors could be effective in achieving high-precision measurements of parameters for stellar objects.
@@
 \cite{GerchbergSaxton1972} suggested an iterative method to determine the phase from the image and diffraction plane pictures.
-This method relies on accurate initial estimates and may struggle with slow convergence otherwise.
+This method relies on accurate initial estimates and is vulnerable to slow convergence otherwise.
 \cite{Fienup1982} introduced a Hybrid Input-Output algorithm that incorporates feedback mechanisms to improve convergence rate and robustness, particularly in noisy environments.
 
-Later, \cite{holmes2010two} proposed an alternative method that utilizes the Cauchy-Riemann relations to reconstruct 1-D images and extends the approach to 2-D images across a range of signal-to-noise (SNR) values.
+Later, \cite{holmes2010two} proposed an alternative method that utilizes the Cauchy-Riemann relations to reconstruct 1-D images.
+They also extended the approach to 2-D images across a range of signal-to-noise (SNR) values.
 This algorithm was applied to simulated data of stellar objects using II, considering both existing and forthcoming Imaging Cherenkov Telescope Arrays (IACTs) with a large number of telescopes \citep{nunez2010stellar, nunez2012high, nunez2012imaging}.
@@
 \cite{Zhang2020} proposed a method to obtain a \textquotedblleft universal solution\textquotedblright\ to the TIE by employing a \textquotedblleft maximum intensity assumption\textquotedblright, thereby converting the TIE into a Poisson equation which is then solved iteratively.
-More recently, \cite{Kirisits2024} explored hybrid methods that combine the TIE with other equations, such as the Transport of Phase Equation (TPE).
+More recently, \cite{Kirisits2024} have explored hybrid methods that combine the TIE with other equations, such as the Transport of Phase Equation (TPE).
 These approaches leverage the strengths of both equations to improve phase retrieval accuracy.
@@
 Furthermore, given that achieving a high signal-to-noise ratio (SNR) is often challenging in astronomical datasets, it is immensely beneficial if additional data can be generated using the available information from the observed sky density distribution and ground-based observations (II data, in our case) of the sources under investigation.
-Generative Adversarial Networks (GANs), introduced by \cite{goodfellow2014generative}, have been successful in data augmentation tasks.
+Generative Adversarial Networks (GANs), introduced by \cite{goodfellow2014generative}, have been successful in such data augmentation tasks.
 Conditional GAN (cGAN) architectures, proposed by \cite{mirza2014conditional} and applied to a wide variety of datasets by \cite{isola2017image}, leverage additional information about the images in the training datasets and have demonstrated remarkable robustness in image recovery across diverse data types.
 
-In the astrophysical context, \cite{schawinski2017galaxypics} employed a GAN model to recover features—such as spiral arms, central bulges, and disk structures—of galaxies from noise-affected images.
-\cite{mustafa2019cosmogan} developed and customized a Deep Convolutional GAN, dubbed \textquotedblleft CosmoGAN\textquotedblright, capable of generating high-fidelity weak-lensing convergence maps of the dark matter distribution that statistically reproduce real weak lensing structures.
+In the astrophysical context, \cite{schawinski2017galaxypics} employed a GAN model to recover features — such as spiral arms, central bulges, and disk structures of galaxies — from noise-affected images.
+\cite{mustafa2019cosmogan} developed and customized a Deep Convolutional GAN, dubbed \textquotedblleft CosmoGAN\textquotedblright, capable of generating high-fidelity weak-lensing convergence maps of dark matter distribution that statistically reproduce real weak lensing structures.
 \cite{coccomini2021lightweightgan} have successfully generated credible images of planets, nebulae, and galaxies using \textquotedblleft lightweight\textquotedblright\ and \textquotedblleft physics-uninformed\textquotedblright\ GANs to produce synthetic images of celestial bodies.
@@
 In this paper, we propose a conditional Generative Adversarial Network (cGAN) model \citep[following][]{isola2017image} to reconstruct images of fast-rotating stars using their simulated Intensity Interferograms and simulated sky-intensity distributions as input data for training, testing, and validation.
-We consider four Imaging Cherenkov Telescope Arrays (IACTs) and simulation observation of a fast-rotating star.
+We consider four Imaging Cherenkov Telescope Arrays (IACTs) and simulate observation of a fast-rotating star.
 The image predicted by the trained GAN shows promising results in reconstructing the star’s shape and size.
@@
 Finally, the paper concludes with a discussion of the overall results.
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{fig/telescope.png}
+	\caption{The telescope configuration with similar properties each used to simulate the signal for II observation.}
+	\label{fig:teles}
+\end{figure}

### 2025-07-31 Phase_II/draft/main.tex
figure
..
Para and result
final draft

@@
 \usepackage{amsmath}
+\usepackage[colorlinks=true,
+linkcolor=blue,
+citecolor=blue,
+urlcolor=cyan]{hyperref}
 
@@
 \begin{abstract}
-In the last few years Intensity Interferometry has made significant strides in achieving high-precision resolution of stellar objects at optical wavelengths.
+In the last few years Intensity Interferometry (II) has made significant strides in achieving high-precision resolution of stellar objects at optical wavelengths.
 Despite these advancements, phase retrieval remains a major challenge due to the nature of photon correlation.
@@
 \input{conclusion}
+\begin{acknowledgements}
+\textbf{Acknowledgment:} One of the authors (SS) gratefully acknowledges the computing facilities and the local hospitality extended to him by the Inter-University Centre for Astronomy and Astrophysics (IUCAA), Pune, India under its Visiting Associate Programme during the preparation of this manuscript.
+\end{acknowledgements}
 
-\bibliographystyle{aa}
+\bibliographystyle{aasjournal}
 \bibliography{refs}

### 2025-08-02 Phase_II/draft/main.tex
edits

@@
 \author{Km Nitu Rai,$^{1,2}$, Yuri van der Burg$^{3}$, Soumen
-  Basak$^{1}$, Prasenjit Saha,$^{3}$ and Subrata Sarangi$^{4,5}$}
+  Basak$^{1}$, {Prasenjit Saha\altaffilmark{3,*}}, and Subrata Sarangi$^{4,5}$}
 
@@
 \affiliation{$^5$ Visiting Associate, Inter-University Centre for Astronomy and Astrophysics, Post Bag 4, Ganeshkhind, Pune 411 007, Maharashtra, India.}
+
+\altaffiltext{*}{Corresponding author; email: \href{mailto:psaha@physik.uzh.ch}{psaha@physik.uzh.ch}}
 
@@
 
-\bibliographystyle{aasjournal}
+\bibliographystyle{aa}
 \bibliography{refs}

### 2025-08-29 Phase_II/draft/response.txt
starting response

|  Reviewer:
|  Dear Editor,
|  Thank you for sending me this manuscript by Rai et al on image
|  reconstruction from intensity interferometry. It addresses an important
|  topic, and may after major revision be suitable for publication in AJ. At a
|  high level, the paper does not demonstrate that the GAN presented actually
|  recovers much of the information about the stars presented; or that it
|  would be able to reconstruct images of other objects or with different uv
|  sampling.
|  Kind regards,
|  The Reviewer
|  
|  Comments
|
|  - Rapidly rotating stars can be fit analytically to these data. It may be
|  worth considering an example of an astrophysical source that would be more
|  interesting to fit, where the data analysis problem is less analytically
|  tractable, such as for complex scenes (spotted stars, or disks, for
|  instance).

Counter-argument: We can justify the choice of gravity-darkened stars.

1. Other image-reconstruction methods have been used with Michelson
   interferometry for this type of source.

2. SII has recently measured ellipticity, so gravity-darkening is a
   natural next step.

|  - On the first page: "However, because the primary observable in 69 II is
|  the electromagnetic field intensity rather than the 70 field amplitude, the
|  phase of the interferometric signal 71 is lost." This is not unique to
|  intensity interferometry - you also only measure the field amplitudes in
|  normal interferometry too. What is different about intensity interferometry
|  is you measure electromagnetic field intensity correlations, which
|  translates to getting fringe visibilities but not fringe phases in the uv
|  plane.

|  - On the second page, there is quite a long discussion of the problem of
|  phase retrieval, including many citations. This is good, though perhaps a
|  little long and could be condensed. But there needs to be a clearer
|  statement of why phase retrieval matters - the Fourier transform is
|  Hermitian, and the consequence is that image modes that have even symmetry
|  under inversion are encoded strictly in amplitudes, and with odd symmetry
|  under inversion in phases. The result is that it intensity interferometry
|  strictly contains no information about odd modes of the image and these
|  must be constrained by the even modes through regularization/priors. This
|  idea needs to be discussed.

|  - I think we are seeing the Hermitian symmetry issue in Figure 13: while
|  the GANs do reasonable reconstructions of the equator-on gravity-darkened
|  stars, in the third and separately in the final examples, you see a pole-on
|  star with significant asymmetry in the ground-truth image, which the GANs
|  completely miss. In this figure, the Difference image is illegible; you
|  should try to unravel this into a residuals plot in 1D by mapping those
|  pixelized residuals back to baselines, and where differences are used in
|  images, use a diverging colourmap like coolwarm or seismic rather than
|  viridis.

|  - Figures should be explained fully in their captions, rather than the
|  layout explained like Figure 13 in Sec 5.1.

|  - This discussion of phase retrieval should be separated in the
|  introduction from the discussion of GANs.

|  - There is quite an extensive lit review on the core ideas of intensity
|  interferometry and their corresponding equations, that could perhaps be
|  condensed.

|  - In Figure 2 we have a single sparse sampling map. It appears to be used
|  in all of the other figures throughout the paper. How well does the network
|  perform with different uv sampling? If it's trained only on one, I would
|  expect very poorly - and it's extremely important to test this and think of
|  ways to extend to a more flexible sampling, because you really don't want
|  to have to train your image reconstruction model separately for every
|  single observation.

Counter-argument: the (u,v) sampling for any given data set is fixed
and known, so if computationally feasible [which it is] you do want to
train on the sampling used.

|  - Figures 4 and 5 could be merged to illustrate ideas better; the linear
|  stretch doesn't really tell us anything. What is the story being told here?
|  I would also suggest the authors consider how their subplots are arranged
|  to make better use of space and avoid small figures embedded in large areas
|  of white space. This comment about spatial arrangement applies to Figures
|  14-16 too. (The labels in those figures don't need "The" in "The Ground
|  Truth").

|  - Figure 6 is too small to be easily legible - could this be a two-column
|  figure, with a clearer colourmap? Anyway - this is likely to need to be
|  explained clearly to an astronomer reader, as it may be confusing why the
|  ground truth and observations are merged. A block diagram is essential,
|  showing as a sequence of operations what the workflow is for training and
|  what the workflow is for inference.

|  - Figures 7-12 occupy a great space with very narrow lines that are hard to
|  read, and do not appear to be especially informative in their current form.
|  The loss functions bounce all over the place and just these trace plots vs
|  epoch don't really tell us anything. If you want to make arguments about
|  stability in training vs hyperparameters, it might be better to extract and
|  parametrize the variability (eg mean, std, skewness moments) and plot this
|  as a function of hyperparameters, rather than this quite confusing set of
|  figures.

|  - Section 4.2 refers to a TensorFlow tutorial, and mentions that
|  modifications are essential - what are the modifications? It doesn't appear
|  to be explained in the subsequent sections. Is any of the paper's code
|  being provided open-source? It is more or less essential for a methods
|  paper mainly about software to provide the code in an appropriate open
|  source format, for reproducibility and extensibility.

|  - gravitational darkening -> gravity darkening

|  - The sentence referring to the "ground truth, which the Discriminator uses
|  to distinguish between real images and those generated by the Generator.
|  During training, the GAN aims to replicate these ground truth images."
|  seems to be confused about GANs in theory. The references to this
|  throughout the paper, including in the context of the merged data, need to
|  be clearer. The discriminator doesn't have access to the ground truth, the
|  discriminator has to distinguish between simulated and ground-truth data.

|  - There appears to be no correlation between the x and y centroids of the
|  star relative to the ground truth. This would be a serious problem? It
|  seems to do ok on the second moments, but no recovery at all of the third
|  moments. This may be related to section 5.3 which seems to lack any account
|  of gravity darkening, which is in the simulations.

Counter-argument: yes the centroids are showing noise -- all values
are around (63.5,63.5) which is the centre of the field -- but
absolute centroid is not a measurable quantity in interferometry

|  - No information is provided in the paper about computer systems. What
|  hardware was used (CPUs? GPUs?), and how long did it take for training and
|  for inference? It is important to quantify computational performance.

### 2025-08-29 Phase_II/draft/response.txt
edits

@@
 
+Clarify that we mean phase of the complex visibility.
+
 |  - On the second page, there is quite a long discussion of the problem of
@@
 
+Revise text.
+
 |  - I think we are seeing the Hermitian symmetry issue in Figure 13: while
@@
 |  viridis.
+
+Asymmetry is recovered in some cases: investigate!
 
@@
 
+Merge figs 4 and 5, also 14-16.
+
 |  - Figure 6 is too small to be easily legible - could this be a two-column
@@
 |  what the workflow is for inference.
+
+Improve this.
 
@@
 
+Revise these figures.
+
 |  - Section 4.2 refers to a TensorFlow tutorial, and mentions that
@@
 |  source format, for reproducibility and extensibility.
+
+Give github repo, maybe give most recent version a DOI.
 
@@
 Counter-argument: yes the centroids are showing noise -- all values
-are around (63.5,63.5) which is the centre of the field -- but
-absolute centroid is not a measurable quantity in interferometry
+are around (63.5,63.5) which is the centre of the field -- but it is
+not important, because absolute centroid is not a measurable quantity
+in interferometry.
 

### 2025-08-29 Phase_II/draft/AJsubmitted/GAN.tex
setting up redblue wrt AJ submitted

--- 2025-07-31 Phase_II/draft/GAN.tex
@@
 	\includegraphics[width=0.49\textwidth]{fig/analysis/Plot_N_telescopes_gen_total_loss.pdf}\hfil
-	\caption{Discriminator loss (left panel) and Generator loss (right panel) for different numbers of telescopes.
-The number of telescopes has a very significant impact on the model performance.
-If there are only two telescopes (1 baseline), both Discriminator and Generator are not trained smoothly: One gains a big advantage over the other.
-The result of four telescopes (6 baselines) is a lot better because the loss functions change only slightly with increasing steps.}
+	\caption{Discriminator and Generator loss for different numbers of telescopes.
+It has a very significant impact on the model performance.
+If there are only two telescopes, both Discriminator and Generator are not trained smoothly.
+The result of four telescopes is a lot better because the loss functions change only slightly with increasing steps.}
 	\label{fig:Plot_telescopes_loss}

### 2025-08-29 Phase_II/draft/AJsubmitted/II.tex
setting up redblue wrt AJ submitted

--- 2025-07-17 Phase_II/draft/II.tex
@@
   \includegraphics[width=\linewidth]{fig/baseline.png}
-  \caption{The tracking of baselines with four telescopes arranged in fig.~\ref{fig:teles} for one night of observation.}
+  \caption{The tracks of the baselines provided by the four telescopes arranged in fig.~\ref{fig:teles} for one night of observation.}
   \label{fig:base}
@@
   \includegraphics[width=\linewidth]{fig/ellipse/ellipse1612.jpg}
-  \caption{This figure shows the simulated fast rotating star. The brightness is highest at the pole and there is gravitational darkening at the equator.}
+  \caption{This figure shows the simulated fast rotating star. The brightness is highest at the poles and there is gravitational darkening along the equator.}
   \label{fig:image}
@@
 	%\end{subfigure}
-	\caption{Absolute value of the two-dimensional Fast Fourier Transform of Fig.~\ref{fig:image} measured by Intensity Interferometry in the $(u, v)$ plane.
-\textit{Left.}~Signal on a linear scale.
-\text{Right}.~Signal on a logarithmic scale.}
+	\caption{Absolute value of the two-dimensional Fast Fourier Transform of the source depicted in Fig.~\ref{fig:image} in linear scale (left panel) and logarithmic scale (right panel).
+These figures represent the intensity interferometric ($u,v$) plane image of the source that would be obtained by an infinite number of baselines (or infinite number of telescopes observing the source).
+Both the linear and the logarithmic scales are normalized to the maximum intensity obtained at the centre of figures.
+}
 	\label{fig:ft}
@@
 	%\end{subfigure}
-  \caption{The left panel shows the absolute value of the two-dimensional Fast Fourier Transform of Fig.~\ref{fig:image} measured by baselines shown in Fig.~\ref{fig:teles}.
-The right panel shows the same on logarithmic scale}
+  \caption{Absolute value of the two-dimensional Fast Fourier Transform of the source depicted in Fig.~\ref{fig:image} and measured along the tracks shown in Fig.~\ref{fig:base} covered by the baselines shown in Fig.~\ref{fig:teles}.
+Both the left panel (in linear scale) and the right panel (in logarithmic scale) are normalized to the maximum pixel value in the respective figures.
+The panels of Fig.~\ref{fig:ft_base} reflect the sparse nature of the signal received by the realistic finite number of telescopes and baselines sampled from the full ($u,v$) plane signal space of Fig.~\ref{fig:ft}.}
 	\label{fig:ft_base}
@@
 \end{equation}
-where $\Delta f$ is the electronic bandwidth of the photon detectors which measure the intensities.
+where $\Delta f$ is the electronic bandwidth of the photon detectors which measure the intensities and $\Delta \nu$ is the frequency bandwidth of the filters employed in the telescopes to observe the star.
 Values of $\Delta\nu\sim 1\,\mathrm{THz}$ and $\Delta f \sim 1\,\mathrm{GHz}$ are typical of recent work.
 In Eq.~\eqref{eqn:HBT2}, $V_{12}$, referred to as the complex visibility function, is the Fourier transform of the source brightness distribution.
-For a uniform disk it is given by
+For a uniform disk source representing the star, it is given by
 \begin{equation}
@@
 where, $\left\langle I_1 \right\rangle$ and $\left\langle I_2 \right\rangle$ denote the mean intensities from the two telescopes.
-Therefore, the signal measured by the photon detector in II, operating with an electronic bandwidth $\Delta f$ within the optical bandwidth $\Delta {\mathrm {\nu}}$ of the observational radiation, is
+Therefore, the signal measured by the photon detectors in II, operating with an electronic bandwidth $\Delta f$ within the optical bandwidth $\Delta {\mathrm {\nu}}$ of the observational (filtered) radiation, is
 \begin{equation}
@@
 \end{equation}
-$\abs{V_{12}}^2$ is a function of baseline $d = \sqrt{u^2 + v^2}$ on observational plane. Consequently, the strength of the signal is enhanced by employing a large number of baselines.
+with $\abs{V_{12}}^2$ being a function of baseline $b = \sqrt{u^2 + v^2}$ on the observational plane.
+This implies the strength of the signal would be enhanced if a larger number of baselines or pairs of telescopes are employed.
 
@@
 The use of filters not only reduces background noise but also improves the signal quality and the efficiency of the PMTs.
-Filtering background skylight becomes even more significant in II observations, as these are carried out during full moon nights.
-It is important to note that the light from the stellar source is focused on the PMT during II observations.
+Filtering background skylight becomes even more significant in II observations, as, currently, these are carried out during full moon nights when the primary function of the IACTs (of observing Cherenkov Showers) is rendered infeasible.
+It is important to note that the light from the stellar source is focused on a PMT attached with each of the telescopes during II observations.
 
@@
 The excess noise factor of the PMTs is represented by $F$, $T$ denotes the observation time, and $\sigma$ is the normalized spectral distribution of the light (including filters) \citep[e.g.,][]{acciari2020optical}.
-The signal (S) and noise (N) can be understood using eqns.\ref{eq:signal} and \ref{eq:SNR} as:
+The signal ($S$) and noise ($N$) can be inferred using eqns.\ref{eq:signal} and \ref{eq:SNR} as:
 \begin{equation}
@@
 \end{equation}
-While most of the parameters can be optimized with hardware, the only way to achieve a better SNR with fixed telescopes is to increase the observation time $T$.
+While most of the parameters can be optimized with hardware, the only way to achieve a better SNR with fixed telescopes that is at the disposal of the astronomer is to increase the observation time $T$.
 
 \subsection{Baseline considerations}
-The measurement of the size of stellar objects via absolute visibility depends on the distance between the telescopes, known as the baseline $d$.
+The measurement of the size of stellar objects via squared visibility depends on the distance between the telescopes, known as the baseline $b$.
 \begin{equation}
-	|V_{12}(d)|^2 = \frac{c(d)}{c(0)}
+	|V_{12}(b)|^2 = \frac{c(b)}{c(0)}
 	\label{eq:angular_size_meas}
@@
 \begin{equation}
-	(u,v) = \frac{1}{\lambda} (d_E, d_N)
+	(u,v) = \frac{1}{\lambda} (b_E, b_N)
 \end{equation}
-where $d_E$ and $d_N$ are the baselines expressed in east and north coordinates.
-However, of course sources can be anywhere on the sky, and the telescopes are stationary and may also have different relative altitudes $d_A$ depending on the available terrain.
+where $b_E$ and $b_N$ are the baselines expressed in east and north coordinates.
+However, of course sources can be anywhere on the sky, and the telescopes are stationary and may also have different relative altitudes $b_A$ depending on the available terrain.
 Therefore, the Earth's rotation must be taken into account to cover the maximum observational plane using rotated baselines.
@@
 \begin{equation}
-\begin{pmatrix} u\\ v\\ w\\ \end{pmatrix} = R_x(\delta) \cdot R_y(h) \cdot R_x(-l) \begin{pmatrix} d_E \\ d_N \\ d_A \\ \end{pmatrix}
+\begin{pmatrix} u\\ v\\ w\\ \end{pmatrix} = R_x(\delta) \cdot R_y(h) \cdot R_x(-l) \begin{pmatrix} b_E \\ b_N \\ b_A \\ \end{pmatrix}
 	\label{eq:baseline_rot}
@@
 As the number of baselines increases non-linearly, Intensity Interferometry (II) benefits greatly from a large number of telescopes.
-The CTAO can offer many more baselines --- \cite{2013APh....43..331D} considered the telescope configurations then being considered, and all provided dense coverage of the interferometric plane.
+The CTAO can offer many more baselines --- \cite{2013APh....43..331D} considered the telescope configurations then being planned and showed how it would provide a dense coverage of the interference plane.
 
-\subsection{Fast Rotating Stars: The Objects Considered}
+\subsection{A Fictitious Fast Rotating Star: Our Test Case}
 In our work presented here, we simulate a single fast-rotating star to test image reconstruction using a GAN.
 Fast rotation causes stars to adopt an oblate shape, flattening at the poles and bulging at the equator due to the stronger centrifugal force \citep[e.g.,][]{von1924radiative, 1999A&A...347..185M}.
-Fig.~\ref{fig:image} shows a fictitious image qualitatively representing a fast-rotating star, with brightness distributed across its surface.
+Fig.~\ref{fig:image} shows an image qualitatively representing a fictitious fast-rotating star, with brightness distributed across its surface.
 The brightness is highest at the poles and lowest at the equator, a phenomenon known as gravity darkening \citep{lucy1967gravity}.
@@
 The correlation of these photon arrivals at the telescopes yields the squared visibility Eq.~\eqref{eq:angular_size_meas}, as explained in subsection~\ref{sec:signal}.
-Fig.~\ref{fig:ft} shows the signal from the source shown in Fig.~\ref{fig:image} using II, displayed on both linear and logarithmic scales.
-In practice, only a small part of this information is available, because one has a finite number of baselines corresponding to the finite number $N_T$ of telescopes at our disposal and a limited observation schedule.
-Therefore, we have simulated the II observation of a sky source by four telescopes (correlated in pairs) over one night.
+Fig.~\ref{fig:ft} shows the signal from the source shown in Fig.~\ref{fig:image} using II, displayed in both linear and logarithmic scales.
+Point to note here is that this figure represents the signal from the source that would be recorded by an infinite number of baselines provided by an infinite number of telescopes on the interferometric plane.
+In practice, only a small part of this information is available (as seen Fig.~\ref{fig:ft_base}), because one has a finite number of baselines corresponding to the finite number $N_T$ of telescopes at our disposal and a limited observation schedule.
+We have simulated the II observation of the fictitious star by four telescopes (correlated with baselines as seen in Fig.~\ref{fig:teles}) over one night.
 Using this modest amount of signal from one night's observation, we have trained a cGAN to construct the image of the source.
 \begin{figure}
-  \includegraphics[width=\linewidth]{fig/ellipse1612.jpg}
-  \caption{Merged image, which includes the original and the sparsely sampled Fourier plane. It is exactly what the GAN receives.}
+  \includegraphics[width=\linewidth]{fig/ellipse1612.png}
+  \caption{Merged image, which includes the original and the sparsely sampled Fourier plane.
+It is exactly what the GAN receives.
+The grey scale of the figure is normalized to the brightest pixel in the image.}
   \label{fig:GANinput}

### 2025-08-29 Phase_II/draft/AJsubmitted/ParaGan.tex
setting up redblue wrt AJ submitted

--- 2025-07-31 Phase_II/draft/ParaGan.tex
@@
 	\centering
-	\includegraphics[width=\linewidth]{fig/testing_image/image_0.png}
-	\includegraphics[width=\linewidth]{fig/testing_image/image_16.png}
-	\includegraphics[width=\linewidth]{fig/testing_image/image_35.png}
-	\includegraphics[width=\linewidth]{fig/testing_image/image_38.png}
+	\includegraphics[width=\linewidth]{fig/testing_image/image_3.png}
+	\includegraphics[width=\linewidth]{fig/testing_image/image_14.png}
+	\includegraphics[width=\linewidth]{fig/testing_image/image_15.png}
+	\includegraphics[width=\linewidth]{fig/testing_image/image_18.png}
 	\includegraphics[width=\linewidth]{fig/testing_image/image_42.png}

### 2025-08-29 Phase_II/draft/AJsubmitted/main.tex
setting up redblue wrt AJ submitted

--- 2025-07-31 Phase_II/draft/main.tex
@@
-\documentclass[twocolumn]{emulateapj}
-
+\documentclass[linenumbers, twocolumn]{aastex701}
 \usepackage{amsmath}
-\usepackage[colorlinks=true,
-linkcolor=blue,
-citecolor=blue,
-urlcolor=cyan]{hyperref}
 
@@
 
-\title{Generative AI for image reconstruction\\ in Intensity Interferometry: a first attempt}
+\title{Generative AI for image reconstruction in Intensity Interferometry: a first attempt}
 
-\author{Km Nitu Rai,$^{1,2}$, Yuri van der Burg$^{3}$, Soumen
-  Basak$^{1}$, Prasenjit Saha,$^{3}$ and Subrata Sarangi$^{4,5}$}
+\author{Km Nitu Rai}
+\affiliation{School of Physics, Indian Institute of Science Education and Research Thiruvananthapuram, Maruthamala PO, Vithura, Thiruvananthapuram 695551, Kerala, India.}
+\affiliation{Aryabhatta Research Institute of Observational Sciences, Manora Peak, Nainital 263129, India.}
+\email{niturai201296@gmail.com}
 
-\affiliation{$^{1}$School of Physics, Indian Institute of Science
-  Education and Research Thiruvananthapuram, Maruthamala PO, Vithura,
-  Thiruvananthapuram 695551, Kerala, India.}
+\author{Yuri van der Burg} 
+\affiliation{Physik-Institut, University of Zurich,	Winterthurerstrasse 190, 8057 Zurich, Switzerland.}
+\email{yuri.vanderburg@uzh.ch}
 
-\affiliation{$^{2}$Aryabhatta Research Institute of Observational Sciences, Manora Peak, Nainital 263129, India.}
+\author{Soumen Basak}
+\affiliation{School of Physics, Indian Institute of Science Education and Research Thiruvananthapuram, Maruthamala PO, Vithura, Thiruvananthapuram 695551, Kerala, India.}
+\email{sbasak2006@gmail.com}
 
-\affiliation{$^{3}$Physik-Institut, University of Zurich,
-  Winterthurerstrasse 190, 8057 Zurich, Switzerland.}
+\author{Prasenjit Saha}
+\affiliation{Physik-Institut, University of Zurich,	Winterthurerstrasse 190, 8057 Zurich, Switzerland.}
+\email{psaha@physik.uzh.ch}
 
-\affiliation{$^{4}$School of Applied Sciences, Centurion University of
-  Technology and Management, Odisha-752050, India.}
-
-\affiliation{$^5$ Visiting Associate, Inter-University Centre for Astronomy and Astrophysics, Post Bag 4, Ganeshkhind, Pune 411 007, Maharashtra, India.}
+\author{Subrata Sarangi}
+\affiliation{School of Applied Sciences, Centurion University of	Technology and Management, Odisha-752050, India.}
+\affiliation{Visiting Associate, Inter-University Centre for Astronomy and Astrophysics, Post Bag 4, Ganeshkhind, Pune 411 007, Maharashtra, India.}
+\email{ssarangi.itech@gmail.com}
 
@@
 \end{abstract}
-
-\maketitle
 
@@
 
-\bibliographystyle{aasjournal}
+\bibliographystyle{aasjournalv7}
 \bibliography{refs}

### 2025-09-24 Phase_II/draft/response.txt
first small modification

@@
 
+Modified
+
 |  - The sentence referring to the "ground truth, which the Discriminator uses
@@
 |  discriminator has to distinguish between simulated and ground-truth data.
+
+It has been rephrased and clear now. Yes, the Discriminator doesn't have access to the ground truth.
+Even Discriminator loss function use Ground truth and generated images to give feedback to the Discriminator
 
@@
 |  for inference? It is important to quantify computational performance.
+
+The information is provided and we use CPU for training. This work has used 2 nodes with 96 threads each,
+which takes around 9 hour to train the model.

### 2025-09-24 Phase_II/draft/ParaGan.tex
first small modification

@@
 	\centering
-	\includegraphics[width=\linewidth]{fig/testing_image/image_0.png}
-	\includegraphics[width=\linewidth]{fig/testing_image/image_16.png}
-	\includegraphics[width=\linewidth]{fig/testing_image/image_35.png}
-	\includegraphics[width=\linewidth]{fig/testing_image/image_38.png}
-	\includegraphics[width=\linewidth]{fig/testing_image/image_42.png}
-	\includegraphics[width=\linewidth]{fig/testing_image/image_47.png}
+	\includegraphics[width=\linewidth]{fig/testing_image/image_1.png}
+	\includegraphics[width=\linewidth]{fig/testing_image/image_3.png}
+	\includegraphics[width=\linewidth]{fig/testing_image/image_4.png}
+	\includegraphics[width=\linewidth]{fig/testing_image/image_10.png}
+	\includegraphics[width=\linewidth]{fig/testing_image/image_12.png}
+	\includegraphics[width=\linewidth]{fig/testing_image/image_15.png}
 \caption{Example results of image reconstruction using the GAN model along with the II observations simulated in this work.

### 2025-09-24 Phase_II/draft/Result.tex
first small modification

@@
 In this section, we begin by discussing phase retrieval using hyperparameters, as mentioned earlier, followed by an analysis in which multiple sources are trained simultaneously.
-The best performance for image reconstruction has been observed with a learning rate of \(2 \cdot 10^{-4}\), a kernel size of 5×5, and equal noise percentages applied to both the original and generated images.
+The best performance for image reconstruction has been observed with a learning rate of \(2 \cdot 10^{-4}\), a kernel size of 5×5, and equal noise percentages (alpha/beta = 1) applied to both the original and generated images.
 A batch size of 1 is used, and equal training is provided to both the Discriminator and the Generator.
@@
 \subsection{Predicted Image from the Trained GAN}
-Fig.~\ref{fig:GAN} demonstrates the success of the GAN in training a model for Intensity Interferometry (II) to reconstruct images of fast-rotating stars.
-The GAN was trained on the training datasets for 60,000 steps and subsequently tested on various validation datasets to produce predicted images of a fast-rotating star.
-In Fig.~\ref{fig:GAN}, four combined images illustrate the GAN's performance in reconstructing the star’s shape, size, and brightness distribution using II.
+Fig.~\ref{fig:GAN} demonstrates the success of the GAN in training a model to reconstruct the images of  fast-rotating stars using their Intensity Interferometry (II) observation .
+The GAN was trained on the training datasets for 60,000 steps and subsequently tested on various validation datasets to produce predicted images of the stars.
+The training was performed on a CPU using two nodes, each with 96 threads, and required approximately nine hours.
+In Fig.~\ref{fig:GAN}, four combined images illustrate the GAN's performance in reconstructing the stars' shape, size, and brightness distribution using II.
 \begin{itemize}
 \item{The left panel shows the signals collected from six baselines, which serve as the input for the Generator during training.}
-\item{The first middle panel displays the real image, or ground truth, which the Discriminator uses to distinguish between real images and those generated by the Generator.
-During training, the GAN aims to replicate these ground truth images.}
+\item{The first middle panel displays the real image, or ground truth, which the Disciminator loss function uses to distinguish from the images generated by the Generator.
+During training, the GAN aims to keep minimum difference between these ground truth image and generated images.}
 \item{The second middle panel presents the reconstructed, or predicted, image produced by the trained GAN, highlighting its success in image reconstruction.}
-\item{The right panel shows the difference between the ground truth and the predicted image, with a smaller difference indicating higher precision in image reconstruction.}
+\item{The right panel shows the difference between the ground truth and the predicted image in the interferometric plane.
+The uniform background color of the frames suggests that the GAN model picks up white noise in the interferometric plane.}
 \end{itemize}
@@
 
-The raw moment $M_{ij}$ of an image $I(x, y)$ is defined as \citep{hu1962visual}
+The raw moment $M_{ij}$ of an image is defined as \citep{hu1962visual}
 \begin{equation}
-	M_{ij} = \sum_{x} \sum_{y} x^i y^j I(x, y).
+	M_{ij} = \sum_{x} \sum_{y} x^i y^j I(x, y)
 	\label{eqn:Mom}
 \end{equation}
+where $I(x,y)$ represents the intensity at pixel $(x,y)$.
 The zeroth order raw moment, or monopole, represents the total intensity of an image.
@@
 
-The center of mass for the fast-rotating star or any other stellar object is calculated using the centroid ($x$-centroid and $y$-centroid).
-It represents the spatial position of the image and is calculated using first-order raw moment and monopole.
-The formulation of centroid along the $x$ and $y$ directions is
-\begin{equation}
-	\begin{aligned}
-		&m_x = \frac{\sum_{x} x I(x,y)}{\sum_{x} \sum_{y} I(x, y)} = \frac{M_{10}}{M_{00}} \\
-		&m_y = \frac{\sum_{y} y I(x,y)}{\sum_{x} \sum_{y} I(x, y)} = \frac{M_{01}}{M_{00}}
-	\end{aligned}  
-\end{equation}
-The middle and right figure of Fig.~\ref{fig:cen} show the comparison of the $x$-centroid and $y$-centroid for 50 predicted images with respect to ground truths, respectively.
-The clustering of centroids in a given scale range for all the results explains that the reconstructed image correctly represents the spatial location of the fast-rotating star compared with the ground truth.
-
-The center of mass of a fast-rotating star, or any stellar object, is determined by its centroid, which provides the $x$ and $y$ coordinates representing the spatial position of the image.
+The center of mass of the sky image of any stellar object, is determined by its centroid, which provides the $x$ and $y$ coordinates representing the spatial position of the image.
 This centroid is computed using the first-order raw moments in conjunction with the monopole (the zeroth-order moment).
@@
 \end{eqnarray}
-Here, \(I(x,y)\) represents the intensity at pixel \((x,y)\), \(M_{00}\) is the monopole (total intensity), and \(M_{10}\) and \(M_{01}\) are the first-order raw moments along the $x$ and $y$ axes, respectively.
+Here, \(I(x,y)\) represents the intensity at pixel \((x,y)\), \(M_{00}\) is the monopole (total intensity), and \(M_{10}\) and \(M_{01}\) are the first-order raw moments along the $x$ and $y$ axes respectively.
 This formulation accurately captures the spatial center of mass of the stellar object in the image.
 
-The middle and right panel of Fig.~\ref{fig:cen} compare the centroids ($x_{c}$, $y_{c}$) of 50 predicted images with their corresponding ground truths, respectively.
+The middle and right panel of Fig.~\ref{fig:cen} compare the centroids ($x_{c}$, $y_{c}$) of 50 predicted images with their corresponding ground truths respectively.
 The clustering of centroids within a specific scale range across all results indicates that the reconstructed images accurately represent the spatial location of the fast-rotating star relative to the ground truth.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Furthermore, these calculated centroids are instrumental in analyzing the shape, size, and brightness distribution of fast-rotating stars using higher-order image moments.
+Furthermore, these calculated centroids are instrumental in analyzing the shape, size, and brightness distribution of the stars using higher-order image moments.
 To this end, the central moment of an image is calculated according to:
@@
 \subsection{The reconstructed Parameters for object}
-The centroids \((x_c, y_c)\) indicate only the center of the fast-rotating star and its spatial location in the image.
+The centroids \((x_c, y_c)\) indicate only the center of the star and its spatial location in the image.
 In contrast, the second-order central moments determine the orientation, semi-major axis, and eccentricity relative to the source's center \citep{teague1980image}.

### 2025-09-25 Phase_II/draft/GAN.tex
modified intro

@@
 \section{Generative Adversarial Networks}
-\begin{figure*}
-	\includegraphics[width=.49\textwidth]{fig/analysis/Plot_learning_rate_disc_loss.pdf}\hfil
-	\includegraphics[width=.49\textwidth]{fig/analysis/Plot_learning_rate_gen_total_loss.pdf}
-	\caption{Discriminator and Generator losses for three different learning rates.
-The left panel and the right panel show the total discriminator loss and the total generator loss (Eq.~\ref{eq:total_gen_loss}) respectively.
-There is no significant difference, but these figures indicate that higher learning rates might render the training prone to outliers.}
-	\label{fig:Plot_learning_rate_loss}
-\end{figure*}
-\begin{figure*}
-	\includegraphics[width=.49\textwidth]{fig/analysis/Plot_Kernel_size_disc_loss.pdf}
-	\includegraphics[width=.49\textwidth]{fig/analysis/Plot_Kernel_size_gen_total_loss.pdf}
-	\caption{Discriminator and Generator losses (left and right panels respectively) for three different kernel sizes in the convolutional layers.
-Here, the smallest kernel size has many outliers, while the largest kernel size seems to be the most stable.}
-	\label{fig:Plot_kernel_size_loss}
-\end{figure*}
-\begin{figure*}
-	\includegraphics[width=.49\textwidth]{fig/analysis/Plot_noise_factor_disc_loss.pdf}
-	\includegraphics[width=.49\textwidth]{fig/analysis/Plot_noise_factor_gen_total_loss.pdf}
-	\caption{Effect of the Salt (alpha) and Pepper (beta) noise (explained in the text) introduced into the images.
-There is no significant effect of the alpha/beta ratio.
-These results are from training on $64\times64$-pixel images.}
-	\label{fig:Plot_noise_loss}
-\end{figure*}
-\begin{figure*}
-	\includegraphics[width=.49\textwidth]{fig/analysis/Plot_Batchsize_disc_loss.pdf}\hfill
-	\includegraphics[width=.49\textwidth]{fig/analysis/Plot_Batchsize_gen_total_loss.pdf}
-	\caption{Loss functions for two different batch sizes. Large batch sizes seem to make the training more robust, but also increase training time significantly. }
-	\label{fig:Plot_batchsize_loss}
-\end{figure*}
-\begin{figure*}
-	\includegraphics[width=.49\textwidth]{fig/analysis/Plot_Disc_rep_disc_loss.pdf}\hfil
-	\includegraphics[width=.49\textwidth]{fig/analysis/Plot_Disc_rep_gen_total_loss.pdf}
-	\caption{The number of episodes of Discriminator training per every episode of Generator training (termed Discriminator repetition or Disc.
-rep.), understandably, has a higher impact on the Discriminator loss than on the Generator loss.
-The left and the right panel show this effect on the Discriminator loss and the Generator loss respectively.}
-	\label{fig:Plot_discrep_loss}
-\end{figure*}
-\begin{figure*}
-	\includegraphics[width=.49\textwidth]{fig/analysis/Plot_N_telescopes_disc_loss.pdf}\hfil
-	\includegraphics[width=0.49\textwidth]{fig/analysis/Plot_N_telescopes_gen_total_loss.pdf}\hfil
-	\caption{Discriminator loss (left panel) and Generator loss (right panel) for different numbers of telescopes.
-The number of telescopes has a very significant impact on the model performance.
-If there are only two telescopes (1 baseline), both Discriminator and Generator are not trained smoothly: One gains a big advantage over the other.
-The result of four telescopes (6 baselines) is a lot better because the loss functions change only slightly with increasing steps.}
-	\label{fig:Plot_telescopes_loss}
-\end{figure*}
+
 Generative Adversarial Networks (GANs) were introduced by \cite{goodfellow2014generative}.
@@
 These will be referred to as generated images.
-The second network, the Discriminator, attempts to distinguish between the generated image (predicted image) and the real image (ground truth).
+The second network, the Discriminator, attempts to distinguish between the generated image (predicted image) and the real image (ground truth) using Discriminator loss function.
 

### 2025-09-25 Phase_II/draft/II.tex
normalized figure
modified intro

@@
   \includegraphics[width=\linewidth]{fig/ellipse/ellipse1612.jpg}
-  \caption{This figure shows the simulated fast rotating star. The brightness is highest at the pole and there is gravitational darkening at the equator.}
+  \caption{This figure shows the simulated fast rotating star. The brightness is highest at the poles and there is gravity darkening along the equator.}
   \label{fig:image}
@@
 \end{equation}
-where $\Delta f$ is the electronic bandwidth of the photon detectors which measure the intensities.
+where $\Delta f$ is the electronic bandwidth of the photon detectors which measure the intensities and $\Delta \nu$ is the frequency bandwidth of the filters employed in the telescopes to observe the star.
 Values of $\Delta\nu\sim 1\,\mathrm{THz}$ and $\Delta f \sim 1\,\mathrm{GHz}$ are typical of recent work.
 In Eq.~\eqref{eqn:HBT2}, $V_{12}$, referred to as the complex visibility function, is the Fourier transform of the source brightness distribution.
-For a uniform disk it is given by
-\begin{equation}
- V_{12} = 2 \frac{J_1(\pi\theta_D b)}{(\pi\theta_D b)}
-\label{eqn:absvisib}
-\end{equation}
-where $\theta_D$ is the angular diameter of the star and $b$ is the radial coordinate in the conventional interferometric $(u , v) = (x/\lambda, y/\lambda)$ plane, with $\lambda$ representing the optical wavelength of the filter used for observation.
-It is evident from Eq.~\eqref{eqn:absvisib} that $V_{12}$ contains information about the star's angular diameter.
+It contains information about the star's angular diameter.
 However, the phase information is lost since we measure only the absolute value $\vert V_{12} \vert^2$.
 In observational astronomy, the correlation is often expressed in terms of the normalized contrast, given by:
-\begin{equation}
-	c = \frac{\left\langle \left( I_1(t) - \left\langle I_1 \right\rangle \right) \cdot \left( I_2(t + \tau) - \left\langle I_2 \right\rangle \right) \right\rangle}{\langle I_1(t) \rangle \cdot \langle I_2(t) \rangle} = g^{(2)} - 1
-\end{equation}
-where, $\left\langle I_1 \right\rangle$ and $\left\langle I_2 \right\rangle$ denote the mean intensities from the two telescopes.
-Therefore, the signal measured by the photon detector in II, operating with an electronic bandwidth $\Delta f$ within the optical bandwidth $\Delta {\mathrm {\nu}}$ of the observational radiation, is
 \begin{equation}
@@
 \end{equation}
-$\abs{V_{12}}^2$ is a function of baseline $d = \sqrt{u^2 + v^2}$ on observational plane. Consequently, the strength of the signal is enhanced by employing a large number of baselines.
+with $\abs{V_{12}}^2$ being a function of baseline $b = \sqrt{u^2 + v^2}$ on the observational plane $(u, v)$.
+This implies the strength of the signal would be enhanced if a larger number of baselines or pairs of telescopes are employed.
 
@@
 The excess noise factor of the PMTs is represented by $F$, $T$ denotes the observation time, and $\sigma$ is the normalized spectral distribution of the light (including filters) \citep[e.g.,][]{acciari2020optical}.
-The signal (S) and noise (N) can be understood using eqns.\ref{eq:signal} and \ref{eq:SNR} as:
-\begin{equation}
-	S = \frac{\Delta f}{\Delta \nu} \abs{V_{12}}^2
-\end{equation}
-and
-\begin{equation}
-	N = (A \cdot \alpha \cdot q \cdot n \cdot F \cdot \sigma \cdot \Delta \nu)^{-1}\sqrt{\frac{2 \Delta f}{T}}.
-\end{equation}
-While most of the parameters can be optimized with hardware, the only way to achieve a better SNR with fixed telescopes is to increase the observation time $T$.
 
 \subsection{Baseline considerations}
-The measurement of the size of stellar objects via absolute visibility depends on the distance between the telescopes, known as the baseline $d$.
+The measurement of the size of stellar objects via squared visibility depends on the distance between the telescopes, known as the baseline $b$.
 \begin{equation}
-	|V_{12}(d)|^2 = \frac{c(d)}{c(0)}
+	|V_{12}(b)|^2 = \frac{c(b)}{c(0)}
 	\label{eq:angular_size_meas}
@@
 Fast-rotating stars are important test cases for understanding various astrophysical processes, including stellar evolution, internal structure, and dynamical behavior over time.
+It has not yet been observed using intensity interferometry, but oblateness has recently been measured \citep{2025arXiv250615027A} and gravity darkening is a natural next step.
 

### 2025-09-25 Phase_II/draft/intro.tex
modified intro

@@
 In the context of II, this involves reconstructing the source's image from the intensity correlations recorded by pairs of telescopes (light buckets) on the ground.
-However, because the primary observable in II is the electromagnetic field intensity rather than the field amplitude, the phase of the interferometric signal is lost.
-Since a complete reconstruction of a source's brightness distribution requires phase information, the challenge is to recover the phase of the signal.
+However, because the primary observable in II is the intensity of electromagnetic field rather than the amplitude, the phase of the interferometric signal is lost.
+So, there is a challenge to recover the phase of the signal, since a complete reconstruction of a source's brightness distribution requires phase information.
 

### 2025-09-25 Phase_II/draft/response.txt
modified intro
before figure 7

@@
 
-Clarify that we mean phase of the complex visibility.
+Clarify that we mean phase of the complex visibility. However, we have rephrased the line
+to be more clear.
 
@@
 |  condensed.
+
+The equations have been condensed now.
 
@@
 The information is provided and we use CPU for training. This work has used 2 nodes with 96 threads each,
-which takes around 9 hour to train the model.
+which takes around 20 hours to train the model with 100000 training steps.

### 2025-09-25 Phase_II/draft/GAN.tex
before figure 7

@@
 
-Subsequently, zero padding is applied—adding rows and columns of zeros around the images—to prevent the loss of spatial information during convolution and to facilitate the extraction of deeper features from the downsampled output.
+Subsequently, zero padding is applied, adding rows and columns of zeros around the images to prevent the loss of spatial information during convolution and to facilitate the extraction of deeper features from the downsampled output.
 Following this, batch normalization is employed to stabilize learning by normalizing activations, and the Discriminator begins classifying each patch as real or fake.

### 2025-09-25 Phase_II/draft/ParaGan.tex
before figure 7

@@
 Here, we discuss the parameters of the GAN architecture used for reconstructing images of stellar objects using II.
-Given the adversarial nature of GANs—where the Generator and Discriminator engage in a min-max game—careful tuning of key parameters is critical to ensure that both networks are well-balanced for effective training.
+Given the adversarial nature of GANs, where the Generator and Discriminator engage in a min-max game, careful tuning of key parameters is critical to ensure that both networks are well-balanced for effective training.
 

### 2025-09-25 Phase_II/draft/Result.tex
before figure 7

@@
 Fig.~\ref{fig:GAN} demonstrates the success of the GAN in training a model to reconstruct the images of  fast-rotating stars using their Intensity Interferometry (II) observation .
-The GAN was trained on the training datasets for 60,000 steps and subsequently tested on various validation datasets to produce predicted images of the stars.
-The training was performed on a CPU using two nodes, each with 96 threads, and required approximately nine hours.
+The GAN was trained on the training datasets for 100,000 steps and subsequently tested on various validation datasets to produce predicted images of the stars.
+The training was performed on a CPU using two nodes, each with 96 threads, and required approximately 20 hours.
 In Fig.~\ref{fig:GAN}, four combined images illustrate the GAN's performance in reconstructing the stars' shape, size, and brightness distribution using II.

### 2025-09-26 Phase_II/draft/GAN.tex
some more modification

@@
 \section{Generative Adversarial Networks}
-
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{fig/analysis/Discrep_Runs_Losses_disc_loss.png}
+	\includegraphics[width=\linewidth]{fig/analysis/Discrep_Runs_Losses_gen_total_loss.png}
+	\caption{The number of episodes of Discriminator training per every episode of Generator training (termed Discriminator repetition or Disc.
+rep.), understandably, has a higher impact on the Discriminator loss than on the Generator loss.
+The left	and the right panel show this effect on the square root of cumulative mean of Discriminator loss and the Generator loss respectively.}
+	\label{fig:Plot_discrep_loss}
+\end{figure}
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{fig/analysis/Telescope_Runs_Losses_disc_loss.png}
+	\includegraphics[width=\linewidth]{fig/analysis/Telescope_Runs_Losses_gen_total_loss.png}
+	\caption{The square root of cumulative mean of Discriminator and Generator loss for different numbers of telescopes.
+It has a very significant impact on the model performance.
+If there are only two telescopes, both Discriminator and Generator are not trained smoothly.
+The result of four telescopes is a lot better because the cumulative mean of loss functions is smaller compare to other parameters.}
+	\label{fig:Plot_telescopes_loss}
+\end{figure}
 Generative Adversarial Networks (GANs) were introduced by \cite{goodfellow2014generative}.

### 2025-09-26 Phase_II/draft/II.tex
some more modification

@@
 \begin{figure}[hbt]
-  \includegraphics[width=\linewidth]{fig/ellipse/ellipse1612.jpg}
+  \includegraphics[width=\linewidth]{fig/ellipse/ellipse1612.png}
   \caption{This figure shows the simulated fast rotating star. The brightness is highest at the poles and there is gravity darkening along the equator.}
@@
 \begin{figure*}
-	%\begin{subfigure}{0.5\linewidth}
 	\includegraphics[width=.49\linewidth]{fig/ft/ft.jpg}\hfil
-	%\caption{The signal (absolute value of the Fourier transform of the source).}
-	%\end{subfigure}\hfill
-	%\begin{subfigure}{0.5\linewidth}
-		\includegraphics[width=.49\linewidth]{fig/ft/ft_log.jpg}
-		%\caption{The logarithm of the signal.}
-	%\end{subfigure}
-	\caption{Absolute value of the two-dimensional Fast Fourier Transform of the source depicted in Fig.~\ref{fig:image} in linear scale (left panel) and logarithmic scale (right panel).
-These figures represent the intensity interferometric ($u,v$) plane image of the source that would be obtained by an infinite number of baselines (or infinite number of telescopes observing the source).
-Both the linear and the logarithmic scales are normalized to the maximum intensity obtained at the centre of figures.
-}
+	\includegraphics[width=.49\linewidth]{fig/ft/ft_base.jpg}
+	\caption{Absolute value of the two-dimensional Fast Fourier Transform of the source depicted in Fig.~\ref{fig:image} on linear scale (left panel).
+It represent the intensity interferometric ($u,v$) plane image of the source that would be obtained by an infinite number of baselines (or infinite number of telescopes observing the source).
+The right panel shows the absolute value of the two-dimensional Fast Fourier Transform of the source depicted in Fig.~\ref{fig:image} and measured along the tracks shown in Fig.~\ref{fig:base} covered by the baselines shown in Fig.~\ref{fig:teles}.
+This figure reflects the sparse nature of the signal received by the realistic finite number of telescopes and baselines sampled from the full ($u,v$) plane signal space of left figures.
+Both figures are normalized to the maximum pixel value in the respective figures.}
 	\label{fig:ft}
@@
 This section presents a brief conceptual overview of how an array of telescopes is used to perform II observations, and explains the Signal-to-Noise Ratio (SNR) from these measurements.
-\begin{figure*}
-	%\centering
-	%\begin{subfigure}{0.5\linewidth}
-  \includegraphics[width=.49\linewidth]{fig/ft/ft_base.jpg}\hfil
-		%\caption{The signal as samples by the baselines.}
-	%\end{subfigure}\hfill
-	%\begin{subfigure}{0.5\linewidth}
-  \includegraphics[width=.49\linewidth]{fig/ft/ft_log_base.jpg}
-		%\caption{The logarithmic signal as sampled by the baselines.}
-	%\end{subfigure}
-  \caption{Absolute value of the two-dimensional Fast Fourier Transform of the source depicted in Fig.~\ref{fig:image} and measured along the tracks shown in Fig.~\ref{fig:base} covered by the baselines shown in Fig.~\ref{fig:teles}.
-Both the left panel (in linear scale) and the right panel (in logarithmic scale) are normalized to the maximum pixel value in the respective figures.
-The panels of Fig.~\ref{fig:ft_base} reflect the sparse nature of the signal received by the realistic finite number of telescopes and baselines sampled from the full ($u,v$) plane signal space of Fig.~\ref{fig:ft}.}
-	\label{fig:ft_base}
-\end{figure*}
 \subsection{The signal for II}\label{sec:signal}
@@
 The correlation of these photon arrivals at the telescopes yields the squared visibility Eq.~\eqref{eq:angular_size_meas}, as explained in subsection~\ref{sec:signal}.
-Fig.~\ref{fig:ft} shows the signal from the source shown in Fig.~\ref{fig:image} using II, displayed in both linear and logarithmic scales.
+The left panel of fig.~\ref{fig:ft} shows the signal from the source shown in Fig.~\ref{fig:image} using II, displayed on linear scales.
 Point to note here is that this figure represents the signal from the source that would be recorded by an infinite number of baselines provided by an infinite number of telescopes on the interferometric plane.
-In practice, only a small part of this information is available (as seen Fig.~\ref{fig:ft_base}), because one has a finite number of baselines corresponding to the finite number $N_T$ of telescopes at our disposal and a limited observation schedule.
+In practice, only a small part of this information is available (as seen in right panel of Fig.~\ref{fig:ft}), because one has a finite number of baselines corresponding to the finite number $N_T$ of telescopes at our disposal and a limited observation schedule.
 We have simulated the II observation of the fictitious star by four telescopes (correlated with baselines as seen in Fig.~\ref{fig:teles}) over one night.

### 2025-09-26 Phase_II/draft/ParaGan.tex
some more modification

@@
 Each row in this figure represents the results for a hypothetical fast-rotating star.
-Going from left to right in each row, the first panel represents the simulated $(u,v)$ plane II signals obtained using the six baselines (of Fig.\ref{fig:ft_base}).
+Going from left to right in each row, the first panel represents the simulated $(u,v)$ plane II signals obtained using the six baselines (right panel of of fig.\ref{fig:ft}).
 This image is presented, as the input, to the trained GAN to produce a predicted image.
@@
 Next, sparse sampling is introduced via pixel-wise multiplication between the absolute-valued Fourier-transformed image (Fig.~\ref{fig:ft}) and the sparse sampling map (Fig.~\ref{fig:base}).
-The result is a map in the Fourier plane featuring several ellipses, which is also referred to as the sparse sampling map (Fig.~\ref{fig:ft_base}).
+The result is a map in the Fourier plane featuring several ellipses, which is also referred to as the sparse sampling map (right panel of fig.~\ref{fig:ft}).
 This map represents the sparse sampling of the signal space (Fig.~\ref{fig:ft}) corresponding to the source (Fig.~\ref{fig:image}) observed with four telescopes (Fig.~\ref{fig:teles}).
@@
 This image represents the sparsely sampled phaseless visibility as it can be measured with II.
-The image shown in Fig.~\ref{fig:ft_base} serves as the input for the GAN, which also requires the corresponding ground truth image.
+The image shown in right panel of fig.~\ref{fig:ft} serves as the input for the GAN, which also requires the corresponding ground truth image.
 Consequently, the simulated stars are resized using the same algorithm and converted to 8-bit integers to reduce bias.
@@
 Therefore, selecting an appropriate learning rate is crucial \citep{murphy2022probabilistic}.
-Fig.~\ref{fig:Plot_learning_rate_loss} illustrates the effect of different learning rates on both the Generator and Discriminator losses.
-As expected, lower learning rates result in fewer outliers in the loss functions, indicating more stable updates.
-Although all models eventually stabilize at a similar level, lower learning rates are preferred.
 
@@
 A larger kernel size can capture features spanning several pixels, but it may also incorporate unrelated features.
-As shown in Fig.~\ref{fig:Plot_kernel_size_loss}, the kernel size does not have a significant impact on the loss functions; however, smaller kernel sizes tend to produce more outliers, suggesting that either the Generator or Discriminator may gain an advantage.
-Therefore, a kernel size of 5 is preferred.
 
-The amount of noise is controlled by two parameters, ``alpha" and ``beta", which indicate the percentage of pixels altered to either white or black — hence the term Salt and Pepper noise.
+The amount of noise is controlled by two parameters, ``alpha" and ``beta", which indicate the percentage of pixels altered to either white or black, hence the term Salt and Pepper noise.
 Here, ``alpha" is applied to the real image, while ``beta" is applied to the generated image.
 Different ratios (``alpha/beta") can lead to varying model performance; however, our results indicate that distinct noise rates do not significantly affect the loss functions.
-Figure~\ref{fig:Plot_noise_loss} shows the loss functions for smaller images ($64 \times 64$), and due to the negligible impact, this analysis was not repeated for larger images.
 
@@
 Smaller batch sizes have been observed to improve generalization \citep{prince2023understanding}.
-As illustrated in Fig.~\ref{fig:Plot_batchsize_loss}, processing two images at once results in fewer outliers.
 However, because a larger batch size significantly increases training time, a batch size of 1 is used.
@@
 When training GANs, one strategy to potentially boost performance is to give the Discriminator an advantage by increasing its number of training steps before returning to the Generator's training.
-While this can lower the Discriminator loss—as shown in Fig.~\ref{fig:Plot_discrep_loss}—it also increases training time and leads to a slight rise in the Generator loss.
+While this can lower the Discriminator loss, as shown in Fig.~\ref{fig:Plot_discrep_loss}, it also increases training time and leads to a slight rise in the Generator loss.
 Since the generated images do not noticeably improve with additional Discriminator training, both networks are typically trained with the same number of steps.
@@
 Overall, the degree of sparse sampling appears to have the most pronounced effect of all the hyperparameters.
+
+All the selected hyperparameters to train the model is summarized in the given table:
+\begin{table}[ht]
+	\centering
+	\caption{Selected hyperparameters used for training the model.}
+	\label{tab:hyperparameters}
+	\begin{tabular}{ll}
+		\hline
+		\textbf{Hyperparameter} & \textbf{Value} \\
+		\hline
+		Learning rate           & 2e-4 \\
+		Kernel size             & 5 \\
+		Alpha/Beta              & 1 \\
+		Batch size              & 1 \\
+		Buffer Size             & 1400 \\
+		Discriminator repetition  & 1 \\
+		No. of Telescope        & 4 \\
+		Output Channels         & 1 \\
+		Lambda                  & 100 \\
+		\hline
+	\end{tabular}
+\end{table}

### 2025-09-29 Phase_II/draft/ParaGan.tex
fig6

@@
 \end{table}
+
+The process to train the model is summarized here:
+\begin{figure*}[htbp]
+	\centering
+	\begin{tikzpicture}[node distance=0.9cm]
+
+		% Data pipeline
+		\node[block, fill=blue!15] (data) {Ground Truth \\ (Create $N$ Images of Stellar Objects)};
+		\node[block, fill=red!10, below=of data] (pre) {Simulation \\ (Intensity Interferometry (II) Data)};
+		\node[block, fill=green!20, below=of pre, minimum width=5cm] (split) {Input Dataset (Merge of Ground Truth \\ and Simulation of II) Split \\ (Training, Validation, Testing)};
+
+		% Split branches
+		\node[block, fill=green!15, below left=0.6cm and 2.5cm of split] (train) {Training Set \\ (Learn Model Parameters)};
+		\node[block, fill=yellow!20, below=0.6cm of split] (val) {Validation Set \\ (Tune Hyperparameters)};
+		\node[block, fill=orange!20, below right=0.6cm and 2.5cm of split] (test) {Testing Set \\ (Final Evaluation)};
+
+		% Model training big box
+		\node[block, fill=orange!20, below=3cm of val, minimum width=10cm, minimum height=1.2cm] (mod) {Train the Model \\ (Generator + Discriminator)};
+
+		% Generator side (left)
+		\node[block, fill=cyan!15, below=1.2cm of mod, xshift=-3.5cm] (noise) {Random Noise $z$};
+		\node[block, fill=green!20, below=of noise] (gen) {Generator $G(z)$};
+		\node[block, fill=blue!10, below=of gen] (fake) {Generated Image};
+		\node[block, fill=purple!20, below=of fake] (gloss) {Generator Loss \\ (Update $G$)};
+
+		% Discriminator side (right)
+		\node[block, fill=yellow!20, below=1.2cm of mod, xshift=+3.5cm] (real) {Real Image \\ (From Training Set)};
+		\node[block, fill=orange!20, below=of real] (disc) {Discriminator $D(x)$};
+		\node[block, fill=red!20, below=of disc] (out) {Output: Real/Fake};
+		\node[block, fill=purple!30, below=of out] (dloss) {Discriminator Loss \\ (Update $D$)};
+
+		% Final result block
+		\node[block, fill=teal!20, below=4.2cm of val, minimum width=5cm] (res) {Result / Evaluation \\ (Performance Metrics: Accuracy)};
+
+		% Connections for data pipeline
+		\draw[arrow] (data) -- (pre);
+		\draw[arrow] (pre) -- (split);
+		\draw[arrow] (split.south west) |- (train.north);
+		\draw[arrow] (split.south) -- (val.north);
+		\draw[arrow] (split.south east) |- (test.north);
+		\draw[arrow] (train.south) |- (mod.north);
+
+		% GAN arrows
+		\draw[arrow] (mod) -- (noise);
+		\draw[arrow] (mod) -- (real);
+		\draw[arrow] (noise) -- (gen);
+		\draw[arrow] (gen) -- (fake);
+		\draw[arrow] (fake.east) -- ++(0.5,0) |- (disc.west);
+		\draw[arrow] (real) -- (disc);
+		\draw[arrow] (disc) -- (out);
+
+		% Feedback loops
+		\draw[arrow] (out.south west) -- ++(-3,0) |- (gloss.east);
+		\draw[arrow] (gloss.west) -- ++(-3,0) |- (gen.west);
+		\draw[arrow] (out.south east) -- ++(3,0) |- (dloss.east);
+		\draw[arrow] (dloss.east) -- ++(3,0) |- (disc.east);
+
+		% Validation & Testing to Result
+		\draw[arrow] (val.south) -- (res.north);
+		\draw[arrow] (test.south) -- (res.north);
+
+	\end{tikzpicture}
+	\caption{The cGAN-based image reconstruction block diagram.
+Data is split into training (used for GAN optimization), validation (for hyperparameter tuning), and testing (for final evaluation).
+The GAN training loop optimizes Generator and Discriminator, while validation and testing feed into performance evaluation metrics.}
+	\label{fig:gan_block}
+\end{figure*}

### 2025-09-29 Phase_II/draft/main.tex
for journal
fig6

--- 2025-07-31 Phase_II/draft/main.tex
@@
-\documentclass[twocolumn]{emulateapj}
+\documentclass[linenumbers, twocolumn]{aastex701}
+\usepackage{amsmath}
+\usepackage{tikz}
+\usetikzlibrary{shapes, arrows.meta, positioning, calc}
 
-\usepackage{amsmath}
-\usepackage[colorlinks=true,
-linkcolor=blue,
-citecolor=blue,
-urlcolor=cyan]{hyperref}
+\tikzset{
+	block/.style={
+		rectangle,
+		draw,
+		rounded corners,
+		minimum height=1cm,
+		minimum width=3cm,
+		align=center
+	},
+	arrow/.style={
+		thick,
+		-{Stealth}
+	}
+}
 

### 2025-09-30 Phase_II/draft/image-reconstruction-past-efforts.tex
Section Introduction re-written and anew section on Past efforts introduced

--- 2025-07-31 Phase_II/draft/intro.tex
@@
-\section{Introduction}
-
-Intensity Interferometry (II) was first reported by Hanbury Brown and Twiss (HBT) during the 1950s \citep{brown1954lxxiv, HBT56} as a \textquotedblleft new type of interferometry\textquotedblright\ to measure stellar parameters such as angular diameter, orbits, and limb darkening coefficients.
-Later, theoretical results reported by \cite{brown1957interferometry, brown1958interferometry}, along with those of \cite{glauber1963quantum} and others, demonstrated the deeper physical properties of photon correlations that lie at the core of II and laid the foundation for Quantum Optics \cite[for textbook treatments see][]{MandelWolf1995, Hecht2002}.
-
-By the 1970s, with stellar parameter measurements of 32 stars in single and multiple star systems conducted by Hanbury Brown and his collaborators \citep{hanbury1974angular} at the historic Narrabri Stellar Intensity Interferometer (NSII) in Australia, II had emerged as an alternative to the already established technique of Michelson Interferometry for measuring stellar parameters.
-Despite these significant achievements, the method did not gain widespread adoption in the ensuing decades, primarily due to the unavailability of sensitive photon detectors and advanced data analysis equipment.
-
-More recently, proposals to utilize Imaging Atmospheric Cherenkov Telescope (IACT) facilities for conducting II observations of stars have emerged\citep{LeBohec2006, nunez2010stellar, nunez2012high, 2013APh....43..331D}.
-It has been demonstrated that such observations could be carried out during bright, moonlit nights when $\gamma$-ray observations based on upper atmospheric Cherenkov showers were not feasible.
-This approach has the potential to enhance the scientific output of existing IACT facilities, and especially of the upcoming Cherenkov Telescope Array Observatory (CTAO).
-SII observations at VERITAS, MAGIC, and HESS are now being reported \citep[e.g.,][]{2024ApJ...966...28A,2024MNRAS.529.4387A,2025MNRAS.537.2334V}.
-Simulations \citep[e.g.,][]{10.1093/mnras/stab2391, 10.1093/mnras/stac2433} have argued that recent advancements in photon detectors could be effective in achieving high-precision measurements of parameters for stellar objects.
-
-Beyond measuring stellar diameters and other parameters of star systems, a fundamental goal of optical astronomy is to image stellar systems at high angular resolution.
-In the context of II, this involves reconstructing the source's image from the intensity correlations recorded by pairs of telescopes (light buckets) on the ground.
-However, because the primary observable in II is the electromagnetic field intensity rather than the field amplitude, the phase of the interferometric signal is lost.
-Since a complete reconstruction of a source's brightness distribution requires phase information, the challenge is to recover the phase of the signal.
-
+\section{Past Efforts at Image Reconstruction in Intensity Interferometry}
 Several theoretical and computational approaches for phase reconstruction with II have been proposed.
@@
 
-In this paper, we propose a conditional Generative Adversarial Network (cGAN) model \citep[following][]{isola2017image} to reconstruct images of fast-rotating stars using their simulated Intensity Interferograms and simulated sky-intensity distributions as input data for training, testing, and validation.
-We consider four Imaging Cherenkov Telescope Arrays (IACTs) and simulate observation of a fast-rotating star.
-The image predicted by the trained GAN shows promising results in reconstructing the star’s shape and size.
-The reconstructed brightness distributions are then assessed using moments.
+Let us now discuss the details of our procedure and method.
 
-This paper is organized as follows.
-The next section discusses Intensity Interferometry, focusing on its signal and noise characteristics for fast-rotating stars along the Earth’s rotation.
-The following section introduces the GAN formulation and its structure.
-The fourth section details the parameter selection for training the GAN for image reconstruction.
-The fifth section presents the results of the trained GAN both visually and via image moments.
-Finally, the paper concludes with a discussion of the overall results.
 \begin{figure}

### 2025-09-30 Phase_II/draft/intro_reformatted.tex
Section Introduction re-written and anew section on Past efforts introduced

\section{Introduction}
Intensity Interferometry (II), as a \textquotedblleft new type of interferometry\textquotedblright\ to observe stars other than the Sun and other star systems as extended objects, was first reported by Hanbury Brown and Twiss (HBT) in 1954 \citep{brown1954lxxiv} in the domain of radio astronomy and, later in 1956, in the domain of optical  (visible light) astronomy \citep{HBT56Sirius}. In their work of 1956 \citep{HBT56Sirius}, HBT presented a method to measure the angular diameter of the star Sirius using the correlation of observed intensity fluctuations of the light received from the star. This method was an alternative to the then established method of Michelson Interferometry (MI) following the work of Michelson and Pease \citep{MichelsonPease1921}. Michelson and Pease had measured, in 1921, the angular diameter of Betelgeuse by using the interference of coherent light received at two suitably chosen sub-apertures of the 100-inch Hooker telescope at Mount Wilson. As the situation stands today, MI and II are two alternative and complementary methods to observe stars and measure stellar parameters. MI requires coherence of the light beams from the two apertures. II dispenses with the requirement of coherence of the light beams from the two apertures, measures the intensity fluctuations, correlates these fluctuations to obtain the interference pattern; but loses the inherent phase information of the beams. The positive compensation for this loss of information, however, is manifold. It is immune to atmospheric turbulences, works with less demanding optical surfaces and optics, is able to use upto km-scale baselines yielding high resolution and can easily integrate any number of baseline pairs leading to good coverage of the ($u$,$v$)-plane signal coverage. However, it faces challenges with low signal-to-noise for faint objects, requires fast electronics and has limited imaging capability due to the lost phase information. The piece of work reported here uses a conditional Generative Adversarial (neural) Network (c-GAN) to simulate phase reconstruction and surface imaging of a rapid rotator.

The foundational basis of II stems from the pioneering experiments and theoretical investigations, widely referred to as the \textquotedblleft HBT effect \textquotedblright, carried out initially by Hanbury Brown and Twiss (HBT) \cite{HBT56Lab,brown1957interferometry, brown1958interferometry} and, later, by Glauber \citep{glauber1963quantum}. HBT reported \cite{HBT56Lab} in 1956, the correlation between photons measured by a pair of photon detectors in two coherent beams of light. A modern-day variant of this experiment, carried out by Rai et al. \cite{Rai2025} with pseudo-thermal light has been reported recently. The HBT Effect and the theoretical investigations laid the foundation for the modern field of Quantum Optics.

Hanbury Brown and his collaborators led the creation and installatopn of the iconic II facility at Narrabri, Australia and reported the measurement of angular diameters of 32 stars and a few results of multiple star-systems \citep{hanbury1974angular}. Nevertheless,  unavailability of fast photon detectors and advanced data processing equipment needed for photon counting and correlation computations stalled stellar II observations following this famous work for over four decades. Following proposals to utilize Imaging Atmospheric Cherenkov Telescope (IACT) facilities for conducting II observations of stars have emerged\citep{LeBohec2006, nunez2010stellar, nunez2012high, 2013APh....43..331D} as a secondary science application of these facilities during moonlit night, SII observations at VERITAS, MAGIC, and HESS are now being reported \citep[e.g.,][]{2024ApJ...966...28A,2024MNRAS.529.4387A,2025MNRAS.537.2334V}. This approach has the potential to enhance the scientific output of existing IACT facilities, and especially of the upcoming Cherenkov Telescope Array Observatory (CTAO). Simulations carried out by Rai et al. \citep[e.g.,][]{10.1093/mnras/stab2391, 10.1093/mnras/stac2433} have shown that recent advancements in photon detectors could be effective in achieving high-precision measurements of parameters for stellar objects.

One of the long-standing aspirations in stellar interferometry — whether through Michelson Interferometry (MI) or Intensity Interferometry (II) — has been to achieve high-fidelity image reconstruction of distant stars. This capability would transcend the measurement of global and average stellar parameters, such as angular diameters, binary separations, and orbital characteristics, which, while invaluable, offer only an integrated view of the star or star system as a whole. Instead, it promises direct insights into dynamic surface phenomena, including limb darkening, convection cells, granulation, star spots, oblateness and gravity darkening in rapid rotators and atmospheric structures, akin to the detailed observations routinely conducted on our own Sun.

As it stands today, studies grappling various issues of image reconstruction are being reported \citep{Haubois2009, Norris2021AZCyg, Liu2024SuperresolutionII, Liu2025}. MI-based image reconstruction has made a lot of progress in this area with efforts at generating constructed images of stars like Betelgeuse \citep{Haubois2009} and AZ Cyg \citep{Norris2021AZCyg}. On the otherhand, II-based methods are in a nascent stage. The recent publications of Liu et al. \cite{Liu2024SuperresolutionII, Liu2025} have demonstrated, through outdoor experiments, imaging millimeter-scale targets at 1.36 km with a resolution ~14 times better than a single telescope’s diffraction limit. A \textquotedblleft flexible computational algorithm \textquotedblright reconstructs images from intensity correlations, overcoming atmospheric turbulence and optical imperfections.

We report here, the results of our attempt, the first of its kind in the context of stellar II, to reconstruct the II-simulated observed gravity-darkened images of fast rotating stars using a cGAN neural network architecture. We emulate the cGAN model of Isola et al. \cite{isola2017image} to reconstruct images of fast-rotating stars using their simulated Intensity Interferograms and simulated sky-intensity distributions as input data for training, testing, and validation. We consider four Imaging Cherenkov Telescope Arrays (IACTs) and simulate observation of a fast-rotating star. The image predicted by the trained GAN shows promising results in reconstructing the star’s shape and size. The reconstructed brightness distributions are then assessed using moments.

This paper is organized as follows. The next section discusses Intensity Interferometry, focusing on its signal and noise characteristics for fast-rotating stars along the Earth’s rotation. The following section introduces the GAN formulation and its structure. The fourth section details the parameter selection for training the GAN for image reconstruction. The fifth section presents the results of the trained GAN both visually and via image moments. Finally, the paper concludes with a discussion of the overall results.
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{fig/telescope.png}
	\caption{The telescope configuration with similar properties each used to simulate the signal for II observation.}
	\label{fig:teles}
\end{figure}

### 2025-09-30 Phase_II/draft/response.txt
some more modification

@@
 
-Merge figs 4 and 5, also 14-16.
+Both figs 4 and 5 is merged and only linear scale is there. Now the visibility 
+pattern is visible as we choose smaller source shown in fig~3. 
+The labels in fig 14-16 have been modified now.
 
@@
 
-Improve this.
+Figure 6 is bigger now and have been explained that why it is merge.
+There is also a block diagram created which explain the image reconstruction using GAN.
 
@@
 
-Revise these figures.
+Figures and text accordingly have been revised.
 

### 2025-10-01 Phase_II/draft/GAN.tex
figure caption

@@
 \section{Generative Adversarial Networks}
-\begin{figure}
+\begin{figure*}
 	\centering
-	\includegraphics[width=\linewidth]{fig/analysis/Discrep_Runs_Losses_disc_loss.png}
-	\includegraphics[width=\linewidth]{fig/analysis/Discrep_Runs_Losses_gen_total_loss.png}
+	\includegraphics[width=0.45\linewidth]{fig/analysis/Discrep_Runs_Losses_disc_loss.png}\hfil
+	\includegraphics[width=0.45\linewidth]{fig/analysis/Discrep_Runs_Losses_gen_total_loss.png}
 	\caption{The number of episodes of Discriminator training per every episode of Generator training (termed Discriminator repetition or Disc.
@@
 	\label{fig:Plot_discrep_loss}
-\end{figure}
-\begin{figure}
+\end{figure*}
+\begin{figure*}
 	\centering
-	\includegraphics[width=\linewidth]{fig/analysis/Telescope_Runs_Losses_disc_loss.png}
-	\includegraphics[width=\linewidth]{fig/analysis/Telescope_Runs_Losses_gen_total_loss.png}
+	\includegraphics[width=0.45\linewidth]{fig/analysis/Telescope_Runs_Losses_disc_loss.png}\hfil
+	\includegraphics[width=0.45\linewidth]{fig/analysis/Telescope_Runs_Losses_gen_total_loss.png}
 	\caption{The square root of cumulative mean of Discriminator and Generator loss for different numbers of telescopes.
@@
 	\label{fig:Plot_telescopes_loss}
-\end{figure}
+\end{figure*}
 Generative Adversarial Networks (GANs) were introduced by \cite{goodfellow2014generative}.

### 2025-10-01 Phase_II/draft/II.tex
figure caption

--- 2025-09-25 Phase_II/draft/II.tex
@@
   \includegraphics[width=\linewidth]{fig/baseline.png}
-  \caption{The tracks of the baselines provided by the four telescopes arranged in fig.~\ref{fig:teles} for one night of observation.}
+  \caption{The tracks of the baselines due to Earth rotation (discribed in sec.~\ref{sec:earth}) provided by the four telescopes arranged in fig.~\ref{fig:teles} for one night of observation.
+The increased number of telescopes will creates more baselines, so the coverage of more observational plane and better image reconstruction.}
   \label{fig:base}
@@
 \begin{figure}[hbt]
-  \includegraphics[width=\linewidth]{fig/ellipse/ellipse1612.jpg}
-  \caption{This figure shows the simulated fast rotating star. The brightness is highest at the poles and there is gravity darkening along the equator.}
+  \includegraphics[width=\linewidth]{fig/ellipse/ellipse1612.png}
+  \caption{This figure shows one of the simulated fast rotating star.
+The brightness is highest at the poles and there is gravity darkening along the equator.
+There is 31460 images has been created with different parameters to train the model.}
   \label{fig:image}
@@
 \begin{figure*}
-	%\begin{subfigure}{0.5\linewidth}
 	\includegraphics[width=.49\linewidth]{fig/ft/ft.jpg}\hfil
-	%\caption{The signal (absolute value of the Fourier transform of the source).}
-	%\end{subfigure}\hfill
-	%\begin{subfigure}{0.5\linewidth}
-		\includegraphics[width=.49\linewidth]{fig/ft/ft_log.jpg}
-		%\caption{The logarithm of the signal.}
-	%\end{subfigure}
-	\caption{Absolute value of the two-dimensional Fast Fourier Transform of the source depicted in Fig.~\ref{fig:image} in linear scale (left panel) and logarithmic scale (right panel).
-These figures represent the intensity interferometric ($u,v$) plane image of the source that would be obtained by an infinite number of baselines (or infinite number of telescopes observing the source).
-Both the linear and the logarithmic scales are normalized to the maximum intensity obtained at the centre of figures.
-}
+	\includegraphics[width=.49\linewidth]{fig/ft/ft_base.jpg}
+	\caption{The left panel shows the absolute value of the two-dimensional Fast Fourier Transform of the source depicted in Fig.~\ref{fig:image}.
+It represents the intensity interferometric ($u,v$) plane image of the source that would be obtained by an infinite number of baselines (or an infinite number of telescopes observing the source).
+The right panel shows the absolute value of the same source measured along the tracks shown in Fig.~\ref{fig:base}.
+This figure reflects the sparse nature of the signal received by a realistic finite number of telescopes and baselines sampled from the full ($u,v$) plane signal space, as shown in the left figures.
+Both figures are plotted on a linear scale and normalized to the maximum pixel value in each respective figure.}
 	\label{fig:ft}
@@
 
-\subsection{Baseline considerations}
+\subsection{Baseline considerations}\label{sec:earth}
 The measurement of the size of stellar objects via squared visibility depends on the distance between the telescopes, known as the baseline $b$.
@@
 The correlation of these photon arrivals at the telescopes yields the squared visibility Eq.~\eqref{eq:angular_size_meas}, as explained in subsection~\ref{sec:signal}.
-Fig.~\ref{fig:ft} shows the signal from the source shown in Fig.~\ref{fig:image} using II, displayed in both linear and logarithmic scales.
+The left panel of fig.~\ref{fig:ft} shows the signal from the source shown in Fig.~\ref{fig:image} using II, displayed on linear scales.
 Point to note here is that this figure represents the signal from the source that would be recorded by an infinite number of baselines provided by an infinite number of telescopes on the interferometric plane.
-In practice, only a small part of this information is available (as seen Fig.~\ref{fig:ft_base}), because one has a finite number of baselines corresponding to the finite number $N_T$ of telescopes at our disposal and a limited observation schedule.
+In practice, only a small part of this information is available (as seen in right panel of Fig.~\ref{fig:ft}), because one has a finite number of baselines corresponding to the finite number $N_T$ of telescopes at our disposal and a limited observation schedule.
 We have simulated the II observation of the fictitious star by four telescopes (correlated with baselines as seen in Fig.~\ref{fig:teles}) over one night.
 Using this modest amount of signal from one night's observation, we have trained a cGAN to construct the image of the source.
-\begin{figure}
-  \includegraphics[width=\linewidth]{fig/ellipse1612.png}
-  \caption{Merged image, which includes the original and the sparsely sampled Fourier plane.
-It is exactly what the GAN receives.
+\begin{figure*}
+   \centering
+  \includegraphics[width=0.85\linewidth]{fig/ellipse1612.jpg}
+  \caption{This merged image shows the input for GAN.
+The left figure is the simulated source, which act as a ground truth for GAN while training the model.
+The right figure shows the signal from the same simulated source observed by the baselines (fig.~\ref{fig:base}), which is the reason both images is merged to provide GAN as input so that it can make the prediction after being trained.
 The grey scale of the figure is normalized to the brightest pixel in the image.}
   \label{fig:GANinput}
-\end{figure}
+\end{figure*}

### 2025-10-01 Phase_II/draft/Result.tex
figure caption

@@
 	\includegraphics[width=.32\linewidth]{fig/moments/mom2.png}\hfil
-	\caption{This set of figures shows the comparison of monopole, x-centroid, and y-centroid for ground truth and predicted images generated by trained GAN.}
+	\caption{This set of figures shows the comparison of monopole, x-centroid, and y-centroid for ground truth and predicted images generated by trained GAN.
+The monopole shows the linear nature, which indicate that as the parameters of ellipsoid will change, the flux (monopole) also change accordingly.
+Clustering nature around the value of 63 for both x and y centroid show the spatial center of mass of the stellar objects.}
 	\label{fig:cen}
@@
 \end{equation}
-The left figure of Fig.~\ref{fig:cen} displays the monopole values for 50 reconstructed images.
+The left figure of Fig.~\ref{fig:cen} displays the monopole values for 100 reconstructed images.
 The plot reveals a linear relationship between the monopole of the ground truth (real image) on the $x$-axis and that of the predicted (reconstructed) image on the $y$-axis, consistent across sources of varying shapes and sizes.
@@
 
-The middle and right panel of Fig.~\ref{fig:cen} compare the centroids ($x_{c}$, $y_{c}$) of 50 predicted images with their corresponding ground truths respectively.
+The middle and right panel of Fig.~\ref{fig:cen} compare the centroids ($x_{c}$, $y_{c}$) of 100 predicted images with their corresponding ground truths respectively.
 The clustering of centroids within a specific scale range across all results indicates that the reconstructed images accurately represent the spatial location of the fast-rotating star relative to the ground truth.
@@
   \includegraphics[width=.32\linewidth]{fig/moments/mom5.png}\hfil
-  \caption{The second-order central moments provide information about the size and shape of stellar objects.
-Shown here are all the second-order central moments for ground truth and predicted images generated by the trained GAN.
-From left to right these are $\mu_{11},\mu_{20},\mu_{02}$.}
+  \caption{The second-order central moments from left to right ($\mu_{11}$, $\mu_{20}$, and $\mu_{02}$) provide information about the size and shape of stellar objects.
+These have been shown here for ground truth and predicted images generated by the trained GAN.
+It is very clear that these moments show the linear nature.}
 	\label{fig:struc}
@@
   \includegraphics[width=.49\linewidth]{fig/moments/mom9.png}\hfil
-  \caption{Shown here are all the third-order central moments for
-    ground truth and predicted images generated by the trained GAN.
-    They represent the skewness of the brightness distributions.  The
-    panels in reading order show
-    $\mu_{30},\mu_{03},\mu_{21},\mu_{12}$.}
+  \caption{Shown here are all the third-order central moments ($\mu_{30}$, $\mu_{03}$, $\mu_{21}$, and $\mu_{12}$) for ground truth and predicted images generated by the trained GAN.
+They represent the skewness of the brightness distributions.
+Here $\mu_{03}$, and $\mu_{21}$ show the linear behaviour.
+However, $\mu_{30}$, and $\mu_{12}$ show the clustering nature, which says that skewness is preserved but not perfectly.
+This aim can be achieved by increasing th enumbe rof telescopes on observational plane.}
   \label{fig:moments}

### 2025-10-01 Phase_II/draft/intro_reformatted.tex
figure caption

@@
 	\includegraphics[width=\linewidth]{fig/telescope.png}
-	\caption{The telescope configuration with similar properties each used to simulate the signal for II observation.}
+	\caption{The telescope configuration with similar properties each, where diameter is 12 meter and baselines are spreaded over more than 100 meter.
+This setup is used to simulate the signal for II observation.}
 	\label{fig:teles}

### 2025-10-01 Phase_II/draft/main.tex
figure caption

@@
 Despite these advancements, phase retrieval remains a major challenge due to the nature of photon correlation.
-This paper explores the application of a conditional Generative Adversarial Network (cGAN) to tackle the problem of image reconstruction in Intensity Interferometry.
+This paper explores the application of a conditional Generative Adversarial Network (cGAN) to tackle the problem of image reconstruction in II.
 This approach successfully reconstructs the shape, size, and brightness distribution of a fast-rotating star from sparsely sampled, spatial power spectrum of the source, corresponding to II with four telescopes.
@@
 
-\input{intro}
+\input{intro_reformatted}
+\input{image-reconstruction-past-efforts}
 \input{II}

### 2025-10-01 Phase_II/code/aperture.py

@@ -61,8 +61,9 @@ class aper():
           n = np.imag(base)
           x, y = np.meshgrid(xcord, ycord)
           plt.close()
-          plt.rcParams.update({'font.size': 14})
-          plt.rcParams["figure.figsize"] = [12,12]
+          plt.rcParams.update({'font.size': 12})
+          plt.rcParams["figure.figsize"] = [8,8]
+          plt.rcParams['axes.facecolor']='ivory'
           plt.rcParams["font.weight"] = "bold"
           plt.rcParams["axes.labelweight"] = "bold"
           for j in range(len(Tposi)):
@@ -72,15 +73,17 @@ class aper():
                  w = self.circ(x-east[j], y-north[j], radii)
               else:
                  w = self.aper(x-east[j], y-north[j], radii, width, orien)
-              plt.contour(x, y, w, colors='darkgrey')
+              plt.contour(x, y, w, colors='darkred')
               tel = Tname[j]
-              plt.annotate(tel,  xy = (east[j], north[j]), size=10, color='black', fontweight='bold')
+              plt.annotate(tel,  xy = (east[j], north[j]), size=10, color='blue', fontweight='bold')
           for i in range(len(e)):   
               plt.plot(e[i], n[i], '--')
           plt.xlabel('East in meter')
           plt.ylabel('North in meter')
           plt.title("Position of Telescopes", fontweight='bold')
-          plt.savefig(fname)
+          plt.gca().set_aspect('equal')
+          plt.tight_layout()
+          plt.savefig(fname, bbox_inches='tight', pad_inches=0, dpi=200)
           
 
       def baseline(self, Tposi, Tname):

### 2025-10-01 Phase_II/code/generate_baseline.py

@@ -55,7 +55,7 @@ zt = distance[:,2]           # baseline in up
 # plot the covered (u,v) plane with baselines (comment out the lines for the visualizations of baseline only)
 plt.close()
 plt.rcParams.update({'font.size': 15})
-plt.rcParams["figure.figsize"] = [12,8]
+plt.rcParams["figure.figsize"] = [8,8]
 plt.rcParams["font.weight"] = "bold"
 plt.rcParams["axes.labelweight"] = "bold"
 st = np.cumsum(step)

### 2025-10-03 Phase_II/draft/II.tex
the first

@@
 The left figure is the simulated source, which act as a ground truth for GAN while training the model.
-The right figure shows the signal from the same simulated source observed by the baselines (fig.~\ref{fig:base}), which is the reason both images is merged to provide GAN as input so that it can make the prediction after being trained.
+The right figure shows the signal from the same simulated source observed by the baselines (fig.~\ref{fig:base}) with salt and paper noise, which is the reason both images is merged to provide GAN as input so that it can make the prediction after being trained.
 The grey scale of the figure is normalized to the brightest pixel in the image.}

### 2025-10-03 Phase_II/draft/ParaGan.tex
the first

@@
 	\centering
-	\includegraphics[width=\linewidth]{fig/testing_image/image_1.png}
-	\includegraphics[width=\linewidth]{fig/testing_image/image_3.png}
-	\includegraphics[width=\linewidth]{fig/testing_image/image_4.png}
-	\includegraphics[width=\linewidth]{fig/testing_image/image_10.png}
+	\includegraphics[width=\linewidth]{fig/testing_image/image_7.png}
 	\includegraphics[width=\linewidth]{fig/testing_image/image_12.png}
-	\includegraphics[width=\linewidth]{fig/testing_image/image_15.png}
+	\includegraphics[width=\linewidth]{fig/testing_image/image_13.png}
+	\includegraphics[width=\linewidth]{fig/testing_image/image_29.png}
+	\includegraphics[width=\linewidth]{fig/testing_image/image_39.png}
 \caption{Example results of image reconstruction using the GAN model along with the II observations simulated in this work.

### 2025-10-03 Phase_II/code/aperture.py

@@ -61,9 +61,8 @@ class aper():
           n = np.imag(base)
           x, y = np.meshgrid(xcord, ycord)
           plt.close()
-          plt.rcParams.update({'font.size': 12})
-          plt.rcParams["figure.figsize"] = [8,8]
-          plt.rcParams['axes.facecolor']='ivory'
+          plt.rcParams.update({'font.size': 14})
+          plt.rcParams["figure.figsize"] = [12,12]
           plt.rcParams["font.weight"] = "bold"
           plt.rcParams["axes.labelweight"] = "bold"
           for j in range(len(Tposi)):
@@ -73,17 +72,15 @@ class aper():
                  w = self.circ(x-east[j], y-north[j], radii)
               else:
                  w = self.aper(x-east[j], y-north[j], radii, width, orien)
-              plt.contour(x, y, w, colors='darkred')
+              plt.contour(x, y, w, colors='darkgrey')
               tel = Tname[j]
-              plt.annotate(tel,  xy = (east[j], north[j]), size=10, color='blue', fontweight='bold')
+              plt.annotate(tel,  xy = (east[j], north[j]), size=10, color='black', fontweight='bold')
           for i in range(len(e)):   
               plt.plot(e[i], n[i], '--')
           plt.xlabel('East in meter')
           plt.ylabel('North in meter')
           plt.title("Position of Telescopes", fontweight='bold')
-          plt.gca().set_aspect('equal')
-          plt.tight_layout()
-          plt.savefig(fname, bbox_inches='tight', pad_inches=0, dpi=200)
+          plt.savefig(fname)
           
 
       def baseline(self, Tposi, Tname):

### 2025-10-03 Phase_II/code/gan_def.py

@@ -6,6 +6,7 @@ import tensorflow as tf
 import numpy as np
 import datetime
 import time
+import csv
 import cv2
 import os
 
@@ -230,8 +231,16 @@ class gan_fun():
              plt.savefig(f"{plot_name}.eps", format='eps', dpi=500)
              plt.savefig(f"{plot_name}.png")
              
+             # save arrays as .npy
+             np.save(f"{plot_name}_input.npy",   test_input[0].numpy())
+             np.save(f"{plot_name}_target.npy",  target[0].numpy())
+             np.save(f"{plot_name}_prediction.npy", prediction)
+
+             if show_diff:
+                np.save(f"{plot_name}_difference.npy", difference)
+             
                          
-      def train_step(self, model1, model2, input_image, target, step):
+      def train_step(self, model1, model2, input_image, target, summary_writer, step):
           """
           Train the input image i.e. visibility data with a target imgae in given number of step.
           
@@ -250,9 +259,26 @@ class gan_fun():
 
           generator_optimizer = tf.keras.optimizers.Adam(self.learning_rate, beta_1 = 0.5)          # Generator Optimizer using the Adam algorithm
           discriminator_optimizer = tf.keras.optimizers.Adam(self.learning_rate, beta_1 = 0.5)      # Discriminator Optimizer using the Adam algorithm
-          log_dir="logs/"                                                                           # name of the main folder
-          checkpoint_dir = "models/models/ellipsoids_run8.15_a0.005_b0.005_discrep1_itk_bs1_lr2em4_teles4_addedlayers_filtersize5_MS/"
-          summary_writer = tf.summary.create_file_writer(log_dir + "fit/" + datetime.datetime.now().strftime(f"%Y%m%d-%H%M%S_{checkpoint_dir[9:]}")) # create file to save summary
+          # Logging dirs
+          # Run name from hyperparameters
+          run_name = (
+                      f"cGAN_b{self.beta}_disc{self.disc_train_iterations}_"
+                      f"bs{1}_lr{self.learning_rate}_f{self.filtersize}"
+                     )
+
+          # --- Directories ---
+          checkpoint_dir = os.path.join("models", run_name)
+          os.makedirs(checkpoint_dir, exist_ok=True)
+
+          log_dir = os.path.join("logs", "fit", run_name)
+          os.makedirs(log_dir, exist_ok=True)
+          summary_writer = tf.summary.create_file_writer(log_dir)
+
+          # CSV logger
[…]

### 2025-10-03 Phase_II/code/gan_def_test.py

@@ -55,10 +55,10 @@ except tf.errors.InvalidArgumentError:
 test_dataset = test_dataset.map(fn.load_image_test)
 test_dataset = test_dataset.batch(BATCH_SIZE)
 
-mfn.fit(generator, discriminator, train_dataset, test_dataset, steps=60000)
+mfn.fit(generator, discriminator, train_dataset, test_dataset, steps=100000)
 
 counter = 0
-for inp, tar in test_dataset.take(20):
+for inp, tar in test_dataset.take(100):
     mfn.generate_images(generator, inp, tar, show_diff = True, sampling = True, save_image = True, counter = counter)
     counter += 1
     

### 2025-10-03 Phase_II/code/generate_baseline.py

@@ -55,7 +55,7 @@ zt = distance[:,2]           # baseline in up
 # plot the covered (u,v) plane with baselines (comment out the lines for the visualizations of baseline only)
 plt.close()
 plt.rcParams.update({'font.size': 15})
-plt.rcParams["figure.figsize"] = [8,8]
+plt.rcParams["figure.figsize"] = [12,8]
 plt.rcParams["font.weight"] = "bold"
 plt.rcParams["axes.labelweight"] = "bold"
 st = np.cumsum(step)

### 2025-10-03 Phase_II/code/generate_image.py

@@ -7,7 +7,7 @@ ep = ellipsoid()
  
 # fixed the parameters
 sx, sy, x, y = ep.grids(1e-10, 512, 1e-6)   # N = 512, shape of the image (255, 255) as np.arange is used in grids
-rad = np.arange(3e-9, 1.6e-8, 2e-9)
+rad = np.arange(3e-9, 1.6e-8, 1e-10)
 inc = np.arange(0, 2*np.pi, np.pi/4)
 pa = np.arange(0, 2*np.pi, np.pi/4)
 sq = np.arange(0.5, 1, 0.1)
@@ -19,27 +19,13 @@ for r in rad:
            i += 0.07
         if (i == 0) or (i == np.pi):
            ellipse = ep.ellip(sx, sy, r, i, 0, 1)
-           img = plt.imshow(ellipse)
-           plt.colorbar(img) 
-           plt.axis('off')
-           plt.savefig(f'ellip_image/ellipse{pic}.jpg')
-           plt.close()
-           np.save(f'ellip_npy/ellipse{pic}.npy', ellipse)
+           plt.imsave('ellip_image/ellipse' + str(pic) + '.jpg', ellipse)
+           np.save('ellip_npy/ellipse' + str(pic) + '.npy', ellipse)
            pic += 1
-           #plt.imsave('ellip_image/ellipse' + str(pic) + '.jpg', ellipse)
-           #np.save('ellip_npy/ellipse' + str(pic) + '.npy', ellipse)
-           #pic += 1
         else:
            for p in pa:
                for s in sq:
                    ellipse = ep.ellip(sx, sy, r, i, p, s)
-                   img = plt.imshow(ellipse)
-                   plt.colorbar(img) 
-                   plt.axis('off')
-                   plt.savefig(f'ellip_image/ellipse{pic}.jpg')
-                   plt.close()
-                   np.save(f'ellip_npy/ellipse{pic}.npy', ellipse)
+                   plt.imsave('ellip_image/ellipse' + str(pic) + '.jpg', ellipse)
+                   np.save('ellip_npy/ellipse' + str(pic) + '.npy', ellipse)
                    pic += 1
-                   #plt.imsave('ellip_image/ellipse' + str(pic) + '.jpg', ellipse)
-                   #np.save('ellip_npy/ellipse' + str(pic) + '.npy', ellipse)
-                   #pic += 1

### 2025-10-03 Phase_II/code/generate_moment.py

@@ -5,128 +5,53 @@ import glob
 import os 
 import re
 
-plt.rcParams.update({'font.size': 10})
-plt.rcParams["figure.figsize"] = [12,6]
-plt.rcParams["font.weight"] = "bold"
-plt.rcParams["axes.labelweight"] = "bold"
-
-# The Directory of all images  
-img_dir = "testing_image/testing_image_npy/" 
-data_path = os.path.join(img_dir,'*.npy') 
-files = glob.glob(data_path)
-files.sort(key=lambda x:[int(c) if c.isdigit() else c for c in re.split(r'(\d+)',x)])
-
-ground_img = []
-pred_img = [] 
-for f1 in files:
-    data = np.load(f1)
-    ground_img.append(data[1])
-    pred_img.append(data[2])
-
-gr_img = np.array(ground_img)       # The ground truth image of stellar object
-pr_img = np.array(pred_img)         # The predicted image of stellar object with trained GAN
-
-# for visualisation of ground truth and predicted image
-pic = 0
-for i in range(len(pr_img)):
-    plt.subplot(1,2,1)
-    plt.imshow(gr_img[i])
-    plt.subplot(1,2,2)
-    plt.imshow(pr_img[i])
-    plt.savefig('result/image/image' + str(pic) + '.png')
-    #plt.show()
-    pic += 1
-   
-# Calculate moment only for one image
-im_g = gr_img[38]
-im_p = pr_img[38]
-
 md = mom()
 
-# the moments
-M00_g, mx_g, my_g, mu11_g, mu20_g, mu02_g, mu30_g, mu03_g, mu21_g, mu12_g = md.mom_def(im_g)
-M00_p, mx_p, my_p, mu11_p, mu20_p, mu02_p, mu30_p, mu03_p, mu21_p, mu12_p = md.mom_def(im_p)
+# The Directory of all images  
+gr_img = "testing_image/testing_image_1/"
+data_path = os.path.join(gr_img, "image_*_target.npy")
+files1 = glob.glob(data_path)
+files1.sort(key=lambda x: [int(c) if c.isdigit() else c for c in re.split(r'(\d+)', x)])  # Natural sort by numeric part
 
-# print the monopole and central moments
-print('Monopole the total intensity for ground truth and predicted image: ', (M00_g, M00_p))
[…]

### 2025-10-03 Phase_II/code/generate_pspec.py

@@ -1,7 +1,8 @@
 import matplotlib.pyplot as plt
-import numpy as np
-from scipy import fft
 from image_noise import Pimage
+from scipy import fft
+import numpy as np
+import random
 import cv2
 import os
 
@@ -46,40 +47,47 @@ for filename in os.listdir(path_in):
     
     image_name = filename[:-4]                                                                        # save or display images > use cv2 instead of matplotlib, this always saves as (64,64,4)
     if save_images:
-            if counter < 150:
-               '''
-               im = plt.imshow(combined_image, cmap='gray')
-               plt.colorbar(shrink=0.55)
-               plt.gca().set_aspect('equal')
-               plt.axis('off')
-               plt.savefig('val/' + image_name + '.jpg')
-               plt.clf()
-               plt.close()
-               '''
-               cv2.imwrite('val/' + image_name + '.jpg', combined_image)
-            elif (counter >= 150) and (counter < 300):
-               '''
-               im = plt.imshow(combined_image, cmap='gray')
-               plt.colorbar(shrink=0.55)
-               plt.gca().set_aspect('equal')
-               plt.axis('off')
-               #plt.show()
-               plt.savefig('test/' + image_name + '.jpg')
-               plt.clf()
-               plt.close()
-               '''
-               cv2.imwrite('test/' + image_name + '.jpg', combined_image)
-            else:
-               '''
-               im = plt.imshow(combined_image, cmap='gray')
-               plt.colorbar(shrink=0.55)
-               plt.gca().set_aspect('equal')
-               plt.axis('off')
-               plt.savefig('train/' + image_name + '.jpg')
-               plt.clf()
-               plt.close()
-               '''
-               cv2.imwrite('train/' + image_name + '.jpg', combined_image)
+       # Choose randomly where to save
+       rnd = random.random()  # returns float in [0,1)
+       plt.figure(figsize=(8, 8))
+       if rnd < 0.1:  # 10% for validation
+            save_path = os.path.join("val", image_name + ".jpg")
+            '''
+            im = plt.imshow(combined_image, cmap='gray', aspect='equal')
+            cbar = plt.colorbar(im, shrink=0.45, fraction=0.046, pad=0.04)
+            cbar.ax.tick_params(labelsize=12, width=1.5)
+            plt.axis('off')
+            plt.tight_layout(pad=1.0)
[…]

### 2025-10-03 Phase_II/code/main_def_test.py

@@ -11,15 +11,24 @@ fn.para(img_size=128)
 # check the signal on observational plane and captured one using baseline of a stellar object
 base = np.load("base_npy/base.npy") 
 train_image = np.load("ellip_npy/ellipse1612.npy")
+im = plt.imshow(train_image, cmap='viridis')
+plt.colorbar(im) 
+plt.tight_layout()
+plt.axis('off')
+plt.savefig("ellipse1612.png")
+plt.close()
+
 train_image = cv2.resize(train_image, dsize=(128, 128), interpolation=cv2.INTER_AREA)
 print('base shape', np.shape(base))
 print('image shape', np.shape(train_image))
 fft = np.abs(fft.fftshift(fft.fft2(fft.fftshift(train_image))))
+
 # the signal on observational plane
 fft1 = fft/fft.max()
 img = plt.imshow(fft1)
 plt.colorbar(img)
 plt.gca().set_aspect('equal')
+plt.tight_layout()
 plt.axis('off')
 plt.savefig('ft/ft.jpg')
 plt.show()
@@ -28,6 +37,7 @@ plt.close()
 img1 = plt.imshow(np.log(fft1))
 plt.colorbar(img1)
 plt.gca().set_aspect('equal')
+plt.tight_layout()
 plt.axis('off')
 plt.savefig('ft/ft_log.jpg')
 plt.show()
@@ -39,6 +49,7 @@ output = output/output.max()
 img2 = plt.imshow(output)
 plt.colorbar(img2)
 plt.gca().set_aspect('equal')
+plt.tight_layout()
 plt.axis('off')
 plt.savefig('ft/ft_base.jpg')
 plt.show()
@@ -48,6 +59,7 @@ plt.close()
 img3 = plt.imshow(np.log10(output+1e-7))
 plt.colorbar(img3)
 plt.gca().set_aspect('equal')
+plt.tight_layout()
 plt.axis('off')
 plt.savefig('ft/ft_log_base.jpg')
 plt.show()

### 2025-10-04 Phase_II/draft/II.tex
II

--- 2025-10-01 Phase_II/draft/II.tex
@@
   \includegraphics[width=0.85\linewidth]{fig/ellipse1612.jpg}
-  \caption{This merged image shows the input for GAN.
-The left figure is the simulated source, which act as a ground truth for GAN while training the model.
-The right figure shows the signal from the same simulated source observed by the baselines (fig.~\ref{fig:base}), which is the reason both images is merged to provide GAN as input so that it can make the prediction after being trained.
-The grey scale of the figure is normalized to the brightest pixel in the image.}
+  \caption{Example of the input used for training the GAN model.
+The left panel shows the simulated source image, which serves as the ground truth during training, while the right panel represents the corresponding intensity distribution obtained from the same simulated source using the telescope baselines (see Fig.~\ref{fig:base}) with added salt-and-pepper noise.
+Together, these images form a training pair, where the GAN learns to reconstruct a predicted image (modeling of observed signal) similar to ground truth (left) from the noisy baseline signal (right).
+The grayscale in both images is normalized to the brightest pixel.}
   \label{fig:GANinput}

### 2025-10-06 Phase_II/draft/response.txt
figure caption
the first
ParaGan.tex, main.tex, response.txt

@@
 
+The response to this in the Introduction:
+
+Image reconstruction in gravity darkened fast rotating stars has long been examined using various methods in MI \citep{vanBelle2001, DomicianodeSouza2003, DomicianodeSouza2005, Monnier2007, Pedretti2009, Zhao2009, Martinez2021}.
+
 2. SII has recently measured ellipticity, so gravity-darkening is a
    natural next step.
+
+The response to this in the Introduction:
+
+Recently photosphere oblateness of $\gamma$-Cassiopeia \citep{2025arXiv250615027A} has been measured at the VERITAS observatory using II.
+These results, and especially, that by Archer et al.
+\cite{2025arXiv250615027A}  put our work in context.
+Thus our simulation is a natural next step of the work of Archer et al and others.
 
@@
 
-Revise text.
+Text has been revised.
 
@@
 Asymmetry is recovered in some cases: investigate!
+We increased the number of training, validation and testing dataset. 
+Also we increase the training time from 60k to 100k and result has 
+been improvised. The difference plot is now in 1-D.
 
@@
 
+Each figure's captions have been revised now.
+
 |  - This discussion of phase retrieval should be separated in the
 |  introduction from the discussion of GANs.
+
+It has been separated now.
 

### 2025-10-06 Phase_II/draft/ParaGan.tex
ParaGan.tex, main.tex, response.txt

@@
 The process to train the model is summarized here:
+\iffalse
 \begin{figure*}[htbp]
-	\centering
-	\begin{tikzpicture}[node distance=0.9cm]
+	%\centering
+	\begin{center}
+		\begin{tikzpicture}[node distance=0.7cm]
 
 			% Data pipeline
-		\node[block, fill=blue!15] (data) {Ground Truth \\ (Create $N$ Images of Stellar Objects)};
+			\node[block, fill=blue!15] (data) {Ground Truth \\ (Create SS Images of Stellar Objects)};
 			\node[block, fill=red!10, below=of data] (pre) {Simulation \\ (Intensity Interferometry (II) Data)};
@@
 
-		% Split branches
+			% Training, Validation, Testing
+			\node[block, fill=green!15, below left=0.6cm and 1.0cm of split] (train) {Training Set \\ (Learn Model Parameters)};
+			\node[block, fill=green!10, below=of split] (val) {Validation Set \\ (Tune Hyperparameters)};
+			\node[block, fill=green!05, below right=0.6cm and 1.0cm of split] (test) {Testing Set \\ (Final Evaluation)};
+
+			% Model training block
+			\node[block, fill=orange!20, below= 1.0cm of val, minimum width=10cm, minimum height=1.2cm] (mod) {Train the Model \\ (Generator + Discriminator)};
+
+			% Generator side (left)
+			\node[block, fill=yellow!15, below=2.2cm of mod, xshift=-3.5cm] (noise) {Random Noise $z$};
+			\node[block, fill=blue!10, below=of noise] (gen) {Generated Image $\hat{x}$};
+			\node[block, fill=purple!20, below=of gen] (gloss) {Generator Loss \\ (Update $G$)};
+
+			% Discriminator side (right)
+			\node[block, fill=yellow!20, below=2.2cm of mod, xshift=+3.5cm] (real) {Real Image \\ (From Training Set)};
+			\node[block, fill=orange!20, below=of real] (disc) {Discriminator $D(x)$};
+			\node[block, fill=red!20, below=of disc] (out) {Discriminator Output};
+			\node[block, fill=purple!30, below=of out] (dloss) {Discriminator Loss \\ (Update $D$)};
+
+			% Final result block
+			\node[block, fill=teal!20, below= 3cm of val, minimum width=5cm] (res) {Result / Evaluation \\ (Performance Metrics: Accuracy)};
+
+			% Connections
+			\draw[arrow] (data) -- (pre);
+			\draw[arrow] (pre) -- (split);
+			%\draw[arrow] (split.south west) |- (train.north);
+			\draw[arrow] (split.west) -| (train.north);
+			\draw[arrow] (split.south) -- (val.north);
+			\draw[arrow] (split.east) -| (test.north);
+			\draw[arrow] (train.south) -- (mod.north);
+
+			%Newly Introduced Connections (S Sarangi)
+			\draw[arrow] (val.south) -- (mod.north);
+			\draw[arrow] (mod.south) -- (res.north);
+
+			% GAN arrows
+			\draw[arrow] (mod.south) -- (noise.north);
+			\draw[arrow] (mod.south) -- (real.north);
+			\draw[arrow] (noise.south) -- (gen.north);
+			\draw[arrow] (gen.south) -- (gloss.north);
+			\draw[arrow] (real.south) -- (disc.north);
+			\draw[arrow] (gen.east) -- ++(0.5,0) |- (disc.west);
+			\draw[arrow] (disc.south) -- (out.north);
+			\draw[arrow] (out.south) -- (dloss.north);
+
+			% Validation & Testing to Result
+			%\draw[arrow] (val.south) -- (res.north);
+			\draw[arrow] (test.south) -- (res.north);
+
+		\end{tikzpicture}
+	\end{center}
+\caption{A block diagram for the process of image reconstruction through GAN.}
+\end{figure*}
+\fi
+
+\iffalse
+\documentclass{article}
+\usepackage{tikz}
+\usetikzlibrary{arrows, arrows.meta, positioning}
+
+\tikzset{
+  block/.style = {draw, rectangle, minimum height=1.5em, minimum width=3em, align=center},
+  arrow/.style = {->, thick},
+}
+
+%\begin{document}
+\fi
+
+\begin{figure}[htbp]
+\centering
+\begin{tikzpicture}[node distance=0.9cm]
+%\begin{tikzpicure}[scale = 0.5]
+
+% Data pipeline
+\node[block, fill=blue!15] (data) {Ground Truth \\ (Create SS Images of Stellar Objects)};
+\node[block, fill=red!10, below=of data] (pre) {Simulation \\ (Intensity Interferometry (II) Data)};
+\node[block, fill=green!20, below=of pre, minimum width=5cm] (split) {Input Dataset (Merge of Ground Truth \\ and Simulation of II) Split \\ (Training, Validation, Testing)};
+
+% Training, Validation, Testing
 \node[block, fill=green!15, below left=0.6cm and 2.5cm of split] (train) {Training Set \\ (Learn Model Parameters)};
-		\node[block, fill=yellow!20, below=0.6cm of split] (val) {Validation Set \\ (Tune Hyperparameters)};
-		\node[block, fill=orange!20, below right=0.6cm and 2.5cm of split] (test) {Testing Set \\ (Final Evaluation)};
+\node[block, fill=green!10, below=of split] (val) {Validation Set \\ (Tune Hyperparameters)};
+\node[block, fill=green!05, below right=0.6cm and 2.5cm of split] (test) {Testing Set \\ (Final Evaluation)};
 
-		% Model training big box
+% Model training block
 \node[block, fill=orange!20, below=3cm of val, minimum width=10cm, minimum height=1.2cm] (mod) {Train the Model \\ (Generator + Discriminator)};
@@
 % Generator side (left)
-		\node[block, fill=cyan!15, below=1.2cm of mod, xshift=-3.5cm] (noise) {Random Noise $z$};
-		\node[block, fill=green!20, below=of noise] (gen) {Generator $G(z)$};
-		\node[block, fill=blue!10, below=of gen] (fake) {Generated Image};
-		\node[block, fill=purple!20, below=of fake] (gloss) {Generator Loss \\ (Update $G$)};
+\node[block, fill=yellow!15, below=1.2cm of mod, xshift=-3.5cm] (noise) {Random Noise $z$};
+\node[block, fill=blue!10, below=of noise] (gen) {Generated Image $\hat{x}$};
+\node[block, fill=purple!20, below=of gen] (gloss) {Generator Loss \\ (Update $G$)};
 
@@
 \node[block, fill=orange!20, below=of real] (disc) {Discriminator $D(x)$};
-		\node[block, fill=red!20, below=of disc] (out) {Output: Real/Fake};
+\node[block, fill=red!20, below=of disc] (out) {Discriminator Output};
 \node[block, fill=purple!30, below=of out] (dloss) {Discriminator Loss \\ (Update $D$)};
@@
 
-		% Connections for data pipeline
+% Connections
 \draw[arrow] (data) -- (pre);
@@
 \draw[arrow] (split.south east) |- (test.north);
-		\draw[arrow] (train.south) |- (mod.north);
+\draw[arrow] (train.south) -- (mod.north);
 
 % GAN arrows
-		\draw[arrow] (mod) -- (noise);
-		\draw[arrow] (mod) -- (real);
-		\draw[arrow] (noise) -- (gen);
-		\draw[arrow] (gen) -- (fake);
-		\draw[arrow] (fake.east) -- ++(0.5,0) |- (disc.west);
-		\draw[arrow] (real) -- (disc);
-		\draw[arrow] (disc) -- (out);
-
-		% Feedback loops
-		\draw[arrow] (out.south west) -- ++(-3,0) |- (gloss.east);
-		\draw[arrow] (gloss.west) -- ++(-3,0) |- (gen.west);
-		\draw[arrow] (out.south east) -- ++(3,0) |- (dloss.east);
-		\draw[arrow] (dloss.east) -- ++(3,0) |- (disc.east);
+\draw[arrow] (mod.south) -- (noise.north);
+\draw[arrow] (mod.south) -- (real.north);
+\draw[arrow] (noise.south) -- (gen.north);
+\draw[arrow] (gen.south) -- (gloss.north);
+\draw[arrow] (real.south) -- (disc.north);
+\draw[arrow] (gen.east) -- ++(0.5,0) |- (disc.west);
+\draw[arrow] (disc.south) -- (out.north);
+\draw[arrow] (out.south) -- (dloss.north);
 
@@
 \end{tikzpicture}
-	\caption{The cGAN-based image reconstruction block diagram.
-Data is split into training (used for GAN optimization), validation (for hyperparameter tuning), and testing (for final evaluation).
-The GAN training loop optimizes Generator and Discriminator, while validation and testing feed into performance evaluation metrics.}
-	\label{fig:gan_block}
-\end{figure*}
+\end{figure}
+
+%\end{document}

### 2025-10-06 Phase_II/draft/image-reconstruction-past-efforts.tex
figure caption
intro_reformatted, past-efforts, refs.bib, main.tex

@@
 \section{Past Efforts at Image Reconstruction in Intensity Interferometry}
+\iffalse
 Several theoretical and computational approaches for phase reconstruction with II have been proposed.
@@
 
+%%%**************************8
+
+%\documentclass{article}
+%\usepackage{amsmath}
+%\begin{document}
+\fi
+Several approaches have been developed for phase reconstruction in intensity interferometry (II).
+\cite{gamo1963triple} introduced triple-intensity correlation, applied by \cite{goldberger1963use} to microscopic systems and extended by \cite{sato1978imaging, sato1979computer, sato1981adaptive} to measure stellar diameters and phases, though limited by low signal-to-noise ratio (SNR).
+\cite{GerchbergSaxton1972} proposed an iterative phase retrieval method using image and diffraction plane data, sensitive to initial estimates and convergence speed.
+\cite{Fienup1982} improved this with the Hybrid Input-Output algorithm, enhancing robustness in noisy conditions.
+\cite{holmes2010two} utilized Cauchy-Riemann relations for 1-D and 2-D image reconstruction, applied to simulated stellar data with Imaging Cherenkov Telescope Arrays \citep{nunez2010stellar, nunez2012high, nunez2012imaging}, but faced computational complexity for higher dimensions.
+\cite{Li2014} introduced a regularized iterative method incorporating priors (e.g., sparsity) to mitigate noise and ill-posedness, though challenged by parameter tuning and initial guess sensitivity.
+The Transport-of-Intensity Equation (TIE), proposed by \cite{Teague1983}, retrieves phase from intensity variations across planes; \cite{Zhang2020} solved TIE as a Poisson equation using a maximum intensity assumption, while \cite{Kirisits2024} combined TIE with the Transport of Phase Equation for improved accuracy across arbitrary apertures and non-uniform illumination, with convergence dependent on initial guesses and boundary conditions.
+
+%\end{document}
+%%%**************
+
 With non-linearity built into their architecture, artificial neural networks (ANNs) empowered by deep learning methods are promising for exploring the task of reconstructing images of stellar objects from ground-based observations.
@@
 Let us now discuss the details of our procedure and method.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{fig/telescope.png}
-	\caption{The telescope configuration with similar properties each used to simulate the signal for II observation.}
-	\label{fig:teles}
-\end{figure}

### 2025-10-06 Phase_II/draft/intro_reformatted.tex
intro_reformatted, past-efforts, refs.bib, main.tex

@@
 \section{Introduction}
-Intensity Interferometry (II), as a \textquotedblleft new type of interferometry\textquotedblright\ to observe stars other than the Sun and other star systems as extended objects, was first reported by Hanbury Brown and Twiss (HBT) in 1954 \citep{brown1954lxxiv} in the domain of radio astronomy and, later in 1956, in the domain of optical  (visible light) astronomy \citep{HBT56Sirius}.
-In their work of 1956 \citep{HBT56Sirius}, HBT presented a method to measure the angular diameter of the star Sirius using the correlation of observed intensity fluctuations of the light received from the star.
-This method was an alternative to the then established method of Michelson Interferometry (MI) following the work of Michelson and Pease \citep{MichelsonPease1921}.
-Michelson and Pease had measured, in 1921, the angular diameter of Betelgeuse by using the interference of coherent light received at two suitably chosen sub-apertures of the 100-inch Hooker telescope at Mount Wilson.
-As the situation stands today, MI and II are two alternative and complementary methods to observe stars and measure stellar parameters.
-MI requires coherence of the light beams from the two apertures.
-II dispenses with the requirement of coherence of the light beams from the two apertures, measures the intensity fluctuations, correlates these fluctuations to obtain the interference pattern; but loses the inherent phase information of the beams.
-The positive compensation for this loss of information, however, is manifold.
-It is immune to atmospheric turbulences, works with less demanding optical surfaces and optics, is able to use upto km-scale baselines yielding high resolution and can easily integrate any number of baseline pairs leading to good coverage of the ($u$,$v$)-plane signal coverage.
-However, it faces challenges with low signal-to-noise for faint objects, requires fast electronics and has limited imaging capability due to the lost phase information.
-The piece of work reported here uses a conditional Generative Adversarial (neural) Network (c-GAN) to simulate phase reconstruction and surface imaging of a rapid rotator.
+The humanity instinctively feels a symbiotic relationship with the stars.
+One of the primary scientific projects of the humanity is to figure out what the stars are and how do they do what they do.
+The first obvious step in this project, beyond measuring their global parameters like diameter, mass, orbital and astromteric elements, is to obtain images of the stars with all details of the stellar surfaces as we do routinely in case of the Sun.
+In other words, the objective is to achieve capability of high fidelity image reconstruction of distant stars.
+Two interferometry based techniques, namely, Michelson Interferometry (MI) or Intensity Interferometry (II) have emerged during the last century to address this objective.
+A discussion of the development of these two approaches and comparison of their respective merits and challenges can be found in \citep{Rai2025}.
+The work reported here presents the results of a first effort at applying a conditional Generative Adversarial (neural) Network (cGAN) to image reconstruction of a fast rotator using its simulated II observations.
 
@@
 HBT reported \cite{HBT56Lab} in 1956, the correlation between photons measured by a pair of photon detectors in two coherent beams of light.
-A modern-day variant of this experiment, carried out by Rai et al.
-\cite{Rai2025} with pseudo-thermal light has been reported recently.
-The HBT Effect and the theoretical investigations laid the foundation for the modern field of Quantum Optics.
+Rai et al.
+\cite{Rai2025} present a modern-day variant of this experiment, carried out with pseudo-thermal light.
+The HBT Effect and the related theoretical investigations laid the foundation for the modern field of Quantum Optics.
 
-Hanbury Brown and his collaborators led the creation and installatopn of the iconic II facility at Narrabri, Australia and reported the measurement of angular diameters of 32 stars and a few results of multiple star-systems \citep{hanbury1974angular}.
-Nevertheless,  unavailability of fast photon detectors and advanced data processing equipment needed for photon counting and correlation computations stalled stellar II observations following this famous work for over four decades.
-Following proposals to utilize Imaging Atmospheric Cherenkov Telescope (IACT) facilities for conducting II observations of stars have emerged\citep{LeBohec2006, nunez2010stellar, nunez2012high, 2013APh....43..331D} as a secondary science application of these facilities during moonlit night, SII observations at VERITAS, MAGIC, and HESS are now being reported \citep[e.g.,][]{2024ApJ...966...28A,2024MNRAS.529.4387A,2025MNRAS.537.2334V}.
+Hanbury Brown and his collaborators led the creation and installation of the iconic II facility at Narrabri, Australia and reported the measurement of angular diameters of 32 stars and a few multiple star-systems \citep{hanbury1974angular}.
+Soon after this work, however, II observations of stars was stalled for over four decades due to the limits of the then available photon detectors and data processing equipment.
+With gradual mitigation of such issues, proposals to utilize Imaging Atmospheric Cherenkov Telescope (IACT) facilities for conducting II observations of stars have emerged\citep{LeBohec2006, nunez2010stellar, nunez2012high, 2013APh....43..331D} as a secondary science application of these facilities during moonlit nights.
+SII observations at VERITAS, MAGIC, and HESS are now being reported \citep[e.g.,][]{2024ApJ...966...28A,2024MNRAS.529.4387A,2025MNRAS.537.2334V}.
 This approach has the potential to enhance the scientific output of existing IACT facilities, and especially of the upcoming Cherenkov Telescope Array Observatory (CTAO).
 Simulations carried out by Rai et al.
-\citep[e.g.,][]{10.1093/mnras/stab2391, 10.1093/mnras/stac2433} have shown that recent advancements in photon detectors could be effective in achieving high-precision measurements of parameters for stellar objects.
+\citep[e.g.,]{10.1093/mnras/stab2391, 10.1093/mnras/stac2433} have shown that recent advancements in photon detectors could be effective in achieving high-precision measurements of parameters for stellar objects.
 
-One of the long-standing aspirations in stellar interferometry — whether through Michelson Interferometry (MI) or Intensity Interferometry (II) — has been to achieve high-fidelity image reconstruction of distant stars.
-This capability would transcend the measurement of global and average stellar parameters, such as angular diameters, binary separations, and orbital characteristics, which, while invaluable, offer only an integrated view of the star or star system as a whole.
-Instead, it promises direct insights into dynamic surface phenomena, including limb darkening, convection cells, granulation, star spots, oblateness and gravity darkening in rapid rotators and atmospheric structures, akin to the detailed observations routinely conducted on our own Sun.
+The thrust of these efforts has been to measure the average global parameters of stars and star systems.
+The high fidelity imagery, however, would transcend the measurement of global and average stellar parameters, such as angular diameters, binary separations, and orbital characteristics, which offer only an integrated view of the star or star system as a whole.
+Such imaging capabilities promise direct insights into the dynamic surface phenomena, including limb darkening, convection cells, granulation, star spots, oblateness and gravity darkening in rapid rotators and atmospheric structures, akin to the detailed observations routinely conducted on our own Sun.
 
 As it stands today, studies grappling various issues of image reconstruction are being reported \citep{Haubois2009, Norris2021AZCyg, Liu2024SuperresolutionII, Liu2025}.
-MI-based image reconstruction has made a lot of progress in this area with efforts at generating constructed images of stars like Betelgeuse \citep{Haubois2009} and AZ Cyg \citep{Norris2021AZCyg}.
-On the otherhand, II-based methods are in a nascent stage.
+MI-based image reconstruction has made substantial progress in this area with efforts at generating constructed images of stars like Betelgeuse \citep{Haubois2009} and AZ Cyg \citep{Norris2021AZCyg}.
+On the other hand, II-based methods are in a nascent stage.
 The recent publications of Liu et al.
@@
 
-We report here, the results of our attempt, the first of its kind in the context of stellar II, to reconstruct the II-simulated observed gravity-darkened images of fast rotating stars using a cGAN neural network architecture.
+We report here, the results of our attempt, the first of its kind, to reconstruct the II-simulated gravity-darkened images of fast rotating stars using a cGAN neural network architecture.
+Image reconstruction in gravity darkened fast rotating stars has long been examined using various methods in MI \citep{vanBelle2001, DomicianodeSouza2003, DomicianodeSouza2005, Monnier2007, Pedretti2009, Zhao2009, Martinez2021}.
+Recently photosphere oblateness of $\gamma$-Cassiopeia \citep{2025arXiv250615027A} has been measured at the VERITAS observatory using II.
+These results, and especially, that by Archer et al.
+\cite{2025arXiv250615027A}  put our work in context.
+Thus our simulation is a natural next step of the work of Archer et al and others.
 We emulate the cGAN model of Isola et al.
@@
 This paper is organized as follows.
-The next section discusses Intensity Interferometry, focusing on its signal and noise characteristics for fast-rotating stars along the Earth’s rotation.
+The next section discusses briefly the past efforts at image reconstruction on II, followed by the section on a discussion of Intensity Interferometry, focusing on its signal and noise characteristics for fast-rotating stars along the Earth’s rotation.
 The following section introduces the GAN formulation and its structure.
-The fourth section details the parameter selection for training the GAN for image reconstruction.
-The fifth section presents the results of the trained GAN both visually and via image moments.
+The fifth section details the parameter selection for training the GAN for image reconstruction.
+The sixth section presents the results of the trained GAN both visually and via image moments.
 Finally, the paper concludes with a discussion of the overall results.

### 2025-10-06 Phase_II/draft/ParaGanX.tex
changing some file names

--- 2025-10-06 Phase_II/draft/ParaGan.tex
@@
 The process to train the model is summarized here:
-\iffalse
 \begin{figure*}[htbp]
@@
 \end{figure*}
-\fi
-
-\iffalse
-\documentclass{article}
-\usepackage{tikz}
-\usetikzlibrary{arrows, arrows.meta, positioning}
-
-\tikzset{
-  block/.style = {draw, rectangle, minimum height=1.5em, minimum width=3em, align=center},
-  arrow/.style = {->, thick},
-}
-
-%\begin{document}
-\fi
-
-\begin{figure}[htbp]
-\centering
-\begin{tikzpicture}[node distance=0.9cm]
-%\begin{tikzpicure}[scale = 0.5]
-
-% Data pipeline
-\node[block, fill=blue!15] (data) {Ground Truth \\ (Create SS Images of Stellar Objects)};
-\node[block, fill=red!10, below=of data] (pre) {Simulation \\ (Intensity Interferometry (II) Data)};
-\node[block, fill=green!20, below=of pre, minimum width=5cm] (split) {Input Dataset (Merge of Ground Truth \\ and Simulation of II) Split \\ (Training, Validation, Testing)};
-
-% Training, Validation, Testing
-\node[block, fill=green!15, below left=0.6cm and 2.5cm of split] (train) {Training Set \\ (Learn Model Parameters)};
-\node[block, fill=green!10, below=of split] (val) {Validation Set \\ (Tune Hyperparameters)};
-\node[block, fill=green!05, below right=0.6cm and 2.5cm of split] (test) {Testing Set \\ (Final Evaluation)};
-
-% Model training block
-\node[block, fill=orange!20, below=3cm of val, minimum width=10cm, minimum height=1.2cm] (mod) {Train the Model \\ (Generator + Discriminator)};
-
-% Generator side (left)
-\node[block, fill=yellow!15, below=1.2cm of mod, xshift=-3.5cm] (noise) {Random Noise $z$};
-\node[block, fill=blue!10, below=of noise] (gen) {Generated Image $\hat{x}$};
-\node[block, fill=purple!20, below=of gen] (gloss) {Generator Loss \\ (Update $G$)};
-
-% Discriminator side (right)
-\node[block, fill=yellow!20, below=1.2cm of mod, xshift=+3.5cm] (real) {Real Image \\ (From Training Set)};
-\node[block, fill=orange!20, below=of real] (disc) {Discriminator $D(x)$};
-\node[block, fill=red!20, below=of disc] (out) {Discriminator Output};
-\node[block, fill=purple!30, below=of out] (dloss) {Discriminator Loss \\ (Update $D$)};
-
-% Final result block
-\node[block, fill=teal!20, below=4.2cm of val, minimum width=5cm] (res) {Result / Evaluation \\ (Performance Metrics: Accuracy)};
-
-% Connections
-\draw[arrow] (data) -- (pre);
-\draw[arrow] (pre) -- (split);
-\draw[arrow] (split.south west) |- (train.north);
-\draw[arrow] (split.south) -- (val.north);
-\draw[arrow] (split.south east) |- (test.north);
-\draw[arrow] (train.south) -- (mod.north);
-
-% GAN arrows
-\draw[arrow] (mod.south) -- (noise.north);
-\draw[arrow] (mod.south) -- (real.north);
-\draw[arrow] (noise.south) -- (gen.north);
-\draw[arrow] (gen.south) -- (gloss.north);
-\draw[arrow] (real.south) -- (disc.north);
-\draw[arrow] (gen.east) -- ++(0.5,0) |- (disc.west);
-\draw[arrow] (disc.south) -- (out.north);
-\draw[arrow] (out.south) -- (dloss.north);
-
-% Validation & Testing to Result
-\draw[arrow] (val.south) -- (res.north);
-\draw[arrow] (test.south) -- (res.north);
-
-\end{tikzpicture}
-\end{figure}
-
-%\end{document}

### 2025-11-05 Phase_II/draft/FlowDiagram_TikZ.tex
intro_reformatted, II.tex, refs.bib, Paragan.tex, main.tex changed

\documentclass{article}
\usepackage{tikz}
\usepackage[margin=0.7in, left=0.7in]{geometry}
\usetikzlibrary{arrows, arrows.meta, positioning}

\tikzset{
  block/.style = {draw, rectangle, minimum height=1.5em, rounded corners, minimum width=3em, align=center},
  arrow/.style = {->, thick},
  d-arrow/.style={thick, dashed, ->, >=stealth, color=blue}, % dashed arrow style
}

% \tikzset{
%   block/.style={rectangle, draw, text centered, rounded corners, minimum height=1cm},
%   arrow/.style={thick, ->, >=stealth},
%   d-arrow/.style={thick, dashed, ->, >=stealth, color=blue}, % dashed arrow style
% }

\begin{document}
%\title{Flow Diagram of the Conditional GAN}
%\date{}
%\maketitle
%\vspace{-5 cm}
\begin{figure}[htbp]
%\centering
\begin{center}
\begin{tikzpicture}[node distance=0.7cm]

% % Data pipeline

%Nodes
% %\node[block, fill=red!20, anchor=north east]
%   (Lat-vector) at ([xshift= 4cm,yshift=1cm]current bounding box.north east)
%   {Random Noise $z$:\\(Latent Vector)};

% Row-1
\node[block, fill=red!20, minimum width = 3 cm, minimum height = 1 cm] (Lat-vector) {Random Noise $z$ \\(Latent Vector)};

\node[block, fill = yellow!15, right= 1.5 cm of Lat-vector, minimum width=3 cm, minimum height=1.2cm] (gen) {{\large \bf{Generator}} \\$log(G(z|y))$};

% Row-2
\node[block, fill = yellow!10, below = 1cm of gen, minimum width=3 cm, minimum height=1.2cm] (gen-out) {Generated (Fake) Image $\hat x$};

\node[block, fill=red!10, left=of gen-out, minimum width = 3 cm, minimum height = 1 cm] (II-sim) {(Additional Info Labels $y$:\\ Simulated II Observation \\ of the Stellar Object)};

\node[block, fill=blue!15, left=of II-sim, minimum width = 3 cm, minimum height = 1 cm] (gr-truth) {Real Image $x$: Model Images of \\ Stellar Object (here, FRS)};

% Row-3
\node[block, fill=green!20, below = of II-sim, minimum width=5cm] (Input-dataset) {Creation of Input Dataset \\ (Merging of Real Images $x$ OR Generated Images $\hat x$ \\ AND II Simulation Data $y$)};

% Row-4
\node[block, fill=green!20, below= 1 cm of Input-dataset, minimum width=5cm] (split) {Split Dataset \\ (Training, Validation, Testing)};

% Row-5
\node[block, fill=green!15, below left= 1 cm and 0.1 cm of split] (train) {Training Set \\ (Learning Model Parameters)};

\node[block, fill=green!10, below= 1 cm of split] (val) {Validation Set \\ (Tuning Hyperparameters)};

\node[block, fill=green!05, below right= 1 cm and 0.1 cm of split] (test) {Testing Set \\ (For Final Evaluation)};

% Row-6
\node[block, fill = blue!20, below left= 2.5 cm and 1cm of val, minimum width=3 cm, minimum height=1.2cm] (disc) {{\large \bf{Discriminator}} \\ $log (D^*(x|y))$};

% Row-7
\node[block, fill = blue!10, below = 1cm of disc, minimum width=3 cm, minimum height=1.2cm] (disc-out) {Binary Decision \\ Real Image OR Fake Image};

\node[block, fill= yellow!10, below = 10 cm of gen-out, minimum width=5 cm, minimum height=1.2cm] (gen-loss) {{\large{\bf {Generator Loss}}}\\ Update $ log(G(z|y)) \equiv log(1-(D^*(G(z|y)|y)) $};

% Row-8
\node[block, fill= blue!10, below = 1cm of disc-out, minimum width=3 cm, minimum height=1.2cm] (disc-loss) {{\large {\bf {Discriminator Loss}}}\\ Update $log(D^*(x|y))$};

% Row-9
\node[block, fill=teal!20, below= 10 cm of val, minimum width=5cm] (res) {Result / Evaluation \\ (Performance Metrics: Accuracy)};

% % Connections
\draw[arrow] (Lat-vector) -- (gen);
\draw[arrow] (gen) -- (gen-out);
\draw[arrow] (gen-out.south) |- (Input-dataset.east);
\draw[arrow] (gr-truth) -- (II-sim);
\draw[arrow] (gr-truth.south) |- (Input-dataset.west);
\draw[arrow] (II-sim) -- (Input-dataset);
\draw[arrow] (Input-dataset) -- (split);

\draw[arrow] (split.west) -| (train.north);
\draw[arrow] (split.south) -- (val.north);
\draw[arrow] (split.east) -| (test.north);
\path (train.south) ++(0,-0.5) coordinate (p1)
      (p1) ++(0.3,0) coordinate (p2);
\draw[arrow] (train.south) -- (p1) -- (p2) -- (disc.north);
\draw[arrow] (val) |- (disc);
\draw[arrow] (disc) -- (disc-out);
\draw[arrow] (disc-out) -- (disc-loss)

% \path (disc-loss.south) ++(0,-1.0) coordinate (p3)
%       (p3) ++(-3.0,0) coordinate (p4)
%       (p4) ++(0,+8.0) coordinate (p5)
%       (p5) ++(2.5, 0) coordinate (p6)
%       (p6) ++(0,-1.3) coordinate (p7);
% \draw[d-arrow] (disc-loss.south) -- (p3) -- (p4) 
% -- (p5) 
% node[pos=1.0,left=10pt, text=blue, font=\large, rotate=90]{ Discriminator Training \\ / Updating Discriminator Parameters}
% -- (p6) -- (p7);

% \path (disc-loss.south) ++(0,-1.0) coordinate (p3)
%       (p3) ++(-3.0,0) coordinate (p4)
%       (p4) ++(0,+8.0) coordinate (p5)
%       (p5) ++(2.5, 0) coordinate (p6)
%       (p6) ++(0,-1.3) coordinate (p7);

% \draw[d-arrow]
%   (disc-loss.south) -- (p3) -- (p4)
%   -- node[midway, left=15pt, text=blue, font=\large, rotate=90, align=center]
%      {Discriminator Training\\Updating Discriminator Parameters}
%   (p5) -- (p6) -- (p7);

\path (disc-loss.south) ++(0,-1.0) coordinate (p3)
      (p3) ++(-3.0,0) coordinate (p4)
      (p4) ++(0,+8.0) coordinate (p5)
      (p5) ++(2.5, 0) coordinate (p6)
      (p6) ++(0,-1.3) coordinate (p7);

% Draw up to p4 first
\draw[d-arrow]
  (disc-loss.south) -- (p3) -- (p4);

% Now draw the vertical dashed segment with centered label
\draw[d-arrow]
  (p4) -- node[pos=0.9, left=15pt, text=blue, font=\large, rotate=90, align=center]
     {Discriminator Training\\Updating Discriminator Parameters}
  (p5);

% Finish the loop
\draw[d-arrow]
  (p5) -- (p6) -- (p7);

\path (disc-out.east) ++ (2.0,0) coordinate (p8)
      (p8) ++(0,1.0) coordinate (p9);
\draw[arrow] (disc-out.east) -- (p8) -- (p9) -- (gen-loss.west);
\path (gen-loss.south) ++(0,-1.0) coordinate (p10)
      (p10) ++(4.5,0) coordinate (p11)
      (p11) ++(0,15) coordinate (p12);
\draw[d-arrow] (gen-loss.south) -- (p10) -- (p11) 
-- node[midway, right=10pt, text=blue, font = \large, rotate=90, anchor=center] {Generator Training/ updating Generator Parameters}
(p12) -- (gen.east);

\path (test.south) ++(0,-3.4) coordinate (p13)
      (p13) ++(-4.5,0) coordinate (p14);
\draw[arrow] (test.south) -- (p13) -- (p14) -- (res.north);

% \node[block, fill=blue!15, minimum width = 3 cm, minimum height = 1 cm] (gr-truth) {Real Image $x$: Model Images of \\ Stellar Object (here, FRS)};
% \node[block, fill=red!10, right=of gr-truth, minimum width = 3 cm, minimum height = 1 cm] (II-sim) {(Additional Info Labels $y$:\\ Simulated II Observation \\ of the Stellar Object)};
% \node[block, fill=red!20, right=of II-sim, minimum width = 3 cm, minimum height = 1 cm] (Lat-vector) {Random Noise $z$:(Latent Vector)};
% \node[block, fill=green!20, below right = 1 cm and 0.1 cm of gr-truth, minimum width=5cm] (Input-dataset) {Creation of Input Dataset \\ (Merging of Ground Truth Images\\ and II Simulation Data)};
% \node[block, fill=green!20, below=of Input-dataset, minimum width=5cm] (split) {Split Dataset \\ (Training, Validation, Testing)};

% \node[block, fill=green!15, below left=0.6cm and 0.1 cm of split] (train) {Training Set \\ (Learning Model Parameters)};
% \node[block, fill=green!10, below=of split] (val) {Validation Set \\ (Tuning Hyperparameters)};
% \node[block, fill=green!05, below right=0.6cm and 0.5 cm of split] (test) {Testing Set \\ (For Final Evaluation)};

% \node[block, fill = blue!15, below left= 3 cm and 0.1 cm of val, minimum width=5 cm, minimum height=1.2cm] (disc) {Discriminator \\ $log (D^*(x|y))$};

% \node[block, fill = blue!10, below = 1cm of disc, minimum width=5 cm, minimum height=1.2cm] (disc-out) {Binary Decision \\ Real Image OR Fake Image};

% \node[block, fill= blue!10, below = 1cm of disc-out, minimum width=5 cm, minimum height=1.2cm] (disc-loss) {Discriminator Loss\\ Update $log(D^*(x|y))$};

% \node[block, fill = yellow!15, below right = 1 cm and 0.5 cm of val, minimum width=5 cm, minimum height=1.2cm] (gen) {Generator \\$G(z|y) \equiv log(1-(D^*(G(z|y)|y))$};

% \node[block, fill = yellow!10, below = 1cm of gen, minimum width=5 cm, minimum height=1.2cm] (gen-out) {Generated (Fake) Image};

% \node[block, fill= yellow!10, below = 1cm of gen-out, minimum width=5 cm, minimum height=1.2cm] (gen-loss) {Generator Loss\\ Update $G(z|y)$};

% % Final result block
% \node[block, fill=teal!20, below= 10 cm of val, minimum width=5cm] (res) {Result / Evaluation \\ (Performance Metrics: Accuracy)};

% % Connections
% \draw[arrow] (gr-truth) -- (II-sim);
% \draw[arrow] (gr-truth.south) |- (Input-dataset.west);
% \draw[arrow] (II-sim) -- (Input-dataset);
% \draw[arrow] (Input-dataset) -- (split); 
% \draw[arrow] (Input-dataset) -- (split);

% \draw[arrow] (split.west) -| (train.north);
% \draw[arrow] (split.south) -- (val.north);
% \draw[arrow] (split.east) -| (test.north);
% \path (train.south) ++(0,-0.5) coordinate (p1)
%       (p1) ++(0.2,0) coordinate (p2);
% \draw[arrow] (train.south) -- (p1) -- (p2) -- (disc.north);
% \draw[arrow] (val) |- (disc);
% \draw[arrow] (disc) -- (disc-out);
% \draw[arrow] (disc-out) -- (disc-loss)

% \path (disc-loss.south) ++(0,-1.0) coordinate (p3)
%       (p3) ++(-3.0,0) coordinate (p4)
%       (p4) ++(0,+8.0) coordinate (p5)
%       (p5) ++(2.5, 0) coordinate (p6)
%       (p6) ++(0,-1.3) coordinate (p7);
% \draw[d-arrow] (disc-loss.south) -- (p3) -- (p4) 
% -- (p5) 
% node[pos=1.0,left=7pt, text=blue, font=\large, rotate=90]{Iteration / Updating Discriminator Parameters}
% -- (p6) -- (p7);

% \path(II-sim.south) ++ (0,-0.5) coordinate (p8)
%      (p8) ++ (7.0,0) coordinate (p9)
%      (p9) ++ (0, -5.5) coordinate (p10)
%      (p10) ++ (-1.5,0) coordinate (p11)
%      (p11) ++ (0, -0.6) coordinate (p12);
% \draw[arrow] (II-sim.south) -- (p8) -- (p9) -- (p10) -- (p11) -- (p12);

% \path(Lat-vector.south) ++ (0, -0.4) coordinate (p13)
%      (p13) ++ (2.0,0) coordinate (p14)
%      (p14) ++ (0,-5.9) coordinate (p15)
%      (p15) ++ (-1.5,0) coordinate (p16)
%      (p16) ++ (0,-0.5) coordinate (p17);
% \draw[arrow] (Lat-vector.south) -- (p13) -- (p14) -- (p15) -- (p16) -- (p17);
% \draw[arrow] (gen) -- (gen-out);
% \draw[arrow] (gen-out) -- (gen-loss);
% \path (gen-out.west) ++ (-1.0,0) coordinate (p18)
%       (p18) ++ (0,0.1) coordinate (p19)
%       (p19) ++ (-4.1,0) coordinate (p20);
% \draw[arrow] (gen-out.west) -- (p18) -- (p19) -- (p20);
%\draw[arrow] (gen-out.west) -- (disc);

\end{tikzpicture}
\end{center}
\end{figure}

\end{document}

### 2025-11-05 Phase_II/draft/II.tex
intro_reformatted, II.tex, refs.bib, Paragan.tex, main.tex changed

--- 2025-10-01 Phase_II/draft/II.tex
@@
   \includegraphics[width=\linewidth]{fig/baseline.png}
-  \caption{The tracks of the baselines due to Earth rotation (discribed in sec.~\ref{sec:earth}) provided by the four telescopes arranged in fig.~\ref{fig:teles} for one night of observation.
-The increased number of telescopes will creates more baselines, so the coverage of more observational plane and better image reconstruction.}
+  \caption{The tracks of the baselines due to Earth rotation (described in sec.~\ref{sec:earth}) provided by \textcolor{blue}{the hypothetical observation facility of four telescopes arranged in fig.~\ref{fig:teles}} for one night of observation.
+\textcolor{blue}{The number of baselines scales as square of number of telescopes in the array thus leading to greater coverage of the observational plane and better image reconstruction prospects.}}
 \label{fig:base}
 \end{figure}
+
 \begin{figure}[hbt]
   \includegraphics[width=\linewidth]{fig/ellipse/ellipse1612.png}
-  \caption{This figure shows one of the simulated fast rotating star.
-The brightness is highest at the poles and there is gravity darkening along the equator.
-There is 31460 images has been created with different parameters to train the model.}
+  \caption{This figure shows one of the simulated fast rotating stars (FRS).
+The brightness is highest at the poles; gravity darkening visible along the equator.
+A total of 31460 such images of FRS with different parameter values have been generated to train the model.}
   \label{fig:image}
@@
 The right panel shows the absolute value of the same source measured along the tracks shown in Fig.~\ref{fig:base}.
-This figure reflects the sparse nature of the signal received by a realistic finite number of telescopes and baselines sampled from the full ($u,v$) plane signal space, as shown in the left figures.
+This figure reflects the sparse nature of the signal received by a realistic finite number of telescopes and baselines sampled from the full ($u,v$) plane signal space, as shown in the figure on the left panel.
 Both figures are plotted on a linear scale and normalized to the maximum pixel value in each respective figure.}
@@
 The primary purpose of IACTs is to study high-energy gamma rays (with energy $E\ \geq 30$ GeV) arriving from cosmic sources, entering the Earth's atmosphere, and initiating Cherenkov showers in the upper atmosphere due to multiple scattering.
-These telescopes feature an array of mirrors that focus light onto a set of photo-multiplier tubes \citep[PMTs, see e.g.,][]{aleksic2016major}.
+These telescopes feature an array of mirrors that focus light received from a sky source onto their respective set of photo-multiplier tubes \citep[PMTs, see e.g.,][]{aleksic2016major} with appropriate specifications needed for II observations.
 In the simulation model adopted here, we consider a set of four IACTs, each with similar properties.
@@
 \end{equation}
-where $b_E$ and $b_N$ are the baselines expressed in east and north coordinates.
-However, of course sources can be anywhere on the sky, and the telescopes are stationary and may also have different relative altitudes $b_A$ depending on the available terrain.
-Therefore, the Earth's rotation must be taken into account to cover the maximum observational plane using rotated baselines.
-For a given stellar source with declination $\delta$ and hour-angle $h$, as observed by telescopes at latitude $l$, equation (\ref{eq:baseline_rot}) provides the rotated baselines for a given pair of telescopes \citep[see e.g., eqs.~8--10 from][]{2020MNRAS.498.4577B}.
+where $b_E$ and $b_N$ are, respectively, the baselines expressed in east and north coordinates.
+However, the sources can be anywhere on the sky, and the telescopes are stationary and may also have different relative altitudes $b_A$ depending on the available terrain.
+In order to gather maximum possible information on the source during the observation session and to cover as much of the observational plane as possible during such sessions, Earth's rotation must be taken into account using rotated baselines.
+For a given stellar source with declination $\delta$ and hour-angle $h$, as observed by telescopes located at latitude $l$, equation (\ref{eq:baseline_rot}) provides the rotated baselines for a given pair of telescopes \citep[see e.g., eqs.~8--10 from][]{2020MNRAS.498.4577B} with the $R$-matrices representing the respective rotation operations.
 \begin{equation}
@@
 \subsection{A Fictitious Fast Rotating Star: Our Test Case}
-In our work presented here, we simulate a single fast-rotating star to test image reconstruction using a GAN.
+In our work presented here, we attempt image reconstruction of a fast-rotating star using its simulated Intensity Interferometric observation in a C-GAN architecture.
+\textcolor{blue}{Fast-rotating stars are important test cases for understanding various astrophysical processes, including stellar evolution, internal structure, and dynamical behaviour over time.
 Fast rotation causes stars to adopt an oblate shape, flattening at the poles and bulging at the equator due to the stronger centrifugal force \citep[e.g.,][]{von1924radiative, 1999A&A...347..185M}.
-Fig.~\ref{fig:image} shows an image qualitatively representing a fictitious fast-rotating star, with brightness distributed across its surface.
-The brightness is highest at the poles and lowest at the equator, a phenomenon known as gravity darkening \citep{lucy1967gravity}.
-This effect was first observed through interferometric and spectroscopic data from the CHARA Array for the fast-rotating star Regulus \cite{mcalister2005first}.
-Fast-rotating stars are important test cases for understanding various astrophysical processes, including stellar evolution, internal structure, and dynamical behavior over time.
-It has not yet been observed using intensity interferometry, but oblateness has recently been measured \citep{2025arXiv250615027A} and gravity darkening is a natural next step.
+Fig.~\ref{fig:image} shows an image qualitatively representing a fictitious fast-rotating star, with brightness (and, therefore, the effective surface temperature) distributed across its surface.
+The brightness (effective temperature) is highest at the poles and lowest at the equator, a phenomenon known as gravity darkening \citep{lucy1967gravity}.
+First direct interferometric detection of stellar photospheric oblateness (of Altair) was pioneered by van Belle et al \cite{vanBelle2001} using the Palomar Testbed Interferometer (PTI) and the Navy Prototype Optical Interferometer (NPOI).
+Gravity darkening due to fast rotation was first observed through interferometric and spectroscopic data from the CHARA Array for the fast-rotating star Regulus \citep{mcalister2005first}.
+As pointed out earlier, these two pieces  of work, all using Michelson Interferometry, make a subset of several others \citep{vanBelle2001, DomicianodeSouza2003, mcalister2005first, DomicianodeSouza2005, Monnier2007, Pedretti2009, Zhao2009, Martinez2021}.
+The first observation of photospheric oblateness (of $\gamma$ Cassiopeiae or $\gamma$-Cas) using Intensity Interfereometry (II) has been recently carried out at VERITAS observatory and is reported by Archer et al.
+\cite{Archer-arXiv-2025}.
+Reportage of such observations of other $\gamma$-Cas like targets and other class of FRS by Cherenkov Telescope arrays, such as  the MAGIC array, are expected by 2026.
+In addition, observation and measurement of gravity darkening using II is the natural next step and is yet to be reported.
+In this context, our work of reconstructing the image of FRSs from their II-simulated observations using C-GAN is an attempt at solving this inverse problem along with mitigation of loss of phase information in II.}
 
@@
 In practice, only a small part of this information is available (as seen in right panel of Fig.~\ref{fig:ft}), because one has a finite number of baselines corresponding to the finite number $N_T$ of telescopes at our disposal and a limited observation schedule.
-We have simulated the II observation of the fictitious star by four telescopes (correlated with baselines as seen in Fig.~\ref{fig:teles}) over one night.
+We have simulated the II observation of the fictitious star \textcolor{blue}{by a hypothetical observation facility having an array of four IACTs} (correlated with baselines as seen in Fig.~\ref{fig:teles}) over one night.
 Using this modest amount of signal from one night's observation, we have trained a cGAN to construct the image of the source.
@@
   \includegraphics[width=0.85\linewidth]{fig/ellipse1612.jpg}
-  \caption{This merged image shows the input for GAN.
-The left figure is the simulated source, which act as a ground truth for GAN while training the model.
-The right figure shows the signal from the same simulated source observed by the baselines (fig.~\ref{fig:base}), which is the reason both images is merged to provide GAN as input so that it can make the prediction after being trained.
-The grey scale of the figure is normalized to the brightest pixel in the image.}
+  \caption{\textcolor{blue}{Example of the input used for training the C-GAN model.
+\textcolor{blue}{The picture on the left shows the source image, which serves as the ground truth or the real data ($x$, as mentioned in the Flow Diagram (Fig.\ref{fig:FlowDiagram} discussed later} during the training.
+The picture on  the right represents the simulated Intensity Interferometry (II) observation pattern of the source (on the left) using \textcolor{blue}{a hypothetical observation facility having as array of four IACTs} (see Fig.~\ref{fig:teles}) and the tracks of the six telescope baselines (see Fig.~\ref{fig:base}) generated  by these four IACTs due to Earth's rotation during the observation session.
+\textcolor{blue}{This pattern referred to as $y$, in the Flow Diagram (Fig.\ref{fig:FlowDiagram} discussed later forms the ``condition" during the training to which the GAN model has to conform.
+Salt-and-pepper noise is added to this pattern for enhancing the robustness of the C-GAN model.} Together, these images form a training pair, where the GAN learns to reconstruct a predicted image (modeling of observed signal) similar to ground truth (left) from the noisy baseline signal (right).
+The grayscale in both images is normalized to the brightest pixel.}}
   \label{fig:GANinput}

### 2025-11-05 Phase_II/draft/image-reconstruction-past-efforts.tex
intro_reformatted, II.tex, refs.bib, Paragan.tex, main.tex changed

@@
 Generative Adversarial Networks (GANs), introduced by \cite{goodfellow2014generative}, have been successful in such data augmentation tasks.
-Conditional GAN (cGAN) architectures, proposed by \cite{mirza2014conditional} and applied to a wide variety of datasets by \cite{isola2017image}, leverage additional information about the images in the training datasets and have demonstrated remarkable robustness in image recovery across diverse data types.
+Conditional GAN (C-GAN) architectures, proposed by \cite{mirza2014conditional} and applied to a wide variety of datasets by \cite{isola2017image}, leverage additional information about the images in the training datasets and have demonstrated remarkable robustness in image recovery across diverse data types.“Do you employ human tutors or human reviewers to supplement AI-generated solutions?”
 

### 2025-11-06 Phase_II/draft/intro_reformatted.tex
intro_reformatted, II.tex, refs.bib, Paragan.tex

@@
 One of the primary scientific projects of the humanity is to figure out what the stars are and how do they do what they do.
-The first obvious step in this project, beyond measuring their global parameters like diameter, mass, orbital and astromteric elements, is to obtain images of the stars with all details of the stellar surfaces as we do routinely in case of the Sun.
-In other words, the objective is to achieve capability of high fidelity image reconstruction of distant stars.
+The first obvious step in this project, beyond measuring their global parameters like diameter, mass, orbital and astrometric elements, is to obtain images of the stars with all details of the stellar surfaces.
+In case of the Sun, this is done routinely by observatories and sun-observation satellites.
+But such routine still remains a challenge even for the $\alpha$-centauri system, our nearest stellar neighbour.
+The objective is to achieve capability of high fidelity image reconstruction of distant stars.
 Two interferometry based techniques, namely, Michelson Interferometry (MI) or Intensity Interferometry (II) have emerged during the last century to address this objective.
 A discussion of the development of these two approaches and comparison of their respective merits and challenges can be found in \citep{Rai2025}.
-The work reported here presents the results of a first effort at applying a conditional Generative Adversarial (neural) Network (cGAN) to image reconstruction of a fast rotator using its simulated II observations.
+The work reported here presents the results of a first effort at applying a Conditional Generative Adversarial (neural) Network (C-GAN) to image reconstruction of a fast rotator using its simulated II observations.
 
@@
 
-We report here, the results of our attempt, the first of its kind, to reconstruct the II-simulated gravity-darkened images of fast rotating stars using a cGAN neural network architecture.
-Image reconstruction in gravity darkened fast rotating stars has long been examined using various methods in MI \citep{vanBelle2001, DomicianodeSouza2003, DomicianodeSouza2005, Monnier2007, Pedretti2009, Zhao2009, Martinez2021}.
-Recently photosphere oblateness of $\gamma$-Cassiopeia \citep{2025arXiv250615027A} has been measured at the VERITAS observatory using II.
-These results, and especially, that by Archer et al.
-\cite{2025arXiv250615027A}  put our work in context.
+We report here, the results of our attempt, the first of its kind, to reconstruct the II-simulated gravity-darkened images of fast rotating stars using a C-GAN neural network architecture.
+Image reconstruction in gravity darkened fast rotating stars has long been examined using various methods in MI \citep{vanBelle2001, DomicianodeSouza2003, DomicianodeSouza2005, mcalister2005first, Monnier2007, Pedretti2009, Zhao2009, Martinez2021}.
+Recently photosphere oblateness of $\gamma$-Cassiopeia \citep{Archer-arXiv-2025} has been measured at the VERITAS observatory using II.
+These results, and especially, that by \cite{Archer-arXiv-2025} put our work in context.
 Thus our simulation is a natural next step of the work of Archer et al and others.
-We emulate the cGAN model of Isola et al.
+We emulate the C-GAN model of Isola et al.
 \cite{isola2017image} to reconstruct images of fast-rotating stars using their simulated Intensity Interferograms and simulated sky-intensity distributions as input data for training, testing, and validation.
-We consider four Imaging Cherenkov Telescope Arrays (IACTs) and simulate observation of a fast-rotating star.
-The image predicted by the trained GAN shows promising results in reconstructing the star’s shape and size.
+We consider an array of four Imaging Cherenkov Telescopes (IACTs) and simulate observation of a fast-rotating star.
+The image predicted by the trained C-GAN shows promising results in reconstructing the star’s shape and size.
 The reconstructed brightness distributions are then assessed using moments.
@@
 The next section discusses briefly the past efforts at image reconstruction on II, followed by the section on a discussion of Intensity Interferometry, focusing on its signal and noise characteristics for fast-rotating stars along the Earth’s rotation.
-The following section introduces the GAN formulation and its structure.
-The fifth section details the parameter selection for training the GAN for image reconstruction.
-The sixth section presents the results of the trained GAN both visually and via image moments.
+The following section introduces the C-GAN formulation and its structure.
+The fifth section details the parameter selection for training the network for image reconstruction.
+The sixth section presents the results of the trained network both visually and via image moments.
 Finally, the paper concludes with a discussion of the overall results.
@@
 	\includegraphics[width=\linewidth]{fig/telescope.png}
-	\caption{The telescope configuration with similar properties each, where diameter is 12 meter and baselines are spreaded over more than 100 meter.
-This setup is used to simulate the signal for II observation.}
+	\caption{A schematic representation of {\textcolor{blue}{a hypothetical observation facility with an the array of four Cherenkov Telescopes (IACTs).
+This array is used in simulating the Intensity Interferometry (II) observation of the fast rotators.}} Each of the telescopes has a diameter of 12m.
+The baselines provided by the array are of the order of 100m.}
 	\label{fig:teles}

### 2025-11-11 Phase_II/draft/ParaGan.tex
Edited ParaGan.tex with TikZ output in pdf format
upto section 3

@@
 	\centering
-	\includegraphics[width=\linewidth]{fig/testing_image/image_7.png}
-	\includegraphics[width=\linewidth]{fig/testing_image/image_12.png}
-	\includegraphics[width=\linewidth]{fig/testing_image/image_13.png}
-	\includegraphics[width=\linewidth]{fig/testing_image/image_29.png}
-	\includegraphics[width=\linewidth]{fig/testing_image/image_39.png}
+	\includegraphics[width=0.785\textwidth]{fig/testing_image/image_7.png}
+	\includegraphics[width=0.785\textwidth]{fig/testing_image/image_12.png}
+	\includegraphics[width=0.785\textwidth]{fig/testing_image/image_13.png}
+	\includegraphics[width=0.785\textwidth]{fig/testing_image/image_29.png}
+	\includegraphics[width=0.785\textwidth]{fig/testing_image/image_39.png}
 \caption{Example results of image reconstruction using the GAN model along with the II observations simulated in this work.
@@
 \end{figure*}
+
 Here, we discuss the parameters of the GAN architecture used for reconstructing images of stellar objects using II.
@@
 
+\iffalse
 \begin{figure}[htbp]
@@
 \end{figure}
+\fi
 
+\begin{figure}
+\begin{center}
+\includegraphics[scale=0.4]{FlowDiagram_TikZ.pdf}
+\caption{A block diagram for the process of image reconstruction through C-GAN.}
+\label{fig:FlowDiagram}
+\end{center}
+\end{figure}
 %\end{document}

### 2025-11-11 Phase_II/draft/intro_reformatted.tex
upto section 3

@@
 The foundational basis of II stems from the pioneering experiments and theoretical investigations, widely referred to as the \textquotedblleft HBT effect \textquotedblright, carried out initially by Hanbury Brown and Twiss (HBT) \cite{HBT56Lab,brown1957interferometry, brown1958interferometry} and, later, by Glauber \citep{glauber1963quantum}.
-HBT reported \cite{HBT56Lab} in 1956, the correlation between photons measured by a pair of photon detectors in two coherent beams of light.
-Rai et al.
+The correlation between photons (called HBT effect) measured by a pair of photon detectors in two coherent beams of light was reported in 1956 \cite{HBT56Lab}.
 \cite{Rai2025} present a modern-day variant of this experiment, carried out with pseudo-thermal light.
@@
 On the other hand, II-based methods are in a nascent stage.
-The recent publications of Liu et al.
-\cite{Liu2024SuperresolutionII, Liu2025} have demonstrated, through outdoor experiments, imaging millimeter-scale targets at 1.36 km with a resolution ~14 times better than a single telescope’s diffraction limit.
+The recent publications \cite{Liu2024SuperresolutionII, Liu2025} have demonstrated, through outdoor experiments, imaging millimeter-scale targets at 1.36 km with a resolution ~14 times better than a single telescope’s diffraction limit.
 A \textquotedblleft flexible computational algorithm \textquotedblright reconstructs images from intensity correlations, overcoming atmospheric turbulence and optical imperfections.
@@
 Thus our simulation is a natural next step of the work of Archer et al and others.
-We emulate the C-GAN model of Isola et al.
-\cite{isola2017image} to reconstruct images of fast-rotating stars using their simulated Intensity Interferograms and simulated sky-intensity distributions as input data for training, testing, and validation.
+We emulate the C-GAN model \cite{isola2017image} to reconstruct images of fast-rotating stars using their simulated Intensity Interferograms and simulated sky-intensity distributions as input data for training, testing, and validation.
 We consider an array of four Imaging Cherenkov Telescopes (IACTs) and simulate observation of a fast-rotating star.

### 2025-11-12 Phase_II/draft/response.txt
edits

@@
 
-Counter-argument: We can justify the choice of gravity-darkened stars.
+In this first attempt, is seems reasonable to consider only
+gravity-darkened stars, for the following reasons.
 
@@
 
-Asymmetry is recovered in some cases: investigate!
 We increased the number of training, validation and testing dataset. 
@@
 
-Counter-argument: the (u,v) sampling for any given data set is fixed
-and known, so if computationally feasible [which it is] you do want to
-train on the sampling used.
+The (u,v) sampling for any given data set is fixed and known.
+Training the network for a single observing run is a tolerable
+computational cost.  Hence we train on the sampling used.
 

### 2025-11-12 Phase_II/draft/intro_reformatted.tex
edits

@@
 \section{Introduction}
-The humanity instinctively feels a symbiotic relationship with the stars.
-One of the primary scientific projects of the humanity is to figure out what the stars are and how do they do what they do.
+Humans instinctively feels a relationship with the stars.
+One of the primary scientific projects of humanity is to figure out what the stars are and how do they do what they do.
 The first obvious step in this project, beyond measuring their global parameters like diameter, mass, orbital and astrometric elements, is to obtain images of the stars with all details of the stellar surfaces.

### 2025-11-13 Phase_II/draft/response.txt
edits
Yuri

@@
 
+The loss of phase (or Hermitian symmetry) means that we cannot the
+truth and its 180-degree-rotated twin.  Asymmetric profiles can,
+however, still be reconstructed.
+
 |  - Figures should be explained fully in their captions, rather than the
@@
 
-Give github repo, maybe give most recent version a DOI.
+The sections have been modified now and the code is published on GitHub with 
+DOI: https://doi.org/10.5281/zenodo.17598807
 

### 2025-11-13 Yuri/cGAN_network/gan_utils/utils.py

@@ -1,0 +1,189 @@
+import os
+import tensorflow as tf
+from keras import layers
+import numpy as np
+
+
+class GanUtils:
+    """
+    Utility functions for loading, preprocessing, and augmenting GAN input data.
+
+    Notes
+    -----
+    - All image preprocessing is Keras-graph safe (uses tf.signal or keras.layers).
+    - Normalization: images are scaled to [-1, 1].
+    - Compatible with both tf.data pipelines and Keras Functional API.
+    """
+
+    def __init__(self, img_size: int = 128):
+        self.img_size = img_size
+        self._resize_layer = layers.Resizing(img_size, img_size, interpolation="nearest")
+        self._flip_layer = layers.RandomFlip("horizontal")
+
+    # ------------------------------------------------------------------
+    # Data loading
+    # ------------------------------------------------------------------
+    def load(self, image_file: str):
+        """
+        Load concatenated image file and split into (observed, real).
+        Input format: [real_image | input_image] concatenated along width.
+        """
+        image = tf.io.read_file(image_file)
+        image = tf.io.decode_jpeg(image, channels=1)
+
+        w = tf.shape(image)[1] // 2
+        real_image = image[:, :w, :]
+        input_image = image[:, w:, :]
+
+        real_image = tf.cast(real_image, tf.float32)
+        input_image = tf.cast(input_image, tf.float32)
+        return input_image, real_image
+
+    # ------------------------------------------------------------------
+    # Preprocessing
+    # ------------------------------------------------------------------
+    def resize(self, input_image, real_image, height, width):
+        """Resize input and real images to (height, width)."""
+        resize_layer = layers.Resizing(height, width, interpolation="nearest")
+        return resize_layer(input_image), resize_layer(real_image)
+
+    def random_crop(self, input_image, real_image):
+        """Randomly crop to (img_size, img_size)."""
+        stacked = tf.stack([input_image, real_image], axis=0)
+        cropped = tf.image.random_crop(
+            stacked, size=[2, self.img_size, self.img_size, tf.shape(input_image)[-1]]
+        )
+        return cropped[0], cropped[1]
+
+    def normalize(self, input_image, real_image):
+        """Normalize pixel values to [-1, 1]."""
+        input_image = (input_image / 127.5) - 1.0
+        real_image = (real_image / 127.5) - 1.0
+        return input_image, real_image
+
+    # ------------------------------------------------------------------
+    # Augmentation
[…]

### 2025-11-13 Yuri/cGAN_network/model/gan.py

@@ -1,0 +1,336 @@
+import matplotlib.pyplot as plt
+from keras import backend as K
+from IPython import display
+import tensorflow as tf
+import numpy as np
+import datetime
+import time
+import cv2
+import os
+import csv
+
+from gan_utils.utils import GanUtils, SaltAndPepper
+
+
+sfun = GanUtils(img_size=128)
+
+class CGAN():
+      """
+      The function used for generator and discriminator
+      """   
+      
+      def gan_para(self, LAMBDA, OUTPUT_CHANNELS, filtersize, beta, learning_rate, disc_train_iterations, base_path, batch_size):
+          """
+          The parameters used in definitions
+          """
+          self.LAMBDA = LAMBDA
+          self.OUTPUT_CHANNELS = OUTPUT_CHANNELS
+          self.filtersize = filtersize
+          self.beta = beta
+          self.learning_rate = learning_rate
+          self.disc_train_iterations = disc_train_iterations
+          self.base_path = base_path
+          self.batch_size = batch_size
+          
+      def Generator(self):
+          """
+          define the generator with different layers of neuron.
+          It returns the generated image according to the downsample and upsample of an input tensor defined by image size.
+          """
+          
+          inputs = tf.keras.layers.Input(shape=[sfun.img_size, sfun.img_size, 1])             # used to instantiate a Keras tensor of a shape given.
+    
+          down_stack = [
+                        sfun.downsample(64, self.filtersize, apply_batchnorm=False),          # downsample the image with different layers and filter
+                        sfun.downsample(128, self.filtersize),
+                        sfun.downsample(256, self.filtersize),
+                        sfun.downsample(512, self.filtersize),
+                        sfun.downsample(512, self.filtersize),
+                        sfun.downsample(512, self.filtersize),
+                        sfun.downsample(512, self.filtersize),
+                       ]
+
+          up_stack = [
+                      sfun.upsample(512, self.filtersize, apply_dropout=True),                # upsample the image with different layers and filter
+                      sfun.upsample(512, self.filtersize, apply_dropout=True),
+                      sfun.upsample(512, self.filtersize),
+                      sfun.upsample(256, self.filtersize),
+                      sfun.upsample(128, self.filtersize),
+                      sfun.upsample(64, self.filtersize),
+                     ]
+        
[…]

### 2025-11-13 Yuri/cGAN_network/train.py

@@ -1,0 +1,161 @@
+"""
+GAN Training and Evaluation Script
+----------------------------------
+
+This script trains a GAN model using TensorFlow/Keras on astronomical images.
+It supports GPU execution if available, and generates visualization outputs 
+for generator and discriminator models, as well as sample predictions.
+"""
+
+import os
+import argparse
+import matplotlib.pyplot as plt
+import tensorflow as tf
+
+gpus = tf.config.list_physical_devices("GPU")
+if gpus:
+    try:
+        for gpu in gpus:
+            tf.config.experimental.set_memory_growth(gpu, True)
+        print(f"[INFO] Using {len(gpus)} GPU(s).")
+    except RuntimeError as e:
+        print(f"[WARNING] GPU setup failed: {e}")
+else:
+    print("[INFO] Running on CPU.")
+
+from gan_utils.utils import GanUtils
+from model.gan import CGAN
+
+
+# -------------------------------------------------------------------------
+# MAIN FUNCTION
+# -------------------------------------------------------------------------
+def main(base_path: str):
+    """
+    Main training pipeline.
+
+    Args:
+        base_path (str): Base path containing `train/`, `test/` or `val/` directories.
+    """
+    # Verify GPUs are used
+    print("Is GPU available?", tf.config.list_physical_devices("GPU"))
+    print("TensorFlow device:", tf.test.gpu_device_name())
+
+    # ---------------------------------------------------------------------
+    # INITIALIZATION
+    # ---------------------------------------------------------------------
+    fn = GanUtils(img_size=128)
+    mfn = CGAN()
+
+    BATCH_SIZE = 1      # Number of samples per training iteration
+    BUFFER_SIZE = 140  # Shuffle buffer size for dataset
+
+    mfn.gan_para(
+        LAMBDA=100,
+        OUTPUT_CHANNELS=1,
+        filtersize=5,
+        beta=0.005,
+        learning_rate=2e-4,
+        disc_train_iterations=1,
+        base_path=base_path, 
+        batch_size=BATCH_SIZE
+    )
+
+    # ---------------------------------------------------------------------
+    # DATA LOADING AND VISUALIZATION
+    # ---------------------------------------------------------------------
+    # Load one sample image for sanity check
+    sample_input, sample_real = fn.load(os.path.join(base_path, "output/train/ellipse_001802.jpg"))
+    os.makedirs("testing_image", exist_ok=True)
+
+    # ---------------------------------------------------------------------
+    # GENERATOR MODEL
[…]

### 2025-11-13 Yuri/data_generation/generate_baseline.py

@@ -1,0 +1,131 @@
+"""
+Generate telescope layout, baselines, and (u, v) plane coverage for intensity interferometry.
+
+Steps:
+1. Define observation times (Julian Dates).
+2. Define telescope positions at Veritas Observatory.
+3. Plot telescope arrangement and save to PNG.
+4. Compute baselines and their evolution with Earth rotation.
+5. Plot covered (u, v) plane and save.
+6. Convert (u, v) coverage to binary mask (grayscale threshold + resize),
+   and save as a NumPy array.
+"""
+
+import os
+import numpy as np
+import matplotlib.pyplot as plt
+import cv2
+import argparse
+from pathlib import Path
+
+from utils.aperture import Aperture
+from utils.obstime import ObsTime
+from utils.obspoint import ObsPoint
+
+
+def main():
+    # --- Initialize classes ---
+    ap = Aperture()
+    obst = ObsTime()
+    obsp = ObsPoint()
+
+
+    # --- Parase base path ---
+    parser = argparse.ArgumentParser(
+        description="Generate telescope layout and baseline coverage."
+    )
+    parser.add_argument(
+        "--path",
+        type=Path,
+        default=Path.cwd() / "base",
+        help="Base directory for saving results (default: ./base)",
+    )
+    parser.add_argument(
+        "--ntele",
+        type=int,
+        default=4,
+        help="Number of telescopes that sample the star (default: 4)",
+    )
+    output_dir = parser.parse_args().path
+    n_tele = parser.parse_args().ntele
+    os.makedirs(output_dir, exist_ok=True)
+
+    # --- Observation time for Intensity Interferometry ---
+    start = [2460311.20167]  # JD (Jan 1, 2024, 7pm)
+    end = [2460311.70833]    # JD (Jan 2, 2024, 5am)
+    step = obst.obslen(start, end, 0.0104167)  # ~15 min steps
+    jd = obst.julday(start, end, step)
+
+    # --- Observatory location (Veritas) ---
+    la = obsp.raddeg(31, 40, 30)
+    lo = obsp.raddeg(110, 57, 7)
+
+    # --- Telescope positions ---
+    x = np.linspace(-60, 150, 500)
+    y = np.linspace(-60, 80, 500)
+    Tname = ["T1", "T2", "T3", "T4"]
[…]

### 2025-11-13 Yuri/data_generation/generate_ellipsoids.py

@@ -1,0 +1,140 @@
+"""
+Batch-generate ellipsoid fields and save previews + compressed arrays.
+
+- Headless matplotlib backend (safe on servers)
+- Zero-padded filenames
+- Optional fast previews (plt.imsave) or slower previews with colorbar
+- Arrays saved as NPZ with metadata (rad, inc, pa, sq, ds, N, lam)
+"""
+
+# --- Headless backend (must come before pyplot import) ---
+import matplotlib
+matplotlib.use("Agg")
+
+from pathlib import Path
+from itertools import product
+import numpy as np
+import matplotlib.pyplot as plt
+from tqdm import tqdm
+import argparse
+import os
+
+# Adjust to your real module path
+from utils.ellipsoid import Ellipsoid
+
+
+# ---------------- Configuration ----------------
+USE_COLORBAR = False         # True = slower w/ colorbar; False = fastest
+SAVE_PREVIEWS = False        # False = skip images entirely
+DPI = 300
+CMAP = None                  # e.g., "inferno" or None for default
+# ------------------------------------------------
+
+
+def _save_preview(arr: np.ndarray, out_path: Path):
+    """Save a quick preview image."""
+    if not SAVE_PREVIEWS:
+        return
+    if USE_COLORBAR:
+        fig, ax = plt.subplots()
+        im = ax.imshow(arr, cmap=CMAP)
+        ax.axis("off")
+        fig.colorbar(im, ax=ax, fraction=0.046, pad=0.04)
+        fig.savefig(out_path, dpi=DPI, bbox_inches="tight", pad_inches=0)
+        plt.close(fig)
+    else:
+        # Fast path: no figure, no colorbar
+        plt.imsave(out_path, arr, cmap=CMAP)
+
+
+def _save_npz(arr: np.ndarray, out_path: Path, *, rad, inc, pa, sq, ds, N, lam):
+    """Save array + parameters in a compressed NPZ (self-describing sample)."""
+    np.savez_compressed(
+        out_path,
+        data=arr.astype(np.float32),  # change to float64 if you need full precision
+        rad=float(rad), inc=float(inc), pa=float(pa), sq=float(sq),
+        ds=float(ds), N=int(N), lam=float(lam),
+    )
+
+
+def main():
+
[…]

### 2025-11-13 Yuri/data_generation/run_data_gen.sh

@@ -1,0 +1,14 @@
+#!/bin/bash
+#SBATCH -q shared
+#SBATCH -C cpu
+#SBATCH -n 1
+#SBATCH -c 1
+#SBATCH --time=25:00:00
+#SBATCH --mem=32GB
+#SBATCH -J data_gen
+
+
+module load python
+conda activate new_env
+
+python -m generate_ellipsoids --path /global/cfs/projectdirs/m2676/users/yuvand/GAN_III/

### 2025-11-17 Phase_II/draft/GAN.tex
upto section 3
GAN.tex subsection 1 rewritten

--- 2025-09-25 Phase_II/draft/GAN.tex
@@
 \section{Generative Adversarial Networks}
-
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{fig/analysis/Discrep_Runs_Losses_disc_loss.png}
+	\includegraphics[width=\linewidth]{fig/analysis/Discrep_Runs_Losses_gen_total_loss.png}
+	\caption{\textcolor{blue}{These figures show the effect of the ratio of episodes of Discriminator training per every episode of Generator training.
+This hyperparameter is termed Discriminator repetition or (discrep) in the figures.
+The square root of the cumulative mean of the losses are plotted against the training steps for 3 values of this ratio.
+Understandably, this ratio has a higher impact on the Discriminator loss than the Generator loss.
+Equal number of episodes of training produces minimum cumulative loss of the Discriminator.
+The dip in the Discriminator loss during the initial phases of its training can be interpreted as its early success in detecting ``fake" (or generated) images because of a poorly trained Generator.
+With gradual training of the Generator, the success rate of the Discriminator decreases and eventually approaches saturation with equal probability of being successful in telling ``fake" from real.
+The continual decrease and eventual saturation of the Generator loss is a result of its training to generate better images with increasing number of steps.}}
+	\label{fig:Plot_discrep_loss}
+\end{figure}
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{fig/analysis/Telescope_Runs_Losses_disc_loss.png}
+	\includegraphics[width=\linewidth]{fig/analysis/Telescope_Runs_Losses_gen_total_loss.png}
+	\caption{The square root of cumulative mean of Discriminator and Generator loss for different numbers of telescopes.
+The number of telescopes is also another hyperparameter that has significant impact on the model performance.
+If there are only two telescopes, both Discriminator and Generator are not trained smoothly.
+The result of four telescopes is a lot better because the cumulative mean of loss functions is smaller compare to other parameters.
+For the same reasons as explained in Fig.(\ref{fig:Plot_discrep_loss}), we observe initial dip and eventual saturation of the Discriminator loss and continual decrease and eventual saturation of the Generator loss with training steps.
+}
+	\label{fig:Plot_telescopes_loss}
+\end{figure}
 Generative Adversarial Networks (GANs) were introduced by \cite{goodfellow2014generative}.
-The underlying concept is straightforward: it involves two competing networks.
-The first network, known as the Generator, produces new images based on an input image.
-These will be referred to as generated images.
-The second network, the Discriminator, attempts to distinguish between the generated image (predicted image) and the real image (ground truth) using Discriminator loss function.
-
-Through the alternating training of these networks, the generated images gradually become indistinguishable from the real images.
-Essentially, this process constitutes a two-player min-max game --- a classic problem in game theory.
-The original formulation of GANs is given by:
+A GAN model involves two competing deep neural network models, referred to as the Generator and the Discriminator.
+These two networks engage in a zero-sum “Minimax” game, as in the Game Theory.
+Given a real data set $\{x_i\}$ (for example, a set of real images) drawn from some unknown distribution $P_{\mathrm{data}}(x)$ generated by some unknown or ill-understood process, the objective here is to generate a new set (of images) whose probability distribution should match $P_{\mathrm{data}}(x)$ as closely as possible.
+During the training of the two models, the Generator samples a latent variable \(z\) from a known prior distribution \(P_z(z)\) ({\it e.g.}, the Normal Distribution) and produces a synthetic sample \(G(z)\) to start with and, subsequently, based on updates received from the Discriminator as its training progresses.
+The Discriminator, being a probabilistic binary classifier, receives either a real data sample \(x\) or a generated sample \(G(z)\), and outputs a probability that the input is real.
+The Discriminator aims to maximise its classification accuracy, while the Generator aims to fool it by trying to minimize it.
+The training of these two networks proceeds alternately leading to the optimization of the adversarial loss function $L(D,G)$ given by
 \begin{equation}
@@
 	\begin{aligned}
-		\min_{G} \max_{D} V(D, G) &= \mathbb{E}_{x \sim p_{\rm data}(x)} \left[ \log D(x) \right] \\
-		&+ \mathbb{E}_{z \sim p_{z}(z)} \left[ \log \left( 1-D(G(z)) \right) \right]
+		L(D,G) & = \min_{G} \max_{D} V(D, G)& \\
+		&= \mathbb{E}_{x \sim p_{\rm data}(x)} \left[ \log D(x) \right] \\
+		&+ \mathbb{E}_{z \sim p_{z}(z)} \left[ \log \left( 1-D(G(z)) \right) \right].
 	\end{aligned}
@@
 \end{equation}
-where $V(D, G)$ denotes the value function of the min-max game.
+The two neural networks \( G(z) \equiv G(z; \theta_G)\) and \(D(x) \equiv D(x; \theta_D)\) are parameterized by \(\theta_i\) with \(i = G \ \mathrm{or}\ D\) respectively.
+During its training, the Generator generates the differentiable function $x_{\mathrm{gen}} \equiv G(z)$ that maps \(z\) to the data space \(x\).
+Through such maps the Generator generates its own distribution $p_{\mathrm G}(x_{\mathrm gen})$ and through the training episodes, specifically by iteratively updating its parameters $\theta_{\mathrm G}$, aligns this distribution with the distribution of real data $p_{\mathrm data}(x)$.
+The training data set provided to the Discriminator is constructed by mixing real data points $x$ and generated data points $x_{\mathrm gen}$ in equal ratio.
+The Discriminator generates the function \(D(x)\) that represents the probability that \(x\) originates from real data.
+Eq.(\ref{eq:Basic_GAN}) implies that training of the GAN model moves towards maximization of the expectation of \(D(x)\).
+Through this process, both the parameters $\theta_{\mathrm G}$ and $\theta_{\mathrm D}$ are optimized such that $p_{\mathrm G}(x_{\mathrm gen})$ gets maximally aligned with $p_{\mathrm data}(x)$.
 
-The objective is to learn the Generator's distribution, \(p_G\), over the data \(x\).
-We begin with input noise variables \(p_z(z)\) and employ two perceptrons, \(G(z; \theta_G)\) and \(D(x; \theta_D)\), parameterized by \(\theta_i\) with \(i = G \ \mathrm{or}\ D\) respectively.
-Here, \(G(z)\) is a differentiable function that maps \(z\) to the data space \(x\), while \(D(x)\) represents the probability that \(x\) originates from real data.
-The problem can be reformulated as:
+For a given fixed Generator $G(z)$, the problem can be reformulated as:
 \begin{equation}
@@
 	\begin{aligned}
-		\max_{D} V(G, D) &= \mathbb{E}_{x \sim p_{\rm data}} \left[ \log D^{*}_{G}(x) \right] \\ 
+		\max_{D} V(D,G) &= \mathbb{E}_{x \sim p_{\rm data}} \left[ \log D^{*}_{G}(x) \right] \\ 
 		&+ \mathbb{E}_{x \sim p_{G}} \left[ \log \left( 1 - D^{*}_{G}(x) \right) \right]
@@
 \end{equation}
-where \(D^{*}_{G}\) denotes the optimum of the discriminator for a given fixed generator, as shown in equation (\ref{eq:Disc_optimum}).
-It can be demonstrated that the global optimum of equation (\ref{eq:GAN_reformulated}) is achieved if and only if \(p_G = p_{\rm data}\).
-Furthermore, if both \(G\) and \(D\) are allowed to reach their respective optima, then \(p_G\) converges to \(p_{\rm data}\).
-A more comprehensive discussion of the problem, including proofs, is provided in \cite{goodfellow2014generative}.
+where \(D^{*}_{G}\) denotes the optimum of the discriminator.
+As seen in equation (\ref{eq:Disc_optimum}), the global optimum of equation (\ref{eq:GAN_reformulated}) is achieved if and only if \(p_G = p_{\rm data}\).
+Furthermore, if both \(G\) and \(D\) are allowed to reach their respective optima, -- the so called Nash point of the Minimax game -- \(p_{\mathrm G}\) converges to \(p_{\rm data}\).
 \begin{equation}
 	\centering
-	D^*_G(x) = \frac{p_{\rm data}(x)}{p_{\rm data}(x) + p_G(g)}
+	D^*_G(x) = \frac{p_{\rm data}(x)}{p_{\rm data}(x) + p_G(x_{\mathrm gen})}
 	\label{eq:Disc_optimum}
 \end{equation}
+At this point, the Discriminator finds its job no better than random guessing. A more comprehensive discussion of the problem, including proofs, is provided in \cite{goodfellow2014generative}.
 
 Subsequently, the GAN framework was extended to a conditional model \citep{mirza2014conditional}.
-In this formulation, both the Generator and the Discriminator receive additional information $y$, and the value function of the conditional GAN (cGAN) is expressed as:
+This new model, known as ``conditional GAN" or cGAN injects a conditioning variable \(y\) into both networks: the Generator now generates \(G(z \mid y)\), and the Discriminator evaluates \(D(x \mid y)\).
+The adversarial objective becomes
 \begin{equation}
@@
 	\begin{aligned}
-		V(D, G) &= \mathbb{E}_{x \sim p_{\rm data}(x)} \left[ \log D(x|y) \right] \\
-		&+ \mathbb{E}_{z \sim p_{z}(z)} \left[ \log \left( 1-D(G(z|y) \right) \right]
+		V(D, G) &= \mathbb{E}_{x,y \sim p_{\rm data}(x)} \left[ \log D(x|y) \right] \\
+		&+ \mathbb{E}_{z,y\sim p_{z}(z)} \left[ \log \left( 1-D(G(z|y) \right) \right]
 	\end{aligned}
@@
 \end{equation}
-\cite{isola2017image} further observed that combining the cGAN from Eq.~\eqref{eq:conditional_GAN} with the traditional L1 loss improves the results, as the Generator is encouraged to produce outputs closer to the ground truth.
-Hence, the function that is minimized is:
+In our work, we specifically use this conditioning mechanism by choosing \(y\) to represent the ground-based intensity-interferometry (II) observation patterns: the Generator is trained to produce stellar surface images that not only look realistic but also conform to the measured II correlations, while the Discriminator judges realism \emph{and} consistency with the II data.
+
+\iffalse 
+During each training session of the Discriminator, it is presented with a series of real images (as seen in Fig.
+(\ref{fig:GANinput}) and generated images taken in equal proportion.
+During the initial phases of its training, as the generated images are sampled from random distribution, the Discriminator finds it easy to distinguish between the real and the generated images.
+This produces a sharp initial dip in the Discriminator loss function.
+On the other hand, the Generator loss function, during the initial phases of its training is high due to the poor quality of its generated images.
+Through the process of alternating training sessions, the Generator gradually learns to do better: generate images which resemble the real images ever more closely.
+As seen in fig.
+(\ref{fig:Plot_discrep_loss}), with further training of both the networks, the Generator loss is gradually minimized and the generated images become gradually indistinguishable from the real images.
+The Discriminator loss, on the other hand, increases from the minimum of the initial phases of training and gradually  saturates to a value halfway between its maximum and minimum values, as expected in the case of a binary classifier.}
+\fi
+
+\cite{isola2017image} further observed that combining the cGAN from Eq.~\eqref{eq:conditional_GAN} with the traditional $L_1(G)$ loss \textcolor{blue}{(also known  as the Mean Absolute Error) improves the results, as the Generator is encouraged to produce outputs closer to the target image in a pixel-wise sense.
+We adopt this approach in the training of our cGAN model by including $L_1(G)$ along with the hyperparameter $\lambda =100$.
+The total loss function that is minimized is}:
 \begin{equation}
@@
 \subsection{Generator}
-As discussed above, in a GAN the Generator is responsible for producing synthetic data—in this case, images that resemble those of a fast-rotating star.
+As discussed above, in a GAN the Generator is responsible for producing synthetic data — in this case, images that resemble those of a fast-rotating star.
 In this work, the Generator is implemented as a U-Net convolutional network \citep{ronneberger2015u}.

### 2025-11-17 Phase_II/draft/II.tex
GAN.tex subsection 1 rewritten

@@
 \subsection{A Fictitious Fast Rotating Star: Our Test Case}
-In our work presented here, we attempt image reconstruction of a fast-rotating star using its simulated Intensity Interferometric observation in a C-GAN architecture.
+In our work presented here, we attempt image reconstruction of a fast-rotating star using its simulated Intensity Interferometric observation in a cGAN architecture.
 \textcolor{blue}{Fast-rotating stars are important test cases for understanding various astrophysical processes, including stellar evolution, internal structure, and dynamical behaviour over time.
@@
 In addition, observation and measurement of gravity darkening using II is the natural next step and is yet to be reported.
-In this context, our work of reconstructing the image of FRSs from their II-simulated observations using C-GAN is an attempt at solving this inverse problem along with mitigation of loss of phase information in II.}
+In this context, our work of reconstructing the image of FRSs from their II-simulated observations using cGAN is an attempt at solving this inverse problem along with mitigation of loss of phase information in II.}
 
@@
   \includegraphics[width=0.85\linewidth]{fig/ellipse1612.jpg}
-  \caption{\textcolor{blue}{Example of the input used for training the C-GAN model.
+  \caption{\textcolor{blue}{Example of the input used for training the cGAN model.
 \textcolor{blue}{The picture on the left shows the source image, which serves as the ground truth or the real data ($x$, as mentioned in the Flow Diagram (Fig.\ref{fig:FlowDiagram} discussed later} during the training.
@@
 \textcolor{blue}{This pattern referred to as $y$, in the Flow Diagram (Fig.\ref{fig:FlowDiagram} discussed later forms the ``condition" during the training to which the GAN model has to conform.
-Salt-and-pepper noise is added to this pattern for enhancing the robustness of the C-GAN model.} Together, these images form a training pair, where the GAN learns to reconstruct a predicted image (modeling of observed signal) similar to ground truth (left) from the noisy baseline signal (right).
+Salt-and-pepper noise is added to this pattern for enhancing the robustness of the cGAN model.} Together, these images form a training pair, where the GAN learns to reconstruct a predicted image (modeling of observed signal) similar to ground truth (left) from the noisy baseline signal (right).
 The grayscale in both images is normalized to the brightest pixel.}}

### 2025-11-17 Phase_II/draft/image-reconstruction-past-efforts.tex
GAN.tex subsection 1 rewritten

--- 2025-10-06 Phase_II/draft/image-reconstruction-past-efforts.tex
@@
 Generative Adversarial Networks (GANs), introduced by \cite{goodfellow2014generative}, have been successful in such data augmentation tasks.
-Conditional GAN (cGAN) architectures, proposed by \cite{mirza2014conditional} and applied to a wide variety of datasets by \cite{isola2017image}, leverage additional information about the images in the training datasets and have demonstrated remarkable robustness in image recovery across diverse data types.
+Conditional GAN (C-GAN) architectures, proposed by \cite{mirza2014conditional} and applied to a wide variety of datasets by \cite{isola2017image}, leverage additional information about the images in the training datasets and have demonstrated remarkable robustness in image recovery across diverse data types.
 
@@
 They also generated a \textquotedblleft Hubble Deep Field-inspired\textquotedblright\ wide-view simulation of the universe.
-
-Let us now discuss the details of our procedure and method.

### 2025-11-17 Phase_II/draft/main.tex
block diagram
intro_reformatted, II.tex, refs.bib, Paragan.tex, main.tex changed
main.tex with DoI added

@@
 \usepackage{tikz}
+\usepackage{xcolor}
+\usepackage[normalem]{ulem}
+\usepackage{hyperref}
+%\newcommand{\paperdoi}{10.5281/zenodo.17598807}
+
+\usepackage{fancyhdr}
+\pagestyle{fancy}
+\fancyfoot{}
+\fancyfoot[L]{DOI: \href{https://doi.org/10.5281/zenodo.17598807}{10.5281/zenodo.17598807}}
+
 \usetikzlibrary{shapes, arrows.meta, positioning, calc}
@@
 \tikzset{
-	block/.style={
-		rectangle,
-		draw,
-		rounded corners,
-		minimum height=1cm,
-		minimum width=3cm,
-		align=center
-	},
-	arrow/.style={
-		thick,
-		-{Stealth}
-	}
+	block/.style = {draw, rectangle, minimum height=1.5em, minimum width=3em, align=center},
+	arrow/.style = {->, thick},
 }
@@
 
+%\maketitle
+%\begin{center}
+%\textbf{DOI:} \href{https://doi.org/\paperdoi}{\paperdoi}
+%\end{center}
+
 \begin{abstract}

### 2025-11-20 Phase_II/draft/GAN.tex
Edit of GAN.texcompleted by SS

@@
 \subsection{Generator}
-As discussed above, in a GAN the Generator is responsible for producing synthetic data — in this case, images that resemble those of a fast-rotating star.
+As discussed above, in a GAN the Generator, a deep neural network in iteself, is responsible for producing synthetic data — in this case, images that resemble those of a fast-rotating star.
 In this work, the Generator is implemented as a U-Net convolutional network \citep{ronneberger2015u}.
-In such architectures, the image's spatial resolution is first reduced through downsampling and then restored via upsampling, resulting in a U-shaped structure.
-The downsampling process typically involves convolutional layers followed by a strided operation (with a stride of 2) to effectively subsample the image, and a leaky version of the Rectified Linear Unit (LeakyReLU) is employed as the activation function.
-
-In contrast, the upsampling process uses only the standard Rectified Linear Unit (ReLU) for neuron activation.
-This stage also comprises convolutional layers followed by operations with a stride of 2 to upscale the image to a higher resolution.
+\textcolor{blue}{The U-Net consists of a symmetric encoder--decoder structure forming a characteristic ``U'' shape: the left (contracting or down-sampling) path, the right (expanding or up-sampling path) and the connecting (bottle-neck) path.
+The left down-sampling path repeatedly applies 3$\times$3 convolutions (padded to preserve spatial dimensions) followed by LeakyReLU activations and strided convolution (with stride of 2), by progressively halving the spatial resolution while doubling the channel depth (typically 64 $\to$ 128 $\to$ 256 $\to$ 512 $\to$ 1024).
+At the bottleneck, high-level features are processed without further spatial reduction.
+The right up-sampling path mirrors this process using 2$\times$2 transposed convolutions (stride 2) for up-sampling, halving the channel count at each level and using ReLU as the activation function for all its layers except the output layer.
 Additionally, a dropout layer is introduced at the beginning of the upsampling phase to mitigate overfitting of the Generator model \citep{isola2017image}.
+Critically, long skip connections concatenate feature maps from each encoder (down-sampling) level to the corresponding decoder (up-sampling level), directly injecting high-resolution details into the reconstruction process.
+This enables the network to ``remember where everything is'' while the deep bottleneck still provides the large receptive field needed to think globally about image structure and semantics.
+Besides the strided convolutions, modern variants of U-Nets used in state-of-the-art GANs incorporate residual blocks within resolution levels, and frequently add spectral normalization and self-attention at the bottleneck for improved training stability and long-range dependency modelling.
+These architectural choices allow our U-Net generator to simultaneously recover sharp, high-frequency details (stellar limb edges, limb-darkening profiles, gravity darkening, and rapid-rotation-induced oblateness) and enforce global coherence (overall disk morphology and physical consistency with the observed interferometric visibilities)---making it ideally suited for high-fidelity sky-image reconstruction of fast-rotating stars from sparse ground-based intensity interferometry observations.}
 
@@
 Unlike a traditional global classifier, PatchGAN evaluates individual patches of the image, outputting a grid of predictions rather than a single scalar value.
+\textcolor{blue}{Each element in the grid corresponds to the ``realness'' of one patch of the image under examination of the Discriminator at a time.
+The final loss is of the Discriminator is the average over all the patch responses.
+Evaluating the ``realness'' of the input image in terms of its constituent patches facilitates capture of texture/ style and other high frequency components in the image.
+As compared to a global discriminator, it also reduces the number of parameters in the network thereby helping reduce computation cost.
+It also works on images with arbitrary sizes.}
 
@@
 Following this, batch normalization is employed to stabilize learning by normalizing activations, and the Discriminator begins classifying each patch as real or fake.
-This is followed by additional layers involving LeakyReLU activation, zero padding, and convolution, culminating in a final prediction that the Generator uses as feedback.
+This is followed by additional layers involving LeakyReLU activation, zero padding, and convolution, culminating in a final prediction that is fed to the Generator as feedback.
 
@@
 This loss is composed of two parts: one that measures how accurately the Discriminator identifies real images (by comparing predictions to a target value of 1) and another that assesses how accurately it identifies fake images (by comparing predictions to a target value of 0).
-Together, these loss components ensure that the Discriminator improves its classification performance, which in turn challenges the Generator to produce increasingly realistic images.
+Together, these loss components ensure that the Discriminator improves its classification performance, which in turn, challenges the Generator to produce increasingly realistic images.

### 2025-11-27 Phase_II/draft/GAN.tex
Edit of GAN drat completed by SS

@@
 \section{Generative Adversarial Networks}
+\begin{figure}
+\centering
+\includegraphics[scale=0.4]{FlowDiagram_TikZ.pdf}
+\caption{\textcolor{blue}{A schematic representation of the cGAN model used in this work.
+The diagram depicts the features of cGAN: (1) the inputs of the real ``ground truth'' images $x$, the conditional images $y$ and the generated image $z$ sampled from a Normal Distribution(2) the creation of the training data of the Discriminator network (3) training of the Discriminator and the Generator networks and optimization of their respective Loss functions.
+The data sets used in training, validation and testing of the networks are sets of merged images $(x|y)$ and $(z|y)$ where $x$ and $y$ represent the source image of the simulated fictitious star (illustrated in Fig.\ref{fig:image}) and its sparse ground observation Intensity Interferometry (II) image (illustrated in the right panel of Fig.(\ref{fig:ft}).
+These data sets are generated by mixing the merged $(x|y)$ and $(z|y)$ images in equal proportions.
+After the training of both the networks is complete (``Nash point'' of the Minimax Game is reached), the success of the model is tested using the testing data.}}
+\label{fig:FlowDiagram}
+\end{figure}
+
 \begin{figure}
@@
 \end{equation}
-In our work, we specifically use this conditioning mechanism by choosing \(y\) to represent the ground-based intensity-interferometry (II) observation patterns: the Generator is trained to produce stellar surface images that not only look realistic but also conform to the measured II correlations, while the Discriminator judges realism \emph{and} consistency with the II data.
+\textcolor{blue}{The conditioning variable $y$ in a cGAN can be various additional information including images, labels or text contextual to ``ground truth'' real data $x$.
+Among various types of cGANs, Pix2Pix GAN with its image-to-image translation design is suitable for the task at hand.
+In our work, we specifically use this conditioning mechanism by choosing \(y\) to represent the ground-based intensity-interferometry (II) observation patterns: the Generator is trained to produce stellar surface images that not only look realistic but also conform to the measured II correlations, while the Discriminator judges realism \emph{and} consistency with the II data.}
 
@@
 In this work, the Generator is implemented as a U-Net convolutional network \citep{ronneberger2015u}.
-\textcolor{blue}{The U-Net consists of a symmetric encoder--decoder structure forming a characteristic ``U'' shape: the left (contracting or down-sampling) path, the right (expanding or up-sampling path) and the connecting (bottle-neck) path.
+\textcolor{blue}{The U-Net consists of a symmetric encoder--decoder structure forming a characteristic ``U'' shape along with skip connections: the left (contracting or down-sampling) path, the right (expanding or up-sampling path) and the connecting (bottle-neck) path.
 The left down-sampling path repeatedly applies 3$\times$3 convolutions (padded to preserve spatial dimensions) followed by LeakyReLU activations and strided convolution (with stride of 2), by progressively halving the spatial resolution while doubling the channel depth (typically 64 $\to$ 128 $\to$ 256 $\to$ 512 $\to$ 1024).

### 2025-11-27 Phase_II/draft/II.tex
Edit of GAN drat completed by SS

@@
 In practice, only a small part of this information is available (as seen in right panel of Fig.~\ref{fig:ft}), because one has a finite number of baselines corresponding to the finite number $N_T$ of telescopes at our disposal and a limited observation schedule.
-We have simulated the II observation of the fictitious star \textcolor{blue}{by a hypothetical observation facility having an array of four IACTs} (correlated with baselines as seen in Fig.~\ref{fig:teles}) over one night.
+We have simulated the II observation of the fictitious star \textcolor{blue}{by a hypothetical observation facility having an array of four IACTs with their relative positions approximating those at VERITAS} (correlated with baselines as seen in Fig.~\ref{fig:teles}) over one night.
 Using this modest amount of signal from one night's observation, we have trained a cGAN to construct the image of the source.

### 2025-11-27 Phase_II/draft/ParaGan.tex
Edit of GAN drat completed by SS

@@
 	\includegraphics[width=0.785\textwidth]{fig/testing_image/image_39.png}
-\caption{Example results of image reconstruction using the GAN model along with the II observations simulated in this work.
+\caption{Example results of image reconstruction using the cGAN model along with the II observations simulated in this work.
 Each row in this figure represents the results for a hypothetical fast-rotating star.
-Going from left to right in each row, the first panel represents the simulated $(u,v)$ plane II signals obtained using the six baselines (right panel of of fig.\ref{fig:ft}).
-This image is presented, as the input, to the trained GAN to produce a predicted image.
-The second panel is the real image of the star, also called the ground truth.
-The third panel is the reconstructed image, or the predicted image, produced by the trained GAN model .
-The fourth and the last panel is the difference between the ground truth and the predicted image in the $(u,v)$ plane.
-The uniform background color in the difference panel suggests that the network is picking up white noise from the $(u,v)$ plane.
-}
+\textcolor{blue}{The left panel represents the sparse II pattern obtained by the simulated observation of the star using the four IACTs illustrated in Fig.\ref{fig:teles}.
+This image acts as the ``condition'' part of the data input to the cGAN model.
+The second panel from left displays the real image, or ground truth, which the Discriminator uses to distinguish from the images generated by the Generator.
+The data generated for training, validation and testing of the cGAN model is a merge of this image and its II pattern presented in the left panel.} The third panel is the reconstructed image, or the predicted image, produced by the trained GAN model .
+\textcolor{red}{The fourth and the last panel is the difference between the ground truth and the predicted image in the $(u,v)$ plane.
+The uniform background color in the difference panel suggests that the network is picking up white noise from the $(u,v)$ plane.} }
 	\label{fig:GAN}
 \end{figure*}
-
-Here, we discuss the parameters of the GAN architecture used for reconstructing images of stellar objects using II.
-Given the adversarial nature of GANs, where the Generator and Discriminator engage in a min-max game, careful tuning of key parameters is critical to ensure that both networks are well-balanced for effective training.
+\textcolor{blue}{An appropriate cGAN architecture along with a set of hyperparameters was optimized by tuning.
+The objective of the model, as already mentioned, was to learn to faithfully reproduce a set of sky-images of fast rotators subject to the condition that those images are consistent with their simulated II observation data.
+We discuss below the architecture and the hyperparameters of the cGAN model used for this task.} Given the adversarial nature of GANs, where the Generator and Discriminator engage in a minimax game, careful tuning of key parameters is critical to ensure that both networks are well-balanced for effective training.
 
 \subsection{Data Preparation}
-First, we simulate fast-rotating stars, modelling them as oblate spheroids with varying radii and an oblateness ranging between 0.5 and 1.
-We also consider different viewing angles, assuming a linear dependence for the effect of gravity darkening.
-The traced ellipses result from integrating over the source's hour angle.
+First, we \st{simulate} \textcolor{blue}{generate fictitious images of} fast-rotating stars, modelling them as oblate spheroids with varying radii and an oblateness ranging between 0.5 and 1.
+We also consider different viewing angles, assuming a linear dependence \textcolor{blue}{on declination angle on the stellar surface for generating} the effect of gravity darkening.
+\st{The traced ellipses result from integrating over the source's hour angle.
 For hyperparameter tuning and comparing different telescopes, the total observing duration is set to approximately 11.5 hours.
-Finally, the ellipses are plotted, converted into grayscale images, resized, and stored as raw arrays to facilitate further analysis.
+Finally, the ellipses are plotted, converted into grayscale images, resized, and stored as raw arrays to facilitate further analysis.}
 
-Next, Salt and Pepper noise is introduced usually at a rate of 0.5\%.
+Next, Salt and Pepper noise is introduced \textcolor{blue}{into these images}; usually this is done at the rate of 0.5\% \textcolor{blue}{of the number of pixels in the image}.
 Then, the images are resized and their mean is subtracted.
-A two-dimensional Fast Fourier Transform, along with a Fourier shift, is applied, yielding a complex number for each pixel.
-Since II does not measure phase, the absolute value is calculated (as shown in Fig.~\ref{fig:ft} on both linear and logarithmic scales for visualization).
+A two-dimensional Fast Fourier Transform, \st{along with a Fourier shift,} is applied, yielding a complex number for each pixel.
+Since II does not measure phase, the absolute value is calculated.
+%\st{(as shown in Fig.~\ref{fig:ft} on both linear and logarithmic scales for visualization)}.
 
-Next, sparse sampling is introduced via pixel-wise multiplication between the absolute-valued Fourier-transformed image (Fig.~\ref{fig:ft}) and the sparse sampling map (Fig.~\ref{fig:base}).
+\textcolor{magenta}{\textbf{Question to discuss: Why are we calculating FFT of the images???
+These images are by themselves the Fourier Transform of the sky image of the source.
+What do we obtain by calculating their FFT???}}
+
+Next, \st{sparse} sampling \textcolor{blue}{of the interferometric plane} is introduced via pixel-wise multiplication of the absolute-valued Fourier-transformed image (left panel of Fig.~\ref{fig:ft}) and the \st{sparse sampling map} \textcolor{blue}{baseline tracks of} (Fig.~\ref{fig:base}) \textcolor{blue}{generated by the four IACTs due to Earth rotation during the II observation}.
 The result is a map in the Fourier plane featuring several ellipses, which is also referred to as the sparse sampling map (right panel of fig.~\ref{fig:ft}).
-This map represents the sparse sampling of the signal space (Fig.~\ref{fig:ft}) corresponding to the source (Fig.~\ref{fig:image}) observed with four telescopes (Fig.~\ref{fig:teles}).
+This map represents the sparse sampling of the signal space
+%\st{(Fig.~\ref{fig:ft})} 
+corresponding to the source (Fig.~\ref{fig:image}) observed with four telescopes (Fig.~\ref{fig:teles}).
+\textcolor{blue}{In essence, the right panel of fig.~\ref{fig:ft} represents the result of simulated II observation of the fictitious fast-rotator illustrated in fig.~\ref{fig:image}.}
 
-Finally, the pixels are normalized and converted to 8-bit integers.
-This image represents the sparsely sampled phaseless visibility as it can be measured with II.
+\iffalse
+\st{Finally, the pixels are normalized and converted to 8-bit integers.
+This image represents the sparsely sampled phaseless visibility as \st{it can be} measured with II.
 The image shown in right panel of fig.~\ref{fig:ft} serves as the input for the GAN, which also requires the corresponding ground truth image.
@@
 The GAN must have access to the ground truth corresponding to each input image; therefore, the input and ground truth images are merged side-by-side (as shown in Fig.~\ref{fig:GANinput}) and used to train the GAN.
-This procedure is applied to all simulated stars, with 10\% used as test data, 10\% as validation data, and the remaining 80\% as training data.
+This procedure is applied to all simulated stars, with 10\% used as test data, 10\% as validation data, and the remaining 80\% as training data.}
+\fi
+
+\textcolor{blue}{Finally, we normalize the pixel values and convert them to 8-bit integers, producing an image that encodes the sparsely sampled, phase-free visibility measured by II.
+The image of the corresponding simulated (fictitious) star, which serves as the ``ground truth'' is processed identically to avoid any bias.
+These two images are merged side-by-side into a single
+image (as shown in Fig.~\ref{fig:GANinput}). The dataset thus created is split into three parts in the proportions of 80\% for training, 10\% for validation, and 10\% as a held-out test set.}
 
 \subsection{GAN Architecture}
-The GAN used in this work is based on pix2pix, which utilizes a conditional GAN (cGAN) as discussed in the previous section \citep{isola2017image}.
-This architecture is highly robust and has already been applied to various problems.
+\textcolor{blue}{The GAN architecture used in this work is a Pix2Pix cGAN, which uses an image-to-image translation strategy with both the ground truth and the condition being images.
+Originally introduced by Isola et al.
+\cite{isola2017image}, this architecture is specifically suitable for image processing and reconstruction objectives.
 For instance, the TensorFlow tutorials\footnote{\url{https://www.tensorflow.org/tutorials/generative/pix2pix}} demonstrate its application to a dataset of architectural facades.
-However, to adapt the pix2pix GAN for the phase retrieval problem, some modifications are necessary.
-The network is implemented using the TensorFlow library \citep{abadi2016tensorflow}, calculations are performed with scipy \citep{virtanen2020scipy}, and plots are generated with matplotlib \citep{4160265}.
+This architecture has been adapted
+for the phase retrieval problem at hand here \st{, some modifications are necessary}.
+The network is implemented using the TensorFlow library \citep{abadi2016tensorflow}, calculations are performed with scipy \citep{virtanen2020scipy}, and plots are generated with matplotlib \citep{4160265}.}
 
 \subsection{Hyperparameter Tuning}
-The GAN used in this work depends on several parameters, which are explained briefly below \citep[for a more in-depth discussion, see][]{murphy2022probabilistic}.
+The cGAN model architecture used in this work employs several hyper-parameters, which are explained briefly below \citep[for a more in-depth discussion, see][]{murphy2022probabilistic}.
 
@@
 When training GANs, one strategy to potentially boost performance is to give the Discriminator an advantage by increasing its number of training steps before returning to the Generator's training.
-While this can lower the Discriminator loss, as shown in Fig.~\ref{fig:Plot_discrep_loss}, it also increases training time and leads to a slight rise in the Generator loss.
-Since the generated images do not noticeably improve with additional Discriminator training, both networks are typically trained with the same number of steps.
+While this can lower the Discriminator loss, as shown in Fig.~\ref{fig:Plot_discrep_loss}, it also increases training time \st{and leads to a slight rise in the Generator loss}.
+\textcolor{blue}{In training our model, we did not notice any significant advantage derived from this strategy.
+Since the generated images do not noticeably improve with additional Discriminator training, both networks are \st{typically} trained with the same number of steps.}
 
-Finally, the degree of sparse sampling can be varied to provide the model with access to more pixels.
+Finally, the degree of sparse sampling can be varied to provide the model with access to more \textcolor{blue}{active (mon-zero)} pixels.
 Increasing the number of telescopes results in more baselines and, consequently, more available pixels.
 Fig.~\ref{fig:Plot_telescopes_loss} shows the loss functions for different numbers of telescopes.
-There is a significant disparity in performance, partly because the relationship between telescopes and baselines is not linear.
-For example, the Fourier plane can be sampled along six tracks when using four telescopes, as compared to only one track if using only two telescopes.
+There is a significant disparity in performance: \textcolor{blue}{at ``Nash point'', both the loss functions are minimized for the case of four telescopes.
+This is partly because the relationship between telescopes and baselines is quadratic: the coverage of the Fourier plane of Intensity Interferometry (II) scales as square of the number of telescopes employed in the II observation.} For example, the Fourier plane can be sampled along six tracks when using four telescopes, as compared to only one track if using only two telescopes.
 In the case of two telescopes, both the Generator and Discriminator exhibit less smooth training, as indicated by the outliers.
@@
 
+\iffalse
 The process to train the model is summarized here:
-\iffalse
 \begin{figure*}[htbp]
@@
 \end{figure*}
+
 \fi
@@
 \end{figure}
-\fi
 
@@
 %\end{document}
+
+\fi

### 2025-11-27 Phase_II/draft/Result.tex
Edit of GAN drat completed by SS

@@
-\section{Images Reconstructed by the GAN}
-In this section, we begin by discussing phase retrieval using hyperparameters, as mentioned earlier, followed by an analysis in which multiple sources are trained simultaneously.
+\section{\texorpdfstring{\textcolor{blue}{Image Reconstruction: Results and Evaluation}}
+                      {Image Reconstruction: Results and Evaluation}}
+
+%section{\textcolor{blue}{Image Reconstruction: Results and Evaluation}}
+%\section{\st{Images Reconstructed by the GAN}\textcolor{blue}{Image Reconstruction: Results and Evaluation}}
+
+In this section, \textcolor{blue}{we discuss the results of phase retrieval and image reconstruction by our cGAN model followed by an analysis of these results using moments.
+The hyperparameter values that produce the best performance in our cGAN  model are tabulated in Table~\ref{tab:hyperparameters}}.
+
+\iffalse
+\st{In this section, we begin by discussing ......in which multiple sources are trained simultaneously.
 The best performance for image reconstruction has been observed with a learning rate of \(2 \cdot 10^{-4}\), a kernel size of 5×5, and equal noise percentages (alpha/beta = 1) applied to both the original and generated images.
-A batch size of 1 is used, and equal training is provided to both the Discriminator and the Generator.
+A batch size of 1 is used, and equal training is provided to both the Discriminator and the Generator.}
+\fi
 
-\subsection{Predicted Image from the Trained GAN}
-Fig.~\ref{fig:GAN} demonstrates the success of the GAN in training a model to reconstruct the images of  fast-rotating stars using their Intensity Interferometry (II) observation .
+\subsection{Predicted Image from the Trained cGAN}
+Fig.~\ref{fig:GAN} demonstrates the success of the trained cGAN model \st{in training a model} in reconstructing the images of  fast-rotating stars using their Intensity Interferometry (II) observation .
 The GAN was trained on the training datasets for 100,000 steps and subsequently tested on various validation datasets to produce predicted images of the stars.
@@
 In Fig.~\ref{fig:GAN}, four combined images illustrate the GAN's performance in reconstructing the stars' shape, size, and brightness distribution using II.
+
+\textcolor{blue}{The four panels from left to right in each row of Fig.~\ref{fig:GAN} represent the following:}
 \begin{itemize}
-\item{The left panel shows the signals collected from six baselines, which serve as the input for the Generator during training.}
-\item{The first middle panel displays the real image, or ground truth, which the Disciminator loss function uses to distinguish from the images generated by the Generator.
-During training, the GAN aims to keep minimum difference between these ground truth image and generated images.}
-\item{The second middle panel presents the reconstructed, or predicted, image produced by the trained GAN, highlighting its success in image reconstruction.}
-\item{The right panel shows the difference between the ground truth and the predicted image in the interferometric plane.
-The uniform background color of the frames suggests that the GAN model picks up white noise in the interferometric plane.}
+\iffalse
+\st{\item{The left panel shows the signals collected from six baselines, which serve as the input for the Generator during training.}}
+\fi
+\item{\textcolor{blue}{The left panel represents the sparse II pattern obtained by the simulated observation using the four IACTs illustrated in Fig.\ref{fig:teles}.
+As explained earlier, this image acts as part of the input, namely its ``condition'' part.
+This image acts as the condition that the sky-images of the star generated by the Generator must conform to.}}
+
+\item{The second panel from left displays the real image, or ground truth, which the Disciminator loss function uses to distinguish from the images generated by the Generator.
+During training, the GAN aims to keep minimum difference between these ground truth image and generated images.
+\textcolor{blue}{The data generated for training, validation and testing of the cGAN model is a merge of this image and its II pattern presented in the left panel.
+}}
+
+\item{The third panel from left presents the reconstructed, or predicted, image produced by the trained GAN, highlighting its success in image reconstruction.}
+
+\item{\textbf{\textcolor{magenta}{Check if correct: The right panel shows the difference between the ground truth and the predicted image in the interferometric plane.
+The uniform background color of the frames suggests that the GAN model picks up white noise in the interferometric plane.
+I also think that axis labels need to be provided.}}}
 \end{itemize}
-The predicted images in Fig.~\ref{fig:GAN} yield encouraging results, accurately conveying visual information about the source's size, shape, and brightness distribution across its surface using only six baselines.
-However, further improvements can be achieved by increasing the number of telescopes to maximize coverage of the $(u, v)$ plane, making the existing and upcoming CTAO an ideal candidate for this approach.
+
+%\iffalse
+
+The predicted images \textcolor{blue}{presented in the third column (from left) of Fig.~\ref{fig:GAN} show} encouraging results, \st{accurately} conveying visual information about the source's size, shape, and brightness distribution across its surface \textcolor{blue}{fairly accurately.
+This has been achieved on the basis of the input provided by II observtion} using only six baselines.
+\st{However,} \textcolor{blue}{Arguably,} further improvements can be achieved by increasing the number of telescopes to maximize coverage of the $(u, v)$ plane.
+\textcolor{blue}{A closer examination of this proposition might be able to contribute to the design and instrumentation aspects in the existing and upcoming CTAO.} \st{an ideal candidate for this approach.}
+
+%\fi
 
@@
 	\includegraphics[width=.32\linewidth]{fig/moments/mom2.png}\hfil 
+\iffalse
 	\caption{This set of figures shows the comparison of monopole, x-centroid, and y-centroid for ground truth and predicted images generated by trained GAN.
-The monopole shows the linear nature, which indicate that as the parameters of ellipsoid will change, the flux (monopole) also change accordingly.
-Clustering nature around the value of 63 for both x and y centroid show the spatial center of mass of the stellar objects.}
+The monopole shows \textcolor{blue}{an approximate} linear nature, which indicate \textcolor{blue}{a correlation between the parameters of the ellipsoids and the flux (monopole) moment.} \st{that as the parameters of ellipsoid will change, the flux (monopole) also change accordingly.}\textcolor{magenta}{\textbf{Unclear statement: Clustering nature around the value of 63 for both x and y centroid show the spatial center of mass of the stellar objects.}}}
+\fi
+\caption{This set of figures shows the comparison of monopole, x-centroid, and y-centroid for ground truth and predicted images generated by trained GAN.
+The monopole shows \textcolor{blue}{an approximate} linear nature, which indicate \textcolor{blue}{a correlation between the parameters of the ellipsoids and the flux (monopole) moment.}\textcolor{magenta}{\textbf{Unclear statement: Clustering nature around the value of 63 for both x and y centroid show the spatial center of mass of the stellar objects.}}}
 	\label{fig:cen}
 \end{figure*}
+
 \subsection{Evaluation of GAN using Moments}
@@
 \end{equation}
-The left figure of Fig.~\ref{fig:cen} displays the monopole values for 100 reconstructed images.
-The plot reveals a linear relationship between the monopole of the ground truth (real image) on the $x$-axis and that of the predicted (reconstructed) image on the $y$-axis, consistent across sources of varying shapes and sizes.
+The left panel of Fig.~\ref{fig:cen} displays the monopole values for 100 reconstructed images.
+The plot reveals \textcolor{blue}{an approximate} linear relationship between the monopole of the ground truth (real image) on the $x$-axis and that of the predicted (reconstructed) image on the $y$-axis, consistent across sources of varying shapes and sizes.
 This linearity confirms that the predicted images have an overall intensity (flux) that closely matches the ground truth.
@@
 
-The center of mass of the sky image of any stellar object, is determined by its centroid, which provides the $x$ and $y$ coordinates representing the spatial position of the image.
+The ``center of mass'' of the sky image of any stellar object, is determined by its centroid, which provides the $x$ and $y$ coordinates representing the spatial position of the image.
 This centroid is computed using the first-order raw moments in conjunction with the monopole (the zeroth-order moment).
@@
 Here, \(I(x,y)\) represents the intensity at pixel \((x,y)\), \(M_{00}\) is the monopole (total intensity), and \(M_{10}\) and \(M_{01}\) are the first-order raw moments along the $x$ and $y$ axes respectively.
-This formulation accurately captures the spatial center of mass of the stellar object in the image.
+This formulation \st{accurately} captures the spatial ``center of mass'' of the stellar object in the image.
 
@@
 These have been shown here for ground truth and predicted images generated by the trained GAN.
-It is very clear that these moments show the linear nature.}
+\st{It is very clear that these moments show the linear nature.}\textcolor{blue}{The indicative approximate linear relation arguably points towards a close correlation between the predicted and the ground truth images.}}
 	\label{fig:struc}
@@
 However, $\mu_{30}$, and $\mu_{12}$ show the clustering nature, which says that skewness is preserved but not perfectly.
-This aim can be achieved by increasing th enumbe rof telescopes on observational plane.}
+This aim can be achieved by increasing the number of telescopes on observational plane.}
   \label{fig:moments}
@@
 Fig.~\ref{fig:struc} presents the second-order central moments (\(\mu_{11}, \mu_{20}, \mu_{02}\)), which are used to study the structure of a fast-rotating star along the line of sight (as explained in the upcoming subsection).
-All three plots demonstrate a linear relationship in the second-order moments, similar to the monopole, thereby confirming the success of applying the GAN to reconstruct images with II.
+All three plots demonstrate \textcolor{blue}{an approximately} linear relationship in the second-order moments, similar to the monopole, thereby confirming the success of applying the GAN to reconstruct images with II.
 

### 2025-11-27 Phase_II/draft/conclusion.tex
Edit of GAN drat completed by SS

@@
 Intensity Interferometry (II) is re-emerging as a promising technique to overcome the challenges of very long baseline interferometry in the optical wavelength range.
-However, compared to radio-interferometry, optical interferometry faces an important hurdle: photon correlation captures only the magnitude of the interferometric signal, resulting in a loss of phase information.
+However, compared to radio-interferometry, optical interferometry faces a major hurdle: photon correlation captures only the magnitude of the interferometric signal, resulting in a loss of phase information.
 
 This work addresses the challenge of phase retrieval in II using a machine-learning technique, specifically a conditional Generative Adversarial Network (cGAN).
-Our study demonstrates that applying a cGAN to II data successfully recovers the size, shape, and brightness distribution of a fast-rotating star.
-Evaluations based on image moments—specifically, the monopole, second, and third-order moments—support the effectiveness of cGAN in achieving accurate image reconstruction from a simulation of II from a single site with four telescopes.
+Our study demonstrates \st{that applying a cGAN to II data successfully recovers the size, shape, and brightness distribution of a fast-rotating star.}  \textcolor{blue}{that the size, shape and brightness distribution of fast rotating stars can be recovered by a cGAN trained on the combined input of the sky-image of known sources  along with their respective II data.
+In this training the sky-image acts as the real ``ground truth'' and the II data acts as the ``condition''.
+The Discriminator of the cGAN model is trained to efficiently distinguish between the real images and fake (generated) images based on the ``ground truth'' images and the respective II data condition.
+The Generator is trained to generate progressively realistic images which are also consistent with the condition of the II data.
+The evaluation of the trained model is then carried out} \st{Evaluations based on} \textcolor{blue}{by comparison of image moments of real images and generated images.} Specifically, the monopole, second, and third-order moments \textcolor{blue}{are compared.
+The results} support the effectiveness of cGAN in achieving \textcolor{blue}{the stated objective.} \st{accurate image reconstruction from a simulation of II from a single site with four telescopes.}
 
-While the results of this study highlight the significant potential of machine learning, and in particular cGAN, for image reconstruction in II, several aspects require further refinement.
+While the results of this study highlight the significant potential of machine learning, and in particular the applicability of cGAN, for image reconstruction in II, several aspects require further refinement.
 First, an important factor in the reconstruction process is the extent of Fourier plane coverage, which depends on the number of available telescopes and the total observing time.
-With more than four telescopes, more complicated systems could be reconstructed.
+The reasonable success of this piece of work suggests that a network of higher number of telescopes providing higher number of baselines and greater coverage of the $(u,v)$ plane signal, \textcolor{blue}{would play a critical role in} projects of image reconstruction of more complicated stellar systems can be undertaken.
 Future work might explore different observatory layouts to assess their impact on image reconstruction quality.
@@
 Third, exploring and comparing alternative methods for image generation could reveal approaches that outperform cGAN in reconstructing stellar images with II.
-Fourth, experimenting with different loss functions could provide additional insights into reconstruction quality.
+Fourth, experimenting with different loss functions could provide additional insights into the reconstruction quality.
 Although further testing is needed to refine the GAN and enhance its robustness and reliability, our findings suggest that machine learning is a promising approach for phase reconstruction in II.

### 2025-11-27 Phase_II/draft/intro_reformatted.tex
Edit of GAN drat completed by SS

@@
 \section{Introduction}
-Humans instinctively feels a relationship with the stars.
+Humans instinctively feel a relationship with the stars.
 One of the primary scientific projects of humanity is to figure out what the stars are and how do they do what they do.
@@
 A discussion of the development of these two approaches and comparison of their respective merits and challenges can be found in \citep{Rai2025}.
-The work reported here presents the results of a first effort at applying a Conditional Generative Adversarial (neural) Network (C-GAN) to image reconstruction of a fast rotator using its simulated II observations.
+The work reported here presents the results of a first effort at applying a Conditional Generative Adversarial (neural) Network (cGAN) to image reconstruction of a fast rotator using its simulated II observations.
 
@@
 
-We report here, the results of our attempt, the first of its kind, to reconstruct the II-simulated gravity-darkened images of fast rotating stars using a C-GAN neural network architecture.
+We report here, the results of our attempt -- the first of its kind -- to construct the gravity-darkened sky-image of fast rotating stars consistent with their respective simulated ground-based II-observations using a cGAN neural network architecture.
 Image reconstruction in gravity darkened fast rotating stars has long been examined using various methods in MI \citep{vanBelle2001, DomicianodeSouza2003, DomicianodeSouza2005, mcalister2005first, Monnier2007, Pedretti2009, Zhao2009, Martinez2021}.
@@
 These results, and especially, that by \cite{Archer-arXiv-2025} put our work in context.
-Thus our simulation is a natural next step of the work of Archer et al and others.
-We emulate the C-GAN model \cite{isola2017image} to reconstruct images of fast-rotating stars using their simulated Intensity Interferograms and simulated sky-intensity distributions as input data for training, testing, and validation.
-We consider an array of four Imaging Cherenkov Telescopes (IACTs) and simulate observation of a fast-rotating star.
-The image predicted by the trained C-GAN shows promising results in reconstructing the star’s shape and size.
+Thus our work presented here is a natural next step of the work of Archer et al and others.
+We emulate the cGAN model \cite{isola2017image} to reconstruct images of fast-rotating stars using their simulated Intensity Interferograms and sky-intensity distributions as input data for training, testing, and validation.
+We consider an array of four Imaging Cherenkov Telescopes (IACTs) whose relative positions approximately mimic those at VERITAS and simulate observations of a set of synthetically generated fast-rotating stars.
+The image predicted by the trained cGAN shows promising results in reconstructing the stars' shapes and sizes.
 The reconstructed brightness distributions are then assessed using moments.
@@
 The next section discusses briefly the past efforts at image reconstruction on II, followed by the section on a discussion of Intensity Interferometry, focusing on its signal and noise characteristics for fast-rotating stars along the Earth’s rotation.
-The following section introduces the C-GAN formulation and its structure.
+The following section introduces the cGAN formulation and its structure.
 The fifth section details the parameter selection for training the network for image reconstruction.
@@
 	\includegraphics[width=\linewidth]{fig/telescope.png}
-	\caption{A schematic representation of {\textcolor{blue}{a hypothetical observation facility with an the array of four Cherenkov Telescopes (IACTs).
+	\caption{A schematic representation of {\textcolor{blue}{a hypothetical observation facility with an the array of four Cherenkov Telescopes (IACTs) whose relative positions approximately mimic those at VERITAS.
 This array is used in simulating the Intensity Interferometry (II) observation of the fast rotators.}} Each of the telescopes has a diameter of 12m.

### 2025-11-27 Phase_II/draft/main.tex
Edit of GAN drat completed by SS

@@
 \usepackage{xcolor}
-\usepackage[normalem]{ulem}
+%\usepackage[normalem]{ulem}
+\usepackage{soul}
 \usepackage{hyperref}
@@
 }
+
+\definecolor{BLUE}{named}{blue}
 
@@
 This paper explores the application of a conditional Generative Adversarial Network (cGAN) to tackle the problem of image reconstruction in II.
-This approach successfully reconstructs the shape, size, and brightness distribution of a fast-rotating star from sparsely sampled, spatial power spectrum of the source, corresponding to II with four telescopes.
-Although this particular example could also be addressed using parameter fitting, the results suggest that with larger arrays much more complicated systems could be reconstructed by applying machine-learning techniques to II.
+\textcolor{blue}{This method successfully reconstructs the shape, size, and brightness distribution of simulated, fast-rotating stars based on a sparsely sampled spatial power spectrum obtained from a hypothetical ground-based II facility composed of four Imaging Atmospheric Cherenkov Telescopes (IACTs).}  Although this particular example could also be addressed using parameter fitting, the results suggest that with larger arrays much more complicated systems could be reconstructed by applying machine-learning techniques to II.
 \end{abstract}

### 2025-12-06 Phase_II/code/generate_moment.py
moment

@@ -17,7 +17,7 @@ pr_img = "testing_image/testing_image_1/"
 data_path = os.path.join(pr_img, "image_*_prediction.npy")
 files2 = glob.glob(data_path)
 files2.sort(key=lambda x: [int(c) if c.isdigit() else c for c in re.split(r'(\d+)', x)])  # Natural sort by numeric part
-
+print(gr_img)
 ground_img = []
 pred_img = []
 # Loop over both lists together
@@ -30,8 +30,7 @@ for f1, f2 in zip(files1, files2):
 # Convert lists to arrays
 gr_img = np.array(ground_img)
 pr_img = np.array(pred_img)
-print(gr_img.shape)
-
+print('gr', gr_img.shape)
 plt.rcParams.update({'font.size': 12})
 plt.rcParams["figure.figsize"] = [6,6]
 plt.rcParams['axes.facecolor']='ivory'
@@ -42,16 +41,21 @@ plt.rcParams["axes.labelweight"] = "bold"
 list_g = []
 list_p = []
 for i in range(len(gr_img)):
+    print('gr', gr_img.shape)
     im_g = gr_img[i].squeeze()   # (128,128)
     im_p = pr_img[i].squeeze()   # (128,128)
+    print('im_gr', im_g.shape)
     list_g.append(md.mom_def(im_g))
     list_p.append(md.mom_def(im_p))
+    
+list_g = list_g
 
 Mth_g = []
 Mth_p = []
 m_name = ['Monopole', 'X-Centroid', 'Y-Centroid', '2nd Moment $\mu_{11}$', 
           '2nd Moment $\mu_{20}$', '2nd Moment $\mu_{02}$', '3rd Moment $\mu_{30}$', 
           '3rd Moment $\mu_{03}$','3rd Moment $\mu_{21}$', '3rd Moment $\mu_{12}$']
+'''
 pic = 0
 for i in range(len(list_g[0])):
     Mth_g = [M[i] for M in list_g]
@@ -69,3 +73,4 @@ for i in range(len(list_g[0])):
     #plt.show()
     plt.clf()
     pic += 1 
+'''

### 2025-12-06 Phase_II/draft/GAN_NoRed.tex
GAN manuscript reviewed and edited

--- 2025-11-20 Phase_II/draft/GAN.tex
@@
 \section{Generative Adversarial Networks}
+\begin{figure}
+\centering
+\includegraphics[scale=0.4]{FlowDiagram_TikZ.pdf}
+\caption{\textcolor{blue}{A schematic representation of the features of a cGAN model used in this work and the iterative process of its training, validation and testing.
+The process constitutes four broad stages: (1) choice of an appropriate GAN architecture including both the Discriminator and the Generator (not shown in this figure) (2) preparation of the Training, Validation and Testing datasets and (3) Training and Validation of the Model (4) Testing and Evaluation of the Model.
+The stages (2), (3) and (4) are depicted in this figure.
+The datasets are prepared
+in three broad steps: (i) generating the ``ground truth'' images of fictitious fast-rotators $x$, the sparse II images $y$ used as the ``condition'' images in the Model and the generated images $z$ sampled from a Normal Distribution (ii)merging these images into individual files with $(x|y)$ and/ or $(z|y)$ (as seen in an illustrated sample in Fig.(\ref{fig:GANinput})) and generating the full dataset in this process, and finally (iii) partitioning the full dataset into Training Set, Validation Set and the Testing Set.
+After the iterative training of the Model and its validation process is complete (``Nash point'' of the Minimax Game is reached), the Model is tested using the Testing Set and evaluated.}}
+\label{fig:FlowDiagram}
+\end{figure}
+
 \begin{figure}
@@
 		V(D, G) &= \mathbb{E}_{x,y \sim p_{\rm data}(x)} \left[ \log D(x|y) \right] \\
-		&+ \mathbb{E}_{z,y\sim p_{z}(z)} \left[ \log \left( 1-D(G(z|y) \right) \right]
+		&+ \mathbb{E}_{z,y\sim p_{z}(z)} \left[ \log \left( 1-D(G(z|y)|y )\right) \right]
 	\end{aligned}
@@
 \end{equation}
-In our work, we specifically use this conditioning mechanism by choosing \(y\) to represent the ground-based intensity-interferometry (II) observation patterns: the Generator is trained to produce stellar surface images that not only look realistic but also conform to the measured II correlations, while the Discriminator judges realism \emph{and} consistency with the II data.
-
-\iffalse 
-During each training session of the Discriminator, it is presented with a series of real images (as seen in Fig.
-(\ref{fig:GANinput}) and generated images taken in equal proportion.
-During the initial phases of its training, as the generated images are sampled from random distribution, the Discriminator finds it easy to distinguish between the real and the generated images.
-This produces a sharp initial dip in the Discriminator loss function.
-On the other hand, the Generator loss function, during the initial phases of its training is high due to the poor quality of its generated images.
-Through the process of alternating training sessions, the Generator gradually learns to do better: generate images which resemble the real images ever more closely.
-As seen in fig.
-(\ref{fig:Plot_discrep_loss}), with further training of both the networks, the Generator loss is gradually minimized and the generated images become gradually indistinguishable from the real images.
-The Discriminator loss, on the other hand, increases from the minimum of the initial phases of training and gradually  saturates to a value halfway between its maximum and minimum values, as expected in the case of a binary classifier.}
-\fi
+\textcolor{blue}{The conditional variable $y$ in a cGAN can be various additional information including images, labels or text contextual to ``ground truth'' real data $x$.
+Among various types of cGANs, Pix2Pix GAN with its image-to-image translation design is suitable for the task at hand.
+In our work, we specifically use this conditional variable by choosing \(y\) to represent the ground-based intensity-interferometry (II) observation patterns: the Generator is trained to produce stellar surface images that not only look realistic but also conform to the measured II correlations, while the Discriminator judges realism \emph{and} consistency with the II data.}
 
 \cite{isola2017image} further observed that combining the cGAN from Eq.~\eqref{eq:conditional_GAN} with the traditional $L_1(G)$ loss \textcolor{blue}{(also known  as the Mean Absolute Error) improves the results, as the Generator is encouraged to produce outputs closer to the target image in a pixel-wise sense.
-We adopt this approach in the training of our cGAN model by including $L_1(G)$ along with the hyperparameter $\lambda =100$.
-The total loss function that is minimized is}:
+We adopt this approach in the training of our cGAN model by including $L_1(G)$ defined in eq.(\ref{eq:l1_loss})}
 \begin{equation}
 	\centering
-	L_{tot} = \arg \min_{G} \max_{D} V(D, G) + \lambda \cdot L_1(G)
+	L_1(G) = \mathbb{E}_{x \sim p_{\mathrm{data}, z \sim p_z(z)}} \bigl[ \lVert x - G(z \mid y) \rVert_{1} \bigr].
+	\label{eq:l1_loss}
+\end{equation}
+The total adversarial loss function, along with the $L_1$ loss modulated by a hyperparameter $\lambda$ then becomes
+\begin{equation}
+	\centering
+	L_{tot} = \arg \min_{G} \max_{D} V(D, G) + \lambda \cdot L_1(G).
 	\label{eq:total_gen_loss}
 \end{equation}
-with the choice $\lambda = 100$ and
-\begin{equation}
-	\centering
-	L_1(G) = \mathbb{E}_{x,y,z} \left[ ||{y - G(x,z)}||_1 \right]
-	\label{eq:l1_loss}
-\end{equation}
+
 This type of network has demonstrated remarkable robustness across a variety of applications.
@@
 
-After generating images, the Generator aims to deceive the Discriminator into classifying the generated images as real.
-The extent to which the Generator succeeds in this deception is quantified by the GAN loss.
-When the Discriminator is unable to distinguish between the generated and real images (i.e., when the GAN loss is minimized), the Generator is considered to have reached an optimal state.
-Conversely, if the generated image fails to fool the Discriminator, the Generator produces a new image for further comparison with the real image.
-Additionally, the Generator's performance is evaluated using another metric known as the L1 loss, which is defined as the mean absolute error between the pixels of the real image and those of the generated image.
-Balancing the minimization of both the GAN loss and the L1 loss enables the Generator to produce images that are not only realistic but also faithful to the input data.
+\textcolor{blue}{During the training, the total Generator Loss function $L_G$ including the $L_1$ loss defined in eq.(\ref{eq:l1_loss}) that is minimized is given by
+\begin{equation}
+\centering
+\begin{aligned}
+L_{G} \; &= \; - \, \mathbb{E}_{z \sim p_{z}(z)} \bigl[ \log D(G(z \mid y)\mid y) \bigr] \\
+& +\; \lambda \; \mathbb{E}_{x \sim p_{\mathrm{data}, z \sim p_z(z)}} \bigl[ \lVert x - G(z \mid y) \rVert_{1} \bigr].  
+\end{aligned}
+\label{eq:total_gen_loss}
+\end{equation}
+Here, 
+\begin{itemize}
+  \item \(x\) denotes a real data sample (e.g.\ the ``ground-truth'' image; here, the synthetically generated fast rotator image) corresponding to condition \(y\), the simulated II observation data.  
+  \item \(z\) is a random latent vector drawn from the prior \(p_z(z)\).  
+  \item \(G(z \mid y)\) is the generator output (the reconstructed / synthesized image) given \(z\) and condition \(y\).  
+  \item \(D(\cdot \mid y)\) is the discriminator’s estimate (probability) that its input is “real,” given the same condition \(y\).  
+  \item \(\lambda\) is a hyperparameter controlling the trade-off between adversarial realism and pixel-wise fidelity (typical values depend on the problem — e.g.\ in pix2pix, \(\lambda = 100\)). 
+\end{itemize}}
 
@@
 \textcolor{blue}{Each element in the grid corresponds to the ``realness'' of one patch of the image under examination of the Discriminator at a time.
-The final loss is of the Discriminator is the average over all the patch responses.
+The final loss of the Discriminator is the average over all the patch responses.
 Evaluating the ``realness'' of the input image in terms of its constituent patches facilitates capture of texture/ style and other high frequency components in the image.
@@
 
-The Discriminator’s architecture begins with an initializer that accepts both the input (generated) images and the corresponding real images.
-Initially, Salt-and-Pepper noise is added to the input images.
+\textcolor{blue}{Prior to the down-sampling of data using PatchGAN, each input image is preprocessed with application of Zero Padding followed by batch normalization.
+The purpose of Zero Padding is to prevent the loss of spatial information and to facilitate the extraction of deeper features from the down-sampled output.
+Batch normalization is required to stabilize the learning (loss minimization) process.
 PatchGAN then reduces the spatial dimensions of the images to extract localized features, ensuring the model focuses on smaller regions.
-In this downsampling stage, a leaky version of the Rectified Linear Unit (LeakyReLU) is applied in the convolutional layers, similar to the approach used in the Generator.
+In this down-sampling stage, a leaky version of the Rectified Linear Unit (LeakyReLU) is applied in the convolutional layers, similar to the approach used in the Generator.
+The probability $D(\cdot|y)$ that the patch of the input image represented by $\cdot$ is ``real'' is evaluated through this process.
+The loss function $D$ of the full input image is obtained by averaging over all the patch responses.}
 
-Subsequently, zero padding is applied, adding rows and columns of zeros around the images to prevent the loss of spatial information during convolution and to facilitate the extraction of deeper features from the downsampled output.
-Following this, batch normalization is employed to stabilize learning by normalizing activations, and the Discriminator begins classifying each patch as real or fake.
-This is followed by additional layers involving LeakyReLU activation, zero padding, and convolution, culminating in a final prediction that is fed to the Generator as feedback.
+\textcolor{blue}{The Discriminator Loss function $L_D$ that is optimized during the training process is given by 
+\begin{equation}
+\centering
+\begin{aligned}
+L_{D} \; &= \; - \, \mathbb{E}_{x \sim p_{\mathrm{data}}(x \mid y)} \bigl[ \log D(x \mid y) \bigr] \\
+& -\; \mathbb{E}_{z \sim p_{z}(z)} \bigl[ \log\bigl( 1 - D(G(z \mid y)\mid y)\bigr) \bigr]
+\end{aligned}
+\end{equation}
+where the arguments of the $D$ and $G$ functions are as noted in the text following eq.(\ref{eq:total_gen_loss}) This loss is composed of two parts: one that assesses how accurately it identifies fake images (by comparing predictions to a target value of 0) and the other that measures how accurately the Discriminator identifies real images (by comparing predictions to a target value of 1).}
 
-The effectiveness of the Discriminator is measured by its ability to distinguish between real and fake images, quantified through the Discriminator loss.
-This loss is composed of two parts: one that measures how accurately the Discriminator identifies real images (by comparing predictions to a target value of 1) and another that assesses how accurately it identifies fake images (by comparing predictions to a target value of 0).
-Together, these loss components ensure that the Discriminator improves its classification performance, which in turn, challenges the Generator to produce increasingly realistic images.
+\textcolor{blue}{The training procedure of these two components of the cGAN model can be outlined as follows:
+\begin{itemize}
+\item{The discriminator \(D\) is updated by minimizing \(L_D\), keeping \(G\) fixed (so that \(D\) becomes better at distinguishing real vs generated images).}  
+\item{The generator \(G\) is updated by minimizing \(L_G\), keeping \(D\) fixed — thus pushing \(G\) to generate images that are (a) judged “real” by \(D\), and (b) close (in pixel-wise sense) to the ground-truth \(x\).}
+\end{itemize}
+}

### 2025-12-06 Phase_II/draft/ParaGAN_NoRed.tex
GAN manuscript reviewed and edited

--- 2025-11-27 Phase_II/draft/ParaGan.tex
@@
 The second panel from left displays the real image, or ground truth, which the Discriminator uses to distinguish from the images generated by the Generator.
-The data generated for training, validation and testing of the cGAN model is a merge of this image and its II pattern presented in the left panel.} The third panel is the reconstructed image, or the predicted image, produced by the trained GAN model .
-\textcolor{red}{The fourth and the last panel is the difference between the ground truth and the predicted image in the $(u,v)$ plane.
-The uniform background color in the difference panel suggests that the network is picking up white noise from the $(u,v)$ plane.} }
+The data generated for training, validation and testing of the cGAN model is a merge of this image and its II pattern presented in the left panel.
+The third panel is the reconstructed image, or the predicted image, produced by the trained GAN model .
+The fourth and the last panel is the difference between the ground truth and the predicted image in the $(u,v)$ plane.}}
 	\label{fig:GAN}
@@
 
-\subsection{Data Preparation}
-First, we \st{simulate} \textcolor{blue}{generate fictitious images of} fast-rotating stars, modelling them as oblate spheroids with varying radii and an oblateness ranging between 0.5 and 1.
-We also consider different viewing angles, assuming a linear dependence \textcolor{blue}{on declination angle on the stellar surface for generating} the effect of gravity darkening.
-\st{The traced ellipses result from integrating over the source's hour angle.
-For hyperparameter tuning and comparing different telescopes, the total observing duration is set to approximately 11.5 hours.
-Finally, the ellipses are plotted, converted into grayscale images, resized, and stored as raw arrays to facilitate further analysis.}
+%\iffalse
+\subsection{Data Preparation}\label{sec:DataPrep}
+First, we \textcolor{blue}{generate synthetic images of} rapidly rotating stars by modelling them as oblate spheroids with varying radii and oblateness parameters between 0.5 and 1.
+To incorporate the effect of gravity darkening, we also consider different viewing angles and assume a linear dependence \textcolor{blue}{on the declination angle of each point on the stellar surface.
+The traced ellipses result from integrating over the source's hour angle.}
 
@@
 Then, the images are resized and their mean is subtracted.
-A two-dimensional Fast Fourier Transform, \st{along with a Fourier shift,} is applied, yielding a complex number for each pixel.
+A two-dimensional Fast Fourier Transform, along with a Fourier shift, is applied, yielding a complex number for each pixel.
 Since II does not measure phase, the absolute value is calculated.
-%\st{(as shown in Fig.~\ref{fig:ft} on both linear and logarithmic scales for visualization)}.
+.
 
-\textcolor{magenta}{\textbf{Question to discuss: Why are we calculating FFT of the images???
-These images are by themselves the Fourier Transform of the sky image of the source.
-What do we obtain by calculating their FFT???}}
-
-Next, \st{sparse} sampling \textcolor{blue}{of the interferometric plane} is introduced via pixel-wise multiplication of the absolute-valued Fourier-transformed image (left panel of Fig.~\ref{fig:ft}) and the \st{sparse sampling map} \textcolor{blue}{baseline tracks of} (Fig.~\ref{fig:base}) \textcolor{blue}{generated by the four IACTs due to Earth rotation during the II observation}.
+Next,  sampling \textcolor{blue}{of the interferometric plane} is introduced via pixel-wise multiplication of the absolute-valued Fourier-transformed image (left panel of Fig.~\ref{fig:ft}) and the \textcolor{blue}{baseline tracks of} (Fig.~\ref{fig:base}) \textcolor{blue}{generated by the four IACTs due to Earth rotation during the II observation}.
 The result is a map in the Fourier plane featuring several ellipses, which is also referred to as the sparse sampling map (right panel of fig.~\ref{fig:ft}).
 This map represents the sparse sampling of the signal space
-%\st{(Fig.~\ref{fig:ft})} 
 corresponding to the source (Fig.~\ref{fig:image}) observed with four telescopes (Fig.~\ref{fig:teles}).
 \textcolor{blue}{In essence, the right panel of fig.~\ref{fig:ft} represents the result of simulated II observation of the fictitious fast-rotator illustrated in fig.~\ref{fig:image}.}
-
-\iffalse
-\st{Finally, the pixels are normalized and converted to 8-bit integers.
-This image represents the sparsely sampled phaseless visibility as \st{it can be} measured with II.
-The image shown in right panel of fig.~\ref{fig:ft} serves as the input for the GAN, which also requires the corresponding ground truth image.
-Consequently, the simulated stars are resized using the same algorithm and converted to 8-bit integers to reduce bias.
-The GAN must have access to the ground truth corresponding to each input image; therefore, the input and ground truth images are merged side-by-side (as shown in Fig.~\ref{fig:GANinput}) and used to train the GAN.
-This procedure is applied to all simulated stars, with 10\% used as test data, 10\% as validation data, and the remaining 80\% as training data.}
-\fi
 
@@
 These two images are merged side-by-side into a single
-image (as shown in Fig.~\ref{fig:GANinput}). The dataset thus created is split into three parts in the proportions of 80\% for training, 10\% for validation, and 10\% as a held-out test set.}
+image (as shown in Fig.~\ref{fig:GANinput}).
+The dataset thus created is split into three parts in the proportions of 80\% for training, 10\% for validation, and 10\% as the test set.
+This partition of the full dataset is indicated in the Fig.\ref{fig:FlowDiagram}.
+In the following, we refer to these three parts as the Training Set, the Validation Set and the Testing Set respectively.}
 
@@
 This architecture has been adapted
-for the phase retrieval problem at hand here \st{, some modifications are necessary}.
+for the phase retrieval problem at hand here.
 The network is implemented using the TensorFlow library \citep{abadi2016tensorflow}, calculations are performed with scipy \citep{virtanen2020scipy}, and plots are generated with matplotlib \citep{4160265}.}
@@
 
-The learning rate of the optimizer determines how much the model updates its parameters with each iteration.
+The learning rate ($lr$) of the optimizer determines how much the model updates its parameters with each iteration.
 A learning rate that is too small may lead to underfitting, while one that is too large can render the model unstable.
 Therefore, selecting an appropriate learning rate is crucial \citep{murphy2022probabilistic}.
+\textcolor{blue}{A canonical choice in Pix2Pix and other GAN models is $lr = 2\times10^{-4}$.
+In our case too, we found this choice to be appropriate.}
 
@@
 A larger kernel size can capture features spanning several pixels, but it may also incorporate unrelated features.
+\textcolor{blue}{Small kernel sizes are preferable in cases where target images finer details or high spatial frequency features.
+Since the ``ground truth'' target images in our case have longer scale gravity darkening features, we have opted for the more canonical choice of kernel size being 5.}
 
@@
 However, because a larger batch size significantly increases training time, a batch size of 1 is used.
+\textcolor{blue}{Besides, in Pix2Pix cGAN implementations found in literature this choice is found to be often preferred.}
 
-When training GANs, one strategy to potentially boost performance is to give the Discriminator an advantage by increasing its number of training steps before returning to the Generator's training.
-While this can lower the Discriminator loss, as shown in Fig.~\ref{fig:Plot_discrep_loss}, it also increases training time \st{and leads to a slight rise in the Generator loss}.
+\textcolor{blue}{Buffer size of a Pix2Pix GAN refers to a small memory of image pool of previously generated images.
+They are occasionally fed to the Discriminator in place of the freshly generated ones.
+This strategy of mixing old and new fakes  mitigates the risk of mode collapse wherein the Discriminator tends to map all or large number of generated images to only one or a few real ``ground truth'' image(s).
+We have chosen a fairly large buffer size (=1400) to protect the model against mode collapse.}
+
+In the training of GANs, one often-followed strategy to potentially boost performance is to give the Discriminator an advantage by increasing its number of training \textcolor{blue}{epochs} before returning to the Generator's training.
+\textcolor{blue}{This hyperparameter is referred to as the Discriminator repetition (as seen in Table \ref{tab:hyperparameters}.} While this can lower the Discriminator loss, as shown in Fig.~\ref{fig:Plot_discrep_loss}, it also increases training time.
 \textcolor{blue}{In training our model, we did not notice any significant advantage derived from this strategy.
-Since the generated images do not noticeably improve with additional Discriminator training, both networks are \st{typically} trained with the same number of steps.}
+Since the generated images did not noticeably improve with additional Discriminator training, we adopted the strategy of}  \textcolor{blue}{training both the networks with equal preference (Discriminator repetition = 1)}.
 
-Finally, the degree of sparse sampling can be varied to provide the model with access to more \textcolor{blue}{active (mon-zero)} pixels.
-Increasing the number of telescopes results in more baselines and, consequently, more available pixels.
-Fig.~\ref{fig:Plot_telescopes_loss} shows the loss functions for different numbers of telescopes.
-There is a significant disparity in performance: \textcolor{blue}{at ``Nash point'', both the loss functions are minimized for the case of four telescopes.
-This is partly because the relationship between telescopes and baselines is quadratic: the coverage of the Fourier plane of Intensity Interferometry (II) scales as square of the number of telescopes employed in the II observation.} For example, the Fourier plane can be sampled along six tracks when using four telescopes, as compared to only one track if using only two telescopes.
-In the case of two telescopes, both the Generator and Discriminator exhibit less smooth training, as indicated by the outliers.
-Performance improves with three telescopes and becomes very promising with four.
-Overall, the degree of sparse sampling appears to have the most pronounced effect of all the hyperparameters.
+\textcolor{blue}{One domain specific hyperparameter of the cGAN model presented here is the Number of Telescopes $N_T$.} The degree of sparse sampling \textcolor{blue}{of the intensity interferometric (II) image plane} can be varied to provide the model with access to more \textcolor{blue}{number of active (non-zero)} pixels.
+\textcolor{blue}{Point to note here, is that the coverage of the Fourier interferometric plane (number of active pixels in the II image) scales with available number of baselines, and the latter scales quadratically with the number of telescopes.
+} Fig.~\ref{fig:Plot_telescopes_loss} shows the loss functions for different numbers of telescopes.
+There is a significant disparity in performance of the model: \textcolor{blue}{at the ``Nash point'', both the loss functions are minimized for the case of four telescopes.} Overall, the degree of sparse sampling appears to have the most pronounced effect of all the hyperparameters.
 
-All the selected hyperparameters to train the model is summarized in the given table:
+\textcolor{blue}{The hyperparameter Output Channels refers to the number of channels in the generator output (e.g., 1 for grayscale, 3 for RGB).
+It is worthwhile to recall that the cGAN model constructed in this work is trained on ``ground truth'' target images and the simulated II data, both in grey scales as seen in Fig.\ref{fig:GANinput}.
+It is natural that the output of this model will be in grey scales only.
+Therefore the value of this hyperparameter is set to 1.
+The choice of hyperparameter \(\lambda\) has been commented upon earlier.}
+
+\textcolor{blue}{An optimized set of hyperparameters is selected through an iterative process of training and validation.
+For a tentatively chosen set of the hyperparameters, the model is trained using the Training Set until the both the Discriminator and the Generator loss functions are minimized.
+This model, thus trained along with its model parameters, is then passed through validation using the Validation Set.
+This cycle of training and validation is iterated till an optimal set of hypermaraters is arrived at.
+During each epoch of training of the model, both the Discriminator and the Generator networks are trained for 100,000 steps.
+Plots of the ''Discriminator Loss'' function and the ``Generator Total Loss'' function presented in Fig.{\ref{fig:Plot_discrep_loss}} and Fig.{\ref{fig:Plot_telescopes_loss} represent the results of this training for two of the hyperparameters, namely, the Disriminator repetition (``discrep'', in short) and the Number of telescopes, respectively}.
+Obviously, the most compute-intensive part of this process is that of the training of the Model.
+The results of training and validation presented in this work were carried out on a CPU using two nodes, each with 96 threads and the entire process of training and validation required approximately 20 hours on the machine employed for this work.
+This iterative process of training and validation of the Model is represented schematically in the Fig.\ref{fig:FlowDiagram}.
+The chosen optimal set of hyperparameters is presented in the table Table-{\ref{tab:hyperparameters}.} }
 \begin{table}[ht]
@@
 		Discriminator repetition  & 1 \\
-		No. of Telescope        & 4 \\
+		Number of Telescope        & 4 \\
 		Output Channels         & 1 \\
@@
 \end{table}
+\textcolor{blue}{This optimized and trained Model is then subjected to testing and evaluation using the Testing Set. The results of this testing and evaluation is presented in the following section.}
 
-\iffalse
-The process to train the model is summarized here:
-\begin{figure*}[htbp]
-	%\centering
-	\begin{center}
-		\begin{tikzpicture}[node distance=0.7cm]
-
-			% Data pipeline
-			\node[block, fill=blue!15] (data) {Ground Truth \\ (Create SS Images of Stellar Objects)};
-			\node[block, fill=red!10, below=of data] (pre) {Simulation \\ (Intensity Interferometry (II) Data)};
-			\node[block, fill=green!20, below=of pre, minimum width=5cm] (split) {Input Dataset (Merge of Ground Truth \\ and Simulation of II) Split \\ (Training, Validation, Testing)};
-
-			% Training, Validation, Testing
-			\node[block, fill=green!15, below left=0.6cm and 1.0cm of split] (train) {Training Set \\ (Learn Model Parameters)};
-			\node[block, fill=green!10, below=of split] (val) {Validation Set \\ (Tune Hyperparameters)};
-			\node[block, fill=green!05, below right=0.6cm and 1.0cm of split] (test) {Testing Set \\ (Final Evaluation)};
-
-			% Model training block
-			\node[block, fill=orange!20, below= 1.0cm of val, minimum width=10cm, minimum height=1.2cm] (mod) {Train the Model \\ (Generator + Discriminator)};
-
-			% Generator side (left)
-			\node[block, fill=yellow!15, below=2.2cm of mod, xshift=-3.5cm] (noise) {Random Noise $z$};
-			\node[block, fill=blue!10, below=of noise] (gen) {Generated Image $\hat{x}$};
-			\node[block, fill=purple!20, below=of gen] (gloss) {Generator Loss \\ (Update $G$)};
-
-			% Discriminator side (right)
-			\node[block, fill=yellow!20, below=2.2cm of mod, xshift=+3.5cm] (real) {Real Image \\ (From Training Set)};
-			\node[block, fill=orange!20, below=of real] (disc) {Discriminator $D(x)$};
-			\node[block, fill=red!20, below=of disc] (out) {Discriminator Output};
-			\node[block, fill=purple!30, below=of out] (dloss) {Discriminator Loss \\ (Update $D$)};
-
-			% Final result block
-			\node[block, fill=teal!20, below= 3cm of val, minimum width=5cm] (res) {Result / Evaluation \\ (Performance Metrics: Accuracy)};
-
-			% Connections
-			\draw[arrow] (data) -- (pre);
-			\draw[arrow] (pre) -- (split);
-			%\draw[arrow] (split.south west) |- (train.north);
-			\draw[arrow] (split.west) -| (train.north);
-			\draw[arrow] (split.south) -- (val.north);
-			\draw[arrow] (split.east) -| (test.north);
-			\draw[arrow] (train.south) -- (mod.north);
-
-			%Newly Introduced Connections (S Sarangi)
-			\draw[arrow] (val.south) -- (mod.north);
-			\draw[arrow] (mod.south) -- (res.north);
-
-			% GAN arrows
-			\draw[arrow] (mod.south) -- (noise.north);
-			\draw[arrow] (mod.south) -- (real.north);
-			\draw[arrow] (noise.south) -- (gen.north);
-			\draw[arrow] (gen.south) -- (gloss.north);
-			\draw[arrow] (real.south) -- (disc.north);
-			\draw[arrow] (gen.east) -- ++(0.5,0) |- (disc.west);
-			\draw[arrow] (disc.south) -- (out.north);
-			\draw[arrow] (out.south) -- (dloss.north);
-
-			% Validation & Testing to Result
-			%\draw[arrow] (val.south) -- (res.north);
-			\draw[arrow] (test.south) -- (res.north);
-
-		\end{tikzpicture}
-	\end{center}
-\caption{A block diagram for the process of image reconstruction through GAN.}
-\end{figure*}
-
-\fi
-
-\iffalse
-\documentclass{article}
-\usepackage{tikz}
-\usetikzlibrary{arrows, arrows.meta, positioning}
-
-\tikzset{
-  block/.style = {draw, rectangle, minimum height=1.5em, minimum width=3em, align=center},
-  arrow/.style = {->, thick},
-}
-
-%\begin{document}
-\fi
-
-\iffalse
-\begin{figure}[htbp]
-\centering
-\begin{tikzpicture}[node distance=0.9cm]
-%\begin{tikzpicure}[scale = 0.5]
-
-% Data pipeline
-\node[block, fill=blue!15] (data) {Ground Truth \\ (Create SS Images of Stellar Objects)};
-\node[block, fill=red!10, below=of data] (pre) {Simulation \\ (Intensity Interferometry (II) Data)};
-\node[block, fill=green!20, below=of pre, minimum width=5cm] (split) {Input Dataset (Merge of Ground Truth \\ and Simulation of II) Split \\ (Training, Validation, Testing)};
-
-% Training, Validation, Testing
-\node[block, fill=green!15, below left=0.6cm and 2.5cm of split] (train) {Training Set \\ (Learn Model Parameters)};
-\node[block, fill=green!10, below=of split] (val) {Validation Set \\ (Tune Hyperparameters)};
-\node[block, fill=green!05, below right=0.6cm and 2.5cm of split] (test) {Testing Set \\ (Final Evaluation)};
-
-% Model training block
-\node[block, fill=orange!20, below=3cm of val, minimum width=10cm, minimum height=1.2cm] (mod) {Train the Model \\ (Generator + Discriminator)};
-
-% Generator side (left)
-\node[block, fill=yellow!15, below=1.2cm of mod, xshift=-3.5cm] (noise) {Random Noise $z$};
-\node[block, fill=blue!10, below=of noise] (gen) {Generated Image $\hat{x}$};
-\node[block, fill=purple!20, below=of gen] (gloss) {Generator Loss \\ (Update $G$)};
-
-% Discriminator side (right)
-\node[block, fill=yellow!20, below=1.2cm of mod, xshift=+3.5cm] (real) {Real Image \\ (From Training Set)};
-\node[block, fill=orange!20, below=of real] (disc) {Discriminator $D(x)$};
-\node[block, fill=red!20, below=of disc] (out) {Discriminator Output};
-\node[block, fill=purple!30, below=of out] (dloss) {Discriminator Loss \\ (Update $D$)};
-
-% Final result block
-\node[block, fill=teal!20, below=4.2cm of val, minimum width=5cm] (res) {Result / Evaluation \\ (Performance Metrics: Accuracy)};
-
-% Connections
-\draw[arrow] (data) -- (pre);
-\draw[arrow] (pre) -- (split);
-\draw[arrow] (split.south west) |- (train.north);
-\draw[arrow] (split.south) -- (val.north);
-\draw[arrow] (split.south east) |- (test.north);
-\draw[arrow] (train.south) -- (mod.north);
-
-% GAN arrows
-\draw[arrow] (mod.south) -- (noise.north);
-\draw[arrow] (mod.south) -- (real.north);
-\draw[arrow] (noise.south) -- (gen.north);
-\draw[arrow] (gen.south) -- (gloss.north);
-\draw[arrow] (real.south) -- (disc.north);
-\draw[arrow] (gen.east) -- ++(0.5,0) |- (disc.west);
-\draw[arrow] (disc.south) -- (out.north);
-\draw[arrow] (out.south) -- (dloss.north);
-
-% Validation & Testing to Result
-\draw[arrow] (val.south) -- (res.north);
-\draw[arrow] (test.south) -- (res.north);
-
-\end{tikzpicture}
-\end{figure}
-
-\begin{figure}
-\begin{center}
-\includegraphics[scale=0.4]{FlowDiagram_TikZ.pdf}
-\caption{A block diagram for the process of image reconstruction through C-GAN.}
-\label{fig:FlowDiagram}
-\end{center}
-\end{figure}
-%\end{document}
-
-\fi
+\textcolor{blue}{The Pix2Picx cGAN architecture along with the choice of the values of the hyperparameters mentioned in the Table -\ref{tab:hyperparameters} and used in the implementation of this architecture constitutes the cGAN model (hereinafter referred to as ``the GAN Model'' or simply ``the Model'')}.

### 2025-12-06 Phase_II/draft/conclusion_NoRed.tex
GAN manuscript reviewed and edited

--- 2025-11-27 Phase_II/draft/conclusion.tex
@@
 This work addresses the challenge of phase retrieval in II using a machine-learning technique, specifically a conditional Generative Adversarial Network (cGAN).
-Our study demonstrates \st{that applying a cGAN to II data successfully recovers the size, shape, and brightness distribution of a fast-rotating star.}  \textcolor{blue}{that the size, shape and brightness distribution of fast rotating stars can be recovered by a cGAN trained on the combined input of the sky-image of known sources  along with their respective II data.
+Our study demonstrates   \textcolor{blue}{that the size, shape and brightness distribution of fast rotating stars can be recovered by a Pix2Pix cGAN model trained on the combined input of the sky-image of known sources  along with their respective II data.
 In this training the sky-image acts as the real ``ground truth'' and the II data acts as the ``condition''.
-The Discriminator of the cGAN model is trained to efficiently distinguish between the real images and fake (generated) images based on the ``ground truth'' images and the respective II data condition.
+The Discriminator of our Model is trained to efficiently distinguish between the real images and fake (generated) images based on the ``ground truth'' images and the respective II data as the condition.
 The Generator is trained to generate progressively realistic images which are also consistent with the condition of the II data.
-The evaluation of the trained model is then carried out} \st{Evaluations based on} \textcolor{blue}{by comparison of image moments of real images and generated images.} Specifically, the monopole, second, and third-order moments \textcolor{blue}{are compared.
-The results} support the effectiveness of cGAN in achieving \textcolor{blue}{the stated objective.} \st{accurate image reconstruction from a simulation of II from a single site with four telescopes.}
+The evaluation of the trained Model is then carried out}  \textcolor{blue}{by comparison of image moments of ground truth images and generated images.} Specifically, the monopole, second, and third-order moments \textcolor{blue}{are compared.
+The results} support the effectiveness of cGAN in achieving \textcolor{blue}{the stated objective.}
 

### 2025-12-07 Phase_II/draft/GAN.tex
before final

--- 2025-11-20 Phase_II/draft/GAN.tex
@@
 \section{Generative Adversarial Networks}
+\begin{figure*}
+\centering
+\includegraphics[width=0.7\linewidth]{fig/FlowDiagram_TikZ.png}
+\caption{A schematic representation of the features of a cGAN model used in this work and the iterative process of its training, validation and testing.
+The process constitutes four broad stages: (1) choice of an appropriate GAN architecture including both the Discriminator and the Generator (not shown in this figure) (2) preparation of the Training, Validation and Testing datasets and (3) Training and Validation of the Model (4) Testing and Evaluation of the Model.
+The stages (2), (3) and (4) are depicted in this figure.
+The datasets are prepared in three broad steps: (i) generating the ``ground truth'' images of fictitious fast-rotators $x$, the sparse II images $y$ used as the ``condition'' images in the Model and the generated images $z$ sampled from a Normal Distribution (ii)merging these images into individual files with $(x|y)$ and/ or $(z|y)$ (as seen in an illustrated sample in Fig.(\ref{fig:GANinput})) and generating the full dataset in this process, and finally (iii) partitioning the full dataset into Training Set, Validation Set and the Testing Set.
+After the iterative training of the Model and its validation process is complete (``Nash point'' of the Minimax Game is reached), the Model is tested using the Testing Set and evaluated.}
+\label{fig:FlowDiagram}
+\end{figure*}
+
 \begin{figure}
@@
 	\includegraphics[width=\linewidth]{fig/analysis/Discrep_Runs_Losses_gen_total_loss.png}
-	\caption{\textcolor{blue}{These figures show the effect of the ratio of episodes of Discriminator training per every episode of Generator training.
+	\caption{These figures show the effect of the ratio of episodes of Discriminator training per every episode of Generator training.
 This hyperparameter is termed Discriminator repetition or (discrep) in the figures.
@@
 With gradual training of the Generator, the success rate of the Discriminator decreases and eventually approaches saturation with equal probability of being successful in telling ``fake" from real.
-The continual decrease and eventual saturation of the Generator loss is a result of its training to generate better images with increasing number of steps.}}
+The continual decrease and eventual saturation of the Generator loss is a result of its training to generate better images with increasing number of steps.}
 	\label{fig:Plot_discrep_loss}
@@
 \end{equation}
-In our work, we specifically use this conditioning mechanism by choosing \(y\) to represent the ground-based intensity-interferometry (II) observation patterns: the Generator is trained to produce stellar surface images that not only look realistic but also conform to the measured II correlations, while the Discriminator judges realism \emph{and} consistency with the II data.
+The conditional variable $y$ in a cGAN can be various additional information including images, labels or text contextual to ``ground truth'' real data $x$.
+Among various types of cGANs, Pix2Pix GAN with its image-to-image translation design is suitable for the task at hand.
+In our work, we specifically use this conditional variable by choosing \(y\) to represent the ground-based intensity-interferometry (II) observation patterns: the Generator is trained to produce stellar surface images that not only look realistic but also conform to the measured II correlations, while the Discriminator judges realism \emph{and} consistency with the II data.
 
-\iffalse 
-During each training session of the Discriminator, it is presented with a series of real images (as seen in Fig.
-(\ref{fig:GANinput}) and generated images taken in equal proportion.
-During the initial phases of its training, as the generated images are sampled from random distribution, the Discriminator finds it easy to distinguish between the real and the generated images.
-This produces a sharp initial dip in the Discriminator loss function.
-On the other hand, the Generator loss function, during the initial phases of its training is high due to the poor quality of its generated images.
-Through the process of alternating training sessions, the Generator gradually learns to do better: generate images which resemble the real images ever more closely.
-As seen in fig.
-(\ref{fig:Plot_discrep_loss}), with further training of both the networks, the Generator loss is gradually minimized and the generated images become gradually indistinguishable from the real images.
-The Discriminator loss, on the other hand, increases from the minimum of the initial phases of training and gradually  saturates to a value halfway between its maximum and minimum values, as expected in the case of a binary classifier.}
-\fi
-
-\cite{isola2017image} further observed that combining the cGAN from Eq.~\eqref{eq:conditional_GAN} with the traditional $L_1(G)$ loss \textcolor{blue}{(also known  as the Mean Absolute Error) improves the results, as the Generator is encouraged to produce outputs closer to the target image in a pixel-wise sense.
-We adopt this approach in the training of our cGAN model by including $L_1(G)$ along with the hyperparameter $\lambda =100$.
-The total loss function that is minimized is}:
+\cite{isola2017image} further observed that combining the cGAN from Eq.~\eqref{eq:conditional_GAN} with the traditional $L_1(G)$ loss (also known  as the Mean Absolute Error) improves the results, as the Generator is encouraged to produce outputs closer to the target image in a pixel-wise sense.
+We adopt this approach in the training of our cGAN model by including $L_1(G)$ defined in eq.(\ref{eq:l1_loss})
 \begin{equation}
 	\centering
-	L_{tot} = \arg \min_{G} \max_{D} V(D, G) + \lambda \cdot L_1(G)
+	L_1(G) = \mathbb{E}_{x \sim p_{\mathrm{data}, z \sim p_z(z)}} \bigl[ \lVert x - G(z \mid y) \rVert_{1} \bigr].
+	\label{eq:l1_loss}
+\end{equation}
+The total adversarial loss function, along with the $L_1$ loss modulated by a hyperparameter $\lambda$ then becomes
+\begin{equation}
+	\centering
+	L_{tot} = \arg \min_{G} \max_{D} V(D, G) + \lambda \cdot L_1(G).
 	\label{eq:total_gen_loss}
 \end{equation}
-with the choice $\lambda = 100$ and
-\begin{equation}
-	\centering
-	L_1(G) = \mathbb{E}_{x,y,z} \left[ ||{y - G(x,z)}||_1 \right]
-	\label{eq:l1_loss}
-\end{equation}
+
 This type of network has demonstrated remarkable robustness across a variety of applications.
@@
 \subsection{Generator}
-As discussed above, in a GAN the Generator, a deep neural network in iteself, is responsible for producing synthetic data — in this case, images that resemble those of a fast-rotating star.
+As discussed above, in a GAN the Generator, a deep neural network in iteself, is responsible for producing synthetic data, in this case, images that resemble those of a fast-rotating star.
 In this work, the Generator is implemented as a U-Net convolutional network \citep{ronneberger2015u}.
-\textcolor{blue}{The U-Net consists of a symmetric encoder--decoder structure forming a characteristic ``U'' shape: the left (contracting or down-sampling) path, the right (expanding or up-sampling path) and the connecting (bottle-neck) path.
+The U-Net consists of a symmetric encoder--decoder structure forming a characteristic ``U'' shape along with skip connections: the left (contracting or down-sampling) path, the right (expanding or up-sampling path) and the connecting (bottle-neck) path.
 The left down-sampling path repeatedly applies 3$\times$3 convolutions (padded to preserve spatial dimensions) followed by LeakyReLU activations and strided convolution (with stride of 2), by progressively halving the spatial resolution while doubling the channel depth (typically 64 $\to$ 128 $\to$ 256 $\to$ 512 $\to$ 1024).
@@
 Besides the strided convolutions, modern variants of U-Nets used in state-of-the-art GANs incorporate residual blocks within resolution levels, and frequently add spectral normalization and self-attention at the bottleneck for improved training stability and long-range dependency modelling.
-These architectural choices allow our U-Net generator to simultaneously recover sharp, high-frequency details (stellar limb edges, limb-darkening profiles, gravity darkening, and rapid-rotation-induced oblateness) and enforce global coherence (overall disk morphology and physical consistency with the observed interferometric visibilities)---making it ideally suited for high-fidelity sky-image reconstruction of fast-rotating stars from sparse ground-based intensity interferometry observations.}
+These architectural choices allow our U-Net generator to simultaneously recover sharp, high-frequency details (stellar limb edges, limb-darkening profiles, gravity darkening, and rapid-rotation-induced oblateness) and enforce global coherence (overall disk morphology and physical consistency with the observed interferometric visibilities)---making it ideally suited for high-fidelity sky-image reconstruction of fast-rotating stars from sparse ground-based intensity interferometry observations.
 
-After generating images, the Generator aims to deceive the Discriminator into classifying the generated images as real.
-The extent to which the Generator succeeds in this deception is quantified by the GAN loss.
-When the Discriminator is unable to distinguish between the generated and real images (i.e., when the GAN loss is minimized), the Generator is considered to have reached an optimal state.
-Conversely, if the generated image fails to fool the Discriminator, the Generator produces a new image for further comparison with the real image.
-Additionally, the Generator's performance is evaluated using another metric known as the L1 loss, which is defined as the mean absolute error between the pixels of the real image and those of the generated image.
-Balancing the minimization of both the GAN loss and the L1 loss enables the Generator to produce images that are not only realistic but also faithful to the input data.
+During the training, the total Generator Loss function $L_G$ including the $L_1$ loss defined in eq.(\ref{eq:l1_loss}) that is minimized is given by
+\begin{equation}
+\centering
+\begin{aligned}
+L_{G} \; &= \; - \, \mathbb{E}_{z \sim p_{z}(z)} \bigl[ \log D(G(z \mid y)\mid y) \bigr] \\
+& +\; \lambda \; \mathbb{E}_{x \sim p_{\mathrm{data}, z \sim p_z(z)}} \bigl[ \lVert x - G(z \mid y) \rVert_{1} \bigr].  
+\end{aligned}
+\label{eq:total_gen_loss}
+\end{equation}
+Here, 
+\begin{itemize}
+  \item \(x\) denotes a real data sample (e.g.\ the ``ground-truth'' image; here, the synthetically generated fast rotator image) corresponding to condition \(y\), the simulated II observation data.  
+  \item \(z\) is a random latent vector drawn from the prior \(p_z(z)\).  
+  \item \(G(z \mid y)\) is the generator output (the reconstructed / synthesized image) given \(z\) and condition \(y\).  
+  \item \(D(\cdot \mid y)\) is the discriminator’s estimate (probability) that its input is “real,” given the same condition \(y\).  
+  \item \(\lambda\) is a hyperparameter controlling the trade-off between adversarial realism and pixel-wise fidelity (typical values depend on the problem, e.g.\ in pix2pix, \(\lambda = 100\)). 
+\end{itemize}
 
@@
 Unlike a traditional global classifier, PatchGAN evaluates individual patches of the image, outputting a grid of predictions rather than a single scalar value.
-\textcolor{blue}{Each element in the grid corresponds to the ``realness'' of one patch of the image under examination of the Discriminator at a time.
-The final loss is of the Discriminator is the average over all the patch responses.
+Each element in the grid corresponds to the ``realness'' of one patch of the image under examination of the Discriminator at a time.
+The final loss of the Discriminator is the average over all the patch responses.
 Evaluating the ``realness'' of the input image in terms of its constituent patches facilitates capture of texture/ style and other high frequency components in the image.
 As compared to a global discriminator, it also reduces the number of parameters in the network thereby helping reduce computation cost.
-It also works on images with arbitrary sizes.}
+It also works on images with arbitrary sizes.
 
-The Discriminator’s architecture begins with an initializer that accepts both the input (generated) images and the corresponding real images.
-Initially, Salt-and-Pepper noise is added to the input images.
+Prior to the down-sampling of data using PatchGAN, each input image is preprocessed with application of Zero Padding followed by batch normalization.
+The purpose of Zero Padding is to prevent the loss of spatial information and to facilitate the extraction of deeper features from the down-sampled output.
+Batch normalization is required to stabilize the learning (loss minimization) process.
 PatchGAN then reduces the spatial dimensions of the images to extract localized features, ensuring the model focuses on smaller regions.
-In this downsampling stage, a leaky version of the Rectified Linear Unit (LeakyReLU) is applied in the convolutional layers, similar to the approach used in the Generator.
+In this down-sampling stage, a leaky version of the Rectified Linear Unit (LeakyReLU) is applied in the convolutional layers, similar to the approach used in the Generator.
+The probability $D(\cdot|y)$ that the patch of the input image represented by $\cdot$ is ``real'' is evaluated through this process.
+The loss function $D$ of the full input image is obtained by averaging over all the patch responses.
 
-Subsequently, zero padding is applied, adding rows and columns of zeros around the images to prevent the loss of spatial information during convolution and to facilitate the extraction of deeper features from the downsampled output.
-Following this, batch normalization is employed to stabilize learning by normalizing activations, and the Discriminator begins classifying each patch as real or fake.
-This is followed by additional layers involving LeakyReLU activation, zero padding, and convolution, culminating in a final prediction that is fed to the Generator as feedback.
+The Discriminator Loss function $L_D$ that is optimized during the training process is given by 
+\begin{equation}
+\centering
+\begin{aligned}
+L_{D} \; &= \; - \, \mathbb{E}_{x \sim p_{\mathrm{data}}(x \mid y)} \bigl[ \log D(x \mid y) \bigr] \\
+& -\; \mathbb{E}_{z \sim p_{z}(z)} \bigl[ \log\bigl( 1 - D(G(z \mid y)\mid y)\bigr) \bigr]
+\end{aligned}
+\end{equation}
+where the arguments of the $D$ and $G$ functions are as noted in the text following eq.(\ref{eq:total_gen_loss}) This loss is composed of two parts: one that assesses how accurately it identifies fake images (by comparing predictions to a target value of 0) and the other that measures how accurately the Discriminator identifies real images (by comparing predictions to a target value of 1).
 
-The effectiveness of the Discriminator is measured by its ability to distinguish between real and fake images, quantified through the Discriminator loss.
-This loss is composed of two parts: one that measures how accurately the Discriminator identifies real images (by comparing predictions to a target value of 1) and another that assesses how accurately it identifies fake images (by comparing predictions to a target value of 0).
-Together, these loss components ensure that the Discriminator improves its classification performance, which in turn, challenges the Generator to produce increasingly realistic images.
+The training procedure of these two components of the cGAN model can be outlined as follows:
+\begin{itemize}
+\item{The discriminator \(D\) is updated by minimizing \(L_D\), keeping \(G\) fixed (so that \(D\) becomes better at distinguishing real vs generated images).}  
+\item{The generator \(G\) is updated by minimizing \(L_G\), keeping \(D\) fixed, thus pushing \(G\) to generate images that are (a) judged “real” by \(D\), and (b) close (in pixel-wise sense) to the ground-truth \(x\).}
+\end{itemize}

### 2025-12-07 Phase_II/draft/II.tex
GAN manuscript reviewed and edited
before final

--- 2025-11-17 Phase_II/draft/II.tex
@@
   \includegraphics[width=\linewidth]{fig/baseline.png}
-  \caption{The tracks of the baselines due to Earth rotation (described in sec.~\ref{sec:earth}) provided by \textcolor{blue}{the hypothetical observation facility of four telescopes arranged in fig.~\ref{fig:teles}} for one night of observation.
-\textcolor{blue}{The number of baselines scales as square of number of telescopes in the array thus leading to greater coverage of the observational plane and better image reconstruction prospects.}}
+  \caption{The tracks of the baselines due to Earth rotation (described in sec.~\ref{sec:earth}) provided by the hypothetical observation facility of four telescopes arranged in fig.~\ref{fig:teles} for one night of observation.
+The number of baselines scales as square of number of telescopes in the array thus leading to greater coverage of the observational plane and better image reconstruction prospects.}
 \label{fig:base}
@@
 In our work presented here, we attempt image reconstruction of a fast-rotating star using its simulated Intensity Interferometric observation in a cGAN architecture.
-\textcolor{blue}{Fast-rotating stars are important test cases for understanding various astrophysical processes, including stellar evolution, internal structure, and dynamical behaviour over time.
+Fast-rotating stars are important test cases for understanding various astrophysical processes, including stellar evolution, internal structure, and dynamical behaviour over time.
 Fast rotation causes stars to adopt an oblate shape, flattening at the poles and bulging at the equator due to the stronger centrifugal force \citep[e.g.,][]{von1924radiative, 1999A&A...347..185M}.
@@
 In addition, observation and measurement of gravity darkening using II is the natural next step and is yet to be reported.
-In this context, our work of reconstructing the image of FRSs from their II-simulated observations using cGAN is an attempt at solving this inverse problem along with mitigation of loss of phase information in II.}
+In this context, our work of reconstructing the image of FRSs from their II-simulated observations using cGAN is an attempt at solving this inverse problem along with mitigation of loss of phase information in II.
 
-Intensity Interferometry counts the photons arriving at the telescopes from the stellar object.
+II counts the photons arriving at the telescopes from the stellar object.
 The correlation of these photon arrivals at the telescopes yields the squared visibility Eq.~\eqref{eq:angular_size_meas}, as explained in subsection~\ref{sec:signal}.
@@
 In practice, only a small part of this information is available (as seen in right panel of Fig.~\ref{fig:ft}), because one has a finite number of baselines corresponding to the finite number $N_T$ of telescopes at our disposal and a limited observation schedule.
-We have simulated the II observation of the fictitious star \textcolor{blue}{by a hypothetical observation facility having an array of four IACTs} (correlated with baselines as seen in Fig.~\ref{fig:teles}) over one night.
+We have simulated the II observation of the fictitious star by a hypothetical observation facility having an array of four IACTs with their relative positions approximating those at VERITAS (correlated with baselines as seen in Fig.~\ref{fig:teles}) over one night.
 Using this modest amount of signal from one night's observation, we have trained a cGAN to construct the image of the source.
@@
   \includegraphics[width=0.85\linewidth]{fig/ellipse1612.jpg}
-  \caption{\textcolor{blue}{Example of the input used for training the cGAN model.
-\textcolor{blue}{The picture on the left shows the source image, which serves as the ground truth or the real data ($x$, as mentioned in the Flow Diagram (Fig.\ref{fig:FlowDiagram} discussed later} during the training.
-The picture on  the right represents the simulated Intensity Interferometry (II) observation pattern of the source (on the left) using \textcolor{blue}{a hypothetical observation facility having as array of four IACTs} (see Fig.~\ref{fig:teles}) and the tracks of the six telescope baselines (see Fig.~\ref{fig:base}) generated  by these four IACTs due to Earth's rotation during the observation session.
-\textcolor{blue}{This pattern referred to as $y$, in the Flow Diagram (Fig.\ref{fig:FlowDiagram} discussed later forms the ``condition" during the training to which the GAN model has to conform.
-Salt-and-pepper noise is added to this pattern for enhancing the robustness of the cGAN model.} Together, these images form a training pair, where the GAN learns to reconstruct a predicted image (modeling of observed signal) similar to ground truth (left) from the noisy baseline signal (right).
-The grayscale in both images is normalized to the brightest pixel.}}
+  \caption{An illustrative example of the input used for training the cGAN model.
+The picture on the left shows the source image, which serves as the ground truth or the real data ($x$), as mentioned in the Flow Diagram (Fig.\ref{fig:FlowDiagram} discussed later during the training).
+The picture on  the right represents the simulated II observation pattern of the source (on the left) using a hypothetical observation facility having as array of four IACTs (see Fig.~\ref{fig:teles}) and the tracks of the six telescope baselines (see Fig.~\ref{fig:base}) generated  by these four IACTs due to Earth's rotation during the observation session.
+This pattern referred to as $y$, in the Flow Diagram (Fig.\ref{fig:FlowDiagram} discussed later) forms the ``condition" during the training to which the GAN model has to conform.
+Salt-and-pepper noise is added to this pattern for enhancing the robustness of the cGAN model.
+Together, these images form a training pair, where the GAN learns to reconstruct a predicted image (modeling of observed signal) similar to ground truth (left) from the noisy baseline signal (right).
+The grayscale in both images is normalized to the brightest pixel.}
   \label{fig:GANinput}

### 2025-12-07 Phase_II/draft/ParaGan.tex
before final

--- 2025-11-11 Phase_II/draft/ParaGan.tex
@@
 	\includegraphics[width=0.785\textwidth]{fig/testing_image/image_39.png}
-\caption{Example results of image reconstruction using the GAN model along with the II observations simulated in this work.
+\caption{Example results of image reconstruction using the cGAN model along with the II observations simulated in this work.
 Each row in this figure represents the results for a hypothetical fast-rotating star.
-Going from left to right in each row, the first panel represents the simulated $(u,v)$ plane II signals obtained using the six baselines (right panel of of fig.\ref{fig:ft}).
-This image is presented, as the input, to the trained GAN to produce a predicted image.
-The second panel is the real image of the star, also called the ground truth.
+The left panel represents the sparse II pattern obtained by the simulated observation of the star using the four IACTs illustrated in Fig.\ref{fig:teles}.
+This image acts as the ``condition'' part of the data input to the cGAN model.
+The second panel from left displays the real image, or ground truth, which the Discriminator uses to distinguish from the images generated by the Generator.
+The data generated for training, validation and testing of the cGAN model is a merge of this image and its II pattern presented in the left panel.
 The third panel is the reconstructed image, or the predicted image, produced by the trained GAN model .
-The fourth and the last panel is the difference between the ground truth and the predicted image in the $(u,v)$ plane.
-The uniform background color in the difference panel suggests that the network is picking up white noise from the $(u,v)$ plane.
-}
+The fourth and the last panel is the difference between the ground truth and the predicted image in the $(u,v)$ plane.}
 	\label{fig:GAN}
 \end{figure*}
+An appropriate cGAN architecture along with a set of hyperparameters was optimized by tuning.
+The objective of the model, as already mentioned, was to learn to faithfully reproduce a set of sky-images of fast rotators subject to the condition that those images are consistent with their simulated II observation data.
+We discuss below the architecture and the hyperparameters of the cGAN model used for this task.
+Given the adversarial nature of GANs, where the Generator and Discriminator engage in a minimax game, careful tuning of key parameters is critical to ensure that both networks are well-balanced for effective training.
 
-Here, we discuss the parameters of the GAN architecture used for reconstructing images of stellar objects using II.
-Given the adversarial nature of GANs, where the Generator and Discriminator engage in a min-max game, careful tuning of key parameters is critical to ensure that both networks are well-balanced for effective training.
+\subsection{Data Preparation}\label{sec:DataPrep}
+First, we generate synthetic images of rapidly rotating stars by modelling them as oblate spheroids with varying radii and oblateness parameters between 0.5 and 1.
+To incorporate the effect of gravity darkening, we also consider different viewing angles and assume a linear dependence on the declination angle of each point on the stellar surface.
+The traced ellipses result from integrating over the source's hour angle.
 
-\subsection{Data Preparation}
-First, we simulate fast-rotating stars, modelling them as oblate spheroids with varying radii and an oblateness ranging between 0.5 and 1.
-We also consider different viewing angles, assuming a linear dependence for the effect of gravity darkening.
-The traced ellipses result from integrating over the source's hour angle.
-For hyperparameter tuning and comparing different telescopes, the total observing duration is set to approximately 11.5 hours.
-Finally, the ellipses are plotted, converted into grayscale images, resized, and stored as raw arrays to facilitate further analysis.
-
-Next, Salt and Pepper noise is introduced usually at a rate of 0.5\%.
+Next, Salt and Pepper noise is introduced into these images; usually this is done at the rate of 0.5\% of the number of pixels in the image.
 Then, the images are resized and their mean is subtracted.
 A two-dimensional Fast Fourier Transform, along with a Fourier shift, is applied, yielding a complex number for each pixel.
-Since II does not measure phase, the absolute value is calculated (as shown in Fig.~\ref{fig:ft} on both linear and logarithmic scales for visualization).
+Since II does not measure phase, the absolute value is calculated.
 
-Next, sparse sampling is introduced via pixel-wise multiplication between the absolute-valued Fourier-transformed image (Fig.~\ref{fig:ft}) and the sparse sampling map (Fig.~\ref{fig:base}).
+Next, sampling of the interferometric plane is introduced via pixel-wise multiplication of the absolute-valued Fourier-transformed image (left panel of Fig.~\ref{fig:ft}) and the baseline tracks of (Fig.~\ref{fig:base}) generated by the four IACTs due to Earth rotation during the II observation.
 The result is a map in the Fourier plane featuring several ellipses, which is also referred to as the sparse sampling map (right panel of fig.~\ref{fig:ft}).
-This map represents the sparse sampling of the signal space (Fig.~\ref{fig:ft}) corresponding to the source (Fig.~\ref{fig:image}) observed with four telescopes (Fig.~\ref{fig:teles}).
+This map represents the sparse sampling of the signal space
+corresponding to the source (Fig.~\ref{fig:image}) observed with four telescopes (Fig.~\ref{fig:teles}).
+In essence, the right panel of fig.~\ref{fig:ft} represents the result of simulated II observation of the fictitious fast-rotator illustrated in fig.~\ref{fig:image}.
 
-Finally, the pixels are normalized and converted to 8-bit integers.
-This image represents the sparsely sampled phaseless visibility as it can be measured with II.
-The image shown in right panel of fig.~\ref{fig:ft} serves as the input for the GAN, which also requires the corresponding ground truth image.
-Consequently, the simulated stars are resized using the same algorithm and converted to 8-bit integers to reduce bias.
-The GAN must have access to the ground truth corresponding to each input image; therefore, the input and ground truth images are merged side-by-side (as shown in Fig.~\ref{fig:GANinput}) and used to train the GAN.
-This procedure is applied to all simulated stars, with 10\% used as test data, 10\% as validation data, and the remaining 80\% as training data.
+Finally, we normalize the pixel values and convert them to 8-bit integers, producing an image that encodes the sparsely sampled, phase-free visibility measured by II.
+The image of the corresponding simulated (fictitious) star, which serves as the ``ground truth'' is processed identically to avoid any bias.
+These two images are merged side-by-side into a single
+image (as shown in Fig.~\ref{fig:GANinput}).
+The dataset thus created is split into three parts in the proportions of 80\% for training, 10\% for validation, and 10\% as the test set.
+This partition of the full dataset is indicated in the Fig.\ref{fig:FlowDiagram}.
+In the following, we refer to these three parts as the Training Set, the Validation Set and the Testing Set respectively.
 
 \subsection{GAN Architecture}
-The GAN used in this work is based on pix2pix, which utilizes a conditional GAN (cGAN) as discussed in the previous section \citep{isola2017image}.
-This architecture is highly robust and has already been applied to various problems.
+The GAN architecture used in this work is a Pix2Pix cGAN, which uses an image-to-image translation strategy with both the ground truth and the condition being images.
+Originally introduced by Isola et al.
+\cite{isola2017image}, this architecture is specifically suitable for image processing and reconstruction objectives.
 For instance, the TensorFlow tutorials\footnote{\url{https://www.tensorflow.org/tutorials/generative/pix2pix}} demonstrate its application to a dataset of architectural facades.
-However, to adapt the pix2pix GAN for the phase retrieval problem, some modifications are necessary.
+This architecture has been adapted
+for the phase retrieval problem at hand here.
 The network is implemented using the TensorFlow library \citep{abadi2016tensorflow}, calculations are performed with scipy \citep{virtanen2020scipy}, and plots are generated with matplotlib \citep{4160265}.
@@
 \subsection{Hyperparameter Tuning}
-The GAN used in this work depends on several parameters, which are explained briefly below \citep[for a more in-depth discussion, see][]{murphy2022probabilistic}.
+The cGAN model architecture used in this work employs several hyper-parameters, which are explained briefly below \citep[for a more in-depth discussion, see][]{murphy2022probabilistic}.
 
-The learning rate of the optimizer determines how much the model updates its parameters with each iteration.
+The learning rate ($lr$) of the optimizer determines how much the model updates its parameters with each iteration.
 A learning rate that is too small may lead to underfitting, while one that is too large can render the model unstable.
 Therefore, selecting an appropriate learning rate is crucial \citep{murphy2022probabilistic}.
+A canonical choice in Pix2Pix and other GAN models is $lr = 2\times10^{-4}$.
+In our case too, we found this choice to be appropriate.
 
@@
 A larger kernel size can capture features spanning several pixels, but it may also incorporate unrelated features.
+Small kernel sizes are preferable in cases where target images finer details or high spatial frequency features.
+Since the ``ground truth'' target images in our case have longer scale gravity darkening features, we have opted for the more canonical choice of kernel size being 5.
 
@@
 However, because a larger batch size significantly increases training time, a batch size of 1 is used.
+Besides, in Pix2Pix cGAN implementations found in literature this choice is found to be often preferred.
 
-When training GANs, one strategy to potentially boost performance is to give the Discriminator an advantage by increasing its number of training steps before returning to the Generator's training.
-While this can lower the Discriminator loss, as shown in Fig.~\ref{fig:Plot_discrep_loss}, it also increases training time and leads to a slight rise in the Generator loss.
-Since the generated images do not noticeably improve with additional Discriminator training, both networks are typically trained with the same number of steps.
+Buffer size of a Pix2Pix GAN refers to a small memory of image pool of previously generated images.
+They are occasionally fed to the Discriminator in place of the freshly generated ones.
+This strategy of mixing old and new fakes  mitigates the risk of mode collapse wherein the Discriminator tends to map all or large number of generated images to only one or a few real ``ground truth'' image(s).
+We have chosen a fairly large buffer size (=1400) to protect the model against mode collapse.
 
-Finally, the degree of sparse sampling can be varied to provide the model with access to more pixels.
-Increasing the number of telescopes results in more baselines and, consequently, more available pixels.
+In the training of GANs, one often-followed strategy to potentially boost performance is to give the Discriminator an advantage by increasing its number of training epochs before returning to the Generator's training.
+This hyperparameter is referred to as the Discriminator repetition (as seen in Table \ref{tab:hyperparameters}.
+While this can lower the Discriminator loss, as shown in Fig.~\ref{fig:Plot_discrep_loss}, it also increases training time.
+In training our model, we did not notice any significant advantage derived from this strategy.
+Since the generated images did not noticeably improve with additional Discriminator training, we adopted the strategy of training both the networks with equal preference (Discriminator repetition = 1).
+
+One domain specific hyperparameter of the cGAN model presented here is the Number of Telescopes $N_T$.
+The degree of sparse sampling of the intensity interferometric (II) image plane can be varied to provide the model with access to more number of active (non-zero) pixels.
+Point to note here, is that the coverage of the Fourier interferometric plane (number of active pixels in the II image) scales with available number of baselines, and the latter scales quadratically with the number of telescopes.
 Fig.~\ref{fig:Plot_telescopes_loss} shows the loss functions for different numbers of telescopes.
-There is a significant disparity in performance, partly because the relationship between telescopes and baselines is not linear.
-For example, the Fourier plane can be sampled along six tracks when using four telescopes, as compared to only one track if using only two telescopes.
-In the case of two telescopes, both the Generator and Discriminator exhibit less smooth training, as indicated by the outliers.
-Performance improves with three telescopes and becomes very promising with four.
+There is a significant disparity in performance of the model: at the ``Nash point'', both the loss functions are minimized for the case of four telescopes.
 Overall, the degree of sparse sampling appears to have the most pronounced effect of all the hyperparameters.
 
-All the selected hyperparameters to train the model is summarized in the given table:
+The hyperparameter Output Channels refers to the number of channels in the generator output (e.g., 1 for grayscale, 3 for RGB).
+It is worthwhile to recall that the cGAN model constructed in this work is trained on ``ground truth'' target images and the simulated II data, both in grey scales as seen in Fig.\ref{fig:GANinput}.
+It is natural that the output of this model will be in grey scales only.
+Therefore the value of this hyperparameter is set to 1.
+The choice of hyperparameter \(\lambda\) has been commented upon earlier.
+
+An optimized set of hyperparameters is selected through an iterative process of training and validation.
+For a tentatively chosen set of the hyperparameters, the model is trained using the Training Set until the both the Discriminator and the Generator loss functions are minimized.
+This model, thus trained along with its model parameters, is then passed through validation using the Validation Set.
+This cycle of training and validation is iterated till an optimal set of hypermaraters is arrived at.
+During each epoch of training of the model, both the Discriminator and the Generator networks are trained for 100,000 steps.
+Plots of the ''Discriminator Loss'' function and the ``Generator Total Loss'' function presented in Fig.{\ref{fig:Plot_discrep_loss}} and Fig.{\ref{fig:Plot_telescopes_loss} represent the results of this training for two of the hyperparameters, namely, the Disriminator repetition (``discrep'', in short) and the Number of telescopes, respectively}.
+Obviously, the most compute-intensive part of this process is that of the training of the Model.
+The results of training and validation presented in this work were carried out on a CPU using two nodes, each with 96 threads and the entire process of training and validation required approximately 20 hours on the machine employed for this work.
+This iterative process of training and validation of the Model is represented schematically in the Fig.\ref{fig:FlowDiagram}.
+The chosen optimal set of hyperparameters is presented in the table Table-{\ref{tab:hyperparameters}.}
 \begin{table}[ht]
@@
 \end{table}
+This optimized and trained Model is then subjected to testing and evaluation using the Testing Set. The results of this testing and evaluation is presented in the following section.
 
-The process to train the model is summarized here:
-\iffalse
-\begin{figure*}[htbp]
-	%\centering
-	\begin{center}
-		\begin{tikzpicture}[node distance=0.7cm]
-
-			% Data pipeline
-			\node[block, fill=blue!15] (data) {Ground Truth \\ (Create SS Images of Stellar Objects)};
-			\node[block, fill=red!10, below=of data] (pre) {Simulation \\ (Intensity Interferometry (II) Data)};
-			\node[block, fill=green!20, below=of pre, minimum width=5cm] (split) {Input Dataset (Merge of Ground Truth \\ and Simulation of II) Split \\ (Training, Validation, Testing)};
-
-			% Training, Validation, Testing
-			\node[block, fill=green!15, below left=0.6cm and 1.0cm of split] (train) {Training Set \\ (Learn Model Parameters)};
-			\node[block, fill=green!10, below=of split] (val) {Validation Set \\ (Tune Hyperparameters)};
-			\node[block, fill=green!05, below right=0.6cm and 1.0cm of split] (test) {Testing Set \\ (Final Evaluation)};
-
-			% Model training block
-			\node[block, fill=orange!20, below= 1.0cm of val, minimum width=10cm, minimum height=1.2cm] (mod) {Train the Model \\ (Generator + Discriminator)};
-
-			% Generator side (left)
-			\node[block, fill=yellow!15, below=2.2cm of mod, xshift=-3.5cm] (noise) {Random Noise $z$};
-			\node[block, fill=blue!10, below=of noise] (gen) {Generated Image $\hat{x}$};
-			\node[block, fill=purple!20, below=of gen] (gloss) {Generator Loss \\ (Update $G$)};
-
-			% Discriminator side (right)
-			\node[block, fill=yellow!20, below=2.2cm of mod, xshift=+3.5cm] (real) {Real Image \\ (From Training Set)};
-			\node[block, fill=orange!20, below=of real] (disc) {Discriminator $D(x)$};
-			\node[block, fill=red!20, below=of disc] (out) {Discriminator Output};
-			\node[block, fill=purple!30, below=of out] (dloss) {Discriminator Loss \\ (Update $D$)};
-
-			% Final result block
-			\node[block, fill=teal!20, below= 3cm of val, minimum width=5cm] (res) {Result / Evaluation \\ (Performance Metrics: Accuracy)};
-
-			% Connections
-			\draw[arrow] (data) -- (pre);
-			\draw[arrow] (pre) -- (split);
-			%\draw[arrow] (split.south west) |- (train.north);
-			\draw[arrow] (split.west) -| (train.north);
-			\draw[arrow] (split.south) -- (val.north);
-			\draw[arrow] (split.east) -| (test.north);
-			\draw[arrow] (train.south) -- (mod.north);
-
-			%Newly Introduced Connections (S Sarangi)
-			\draw[arrow] (val.south) -- (mod.north);
-			\draw[arrow] (mod.south) -- (res.north);
-
-			% GAN arrows
-			\draw[arrow] (mod.south) -- (noise.north);
-			\draw[arrow] (mod.south) -- (real.north);
-			\draw[arrow] (noise.south) -- (gen.north);
-			\draw[arrow] (gen.south) -- (gloss.north);
-			\draw[arrow] (real.south) -- (disc.north);
-			\draw[arrow] (gen.east) -- ++(0.5,0) |- (disc.west);
-			\draw[arrow] (disc.south) -- (out.north);
-			\draw[arrow] (out.south) -- (dloss.north);
-
-			% Validation & Testing to Result
-			%\draw[arrow] (val.south) -- (res.north);
-			\draw[arrow] (test.south) -- (res.north);
-
-		\end{tikzpicture}
-	\end{center}
-\caption{A block diagram for the process of image reconstruction through GAN.}
-\end{figure*}
-\fi
-
-\iffalse
-\documentclass{article}
-\usepackage{tikz}
-\usetikzlibrary{arrows, arrows.meta, positioning}
-
-\tikzset{
-  block/.style = {draw, rectangle, minimum height=1.5em, minimum width=3em, align=center},
-  arrow/.style = {->, thick},
-}
-
-%\begin{document}
-\fi
-
-\iffalse
-\begin{figure}[htbp]
-\centering
-\begin{tikzpicture}[node distance=0.9cm]
-%\begin{tikzpicure}[scale = 0.5]
-
-% Data pipeline
-\node[block, fill=blue!15] (data) {Ground Truth \\ (Create SS Images of Stellar Objects)};
-\node[block, fill=red!10, below=of data] (pre) {Simulation \\ (Intensity Interferometry (II) Data)};
-\node[block, fill=green!20, below=of pre, minimum width=5cm] (split) {Input Dataset (Merge of Ground Truth \\ and Simulation of II) Split \\ (Training, Validation, Testing)};
-
-% Training, Validation, Testing
-\node[block, fill=green!15, below left=0.6cm and 2.5cm of split] (train) {Training Set \\ (Learn Model Parameters)};
-\node[block, fill=green!10, below=of split] (val) {Validation Set \\ (Tune Hyperparameters)};
-\node[block, fill=green!05, below right=0.6cm and 2.5cm of split] (test) {Testing Set \\ (Final Evaluation)};
-
-% Model training block
-\node[block, fill=orange!20, below=3cm of val, minimum width=10cm, minimum height=1.2cm] (mod) {Train the Model \\ (Generator + Discriminator)};
-
-% Generator side (left)
-\node[block, fill=yellow!15, below=1.2cm of mod, xshift=-3.5cm] (noise) {Random Noise $z$};
-\node[block, fill=blue!10, below=of noise] (gen) {Generated Image $\hat{x}$};
-\node[block, fill=purple!20, below=of gen] (gloss) {Generator Loss \\ (Update $G$)};
-
-% Discriminator side (right)
-\node[block, fill=yellow!20, below=1.2cm of mod, xshift=+3.5cm] (real) {Real Image \\ (From Training Set)};
-\node[block, fill=orange!20, below=of real] (disc) {Discriminator $D(x)$};
-\node[block, fill=red!20, below=of disc] (out) {Discriminator Output};
-\node[block, fill=purple!30, below=of out] (dloss) {Discriminator Loss \\ (Update $D$)};
-
-% Final result block
-\node[block, fill=teal!20, below=4.2cm of val, minimum width=5cm] (res) {Result / Evaluation \\ (Performance Metrics: Accuracy)};
-
-% Connections
-\draw[arrow] (data) -- (pre);
-\draw[arrow] (pre) -- (split);
-\draw[arrow] (split.south west) |- (train.north);
-\draw[arrow] (split.south) -- (val.north);
-\draw[arrow] (split.south east) |- (test.north);
-\draw[arrow] (train.south) -- (mod.north);
-
-% GAN arrows
-\draw[arrow] (mod.south) -- (noise.north);
-\draw[arrow] (mod.south) -- (real.north);
-\draw[arrow] (noise.south) -- (gen.north);
-\draw[arrow] (gen.south) -- (gloss.north);
-\draw[arrow] (real.south) -- (disc.north);
-\draw[arrow] (gen.east) -- ++(0.5,0) |- (disc.west);
-\draw[arrow] (disc.south) -- (out.north);
-\draw[arrow] (out.south) -- (dloss.north);
-
-% Validation & Testing to Result
-\draw[arrow] (val.south) -- (res.north);
-\draw[arrow] (test.south) -- (res.north);
-
-\end{tikzpicture}
-\end{figure}
-\fi
-
-\begin{figure}
-\begin{center}
-\includegraphics[scale=0.4]{FlowDiagram_TikZ.pdf}
-\caption{A block diagram for the process of image reconstruction through C-GAN.}
-\label{fig:FlowDiagram}
-\end{center}
-\end{figure}
-%\end{document}
+The Pix2Picx cGAN architecture along with the choice of the values of the hyperparameters mentioned in the Table -\ref{tab:hyperparameters} and used in the implementation of this architecture constitutes the cGAN model (hereinafter referred to as ``the GAN Model'' or simply ``the Model'').

### 2025-12-07 Phase_II/draft/Result.tex
before final

--- 2025-09-25 Phase_II/draft/Result.tex
@@
-\section{Images Reconstructed by the GAN}
-In this section, we begin by discussing phase retrieval using hyperparameters, as mentioned earlier, followed by an analysis in which multiple sources are trained simultaneously.
-The best performance for image reconstruction has been observed with a learning rate of \(2 \cdot 10^{-4}\), a kernel size of 5×5, and equal noise percentages (alpha/beta = 1) applied to both the original and generated images.
-A batch size of 1 is used, and equal training is provided to both the Discriminator and the Generator.
+\section{Image Reconstruction: Results and Evaluation}
 
-\subsection{Predicted Image from the Trained GAN}
-Fig.~\ref{fig:GAN} demonstrates the success of the GAN in training a model to reconstruct the images of  fast-rotating stars using their Intensity Interferometry (II) observation .
-The GAN was trained on the training datasets for 100,000 steps and subsequently tested on various validation datasets to produce predicted images of the stars.
-The training was performed on a CPU using two nodes, each with 96 threads, and required approximately 20 hours.
-In Fig.~\ref{fig:GAN}, four combined images illustrate the GAN's performance in reconstructing the stars' shape, size, and brightness distribution using II.
+In this section, we examine the performance of the GAN Model whose architecture and choice of hyperparameters have been discussed above.
+We subject the trained Model to the task of phase retrieval and image reconstruction on the Testing Dataset.
+
+\subsection{Visual Evaluation of Images Predicted by the Model}
+Fig.~\ref{fig:GAN} demonstrates the success of the trained Model in reconstructing the images of a sample of the fictitious fast-rotators drawn from the Testing Set.
+
+The four panels from left to right in each row of Fig.~\ref{fig:GAN} represent the following:
 \begin{itemize}
-\item{The left panel shows the signals collected from six baselines, which serve as the input for the Generator during training.}
-\item{The first middle panel displays the real image, or ground truth, which the Disciminator loss function uses to distinguish from the images generated by the Generator.
-During training, the GAN aims to keep minimum difference between these ground truth image and generated images.}
-\item{The second middle panel presents the reconstructed, or predicted, image produced by the trained GAN, highlighting its success in image reconstruction.}
-\item{The right panel shows the difference between the ground truth and the predicted image in the interferometric plane.
-The uniform background color of the frames suggests that the GAN model picks up white noise in the interferometric plane.}
+\item{The left panel represents the sparse II pattern obtained by the simulated observation using the four IACTs illustrated in Fig.\ref{fig:teles}.
+As explained earlier, this image acts as part of the input, namely its ``condition'' part.
+This image acts as the condition that the sky-images of the star generated by the Generator must conform to.}
+
+\item{The second panel from left displays the real image, or ground truth target image, which the Discriminator loss function uses to distinguish from the images generated by the Generator.}
+
+\item{The third panel from left presents the reconstructed (or predicted) image corresponding to the ground truth (second panel) and generated by the trained Model.
+The similarity of these two images indicates the success of the Model in its stated objective of image reconstruction.}
+
+\item{The right panel shows the residuals between the ground truth target image and the predicted image in the interferometric plane.
+The small values are indicative of the success of training the Model.}
 \end{itemize}
-The predicted images in Fig.~\ref{fig:GAN} yield encouraging results, accurately conveying visual information about the source's size, shape, and brightness distribution across its surface using only six baselines.
-However, further improvements can be achieved by increasing the number of telescopes to maximize coverage of the $(u, v)$ plane, making the existing and upcoming CTAO an ideal candidate for this approach.
+
+The predicted images and the residuals presented in the third and the fourth columns (from left) of Fig.~\ref{fig:GAN} show encouraging results, conveying visual information about the source's size, shape, and brightness distribution across its surface fairly accurately.
+This has been achieved on the basis of the input provided by II observation using only six baselines.
+Arguably, further improvements can be achieved by increasing the number of telescopes to enhance the coverage of the $(u, v)$ plane.
+A closer examination of this proposition might be able to contribute to the design and instrumentation aspects in the existing and upcoming CTAO.
 
@@
 	\includegraphics[width=.32\linewidth]{fig/moments/mom2.png}\hfil
-	\caption{This set of figures shows the comparison of monopole, x-centroid, and y-centroid for ground truth and predicted images generated by trained GAN.}
+
+\caption{This set of figures shows comparisons of the monopole, and the coordinates of the centroids ($x_c,\, y_c$) of the pixel brightness distribution of the ground truth images and the corresponding images predicted (generated) by the trained model.
+The monopole moment of the images represents the overall pixel brightness of the images.
+The values, as expected of a trained Model, not only lie in same range, but lie close to the diagonal and show an approximate equality.
+The centroids of both the ground truth images and the predicted images lie within small ranges of pixel values as should be expected of an ideally trained model.
+Please see the relevant text for detailed comments.}
 \label{fig:cen}
 \end{figure*}
-\subsection{Evaluation of GAN using Moments}
-The reconstructed images are visually compelling, demonstrating the GAN's effectiveness in using II to reconstruct images.
-However, visual assessment alone is insufficient; statistical evaluation is necessary to validate the results.
-To achieve this, we employ image moments as a statistical method.
-Image moments capture key properties of the reconstructed objects—such as shape, size, and intensity distribution—by quantifying features like position, orientation, and brightness distribution.
-By comparing the moments of the GAN-generated images to those of the ground truth, we can objectively assess the consistency and accuracy of the reconstruction.
+
+\subsection{Evaluation of the Model using Moments}
+The reconstructed images are visually compelling, demonstrating the Model's effectiveness in using II to reconstruct images.
+However, visual assessment alone is insufficient; statistical evaluation of the generated images in comparison with the ground truth images is necessary to validate the results.
+We present here the results of our calculation and comparison of the moments of distribution pixel brightness in the target ``Ground Truth'' images and the ``Predicted'' images.
+
+Image moments capture key properties of the reconstructed objects, such as shape, size, and intensity distribution, by quantifying features like position, orientation, and brightness distribution.
+By comparing the moments of the Model-generated images with those of the ground truth, we can objectively assess the consistency and accuracy of the reconstruction.
 This approach provides a reliable framework for evaluating reconstruction quality, as image moments can reveal subtle differences in geometric and intensity properties that might not be apparent through visual inspection alone.
@@
 It is computed by summing all pixel values across the image, yielding an overall intensity measure.
-In this context, analyzing the monopole provides the total flux of fast-rotating stars.
+In this context, analyzing the monopole provides the total pixel brightness of the images of the fictitious stars.
 According to Eq.~\eqref{eqn:Mom}, the monopole of an image is calculated as:
@@
 \end{equation}
-The left figure of Fig.~\ref{fig:cen} displays the monopole values for 50 reconstructed images.
-The plot reveals a linear relationship between the monopole of the ground truth (real image) on the $x$-axis and that of the predicted (reconstructed) image on the $y$-axis, consistent across sources of varying shapes and sizes.
-This linearity confirms that the predicted images have an overall intensity (flux) that closely matches the ground truth.
-However, while the monopole effectively represents the total brightness, it does not provide information about the position, shape, size, or detailed brightness distribution of the fast-rotating stars.
+
+An ideally trained Model should predict the overall pixel brightness of the generated images to be in the same range of values, if not equal to those of the ground truth images.
+The left panel of Fig.~\ref{fig:cen} displays the monopole values for 100 reconstructed images.
+The plot reveals a broad agreement in the overall intensity of the ground truth targets and the predicted (generated) images.
+However, a slightly higher brightness of reconstructed images in the intermediate range of brightness is evident.
+This could, perhaps, be mitigated by tuning the Batch Size hyperparameter.
+
+While the monopole effectively represents the total brightness, it does not provide information about the position, shape, size, or detailed brightness distribution of the fast-rotating stars.
 For these aspects, higher-order moments are necessary.
 
-The center of mass of the sky image of any stellar object, is determined by its centroid, which provides the $x$ and $y$ coordinates representing the spatial position of the image.
-This centroid is computed using the first-order raw moments in conjunction with the monopole (the zeroth-order moment).
-The formulations for the centroid along the $x$ and $y$ directions are given by:
+The first order raw moments normalized by the respective monopole moments of the images given by 
 \begin{eqnarray}
@@
 \end{eqnarray}
-Here, \(I(x,y)\) represents the intensity at pixel \((x,y)\), \(M_{00}\) is the monopole (total intensity), and \(M_{10}\) and \(M_{01}\) are the first-order raw moments along the $x$ and $y$ axes respectively.
-This formulation accurately captures the spatial center of mass of the stellar object in the image.
-
-The middle and right panel of Fig.~\ref{fig:cen} compare the centroids ($x_{c}$, $y_{c}$) of 50 predicted images with their corresponding ground truths respectively.
-The clustering of centroids within a specific scale range across all results indicates that the reconstructed images accurately represent the spatial location of the fast-rotating star relative to the ground truth.
+represent the centroids $(x_c, y_c)$ of the pixel brightness distribution of the images.
+An ideally trained GAN model should produce the centroids of the target and predicted images within a small range of pixels.
+A larger range would imply a low fidelity in learning the brightness distribution of ground truth images.
+The middle and right panels of Fig.~\ref{fig:cen} compare the centroids ($x_{c}$, $y_{c}$) of 100 predicted images with their corresponding ground truths respectively.
+We notice that the coordinates of the centroids of ground truth images are spread across a range of 2 pixels whereas the those of the predicted images are spread across a span of 4 pixels along $x$-axis and 7 pixels along $y$-axis.
+This clustering of centroids within a small scale range across all results indicates that the reconstructed images represent the spatial distribution of brightness of predicted and ground truth images fairly accurately.
 
@@
   \includegraphics[width=.32\linewidth]{fig/moments/mom5.png}\hfil
-  \caption{The second-order central moments provide information about the size and shape of stellar objects.
-Shown here are all the second-order central moments for ground truth and predicted images generated by the trained GAN.
-From left to right these are $\mu_{11},\mu_{20},\mu_{02}$.}
+  \caption{The second order central moment of the brightness distribution of the images is analogous to the moment of inertia of a mass distribution.
+The panels of this figure show the comparison of the second order moments ($\mu_{11}$, $\mu_{20}$, and $\mu_{02}$) of the predicted images vs.
+the ground truth images from left to right respectively.
+Approximate equality of these moments is evident.
+The small scatter in the moments of the predicted images is indicative of a balanced training of the Model.
+}
 \label{fig:struc}
@@
   \includegraphics[width=.49\linewidth]{fig/moments/mom9.png}\hfil
-  \caption{Shown here are all the third-order central moments for
-    ground truth and predicted images generated by the trained GAN.
-    They represent the skewness of the brightness distributions.  The
-    panels in reading order show
-    $\mu_{30},\mu_{03},\mu_{21},\mu_{12}$.}
+  \caption{Shown here are all the third-order central moments ($\mu_{30}$, $\mu_{03}$, $\mu_{21}$, and $\mu_{12}$) for ground truth and predicted images generated by the trained Model.
+They represent the skewness of the brightness distributions.
+The low skewness in the brightness distribution of the ground truth images is evident.
+One outlier among the predicted images dominates their skewness distribution along the $y$-axis as seen in the values of \(\mu_{03}\) and \(\mu_{12}\).
+The trained Model, however, seems to have learned the approximately uniform distribution of skewness along the $x$-axis as is evident, with a few outliers though, in the values of \(\mu_{30}\) and \(\mu_{21}\).}
 \label{fig:moments}
 \end{figure*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 Furthermore, these calculated centroids are instrumental in analyzing the shape, size, and brightness distribution of the stars using higher-order image moments.
@@
 
-Fig.~\ref{fig:struc} presents the second-order central moments (\(\mu_{11}, \mu_{20}, \mu_{02}\)), which are used to study the structure of a fast-rotating star along the line of sight (as explained in the upcoming subsection).
-All three plots demonstrate a linear relationship in the second-order moments, similar to the monopole, thereby confirming the success of applying the GAN to reconstruct images with II.
+The second order central moment of the brightness distribution of the images is analogous to the moment of inertia of a mass distribution.
+Fig.~\ref{fig:struc} presents the comparison of second-order central moments (\(\mu_{11}, \mu_{20}, \mu_{02}\)), which are used to study the structure of a fast-rotating star along the line of sight (as explained in the upcoming subsection).
+All three plots demonstrate an approximate equality among these moments, similar to the monopole, thereby confirming the success of applying the Model to reconstruct images with II.
+The small scatter in the moments of the predicted images indicates robust learning of the Model without over-fitting.
 
-The brightness distribution is characterized by the skewness of the image, which is quantified by calculating the third-order central moments (\(\mu_{30}, \mu_{03}, \mu_{21}, \mu_{12}\)).
-Fig.~\ref{fig:moments} presents all third-order moments for both the ground truth and the reconstructed image.
-The skewness along the $x$ and $y$ axes (\(\mu_{30}\) and \(\mu_{03}\)) appears acceptable, as shown in both upper panel of Fig.~\ref{fig:moments}, where a linear relationship exists between the ground truth and predicted images.
-However, the other higher-order moments (\(\mu_{21}\) and \(\mu_{12}\))—particularly \(\mu_{12}\), as depicted in both lower panel of Fig.~\ref{fig:moments}—do not align as well.
-This indicates that further improvement is possible and should be investigated.
+The third-order central moments (\(\mu_{30}, \mu_{03}, \mu_{21}, \mu_{12}\)) of the images quantify the degree and direction of asymmetry of the brightness distribution around their respective centroids.
+Fig.~\ref{fig:moments} presents a comparison of all third-order moments for both the ground truth and the reconstructed image.
+All the four panels show a low skewness in the brightness distribution of the ground truth images.
+The skewness of the predicted images along the $y$-axis is dominated by one outlier as seen in the values of \(\mu_{03}\) and \(\mu_{12}\).
+However, the approximately uniform distribution of skewness of the predicted images along the $x$-axis, with a few outliers though, as seen in the values of \(\mu_{30}\) and \(\mu_{21}\) suggests that this feature in the ground truth images has been picked up fairly well during the training of the Model.
 

### 2025-12-07 Phase_II/draft/conclusion.tex
before final

@@
 This work addresses the challenge of phase retrieval in II using a machine-learning technique, specifically a conditional Generative Adversarial Network (cGAN).
-Our study demonstrates \st{that applying a cGAN to II data successfully recovers the size, shape, and brightness distribution of a fast-rotating star.}  \textcolor{blue}{that the size, shape and brightness distribution of fast rotating stars can be recovered by a cGAN trained on the combined input of the sky-image of known sources  along with their respective II data.
+Our study demonstrates that the size, shape and brightness distribution of fast rotating stars can be recovered by a Pix2Pix cGAN model trained on the combined input of the sky-image of known sources  along with their respective II data.
 In this training the sky-image acts as the real ``ground truth'' and the II data acts as the ``condition''.
-The Discriminator of the cGAN model is trained to efficiently distinguish between the real images and fake (generated) images based on the ``ground truth'' images and the respective II data condition.
+The Discriminator of our Model is trained to efficiently distinguish between the real images and fake (generated) images based on the ``ground truth'' images and the respective II data as the condition.
 The Generator is trained to generate progressively realistic images which are also consistent with the condition of the II data.
-The evaluation of the trained model is then carried out} \st{Evaluations based on} \textcolor{blue}{by comparison of image moments of real images and generated images.} Specifically, the monopole, second, and third-order moments \textcolor{blue}{are compared.
-The results} support the effectiveness of cGAN in achieving \textcolor{blue}{the stated objective.} \st{accurate image reconstruction from a simulation of II from a single site with four telescopes.}
+The evaluation of the trained Model is then carried out by comparison of image moments of ground truth images and generated images.
+Specifically, the monopole, second, and third-order moments are compared.
+The results support the effectiveness of cGAN in achieving the stated objective.
 
@@
 First, an important factor in the reconstruction process is the extent of Fourier plane coverage, which depends on the number of available telescopes and the total observing time.
-The reasonable success of this piece of work suggests that a network of higher number of telescopes providing higher number of baselines and greater coverage of the $(u,v)$ plane signal, \textcolor{blue}{would play a critical role in} projects of image reconstruction of more complicated stellar systems can be undertaken.
+The reasonable success of this piece of work suggests that a network of higher number of telescopes providing higher number of baselines and greater coverage of the $(u,v)$ plane signal, would play a critical role in projects of image reconstruction of more complicated stellar systems can be undertaken.
 Future work might explore different observatory layouts to assess their impact on image reconstruction quality.

### 2025-12-07 Phase_II/draft/image-reconstruction-past-efforts.tex
Edit of GAN drat completed by SS
before final

--- 2025-10-06 Phase_II/draft/image-reconstruction-past-efforts.tex
@@
 \section{Past Efforts at Image Reconstruction in Intensity Interferometry}
-\iffalse
-Several theoretical and computational approaches for phase reconstruction with II have been proposed.
-\cite{gamo1963triple} introduced the concept of triple-intensity correlation, which \cite{goldberger1963use} subsequently applied in an experiment to observe scattered particles in microscopic systems.
-Sato conducted experiments to measure the diameter and phase of asymmetrical objects, suggesting that triple correlation could extend II to image stellar bodies \citep{sato1978imaging, sato1979computer, sato1981adaptive}.
-However, achieving a satisfactory signal-to-noise ratio (SNR) remained a significant challenge for this approach.
-
-\cite{GerchbergSaxton1972} suggested an iterative method to determine the phase from the image and diffraction plane pictures.
-This method relies on accurate initial estimates and is vulnerable to slow convergence otherwise.
-\cite{Fienup1982} introduced a Hybrid Input-Output algorithm that incorporates feedback mechanisms to improve convergence rate and robustness, particularly in noisy environments.
-
-Later, \cite{holmes2010two} proposed an alternative method that utilizes the Cauchy-Riemann relations to reconstruct 1-D images.
-They also extended the approach to 2-D images across a range of signal-to-noise (SNR) values.
-This algorithm was applied to simulated data of stellar objects using II, considering both existing and forthcoming Imaging Cherenkov Telescope Arrays (IACTs) with a large number of telescopes \citep{nunez2010stellar, nunez2012high, nunez2012imaging}.
-However, this method faces challenges related to computational complexity when attempting to generalize to higher dimensions.
-
-\cite{Li2014} suggested a flexible iterative Regularization method that incorporates prior information (e.g., sparsity, smoothness, or non-negativity) to reduce the ill-posedness of the phase retrieval problem.
-This method is more robust against noise and stabilizes the solution against artefacts and spurious solutions.
-Nevertheless, it faces challenges regarding the choice of the regularization parameter, computational complexity, and sensitivity to the initial guess.
-
-The Transport-of-Intensity Equation (TIE) method is a non-interferometric technique first proposed by \cite{Teague1983} that relates the intensity variations along the optical axis to the phase of the optical fields.
-This method enables phase retrieval from intensity measurements taken at multiple planes.
-\cite{Zhang2020} proposed a method to obtain a \textquotedblleft universal solution\textquotedblright\ to the TIE by employing a \textquotedblleft maximum intensity assumption\textquotedblright, thereby converting the TIE into a Poisson equation which is then solved iteratively.
-More recently, \cite{Kirisits2024} have explored hybrid methods that combine the TIE with other equations, such as the Transport of Phase Equation (TPE).
-These approaches leverage the strengths of both equations to improve phase retrieval accuracy.
-This method is universally applicable, as it works for arbitrarily shaped apertures, handles non-uniform illumination, and accommodates inhomogeneous boundary conditions.
-It guarantees convergence, although the speed of convergence depends on the quality of the initial guess, and the final results are influenced by the boundary conditions.
-
-%%%**************************8
-
-%\documentclass{article}
-%\usepackage{amsmath}
-%\begin{document}
-\fi
 Several approaches have been developed for phase reconstruction in intensity interferometry (II).
@@
 The Transport-of-Intensity Equation (TIE), proposed by \cite{Teague1983}, retrieves phase from intensity variations across planes; \cite{Zhang2020} solved TIE as a Poisson equation using a maximum intensity assumption, while \cite{Kirisits2024} combined TIE with the Transport of Phase Equation for improved accuracy across arbitrary apertures and non-uniform illumination, with convergence dependent on initial guesses and boundary conditions.
-
-%\end{document}
-%%%**************
 
@@
 
-In the astrophysical context, \cite{schawinski2017galaxypics} employed a GAN model to recover features — such as spiral arms, central bulges, and disk structures of galaxies — from noise-affected images.
+In the astrophysical context, \cite{schawinski2017galaxypics} employed a GAN model to recover features, such as spiral arms, central bulges, and disk structures of galaxies, from noise-affected images.
 \cite{mustafa2019cosmogan} developed and customized a Deep Convolutional GAN, dubbed \textquotedblleft CosmoGAN\textquotedblright, capable of generating high-fidelity weak-lensing convergence maps of dark matter distribution that statistically reproduce real weak lensing structures.

### 2025-12-07 Phase_II/draft/intro_reformatted.tex
before final

@@
 This paper is organized as follows.
-The next section discusses briefly the past efforts at image reconstruction on II, followed by the section on a discussion of Intensity Interferometry, focusing on its signal and noise characteristics for fast-rotating stars along the Earth’s rotation.
+The next section discusses briefly the past efforts at image reconstruction on II, followed by the section on a discussion of II, focusing on its signal and noise characteristics for fast-rotating stars along the Earth’s rotation.
 The following section introduces the cGAN formulation and its structure.
@@
 	\includegraphics[width=\linewidth]{fig/telescope.png}
-	\caption{A schematic representation of {\textcolor{blue}{a hypothetical observation facility with an the array of four Cherenkov Telescopes (IACTs) whose relative positions approximately mimic those at VERITAS.
-This array is used in simulating the Intensity Interferometry (II) observation of the fast rotators.}} Each of the telescopes has a diameter of 12m.
+	\caption{A schematic representation of a hypothetical observation facility with an the array of four Cherenkov Telescopes (IACTs) whose relative positions approximately mimic those at VERITAS.
+This array is used in simulating the II observation of the fast rotators.
+Each of the telescopes has a diameter of 12m.
 The baselines provided by the array are of the order of 100m.}

### 2025-12-07 Phase_II/draft/main.tex
before final

--- 2025-11-17 Phase_II/draft/main.tex
@@
 \usepackage{amsmath}
+\usepackage{graphicx}
 \usepackage{tikz}
@@
 \usepackage{hyperref}
-%\newcommand{\paperdoi}{10.5281/zenodo.17598807}
 
@@
 \pagestyle{fancy}
-\fancyfoot{}
 \fancyfoot[L]{DOI: \href{https://doi.org/10.5281/zenodo.17598807}{10.5281/zenodo.17598807}}
@@
 
-%\maketitle
-%\begin{center}
-%\textbf{DOI:} \href{https://doi.org/\paperdoi}{\paperdoi}
-%\end{center}
-
 \begin{abstract}
@@
 This paper explores the application of a conditional Generative Adversarial Network (cGAN) to tackle the problem of image reconstruction in II.
-This approach successfully reconstructs the shape, size, and brightness distribution of a fast-rotating star from sparsely sampled, spatial power spectrum of the source, corresponding to II with four telescopes.
+This method successfully reconstructs the shape, size, and brightness distribution of simulated, fast-rotating stars based on a sparsely sampled spatial power spectrum obtained from a hypothetical ground-based II facility composed of four Imaging Atmospheric Cherenkov Telescopes (IACTs).
 Although this particular example could also be addressed using parameter fitting, the results suggest that with larger arrays much more complicated systems could be reconstructed by applying machine-learning techniques to II.
@@
 \begin{acknowledgements}
-\textbf{Acknowledgment:} One of the authors (SS) gratefully acknowledges the computing facilities and the local hospitality extended to him by the Inter-University Centre for Astronomy and Astrophysics (IUCAA), Pune, India under its Visiting Associate Programme during the preparation of this manuscript.
+\textbf{Acknowledgment:} One of the authors (SS) gratefully acknowledges the computing facilities and the local hospitality extended to him by the Inter-University Centre for Astronomy and Astrophysics (IUCAA), Pune, India under its Visiting Associate Programme during the preparation and finalization of this manuscript.
 \end{acknowledgements}

### 2025-12-07 Phase_II/draft/ParaGan.tex
to Prof. Saha

@@
 In the training of GANs, one often-followed strategy to potentially boost performance is to give the Discriminator an advantage by increasing its number of training epochs before returning to the Generator's training.
-This hyperparameter is referred to as the Discriminator repetition (as seen in Table \ref{tab:hyperparameters}.
+This hyperparameter is referred to as the Discriminator repetition (as seen in Table \ref{tab:hyperparameters}).
 While this can lower the Discriminator loss, as shown in Fig.~\ref{fig:Plot_discrep_loss}, it also increases training time.
@@
 Obviously, the most compute-intensive part of this process is that of the training of the Model.
-The results of training and validation presented in this work were carried out on a CPU using two nodes, each with 96 threads and the entire process of training and validation required approximately 20 hours on the machine employed for this work.
+The results of training and validation presented in this work were carried out on a CPU using two nodes, each with 48 threads and the entire process of training and validation required approximately 20 hours on the machine employed for this work.
 This iterative process of training and validation of the Model is represented schematically in the Fig.\ref{fig:FlowDiagram}.
@@
 
-The Pix2Picx cGAN architecture along with the choice of the values of the hyperparameters mentioned in the Table -\ref{tab:hyperparameters} and used in the implementation of this architecture constitutes the cGAN model (hereinafter referred to as ``the GAN Model'' or simply ``the Model'').
+The Pix2Pix cGAN architecture along with the choice of the values of the hyperparameters mentioned in the Table -\ref{tab:hyperparameters} and used in the implementation of this architecture constitutes the cGAN model (hereinafter referred to as ``the GAN Model'' or simply ``the Model'').

### 2025-12-07 Phase_II/draft/ParaGan.tex
to Prof. Saha

@@
 	\centering
-	\includegraphics[width=0.785\textwidth]{fig/testing_image/image_7.png}
-	\includegraphics[width=0.785\textwidth]{fig/testing_image/image_12.png}
-	\includegraphics[width=0.785\textwidth]{fig/testing_image/image_13.png}
-	\includegraphics[width=0.785\textwidth]{fig/testing_image/image_29.png}
-	\includegraphics[width=0.785\textwidth]{fig/testing_image/image_39.png}
+	\includegraphics[width=0.8\textwidth]{fig/testing_image/image_4.png}
+	\includegraphics[width=0.8\textwidth]{fig/testing_image/image_17.png}
+	\includegraphics[width=0.8\textwidth]{fig/testing_image/image_22.png}
+	\includegraphics[width=0.8\textwidth]{fig/testing_image/image_30.png}
+	\includegraphics[width=0.8\textwidth]{fig/testing_image/image_50.png}
+	\includegraphics[width=0.8\textwidth]{fig/testing_image/image_75.png}
 \caption{Example results of image reconstruction using the cGAN model along with the II observations simulated in this work.
